### 2021-01-14 docs/cropland_labels.Rmd
Finish labels

---
title: "Cropland labels"
author: "Lei Song"
date: "1/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Object-based cropland labels
```{r ecozones}
ecozones <- st_read('data/ecozones/ecozones_shp.shp', 
                    quiet = T) %>% 
  group_by(PHY_REG) %>% summarise() %>% 
  setNames(c('zone', 'geometry'))
st_write(ecozones, 'data/geoms/ecozones.geojson')
```

### Validation
Choose out 100 grids for evaluation. These 100 grids will be used to evaluate the labeller as well.

```{r val_grids}
set.seed(1000)
vals_grid <- ecozones %>% 
  st_sample(size = rep(10, nrow(.))) %>% 
  st_sf() %>% mutate(id = 1:nrow(.))
```

### Calibration
First, skip the buffered area around validation grids.

```{r cal_grids}
vals_grid_buffer <- vals_grid %>% 
  st_buffer(dist = 0.5, endCapStyle = 'SQUARE') %>% 
  st_union()
ecozones_dif <- st_difference(ecozones, vals_grid_buffer)
```

### 2021-01-14 docs/ensemble_labels.Rmd
Finish labels

---
title: "Ensemble labels"
author: "Lei Song"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown:
    highlight: pygments
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Introduction
In order to make full use of other existing land cover (LC) products, and save the energy to gather new labels. We decided to ensemble these chosen LC products to make new labels for training. We chose these products based upon their relatively high spatial resolution and recent produce time.
These products include:

- Finer Resolution Observation and Monitoring of Global Land Cover (FROM-GLC10) 2017 (10 m)
- S2 prototype land cover map of Africa 2016 (20 m)
- Global Food Security-support Analysis Data (GFSAD) cropland extent of Africa 2015 (30 m)
- Copernicus global land cover map 2018 (100 m) (We chose it because of the most recent year.)

This project provides a practical framework to rapidly generate regional high resolution land cover map on demand. Due to the spatial limitation of Planet NICFI basemap, We only focus on sub-Saharan Africa and take Tanzania as a case study.

## Week near point-level LC labels
First, we redefined LC types to ensure that different products match each other. 
Then, we ensemble all LC products to generate LC type labels, and resample to the highest resolution.

### Read related vectors
```{r read}
library(dplyr)
library(terra)
library(sf)
tiles <- vect('data/geoms/tiles_nicfi.geojson')
```

### Mosaic and clip the products
```{r mosaic}
ext_dir <- '/Volumes/elephant/landcovers'

# ESACCI
esacci <- rast(file.path(ext_dir, 
                         'ESACCI-LC-L4-LC10-Map-20m-P1Y-2016-v1',
                         'ESACCI-LC-L4-LC10-Map-20m-P1Y-2016-v1.0.tif')) %>% 
    crop(tiles) %>% mask(tiles)

# FROM_GLC
fnames <- list.files(file.path(ext_dir, 
                               'FROM_GLC_2017'),
                     full.names = T)
fromglc <- do.call(merge, lapply(fnames, function(fname){
    rast(fname)
})) %>% crop(tiles) %>% mask(tiles)

# GFSAD30AFCE
fnames <- list.files(file.path(ext_dir, 
                               'GFSAD30AFCE_2015'),
                     full.names = T,
                     pattern = 'tif$')
gfsad <- do.call(merge, lapply(fnames, function(fname){
    rast(fname)
})) %>% crop(tiles) %>% mask(tiles)

# ESAGLC
fnames <- list.files(file.path(ext_dir, 
                               'ESA_GLC_2018'),
                     full.names = T)
esaglc <- do.call(merge, lapply(fnames, function(fname){
    rast(fname)
})) %>% crop(tiles) %>% mask(tiles)
```

### Redefine land cover types
**UN-FAO’s Land Cover Classification System (LCCS)**
```
(1) Cultivated and Managed Terrestrial Areas (cropland), 
(2) Natural and Semi-Natural Terrestrial Vegetation, 
(3) Cultivated Aquatic or Regularly Flooded Areas, 
(4) Natural and Semi-Natural Aquatic or Regularly Flooded Vegetation, 
(5) Artificial Surfaces and Associated Areas, 
(6) Bare Areas, 
(7) Artificial Waterbodies, Snow and Ice, and 
(8) Natural Waterbodies, Snow and Ice.
```

**ESACCI**
```
0	No data
1   Tree cover areas
2	Shrubs cover areas
3	Grassland
4	Cropland
5	Vegetation aquatic or regularly flooded
6	Lichens Mosses / Sparse vegetation
7	Bare areas
8	Built up areas
9	Snow and/or Ice
10	Open Water
```

**ESAGLC**
```
0 No input data
111 Closed forest, evergreen needle leaf
113 Closed forest, deciduous needle leaf
112 Closed forest, evergreen, broad leaf
114 Closed forest, deciduous broad leaf
115 Closed forest, mixed
116 Closed forest, unknown
121 Open forest, evergreen needle leaf
123 Open forest, deciduous needle leaf
122 Open forest, evergreen broad leaf
124 Open forest, deciduous broad leaf
125 Open forest, mixed
126 Open forest, unknown
20 Shrubs
30 Herbaceous vegetation
90 Herbaceous wetland
100 Moss and lichen
60 Bare / sparse vegetation
40 Cultivated and managed vegetation / agriculture (cropland)
50 Urban / built up
70 Snow and ice
80 Permanent water bodies
200 Open sea
```

**FROM-GLC**
```
Name	             Code
Cropland	         1
Forest	           2
Grassland	         3
Shrubland	         4
Wetland	           5
Water	             6
Tundra	           7
Impervious surface 8
Bareland	         9
Snow/Ice	         10
```

**GFSAD**
```
Cropland Extent Class Descriptions

Class Label	         Name	           Description
0	                 Water	           Water bodies/no-data
1	                 Non-Cropland	   Non-Cropland areas
2	                 Cropland	       Cropland areas
```

#### Generate convert tables
```{r refine}
# LC type used
lc_types <- data.frame(id = seq(1, 10),
                       name = c('Cropland', 'Forest', 'Grassland', 
                                'Shrubland', 'Wetland', 'Water', 
                                'Tundra', 'Urban/Built up',
                                'Bareland', 'Snow/Ice'))

# types of LC products
esacci_table <- data.frame(id = c(seq(1, 10)),
                           name = c('Tree cover areas', 
                                    'Shrub cover areas', 
                                    'Grassland', 'Cropland', 
                                    'Vegetation aquatic or regularly flooded',
                                    'Lichens Mosses / Sparse vegetation',
                                    'Bare areas', 'Built up areas', 
                                    'Snow and/or Ice', 'Open Water'),
                           convert = c(2, 4, 3, 1, 5, 7, 9, 8, 10, 6))

names <- c('Closed forest, evergreen needle leaf',
           'Closed forest, evergreen, broad leaf',
           'Closed forest, deciduous needle leaf',
           'Closed forest, deciduous broad leaf',
           'Closed forest, mixed',
           'Closed forest, unknown',
           'Open forest, evergreen needle leaf',
           'Open forest, evergreen broad leaf',
           'Open forest, deciduous needle leaf',
           'Open forest, deciduous broad leaf',
           'Open forest, mixed',
           'Open forest, unknown',
           'Shrubs', 'Herbaceous vegetation',
           'Herbaceous wetland', 'Moss and lichen',
           'Bare / sparse vegetation',
           'Cultivated and managed vegetation / agriculture (cropland)',
           'Urban / built up',
           'Snow and ice',
           'Permanent water bodies',
           'Open sea')
esaglc_table <- data.frame(id = c(seq(111, 116), 
                                  seq(121, 126), 
                                  20, 30, 90, 100, 60, 
                                  40, 50, 70, 80, 200),
                           name = names,
                           convert = c(rep(2, 12), 4, 
                                       3, 5, 7, 9, 1,
                                       8, 10, 6, 6))

fromglc_table <- data.frame(id = seq(1, 10),
                            name = c('Cropland', 'Forest', 'Grassland',
                                     'Shrubland', 'Wetland', 'Water',
                                     'Tundra', 'Impervious surface',
                                     'Bareland', 'Snow/Ice'),
                            convert = seq(1, 10))

gfsad_table <- data.frame(id = seq(0, 2),
                          name = c('Water',
                                   'Non-Cropland',
                                   'Cropland'),
                          convert = c(6, NA, 1))
```

#### Convert LC maps
```{r convert}
# Path
dst_path <- 'data/landcovers'
if (!dir.exists(dst_path)) dir.create(dst_path)

# ESACCI reclassification
esacci_rclmat <- data.frame(from = esacci_table$id - 1,
                            to = esacci_table$id, 
                            becomes = esacci_table$convert) %>% 
  as.matrix()
esacci_new <- classify(esacci, esacci_rclmat, 
                       right = FALSE, 
                       othersNA = TRUE,
                       filename = file.path(dst_path, 
                                            'esacci_rcl.tif'),
                       wopt = list(datatype = 'INT1U',
                                   gdal=c("COMPRESS=LZW")))

# ESA-GLC reclassification
esaglc_rclmat <- data.frame(from = esaglc_table$id - 1,
                            to = esaglc_table$id, 
                            becomes = esaglc_table$convert) %>% 
  as.matrix()
esaglc_new <- classify(esaglc, esaglc_rclmat, 
                       right = FALSE, 
                       othersNA = TRUE,
                       filename = file.path(dst_path, 
                                            'esaglc_rcl.tif'),
                       wopt = list(datatype = 'INT1U',
                                   gdal=c("COMPRESS=LZW")))

# FROM-GLC reclassification
fromglc_rclmat <- data.frame(from = fromglc_table$id - 1,
                             to = fromglc_table$id, 
                             becomes = fromglc_table$convert) %>% 
  as.matrix()
fromglc_new <- classify(fromglc, fromglc_rclmat, 
                        right = FALSE, 
                        othersNA = TRUE,
                        filename = file.path(dst_path, 
                                             'fromglc_rcl.tif'),
                        wopt = list(datatype = 'INT1U',
                                    gdal=c("COMPRESS=LZW")))

# GFSAD reclassification
gfsad_rclmat <- data.frame(from = gfsad_table$id - 1,
                           to = gfsad_table$id, 
                           becomes = gfsad_table$convert) %>% 
  as.matrix()
gfsad_new <- classify(gfsad, gfsad_rclmat, 
                      right = FALSE, 
                      othersNA = TRUE,
                      filename = file.path(dst_path, 'gfsad_rcl.tif'),
                      wopt = list(datatype = 'INT1U',
                                  gdal=c("COMPRESS=LZW")))
```

### Make labels
The pixel non-0 value in the image matches with the values in `lc_types`.

```{r make_labels}
# Path
dst_path <- 'data/intermid/lc_labels'
if (!dir.exists(dst_path)) dir.create(dst_path)

# Get the existing types
# Because not all types exist in the current study area
ids <- unique(c(unique(esacci_new), 
                unique(esaglc_new), 
                unique(fromglc_new), 
                1)) # For GFSAD
lc_types <- lc_types %>% filter(id %in% ids)

lapply(1:nrow(lc_types), function(n){
  lc <- lc_types %>% slice(n)
  message(lc$name)
  if (lc$id %in% c(1, 6)){
    message('Use all four products for cropland or water.')
    lc_lb_esacci <- esacci_new == lc$id
    lc_lb_esaglc <- resample(esaglc_new == lc$id, 
                             lc_lb_esacci, 
                             method = 'near')
    lc_lb_fromglc <- resample(fromglc_new == lc$id,
                              lc_lb_esacci, 
                              method = 'near')
    lc_lb_gfsad <- resample(gfsad_new == lc$id, 
                            lc_lb_esacci, 
                            method = 'near')
    lc_lb_emb <- (lc_lb_esacci + 
                    lc_lb_esaglc + 
                    lc_lb_fromglc + 
                    lc_lb_gfsad) == 4
    rm(lc_lb_esacci, lc_lb_esaglc, 
       lc_lb_fromglc, lc_lb_gfsad); gc()
  } else {
    message('Not use GFSAD for other types.')
    lc_lb_esacci <- esacci_new == lc$id
    lc_lb_esaglc <- resample(esaglc_new == lc$id, 
                             lc_lb_esacci,
                             method = 'near')
    lc_lb_fromglc <- resample(fromglc_new == lc$id, 
                              lc_lb_esacci, 
                              method = 'near')
    lc_lb_emb <- (lc_lb_esacci + 
                    lc_lb_esaglc + 
                    lc_lb_fromglc) == 3
    rm(lc_lb_esacci, lc_lb_esaglc, 
       lc_lb_fromglc); gc()
  }

  # Save out
  lc_lb_emb[lc_lb_emb == 1] <- n
  fn <- file.path(dst_path, 
                  paste0(gsub('/| ', '_', 
                              lc$name), 
                         '.tif'))
  writeRaster(lc_lb_emb, fn, 
              wopt = list(datatype = 'INT1U',
                          gdal=c("COMPRESS=LZW")))
  rm(lc_lb_emb);gc()
})
```

### Labels summary

```{r summary}
labels_sum <- do.call(rbind, 
                      lapply(1:nrow(lc_types), 
                             function(n){
  lc <- lc_types %>% slice(n)
  message(lc$name)
  fn <- file.path(dst_path, 
                  paste0(gsub('/| ', '_', lc$name), 
                         '.tif'))
  lb_sum <- rast(fn) %>% freq()
  label_count <- 0
  label_frac <- 0
  if (nrow(lb_sum) > 1){
    label_count <- lb_sum[2, 3]
  label_frac <- lb_sum[2, 3] / 
    (lb_sum[1, 3] + lb_sum[2, 3])
  }
  data.frame(name = lc$name, 
             count = label_count,
             frac = label_frac)
}))

# Save out
dst_path <- 'data/intermid'
if (!dir.exists(dst_path)) dir.create(dst_path)
write.csv(labels_sum, 
          file.path(dst_path,
                    'labels_sum.csv'),
          row.names = F)
```

```{r show, eval=T, echo=F, message=F, warning=F}
library(here)
library(kableExtra)
dst_path <- 'data/intermid'
labels_sum <- read.csv(here(file.path(dst_path,
                                      'labels_sum.csv')),
                       stringsAsFactors = F)
labels_sum %>%
  kbl(caption = "Ensemble label summary table") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

For Tanzania case, there is no Tundra and Snow/Ice type because Tanzania is a tropical country.

### Independent validation labels
Based on the extent of all labels generated above, we selected 4000 random points to manually check the LC type by visual interpretation. In order to cover all LC types, we use strata sampling for each types. The result validation labels will be used for

- Label quality evaluation, and
- Model result evaluation.

We also selected 4000 random points outside of the label extent to evaluate the result outside.

```{r valid}
dst_path <- 'data/intermid/lc_labels'
labels <- do.call(c, 
                  lapply(1:nrow(lc_types), 
                         function(n){
  lc <- lc_types %>% slice(n)
  message(lc$name)
  fn <- file.path(dst_path, 
                  paste0(gsub('/| ', '_', lc$name), 
                         '.tif'))
  rast(fn)
}))

########### Get samples inside ############
size <- 500
labels_sum <- labels_sum %>% filter(count > 0)
pts_inside <- do.call(rbind, 
                      lapply(1:nrow(labels_sum), 
                      function(n){
  lc <- labels_sum %>% slice(n)
  message(lc$name)
  fn <- file.path(dst_path, 
                  paste0(gsub('/| ', '_', lc$name), 
                         '.tif'))
  each <- rast(fn)
  set.seed(123)
  cells <- spatSample(each, 100000, 
                      "random", cells = TRUE)
  v <- each[cells]
  xy <- xyFromCell(each, cells)
  pts <- data.frame(xy, v) %>% 
    setNames(c('x', 'y', 'label_ensemble')) %>% 
    filter(label_ensemble != 0)
  if (nrow(pts) < 500){
    cells <- spatSample(each, 600000 * 3, 
                      "random", cells = TRUE)
    v <- each[cells]
    xy <- xyFromCell(each, cells)
    pts <- data.frame(xy, v) %>% 
      setNames(c('x', 'y', 'label_ensemble')) %>% 
      filter(label_ensemble != 0)

    if (nrow(pts) < 500){
    cells <- spatSample(each, 600000 * 8, 
                      "random", cells = TRUE)
    v <- each[cells]
    xy <- xyFromCell(each, cells)
    pts <- data.frame(xy, v) %>% 
      setNames(c('x', 'y', 'label_ensemble')) %>% 
      filter(label_ensemble != 0)
  }
  }
  set.seed(456)
  pts <- pts %>% 
    sample_n(size) %>% 
    st_as_sf(coords = c('x', 'y'),
             crs = 4326) %>% 
    mutate(type = NA) %>% 
    dplyr::select(type, label_ensemble)
  rm(each, cells, v, xy);gc();pts
}))

########## Get samples outside ############
# 1 for labeling region, 
# and 2 for other region within the study area
labels_ext <- sum(labels) >= 1
labels_ext <- mask(labels_ext, tiles)
labels_ext[labels_ext == 0] <- 2

# Generate points outside
size <- 4000
set.seed(123)
# Because we use terra 0.9-11, in which spatSample can't ignore NAs.
# So we complex it a bit.
# Using terra >= 1.0-7, you could ignore NAs when sampling.
# In order to reproduce the code, you could set ma.rm = F in the newer version of the function.
cells <- spatSample(labels_ext, 400000, 
                    "random", cells = TRUE)
v <- labels_ext[cells]
xy <- xyFromCell(labels_ext, cells)
set.seed(456)
pts_outside <- data.frame(xy, v) %>% 
  filter(sum == 2) %>% 
  dplyr::select(-sum) %>% 
  sample_n(size) %>% 
  st_as_sf(coords = c('x', 'y'),
           crs = 4326) %>% 
  mutate(type = NA, label_ensemble = NA) %>% 
  dplyr::select(type, label_ensemble)
rm(cells, v, xy);gc()

pts <- rbind(pts_inside, pts_outside) %>% 
  mutate(id = 1:nrow(.))

# Save out
dst_path <- 'data/intermid'
fn <- file.path(dst_path, 'labels_extent.tif')
writeRaster(labels_ext, fn, 
              wopt = list(datatype = 'INT1U',
                          gdal=c("COMPRESS=LZW")))
st_write(pts, file.path(dst_path, 'validation_ipd_full.geojson'))
pts <- pts %>% dplyr::select(-label_ensemble)
st_write(pts, file.path(dst_path, 'validation_ipd_labelling.geojson'))
```

The rest work out of this document is to manually check the LC type for these random points using human interpretation. The user can drop the points that are not clear to tell.

```{r pts, eval=T, echo=F, warning=F, message=F}
library(sf)
library(here)
library(ggplot2)
pts <- st_read(here(file.path(dst_path, 
                              'validation_ipd_full.geojson')), 
               quiet = T)
ggplot(pts) + geom_sf() + 
  theme_bw()
```

### Generate weak labels

#### Generate the overall labels 
```{r}
val_pts <- st_read('data/intermid/validation_ipd_full.geojson',
                   quiet = T) %>% st_coordinates()

# Because of the maximum number for matrix in R is 2^31 - 1,
# so we have to split the whole raster into blocks to process.
blocks <- aggregate(labels, fact = floor(sqrt(ncell(labels)/3.5)))
values(blocks) <- 1:ncell(blocks)
blocks <- as.polygons(blocks)
labels_exd_val <- do.call(merge, lapply(1:nrow(blocks), function(n){
  block <- blocks[n, ]
  labels_blk <- crop(labels, block)
  val_cells <- na.omit(cellFromXY(labels_blk, val_pts))
  labels_blk[val_cells] <- NA
  rm(block, val_cells);gc();labels_blk
}))

writeRaster(labels, 'data/intermid/lc_labels_exd_val.tif',
            wopt = list(datatype = 'INT1U',
                        gdal=c("COMPRESS=LZW")))
```

#### Select out sub-grids

But in order to get more labels for minor type, we:

- For bareland, wetland, and urban, we sample 95% as train;
- For shrubland and grassland, we sample 20% as train;
- For cropland we sample 10% as train;
- For water and forest, we sample 5% as train.

```{r}
library(tidyr)
library(parallel)
lc_labels <- rast('data/intermid/lc_labels_exd_val.tif')
tiles <- st_read('data/geoms/tiles_nicfi.geojson',
                 quiet = T) %>% dplyr::select(tile)
tiles <- do.call(rbind, mclapply(1:nrow(tiles), function(n){
  tile <- tiles %>% slice(n)
  tiles_grids <- st_make_grid(tile, n = c(8, 8)) %>% 
    st_sf() %>% arrange() %>% 
    mutate(tile = tile$tile,
                       index = c(1:64))
}, mc.cores = 10))
st_write(tiles, 'data/geoms/tiles_grids.geojson')
tiles <- tiles %>% vect()

tiles_labels <- do.call(bind_rows, mclapply(1:nrow(tiles), function(n){
  labels_each <- crop(lc_labels, tiles[n, ])
  freq(labels_each) %>% data.frame() %>% 
    filter(value != 0) %>%
    mutate(count = count / (dim(labels_each)[1] * dim(labels_each)[2])) %>%
    left_join(., lc_types, by = c('value' = 'id')) %>%
    dplyr::select(-c(value, layer)) %>%
    pivot_wider(names_from = name, values_from = count) %>%
    mutate(tile = tiles[n, ]$tile,
           index = tiles[n, ]$index)
}, mc.cores = 12))

labels_sum <- labels_sum %>% filter(count > 0)
tiles_grids_selected <- do.call(rbind, 
        lapply(labels_sum$name, 
               function(nm){
  if (nm %in% c('Forest', 'Grassland', 'Cropland', 'Shrubland')){
    tile_select <- tiles_labels %>% 
      dplyr::select(tile, index, nm) %>% 
      # arrange_at(nm, funs(desc)) %>% 
      filter(!is.na(!!rlang::sym(nm))) %>% 
      filter((!!rlang::sym(nm)) >= 0.4) %>% 
      mutate(group = ifelse(!!rlang::sym(nm) >= 0.8, 1, 
                            ifelse(!!rlang::sym(nm) >= 0.6, 2, 3))) 
    ns <- tile_select %>% group_by(group) %>% summarise(n = n()) %>% 
      mutate(n = ifelse(n < 1000, n, 1000))
    tile_select <- do.call(rbind, 
                           lapply(unique(tile_select$group), 
                                  function(g){
      set.seed(124 + g)
      tile_select %>% filter(group == g) %>% 
        sample_n(size = ns %>% 
                   filter(group == g) %>% 
                   pull(n))
    }))
  } else if (nm == 'Water'){
    tile_select <- tiles_labels %>% 
      dplyr::select(tile, index, nm) %>% 
      # arrange_at(nm, funs(desc)) %>% 
      filter(!is.na(!!rlang::sym(nm))) %>% 
      filter((!!rlang::sym(nm)) >= 0.4) %>% 
      mutate(group = ifelse(!!rlang::sym(nm) >= 0.8, 1, 
                            ifelse(!!rlang::sym(nm) >= 0.6, 2, 3))) 
    ns <- tile_select %>% group_by(group) %>% summarise(n = n()) %>% 
      mutate(n = ifelse(n < 500, n, 500))
    tile_select <- do.call(rbind, 
                           lapply(unique(tile_select$group), 
                                  function(g){
      set.seed(124 + g)
      tile_select %>% filter(group == g) %>% 
        sample_n(size = ns %>% 
                   filter(group == g) %>% 
                   pull(n))
   }))
  } else {
    # Bare land, wetland, and urban are classes that are hard to tell,
    # and the ensemble labels are less,
    # so we keep as many samples as possible.
    # but also if there are too few labels within a grid,
    # we assume the labels are not reliable anymore.
    # So we use a threshold 0.1.
    tile_select <- tiles_labels %>% 
      dplyr::select(tile, index, nm) %>%
      filter(!is.na(!!rlang::sym(nm))) %>%
      filter((!!rlang::sym(nm)) > 0.1)
  }
  data.frame(name = nm, 
             tile = tile_select$tile, 
             index = tile_select$index)
}))
```

#### Split training, validation, and test

```{r split}
set.seed(1000)
tiles_grids_train <- tiles_grids_selected %>% 
  group_by(name) %>% sample_frac(0.6) %>% 
  ungroup() %>% dplyr::select(-name) %>% 
  unique() %>% mutate(usage = 'train') %>%
  dplyr::select(tile, index, usage)
set.seed(1200)
tiles_grids_valid <- tiles_grids_selected %>% 
  anti_join(tiles_grids_train, 
            by = c('tile', 'index')) %>% 
  group_by(name) %>% sample_frac(0.5) %>% 
  ungroup() %>% dplyr::select(-name) %>% 
  unique() %>% mutate(usage = 'validate') %>%  
  dplyr::select(tile, index, usage)
tiles_grids_test <- tiles_grids_selected %>%
  dplyr::select(-name) %>% unique() %>% 
  anti_join(tiles_grids_train) %>% 
  anti_join(tiles_grids_valid) %>% 
  mutate(usage = 'test') %>% 
  dplyr::select(tile, index, usage)
catalog_pred_val_test <- rbind(tiles_grids_train, 
                               tiles_grids_valid, 
                               tiles_grids_test)
write.csv(catalog_pred_val_test, 
          'data/intermid/catalog_pred_val_test.csv',
          row.names = T)
```

#### Generate labels images
```{r labels_img}
tiles <- st_read('data/geoms/tiles_grids.geojson',
                 quiet = T)
lc_labels <- rast('data/intermid/lc_labels_exd_val.tif')

plt_path <- '/Volumes/elephant/plt_nicfi'
plt_nms <- list.files(plt_path, full.names = T)
labels_path <- '/Volumes/elephant/labels'

lapply(unique(catalog_pred_val_test$tile), function(tile_nm){
  tiles_each <- catalog_pred_val_test %>% filter(tile == tile_nm)
  lc_labels_each <- crop(lc_labels, tiles %>% 
                           filter(tile == tile_nm) %>% 
                           st_union() %>% 
                           st_buffer(0.01) %>% 
                           st_sf() %>% vect())
  nm <- grep(tile_nm, plt_nms, value = TRUE)[1]
  temp <- rast(nm)[[1]] %>% aggregate(fact = 512)
  vals <- matrix(1:64, nrow = 8, ncol = 8) %>% t()
  vals <- vals[nrow(vals):1, ]
  values(temp) <- vals
  lapply(1:nrow(tiles_each), function(n){
    tile_each <- tiles_each %>% slice(n)
    temp_each <- temp
    index <- tile_each$index
    temp_each[temp_each != index] <- NA
    temp_each <- trim(temp_each) %>% 
      disaggregate(fact = 512)
    label_each <- resample(lc_labels_each, temp_each, method = 'near')
    writeRaster(label_each, 
                file.path(labels_path, 
                          glue('labels_{tile_nm}_{index}.tif')),
                wopt = list(datatype = 'INT1U',
                        gdal=c("COMPRESS=LZW")))
    rm(tile_each, temp_each, label_each, index);gc()
  })
  rm(tiles_each, lc_labels_each, nm, temp, vals);gc()
})
```

### Sampling the label points [DEPRECATED]
*Purely point-based deep learning is not very ideal for such a big area, since it will waste
a lot of hardware resources, or waste time on prediction. But it might be an idea for a small region or an idea for traditional machine learning (e.g. random forest). Here we keep the details here.*

Since these labels are ensemble and distribute across the whole study area, we assume that they are representative enough. To reduce the training time and the potential noises within the labels due to the spatial resolution mismatch, we sample 20% from the label ensemble to calibrate the model, and 10% to evaluate.
we designed to sample from the ensemble labels:

- 20% as training pool, separately.

But in order to get more labels for minor type, we:

- For bareland, wetland, and urban, we sample 95% as train;
- For shrubland and grassland, we sample 20% as train;
- For cropland we sample 10% as train;
- For water and forest, we sample 5% as train.

And we sample 5% * smallest ensemble label size (Bareland) as validation.

```{r sampling}
library(glue)
library(rgrass7)

# Get the sample size for each type
labels_sum <- labels_sum %>% filter(count > 0)
sample_lb_size <- do.call(rbind, 
                  lapply(1:nrow(labels_sum), 
                  function(n){
  lc <- labels_sum %>% slice(n)
  message(lc$name)
  # Because forest and water have very clear characteristics
  # comparing to others, and the amount of ensemble labels are large,
  # so we choose less samples for these two classes.
  if (lc$name %in% c('Forest', 'Water')){
    size <- floor(lc$count * 0.05)
  } else if (lc$name == 'Cropland'){
    size <- floor(lc$count * 0.1)
  } else if (lc$name %in% c('Grassland', 'Shrubland')){
    size <- floor(lc$count * 0.2)
  } else{
    # Bare land, wetland, and urban are classes that are hard to tell,
    # and the ensemble labels are less,
    # so we keep as many samples as possible.
    size <- floor(lc$count * 0.95)
  }
  data.frame(name = lc$name, sample_size = size)
}))
sample_lb_size <- merge(sample_lb_size, lc_types, by = 'name') %>% 
  arrange(id)

fn <- 'data/intermid/lc_labels_exd_val.tif'
gisBase <- "/Applications/GRASS-7.9.app/Contents/Resources"
initGRASS(gisBase = gisBase,
          home = tempdir(),
          gisDbase = tempdir(),  
          mapset = 'PERMANENT', 
          location = 'sampling', 
          override = TRUE)
execGRASS("g.proj", flags = "c", 
          proj4="+proj=longlat +datum=WGS84 +no_defs")
execGRASS('r.in.gdal', flags = c("o", "overwrite"),
          input = here(fn),
          band = 1,
          output = "label")
execGRASS("g.region", raster = "label")
execGRASS("r.null", parameters = list(map = 'label', 
                                      setnull = '0'))
execGRASS("r.sample.category", flags = c("overwrite"), 
          parameters = list(input = 'label', 
                            output = 'pts',
                            npoints = sample_lb_size$sample_size,
                            random_seed = 345))
## Read out
use_sf()
pts <- readVECT("pts") %>% dplyr::select(-cat)
st_write(pts, 'data/intermid/lc_labels.geojson')

## Sign the labels into tiles
tiles <- st_read('data/geoms/tiles_nicfi.geojson',
                 quiet = T) %>% dplyr::select(tile)
pts_its <- st_intersects(tiles, pts)
dst_path <- '/Volumes/elephant/labels'
for (n in 1:length(pts_its)){
  print(n)
  nm <- tiles %>% slice(n) %>% pull(tile)
  pts_tile <- pts %>% slice(pts_its[[n]])
  if (nrow(pts_tile) > 0){
    st_write(pts_tile, glue('{dst_path}/labels_{nm}.geojson'),
             quiet = T)
  }
  rm(nm, pts_tile);gc()
}

pts_assigned <- lapply(1:nrow(tiles), function(n){
  tile <- tiles %>% slice(n)
  pts_tile <- st_intersection(pts, tile)
  rm(tile);gc();pts_tile
})
```

## Other avaliable labels from ground observation
We collected a few public available LC/cropland labels. The objective of these labels are:

1. Evaluate the performance of just using ensemble labels by comparing the results with/without these extra labels.
2. As an independent evaluation dataset to test the method performance.

The labels include:

- Radiant Earth MLHub crop type labels (`ref_crops.geojson`) (2018).
- Manually collected labels (`user_maps_tz.geojson`) (2018).
- Tanzania TAMASA (2017)
- TANSIS (2017)
- more [NEED TO UPDATE]

### Radiant earth MLHub
The files were parsed based on [MLHub API tutorials](https://github.com/radiantearth/mlhub-tutorials). We only used crop type labels in our study area Tanzania. The labels are ground collection with boundary drawn using imagery. The labels are concentrated in the Northern area, which is a large agricultural region in Tanzania.

```{r mlhub, eval=T, echo=F, warning=F, message=F}
library(sf)
library(here)
library(ggplot2)
bry <- st_read(here('data/geoms/tanzania.geojson'), quiet = T)
ref_tz_crops <- st_read(here('data/references/ref_crops.geojson'), quiet = T)
ggplot(bry) + geom_sf() + 
  geom_sf(data = ref_tz_crops, aes(color = crop)) +
  scale_color_brewer(palette = "Dark2") + 
  theme_bw()
```

### Collected labels
These labels are collected by us using PlanetScope image in 2018 and other base maps. The labels are also concentrated in north.

```{r clt, eval=T, echo=F, warning=F, message=F}
user_maps <- st_read(here('data/references/user_maps_tz.geojson'), quiet = T)
ggplot(bry) + geom_sf() + 
  geom_sf(data = user_maps, color = "#FC4E07") +
  theme_bw()
```

### TAMASA

```{r}
tamasa_tz <- read.csv("data/TAMASA/TAMASA_TZ_APS_2017_CC_MaizeYield.csv",
                       stringsAsFactors = F) %>% 
  filter(!is.na(Longitude) & !is.na(Latitude)) %>% 
  st_as_sf(coords = c('Longitude', 'Latitude'), crs = 4326)
st_write(tamasa_tz, "data/TAMASA/tamasa_tz_maize_2017.geojson")

tamasa_tz_mt <- read.csv("data/TAMASA/TZ_TAMASA_APS_2017_Maize_Yield_MetaData_v2.csv",
                       stringsAsFactors = F) %>% 
  filter(!is.na(Longitude) & !is.na(Latitude)) %>% 
  st_as_sf(coords = c('Longitude', 'Latitude'), crs = 4326)
st_write(tamasa_tz_mt, "data/TAMASA/tamasa_tz_maize_2017_metadata.geojson")
```

### 2021-01-14 docs/ensemble_labels.Rmd
Finish pre_train preparation

@@
   dplyr::select(tile, index, usage)
-catalog_pred_val_test <- rbind(tiles_grids_train, 
+catalog_train_val_test <- rbind(tiles_grids_train, 
                                tiles_grids_valid, 
                                tiles_grids_test)
-write.csv(catalog_pred_val_test, 
-          'data/intermid/catalog_pred_val_test.csv',
-          row.names = T)
+write.csv(catalog_train_val_test, 
+          'data/intermid/catalog_train_val_test.csv',
+          row.names = F)
 ```

### 2021-01-14 docs/pre_train.Rmd
Finish pre_train preparation

---
title: "Some prework before model traning"
author: "Lei Song"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown:
    highlight: pygments
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Introduction
Some pre-work before model training:

- Upload files to our AWS S3 bucket.
- Make the data catalog.

## Upload imagery
Upload the images and labels to AWS S3 bucket.

```{r upload}
library(aws.s3)
library(parallel)

## PlanetScope quads
plt_quads_rain_season <- list.files('/Volumes/elephant/plt_nicfi',
                        full.names = T, pattern = '2017-12_2018-05')
plt_quads_dry_season <- list.files('/Volumes/elephant/plt_nicfi',
                        full.names = T, pattern = '2018-06_2018-11')
## Labels
lc_labels <- list.files('/Volumes/elephant/labels',
                        full.names = T, pattern = '.tif')

## Upload function
s3_upload <- function(fnames, prefix, bucket){
    mclapply(fnames, function(src_path){
    put_object(file = src_path, 
           object = file.path(prefix, 
                              basename(src_path)), 
           bucket = bucket)
}, mc.cores = 6)
}

## Upload
s3_upload(plt_quads_rain_season, 
          "tz_dl_data/planet_quads/rain", 
          'activemapper')
s3_upload(plt_quads_dry_season, 
          "tz_dl_data/planet_quads/dry", 
          'activemapper')
s3_upload(lc_labels, 
          "tz_dl_data/lc_labels", 
          'activemapper')
```

## Make catalog

```{r catalog}
library(dplyr)
library(stringr)
library(tidyr)

# Rain season
items <- get_bucket(bucket = 'activemapper', 
                    prefix = 'tz_dl_data/planet_quads/rain', 
                    max = Inf)
keys <- lapply(c(2:length(items)), function(i) {
    basename(items[[i]]$Key)
})
plts_rain <- unlist(keys) %>% 
    paste0('s3://activemapper/tz_dl_data/planet_quads/rain/', .) %>% 
    data.frame(dir_gs = .) %>% 
    mutate(tile = str_extract(str_extract(dir_gs, 
                                          '[0-9]+-[0-9]+.tif'), 
                              '[0-9]+-[0-9]+'))

# Dry season
items <- get_bucket(bucket = 'activemapper', 
                    prefix = 'tz_dl_data/planet_quads/dry', 
                    max = Inf)
keys <- lapply(c(2:length(items)), function(i) {
    basename(items[[i]]$Key)
})
plts_dry <- unlist(keys) %>% 
    paste0('s3://activemapper/tz_dl_data/planet_quads/dry/', .) %>% 
    data.frame(dir_os = .) %>% 
    mutate(tile = str_extract(str_extract(dir_os, 
                                          '[0-9]+-[0-9]+.tif'), 
                              '[0-9]+-[0-9]+'))
plts <- merge(plts_rain, plts_dry, by = 'tile')
rm(plts_rain, plts_dry)

# Labels
items <- get_bucket(bucket = 'activemapper', 
                    prefix = 'tz_dl_data/lc_labels', 
                    max = Inf)
keys <- lapply(c(2:length(items)), function(i) {
    basename(items[[i]]$Key)
})
lc_labels <- unlist(keys) %>% 
    paste0('s3://activemapper/tz_dl_data/lc_labels/', .) %>% 
    data.frame(dir_label = .) %>% 
    mutate(name = str_extract(dir_label, 
                              '[0-9]+-[0-9]+_[0-9]+')) %>% 
    separate(name, c('tile', 'index'), '_')
imgs <- merge(lc_labels, plts, by = 'tile')
rm(plts, lc_labels)

catalog_train_val_test <- read.csv('data/intermid/catalog_train_val_test.csv',
                                  stringsAsFactors = F) %>% 
    merge(imgs, by = c('tile', 'index')) %>% 
    mutate(name = paste(tile, index, sep = '-')) %>% 
    select(name, usage, dir_gs, dir_os, dir_label)
write.csv(catalog_train_val_test, 'data/intermid/catalog_DL_train_val_test.csv',
          row.names = F)
put_object(file = 'data/intermid/catalog_DL_train_val_test.csv', 
           object = 'tz_dl_data/catalogs/catalog_DL_train_val_test.csv', 
           bucket = 'activemapper')
```

### 2021-01-14 docs/run_dl_aws.Rmd
Finish pre_train preparation

---
title: "Run deep learning on AWS instance"
author: "Lei Song"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown:
    highlight: pygments
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Launch instance

## Parameters setting

## Result visualization

### 2021-01-16 docs/ensemble_labels.Rmd
Prepare data for DL

--- 2021-01-14 docs/ensemble_labels.Rmd
@@
 
-tiles_labels <- do.call(bind_rows, mclapply(1:nrow(tiles), function(n){
+tiles_labels <- mclapply(1:nrow(tiles), function(n){
   labels_each <- crop(lc_labels, tiles[n, ])
-  freq(labels_each) %>% data.frame() %>% 
+  lb <- freq(labels_each) %>% data.frame() %>% 
     filter(value != 0) %>%
@@
            index = tiles[n, ]$index)
-}, mc.cores = 12))
+  if (nrow(lb) > 0) lb
+}, mc.cores = 12) %>% bind_rows()
+save(tiles_labels, file = 'data/intermid/tiles_labels.rda')
 
@@
     tile_select <- tiles_labels %>% 
-      dplyr::select(tile, index, nm) %>% 
+      dplyr::select(tile, index, all_of(nm)) %>% 
       # arrange_at(nm, funs(desc)) %>% 
@@
 tiles_grids_train <- tiles_grids_selected %>% 
-  group_by(name) %>% sample_frac(0.6) %>% 
+  group_by(name) %>% sample_frac(0.7) %>% 
   ungroup() %>% dplyr::select(-name) %>% 

### 2021-01-16 docs/pre_train.Rmd
Prepare data for DL

@@
                               '[0-9]+-[0-9]+_[0-9]+')) %>% 
-    separate(name, c('tile', 'index'), '_')
+    tidyr::separate(name, c('tile', 'index'), '_')
 imgs <- merge(lc_labels, plts, by = 'tile')
@@
     mutate(name = paste(tile, index, sep = '-')) %>% 
-    select(name, usage, dir_gs, dir_os, dir_label)
+    dplyr::select(name, usage, dir_gs, dir_os, dir_label)
 write.csv(catalog_train_val_test, 'data/intermid/catalog_DL_train_val_test.csv',

### 2021-01-16 docs/run_dl_aws.Rmd
Prepare data for DL

@@
 ## Launch instance
+The information of instance that we used:
+
+- AMI ID: `ami-0643df3b347740189`, which is our customized deep learning AWS instance.
+- Instance type: `g3.8xlarge`.
+- Security group: `labeller-security`.
+
+Before start, install `jq`.
+Then use the scripts in `pytorch_planet/aws_tools/create_spot_instance.sh` using the template:
+```
+cd /path/to/pytorch_planet/folder
+chmod 777 ./aws_tools/create_spot_instance.sh
+./aws_tools/create_spot_instance.sh <ami_id> <instance_type> <security_group_id> <new_instance_name> <spot_type> <valid_until> <key_name>
+```
+For example:
+```
+cd /path/to/pytorch_planet/folder
+chmod 777 ./aws_tools/create_spot_instance.sh
+./aws_tools/create_spot_instance.sh ami-0643df3b347740189 g3.8xlarge sg-0a8bbc91697d6a76b lc_tz persistent 2021-01-20T23:00:00 lsong-keypair
+```
 
 ## Parameters setting
+After successfully launched the instance, then it is ready to get into the instance to work.
+
+The most essential work are arguably to clone project and set jupyter notebook:
+
+- STEP 1: Set up GitHub token (because the repo is private).
+More details could be found in this [tutorial](https://docs.github.com/en/free-pro-team@latest/github/authenticating-to-github/generating-a-new-ssh-key-and-adding-it-to-the-ssh-agent).
+
+  ```
+  ssh-keygen -t ed25519 -C "your_email@example.com"
+  eval "$(ssh-agent -s)"
+  ssh-add ~/.ssh/id_ed25519
+  vim ~/.ssh/id_ed25519.pub
+  ```
+  Copy out the ssh key, and type `:q` to exit, and then go to GitHub page to add into the records.
+
+- STEP 2: Clone the repo into instance:
+
+  ```
+  git clone git@github.com:agroimpacts/pytorch_planet.git
+  ```
+
+  If necessary, use `git checkout` to switch branch and use `git pull` to grab the updates.
+
+- STEP 3: Set up jupyter notebook
+
+  ```
+  jupyter notebook password
+  ```
+  to set a log in password for jupyter notebook, then
+  ```
+  jupyter notebook
+  ```
+  replace the private IP with the public IP to open it in browser. If you can log in without issues, then it is ready to go.
 

### 2021-01-23 docs/ensemble_labels.Rmd
Add acknowledgement

--- 2021-01-14 docs/ensemble_labels.Rmd
@@
 library(parallel)
+# Define the width of chips to cut
+# In this case, 256 *256 chip.
+width_chips <- 16
 lc_labels <- rast('data/intermid/lc_labels_exd_val.tif')
@@
   tile <- tiles %>% slice(n)
-  tiles_grids <- st_make_grid(tile, n = c(8, 8)) %>% 
+  tiles_grids <- st_make_grid(tile, n = c(width_chips, width_chips)) %>% 
     st_sf() %>% arrange() %>% 
     mutate(tile = tile$tile,
-                       index = c(1:64))
-}, mc.cores = 10))
-st_write(tiles, 'data/geoms/tiles_grids.geojson')
+                       index = c(1:(width_chips^2)))
+}, mc.cores = 12))
+st_write(tiles, 'data/intermid/tiles_grids_256.geojson')
 tiles <- tiles %>% vect()
 
-tiles_labels <- do.call(bind_rows, mclapply(1:nrow(tiles), function(n){
+tiles_labels <- mclapply(1:nrow(tiles), function(n){
   labels_each <- crop(lc_labels, tiles[n, ])
-  freq(labels_each) %>% data.frame() %>% 
+  lb <- freq(labels_each) %>% data.frame() %>% 
     filter(value != 0) %>%
@@
            index = tiles[n, ]$index)
-}, mc.cores = 12))
+  if (nrow(lb) > 0) lb
+}, mc.cores = 12) %>% bind_rows()
+save(tiles_labels, file = 'data/intermid/tiles_labels_256.rda')
 
@@
                                        function(nm){
+    message(nm)
     if (nm %in% c('Forest', 'Grassland', 'Cropland', 'Shrubland')){
+        set.seed(123)
         tile_select <- tiles_labels %>% 
@@
             filter(!is.na(!!rlang::sym(nm))) %>% 
-      filter((!!rlang::sym(nm)) >= 0.4) %>% 
-      mutate(group = ifelse(!!rlang::sym(nm) >= 0.8, 1, 
-                            ifelse(!!rlang::sym(nm) >= 0.6, 2, 3))) 
-    ns <- tile_select %>% group_by(group) %>% summarise(n = n()) %>% 
-      mutate(n = ifelse(n < 1000, n, 1000))
-    tile_select <- do.call(rbind, 
-                           lapply(unique(tile_select$group), 
-                                  function(g){
-      set.seed(124 + g)
-      tile_select %>% filter(group == g) %>% 
-        sample_n(size = ns %>% 
-                   filter(group == g) %>% 
-                   pull(n))
-    }))
+            filter((!!rlang::sym(nm)) >= 0.7) %>% 
+            sample_n(min(1000, nrow(.)))
     } else if (nm == 'Water'){
+        set.seed(566)
         tile_select <- tiles_labels %>% 
@@
             filter(!is.na(!!rlang::sym(nm))) %>%
+            filter((!!rlang::sym(nm)) <= 0.8) %>%
             filter((!!rlang::sym(nm)) >= 0.4) %>% 
-      mutate(group = ifelse(!!rlang::sym(nm) >= 0.8, 1, 
-                            ifelse(!!rlang::sym(nm) >= 0.6, 2, 3))) 
-    ns <- tile_select %>% group_by(group) %>% summarise(n = n()) %>% 
-      mutate(n = ifelse(n < 500, n, 500))
-    tile_select <- do.call(rbind, 
-                           lapply(unique(tile_select$group), 
-                                  function(g){
-      set.seed(124 + g)
-      tile_select %>% filter(group == g) %>% 
-        sample_n(size = ns %>% 
-                   filter(group == g) %>% 
-                   pull(n))
-   }))
+            sample_n(500)
     } else {
@@
         tile_select <- tiles_labels %>% 
-      dplyr::select(tile, index, nm) %>%
+            dplyr::select(tile, index, all_of(nm)) %>%
             filter(!is.na(!!rlang::sym(nm))) %>%
@@
             by = c('tile', 'index')) %>% 
-  group_by(name) %>% sample_frac(0.5) %>% 
+  group_by(name) %>% sample_frac(0.6) %>% 
   ungroup() %>% dplyr::select(-name) %>% 
@@
 #### Generate labels images
+In order to save the resources for deep learning, we re-defined the class index to be continuous. So:
+
+```
+id          name
+1       Cropland
+2         Forest
+3      Grassland
+4      Shrubland
+5        Wetland
+6          Water
+7 Urban/Built up (8)
+8       Bareland (9)
+```
+
 ```{r labels_img}
-tiles <- st_read('data/geoms/tiles_grids.geojson',
+library(glue)
+tiles <- st_read('data/intermid/tiles_grids.geojson',
                  quiet = T)
@@
 
-lapply(unique(catalog_pred_val_test$tile), function(tile_nm){
-  tiles_each <- catalog_pred_val_test %>% filter(tile == tile_nm)
+mclapply(unique(catalog_train_val_test$tile), 
+         function(tile_nm){
+  tiles_each <- catalog_train_val_test %>% 
+    filter(tile == tile_nm)
   lc_labels_each <- crop(lc_labels, tiles %>% 
@@
   nm <- grep(tile_nm, plt_nms, value = TRUE)[1]
-  temp <- rast(nm)[[1]] %>% aggregate(fact = 512)
-  vals <- matrix(1:64, nrow = 8, ncol = 8) %>% t()
+  temp <- rast(nm)[[1]] %>% 
+    aggregate(fact = 4096/width_chips)
+  vals <- matrix(1:(width_chips^2), 
+                 nrow = width_chips, 
+                 ncol = width_chips) %>% t()
   vals <- vals[nrow(vals):1, ]
@@
     temp_each[temp_each != index] <- NA
-    temp_each <- trim(temp_each) %>% 
-      disaggregate(fact = 512)
+    temp_each <- terra::trim(temp_each) %>% 
+      disaggregate(fact = 4096/width_chips)
     label_each <- resample(lc_labels_each, temp_each, method = 'near')
+    label_each[label_each == 8] <- 7
+    label_each[label_each == 9] <- 8
     writeRaster(label_each, 
@@
   rm(tiles_each, lc_labels_each, nm, temp, vals);gc()
-})
+}, mc.cores = 12)
 ```

### 2021-01-23 docs/pre_train.Rmd
Add acknowledgement

@@
 lc_labels <- list.files('/Volumes/elephant/labels',
-                        full.names = T, pattern = '.tif')
+                        full.names = T, pattern = '.tif$')
 
@@
 library(tidyr)
+library(aws.s3)
 

### 2021-01-23 docs/run_dl_aws.Rmd
Add acknowledgement

@@
 chmod 777 ./aws_tools/create_spot_instance.sh
-./aws_tools/create_spot_instance.sh ami-0643df3b347740189 g3.8xlarge sg-0a8bbc91697d6a76b lc_tz persistent 2021-01-20T23:00:00 lsong-keypair
+./aws_tools/create_spot_instance.sh ami-0643df3b347740189 g3.16xlarge sg-0a8bbc91697d6a76b lc_dl_tz persistent 2021-01-22T23:00:00 lsong-keypair
 ```
@@
 
-## Result visualization
+## Experiemnts
+
+### Experiment 1
+
+```
+Model: Deeplab3+
+train_batch = 32
+val_batch = 16
+transformation = ['vflip', 'hflip', 'rotate', 'resize']
+rotate_degree = [-90, 90]
+epoch = 30
+lr_init = 0.0005
+lr_decay = 0.1
+lr_decay_step = 1
+momentum = 0.99
+criterion = BalancedTverskyFocalLoss(ignore_index=0)
+optimizer = "adam"
+```
+
+**Result**: terminate early. The model performance stuck quickly. Then it got stuck here.
+
+```
+train loss: 0.6423281792689253
+train acc: 0.7882347084857799
+validation loss: 0.872987336890642
+validation acc: 0.8824300759060438
+time: 409
+[14/100]
+train loss: 0.6659585610032082
+train acc: 0.7867565039131377
+validation loss: 0.8747954650153947
+validation acc: 0.8814900846675385
+time: 391
+```
+
+Seems like BalancedTverskyFocalLoss and adam is a good combination of compiler parameters.
+The problems left is which model and the learning rate.
+The experiments shown that the complexity of the model is not enough.
+
+### Experiments
+
+```
+Model: Unet
+
+train loss: 0.6717923217349582
+train acc: 0.7490688176066788
+validation loss: 0.8887722446301649
+validation acc: 0.8503072788549024
+```
+
+```
+Model: Deeper Unet
+
+train loss: 0.6798290364720203
+train acc: 0.7305447139121868
+validation loss: 0.8891407523390858
+validation acc: 0.8469047265690427
+time: 245
+```
+
+```
+Model: VGG 
+```
+
+```
+Model: ResNet 
+```
+
+```
+Model: DenseNet 
+```
+
+```
+Model: SegNet 
+```

### 2021-01-26 docs/ensemble_labels.Rmd
Move to a new method to select ensemble labels

@@
 ```{r}
+library(ggplot2)
 library(tidyr)
@@
 # Define the width of chips to cut
-# In this case, 256 *256 chip.
+# In this case, 256 * 256 chip.
+# The chip size is the trade-off between computing cost, 
+# purity of ensemble labels, and the keep of geographic context.
 width_chips <- 16
@@
 
+labels_sum <- labels_sum %>% filter(count > 0)
+tiles_grids_pure <- do.call(rbind, 
+                            lapply(labels_sum$name, 
+                                   function(nm){
+    message(nm)
+    tile_select <- tiles_labels %>% 
+        dplyr::select(tile, index, all_of(nm)) %>% 
+        filter(!is.na(!!rlang::sym(nm))) %>% 
+        filter((!!rlang::sym(nm)) >= 0.8)
+    data.frame(name = nm, 
+               tile = tile_select$tile, 
+               index = tile_select$index)
+}))
+
+grids_pure_count <- tiles_grids_pure %>% 
+  group_by(name) %>% summarize(n = n()) %>% 
+  arrange(n)
+```
+
+```{r, eval=T, echo=F, message=F, warning=F}
+grids_pure_count <- read.csv('data/intermid/pure_grids_count.csv',
+                             stringsAsFactors = F)
+
+# Based on the table, the first three minor classes 
+grids_pure_count %>%
+  kbl(caption = "Pure label grids summary") %>%
+  kable_classic(full_width = F, html_font = "Cambria")
+```
+
+Based on the table, the first three minor classes (`r grids_pure_count$name[1:3]`) have the similar number of pure grids.
+So we keep all grids from these classes, and then randomly select the average number (`r ceiling(mean(grids_pure_count$n[1:3]))`) of grids from other classes.
+
+##### [ARCHIVED] Get large amount of weak labels.
+Based on the prior experiments, this method didn't do well.
+The train dataset is "under-representative" in terms of DL training (Validate loss curve is below the train loss significantly).
+This might be caused by either the super imbalance in both train and validate dataset, or the noises in the labels.
+
+```{r old-method}
 labels_sum <- labels_sum %>% filter(count > 0)

### 2021-03-06 docs/ensemble_labels.Rmd
Some updates and applying OSM to clean labels

@@
     highlight: pygments
-    toc_depth: 5
+    toc_depth: 6
 ---
@@
 #### Select out sub-grids
-
-But in order to get more labels for minor type, we:
-
-- For bareland, wetland, and urban, we sample 95% as train;
-- For shrubland and grassland, we sample 20% as train;
-- For cropland we sample 10% as train;
-- For water and forest, we sample 5% as train.
+##### Statistic
 
@@
 
-##### [ARCHIVED] Get large amount of weak labels.
+##### Reselect
+```{r reselect}
+grids_pure_count$n[4:nrow(grids_pure_count)] <- ceiling(mean(grids_pure_count$n[1:3]))
+tiles_grids_selected <- do.call(rbind, 
+                                lapply(grids_pure_count$name, 
+                                       function(nm){
+    message(nm)
+    n_grids <- grids_pure_count %>% 
+      filter(name == nm) %>% 
+      pull(n)
+    set.seed(123)
+    tile_select <- tiles_labels %>% 
+      dplyr::select(tile, index, all_of(nm)) %>% 
+      filter(!is.na(!!rlang::sym(nm))) %>% 
+      filter((!!rlang::sym(nm)) >= 0.8) %>% 
+      sample_n(min(n_grids, nrow(.)))
+    data.frame(name = nm, 
+               tile = tile_select$tile, 
+               index = tile_select$index)
+}))
+```
+
+#### Split training and validation
+
+```{r split_pure}
+set.seed(1000)
+tiles_grids_train <- tiles_grids_selected %>% 
+  group_by(name) %>% sample_frac(0.7) %>% 
+  ungroup() %>% dplyr::select(-name) %>% 
+  unique() %>% mutate(usage = 'train') %>%
+  dplyr::select(tile, index, usage)
+tiles_grids_valid <- tiles_grids_selected %>% 
+  anti_join(tiles_grids_train, 
+            by = c('tile', 'index')) %>% 
+  group_by(name) %>% ungroup() %>% 
+  dplyr::select(-name) %>% 
+  unique() %>% mutate(usage = 'validate') %>%  
+  dplyr::select(tile, index, usage)
+catalog_train_val <- rbind(tiles_grids_train, 
+                               tiles_grids_valid)
+write.csv(catalog_train_val, 
+          'data/intermid/catalog_train_val_pure.csv',
+          row.names = F)
+```
+
+#### [ARCHIVED] Get large amount of weak labels.
 Based on the prior experiments, this method didn't do well.
@@
 #### Split training, validation, and test
+Select test dataset for final round.
 
@@
 library(glue)
+
+# Make the script consistent
+catalog_train_val_test <- catalog_train_val
 tiles <- st_read('data/intermid/tiles_grids.geojson',
@@
 plt_nms <- list.files(plt_path, full.names = T)
-labels_path <- '/Volumes/elephant/labels'
+labels_path <- '/Volumes/elephant/labels_pure'
 
-mclapply(unique(catalog_train_val_test$tile), 
+lapply(unique(catalog_train_val_test$tile), 
          function(tile_nm){
@@
   rm(tiles_each, lc_labels_each, nm, temp, vals);gc()
-}, mc.cores = 12)
+})
 ```

### 2021-03-06 docs/ensemble_labels_local.Rmd
Some updates and applying OSM to clean labels

---
title: "Ensemble labels"
author: "Lei Song"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown:
    highlight: pygments
    toc_depth: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Introduction
In order to make full use of other existing land cover (LC) products, and save the energy to gather new labels. We decided to ensemble these chosen LC products to make new labels for training. We chose these products based upon their relatively high spatial resolution and recent produce time. We visually checked the performance of the products, some of them don't make sense even though they might have good classification accuracy. This mainly because these maps are optimized to a much bigger area.

These products include:

- Finer Resolution Observation and Monitoring of Global Land Cover (FROM-GLC10) 2017 (10 m)
- Global Food Security-support Analysis Data (GFSAD) cropland extent of Africa 2015 (30 m)
- Copernicus global land cover map 2018 (100 m) (We chose it because of the most recent year.)

This project provides a practical framework to rapidly generate regional high resolution land cover map on demand. Due to the spatial limitation of Planet NICFI basemap, We only focus on sub-Saharan Africa and take Tanzania as a case study.

## Week LC labels
First, we redefined LC types to ensure that different products match each other. 
Then, we ensemble all LC products to generate LC type labels, and resample to the highest resolution.

### Read related vectors
```{r read}
library(dplyr)
library(terra)
library(sf)
tiles <- vect('data/geoms/tiles_nicfi.geojson')
```

### TANSIS mask
```{r}
url_cp <- 'https://files.osf.io/v1/resources/yrj3h/providers/osfstorage/5c28365528af78001a63ee6d?action=download&direct&version=1'
dir.create('data/tansis')
download.file(url_cp, 'data/tansis/cp_pred.zip')
unzip('data/tansis/cp_pred.zip', exdir = 'data/tansis')
```

### Mosaic and clip the products
```{r mosaic}
ext_dir <- '/Volumes/elephant/landcovers'

# FROM_GLC
fnames <- list.files(file.path(ext_dir, 
                               'FROM_GLC_2017'),
                     full.names = T)
fromglc <- do.call(merge, lapply(fnames, function(fname){
    rast(fname)
})) %>% crop(tiles) %>% mask(tiles)

# GFSAD30AFCE
fnames <- list.files(file.path(ext_dir, 
                               'GFSAD30AFCE_2015'),
                     full.names = T,
                     pattern = 'tif$')
gfsad <- do.call(merge, lapply(fnames, function(fname){
    rast(fname)
})) %>% crop(tiles) %>% mask(tiles)

# ESAGLC
fnames <- list.files(file.path(ext_dir, 
                               'ESA_GLC_2018'),
                     full.names = T)
esaglc <- do.call(merge, lapply(fnames, function(fname){
    rast(fname)
})) %>% crop(tiles) %>% mask(tiles)
```

### Redefine land cover types

**ESAGLC**
```
0 No input data
111 Closed forest, evergreen needle leaf
113 Closed forest, deciduous needle leaf
112 Closed forest, evergreen, broad leaf
114 Closed forest, deciduous broad leaf
115 Closed forest, mixed
116 Closed forest, unknown
121 Open forest, evergreen needle leaf
123 Open forest, deciduous needle leaf
122 Open forest, evergreen broad leaf
124 Open forest, deciduous broad leaf
125 Open forest, mixed
126 Open forest, unknown
20 Shrubs
30 Herbaceous vegetation
90 Herbaceous wetland
100 Moss and lichen
60 Bare / sparse vegetation
40 Cultivated and managed vegetation / agriculture (cropland)
50 Urban / built up
70 Snow and ice
80 Permanent water bodies
200 Open sea
```

**FROM-GLC**
```
Name	             Code
Cropland	         1
Forest	           2
Grassland	         3
Shrubland	         4
Wetland	           5
Water	             6
Tundra	           7
Impervious surface 8
Bareland	         9
Snow/Ice	         10
```

**GFSAD**
```
Cropland Extent Class Descriptions

Class Label	         Name	           Description
0	                 Water	           Water bodies/no-data
1	                 Non-Cropland	   Non-Cropland areas
2	                 Cropland	       Cropland areas
```

#### Generate convert tables
```{r refine}
# LC type used
lc_types <- data.frame(id = seq(1, 10),
                       name = c('Cropland', 'Forest', 'Grassland', 
                                'Shrubland', 'Wetland', 'Water', 
                                'Tundra', 'Urban/Built up',
                                'Bareland', 'Snow/Ice'))

# Based on our check, open forest classes 
# are closer to Shrubland class for other products,
names <- c('Closed forest, evergreen needle leaf',
           'Closed forest, evergreen, broad leaf',
           'Closed forest, deciduous needle leaf',
           'Closed forest, deciduous broad leaf',
           'Closed forest, mixed',
           'Closed forest, unknown',
           'Open forest, evergreen needle leaf',
           'Open forest, evergreen broad leaf',
           'Open forest, deciduous needle leaf',
           'Open forest, deciduous broad leaf',
           'Open forest, mixed',
           'Open forest, unknown',
           'Shrubs', 'Herbaceous vegetation',
           'Herbaceous wetland', 'Moss and lichen',
           'Bare / sparse vegetation',
           'Cultivated and managed vegetation / agriculture (cropland)',
           'Urban / built up',
           'Snow and ice',
           'Permanent water bodies',
           'Open sea')
esaglc_table <- data.frame(id = c(seq(111, 116), 
                                  seq(121, 126), 
                                  20, 30, 90, 100, 60, 
                                  40, 50, 70, 80, 200),
                           name = names,
                           convert = c(rep(2, 6), rep(4, 7), 
                                       3, 5, 7, 9, 1,
                                       8, 10, 6, 6))

fromglc_table <- data.frame(id = seq(1, 10),
                            name = c('Cropland', 'Forest', 'Grassland',
                                     'Shrubland', 'Wetland', 'Water',
                                     'Tundra', 'Impervious surface',
                                     'Bareland', 'Snow/Ice'),
                            convert = seq(1, 10))

gfsad_table <- data.frame(id = seq(0, 2),
                          name = c('Water',
                                   'Non-Cropland',
                                   'Cropland'),
                          convert = c(6, NA, 1))
```

#### Convert LC maps
```{r convert}
# Path
dst_path <- 'data/landcovers'
if (!dir.exists(dst_path)) dir.create(dst_path)

# ESA-GLC reclassification
esaglc_rclmat <- data.frame(from = esaglc_table$id - 1,
                            to = esaglc_table$id, 
                            becomes = esaglc_table$convert) %>% 
  as.matrix()
esaglc_new <- classify(esaglc, esaglc_rclmat, 
                       right = FALSE, 
                       othersNA = TRUE,
                       filename = file.path(dst_path, 
                                            'esaglc_rcl.tif'),
                       wopt = list(datatype = 'INT1U',
                                   gdal=c("COMPRESS=LZW")))

# FROM-GLC reclassification
fromglc_rclmat <- data.frame(from = fromglc_table$id - 1,
                             to = fromglc_table$id, 
                             becomes = fromglc_table$convert) %>% 
  as.matrix()
fromglc_new <- classify(fromglc, fromglc_rclmat, 
                        right = FALSE, 
                        othersNA = TRUE,
                        filename = file.path(dst_path, 
                                             'fromglc_rcl.tif'),
                        wopt = list(datatype = 'INT1U',
                                    gdal=c("COMPRESS=LZW")))

# GFSAD reclassification
gfsad_rclmat <- data.frame(from = gfsad_table$id - 1,
                           to = gfsad_table$id, 
                           becomes = gfsad_table$convert) %>% 
  as.matrix()
gfsad_new <- classify(gfsad, gfsad_rclmat, 
                      right = FALSE, 
                      othersNA = TRUE,
                      filename = file.path(dst_path, 'gfsad_rcl.tif'),
                      wopt = list(datatype = 'INT1U',
                                  gdal=c("COMPRESS=LZW")))
```

### Make labels
The pixel non-0 value in the image matches with the values in `lc_types`.

```{r make_labels}
# Path
dst_path <- 'data/intermid/lc_labels'
if (!dir.exists(dst_path)) dir.create(dst_path)

# Get the existing types
# Because not all types exist in the current study area
ids <- unique(c(unique(esaglc_new), 
                unique(fromglc_new), 
                1)) # For GFSAD and TANSIS
lc_types <- lc_types %>% filter(id %in% ids)
# Even though there is some pixels classified as snow/ice
# this class is too tiny in Tanzania,
# so we delete this class.
lc_types <- lc_types %>% filter(id != 10)

tansis_mask <- rast(list.files('data/tansis', full.names = T, pattern = '.tif$'))
tansis_mask <- tansis_mask$TZ__7
tansis_mask[is.na(tansis_mask)] <- 0
tansis_mask <- resample(tansis_mask != 0,
                        fromglc_new, 
                        method = 'near')

gfsad_mask <- resample(gfsad_new != 0,
                       fromglc_new, 
                       method = 'near')
crop_mask <- (tansis_mask + gfsad_mask) == 0
lapply(1:nrow(lc_types), function(n){
  lc <- lc_types %>% slice(n)
  message(lc$name)
  if (lc$id == 1){
    message('Just use GFSAD for cropland.')
    lc_lb_emb <- resample(gfsad_new == lc$id, 
                          fromglc_new, 
                          method = 'near')
    gc()
  } else if (lc$id == 6){
    message('Use all three products for water.')
    lc_lb_fromglc <- fromglc_new == lc$id
    lc_lb_esaglc <- resample(esaglc_new == lc$id, 
                             lc_lb_fromglc, 
                             method = 'near')
    lc_lb_gfsad <- resample(gfsad_new == lc$id, 
                            lc_lb_fromglc, 
                            method = 'near')
    lc_lb_emb <- (lc_lb_esaglc + 
                    lc_lb_fromglc + 
                    lc_lb_gfsad) >= 3
    lc_lb_emb <- lc_lb_emb * crop_mask
    rm(lc_lb_esaglc, lc_lb_fromglc, lc_lb_gfsad); gc()
  } else {
    message('Not use GFSAD for other types.')
    lc_lb_fromglc <- fromglc_new == lc$id
    lc_lb_esaglc <- resample(esaglc_new == lc$id, 
                             lc_lb_fromglc,
                             method = 'near')
    lc_lb_emb <- (lc_lb_esaglc + 
                    lc_lb_fromglc) == 2
    message('Skip the cropland area defined by gfsad and tansis.')
    lc_lb_emb <- lc_lb_emb * crop_mask
    # lc_lb_emb <- lc_lb_emb * gfsad_mask
    rm(lc_lb_esaglc, lc_lb_fromglc); gc()
  }

  # Save out
  lc_lb_emb[lc_lb_emb == 1] <- lc$id
  fn <- file.path(dst_path, 
                  paste0(gsub('/| ', '_', 
                              lc$name), 
                         '.tif'))
  writeRaster(lc_lb_emb, fn, 
              wopt = list(datatype = 'INT1U',
                          gdal=c("COMPRESS=LZW")))
  rm(lc_lb_emb);gc()
})
```

#### Labels summary
```{r summary}
labels_sum <- do.call(rbind, 
                      lapply(1:nrow(lc_types), 
                             function(n){
  lc <- lc_types %>% slice(n)
  message(lc$name)
  fn <- file.path(dst_path, 
                  paste0(gsub('/| ', '_', lc$name), 
                         '.tif'))
  lb_sum <- rast(fn) %>% freq()
  label_count <- 0
  label_frac <- 0
  if (nrow(lb_sum) > 1){
    label_count <- lb_sum[2, 3]
  label_frac <- lb_sum[2, 3] / 
    (lb_sum[1, 3] + lb_sum[2, 3])
  }
  data.frame(name = lc$name, 
             count = label_count,
             frac = label_frac)
}))

# Save out
dst_path <- 'data/intermid'
if (!dir.exists(dst_path)) dir.create(dst_path)
write.csv(labels_sum, 
          file.path(dst_path,
                    'labels_sum.csv'),
          row.names = F)
```

```{r show, eval=T, echo=F, message=F, warning=F}
library(here)
library(kableExtra)
dst_path <- 'data/intermid'
labels_sum <- read.csv(here(file.path(dst_path,
                                      'labels_sum.csv')),
                       stringsAsFactors = F)
labels_sum %>%
  kbl(caption = "Ensemble label summary table") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

For Tanzania case, there is very tiny Tundra and Snow/Ice type if any because Tanzania is a tropical country. The only possible is on the Q mountain.

#### Save out the consensus labels
```{r}
dst_path <- 'data/intermid/lc_labels'
labels <- do.call(c, 
                  lapply(1:nrow(lc_types), 
                         function(n){
  lc <- lc_types %>% slice(n)
  message(lc$name)
  fn <- file.path(dst_path, 
                  paste0(gsub('/| ', '_', lc$name), 
                         '.tif'))
  rast(fn)
}))

# Reclassify to make sure common label value is 1
# other value is 2, and background is 0.
labels <- sum(labels)
labels_ext <- labels >= 1
labels_ext <- mask(labels_ext, tiles)
labels_ext[labels_ext == 0] <- 2

# save out
dst_path <- 'data/intermid'
fn <- file.path(dst_path, 'lc_labels.tif')
writeRaster(labels, fn, overwrite = TRUE,
              wopt = list(datatype = 'INT1U',
                          gdal=c("COMPRESS=LZW")))
fn <- file.path(dst_path, 'labels_extent.tif')
writeRaster(labels_ext, fn, overwrite = TRUE,
              wopt = list(datatype = 'INT1U',
                          gdal=c("COMPRESS=LZW")))
```

#### Select out sub-grids

Start-up zone: zone 5

```{r g1}
library(ggplot2)
library(tidyr)
library(parallel)
# Define the width of chips to cut
# In this case, 256 * 256 chip.
# The chip size is the trade-off between computing cost, 
# purity of ensemble labels, and the keep of geographic context.
width_chips <- 16
lc_labels <- rast('data/intermid/lc_labels.tif')
tiles <- st_read('data/geoms/tiles_nicfi.geojson',
                 quiet = T) %>% dplyr::select(tile)
ecozones <- st_read('data/intermid/clusters_final.geojson',
                    quiet = T)

tiles <- do.call(rbind, mclapply(1:nrow(tiles), function(n){
  tile <- tiles %>% slice(n)
  tiles_grids <- st_make_grid(tile, n = c(width_chips, width_chips)) %>% 
    st_sf() %>% arrange() %>% 
    mutate(tile = tile$tile,
           index = c(1:(width_chips^2)))
}, mc.cores = 12))
st_write(tiles, 'data/intermid/tiles_grids_ecozones_256.geojson')
tiles <- tiles %>% vect()

tiles_labels <- mclapply(1:nrow(tiles), function(n){
  labels_each <- crop(lc_labels, tiles[n, ])
  lb <- freq(labels_each) %>% data.frame() %>% 
    filter(value != 0) %>%
    mutate(count = count / (dim(labels_each)[1] * dim(labels_each)[2])) %>%
    left_join(., lc_types, by = c('value' = 'id')) %>%
    dplyr::select(-c(value, layer)) %>%
    pivot_wider(names_from = name, values_from = count) %>%
    mutate(tile = tiles[n, ]$tile,
           ecozone = tiles[n, ]$ecozone,
           index = tiles[n, ]$index)
  if (nrow(lb) > 0) lb
}, mc.cores = 12) %>% bind_rows()
save(tiles_labels, file = 'data/intermid/tiles_labels_256.rda')

tiles <- st_read('data/intermid/tiles_grids_ecozones_256.geojson')
tiles <- tiles %>% dplyr::select(-ecozone) %>% unique()
st_write(tiles, 'data/intermid/tiles_grids_256.geojson')

ecozones <- st_read('data/intermid/clusters_final.geojson',
                    quiet = T)
ecozone_5 <- ecozones %>% filter(region == 5)
tiles_zone5 <- tiles %>% 
    filter(st_intersects(ecozone_5, tiles, sparse = F)) %>% 
    vect()
st_write(tiles_zone5, 'data/intermid/tiles_grids_zone5.geojson')

# lc_types <- lc_types %>% filter(!id %in% c(5, 7, 9, 10))
tiles_labels_zone5 <- mclapply(1:nrow(tiles_zone5), function(n){
    labels_each <- crop(lc_labels, tiles_zone5[n, ])
    lb <- freq(labels_each) %>% data.frame() %>% 
        filter(value != 0) %>%
        mutate(count = count / (dim(labels_each)[1] * dim(labels_each)[2])) %>%
        left_join(., lc_types, by = c('value' = 'id')) %>%
        dplyr::select(-c(value, layer)) %>%
        pivot_wider(names_from = name, values_from = count) %>%
        mutate(tile = tiles_zone5[n, ]$tile,
               index = tiles_zone5[n, ]$index)
    if (nrow(lb) > 0) lb
}, mc.cores = 8) %>% bind_rows()

tiles_labels_zone5 <- tiles_labels_zone5 %>%
    dplyr::select(-c('Wetland', 'Bareland', 'Tundra'))

class_nm <- c('Cropland', 'Forest', 'Grassland', 
              'Shrubland', 'Water')
grids_pure_zone5 <- do.call(rbind, 
                      lapply(class_nm, 
                             function(nm){
                                 message(nm)
                                tile_select <- tiles_labels_zone5 %>% 
                                         dplyr::select(tile, index, all_of(nm)) %>% 
                                         filter(!is.na(!!rlang::sym(nm))) %>% 
                                         filter((!!rlang::sym(nm)) >= 0.9)
                                data.frame(name = nm, 
                                            tile = tile_select$tile, 
                                            index = tile_select$index,
                                            purity = tile_select %>% 
                                                dplyr::select((!!rlang::sym(nm))) %>% 
                                                pull)
                             }))

grids_pure_count <- grids_pure_zone5 %>% 
    group_by(name) %>% summarize(n = n()) %>% 
    arrange(n)

# This area covers most of the LC types, only miss enough built-up.
# Fortunately, built-up has very obvious and relatively same feature across the whole regions.
# so we could get some from other regions.
set.seed(123)
grids_labels_zone5 <- grids_pure_zone5 %>% 
    group_by(name) %>% 
    sample_n(250) %>% 
    ungroup()

# built-up
tile_select <- tiles_labels %>% 
    dplyr::select(tile, index, all_of('Urban/Built up')) %>% 
    filter(!is.na(!!rlang::sym(nm))) %>% 
    filter((!!rlang::sym(nm)) >= 0.5)
urbans <- data.frame(name = nm, 
           tile = tile_select$tile, 
           index = tile_select$index,
           purity = tile_select %>% 
               dplyr::select((!!rlang::sym(nm))) %>% 
               pull)
grids_labels_zone5 <- rbind(grids_labels_zone5, urbans)
grids_labels_zone5_json <- st_read('data/intermid/tiles_grids_256.geojson') %>% 
    right_join(grids_labels_zone5, by = c('tile', 'index'))
st_write(grids_labels_zone5_json, 'data/intermid/grids_labels_zone5.geojson')
```

#### Split training and validate

```{r split_pure}
set.seed(100)
grids_train <- grids_labels_zone5 %>% 
  group_by(name) %>% sample_frac(0.71) %>% 
  ungroup() %>% dplyr::select(-name) %>% 
  unique() %>% mutate(usage = 'train') %>%
  dplyr::select(tile, index, usage)

grids_valid <- grids_labels_zone5 %>% 
  anti_join(grids_train, 
            by = c('tile', 'index')) %>% 
  group_by(name) %>% ungroup() %>% 
  dplyr::select(-name) %>% 
  unique() %>% mutate(usage = 'validate') %>%  
  dplyr::select(tile, index, usage)

# In order to set the batch size easily for DL,
# We re-arrange the sites among train and validate
# Train 1020, so 1020 / 30 could be without remainder.
# Validate 410, so 410 / 10 could be without remainder.
set.seed(678)
ids <- sample(1:nrow(grids_valid), 
              size = (nrow(grids_valid) - (1020 - nrow(grids_train))) %% 10)
grids_valid <- grids_valid %>% slice(-ids)

set.seed(568)
ids <- sample(1:nrow(grids_valid), size = 1020 - nrow(grids_train))
grids_valid$usage[ids] <- 'train'

catalog_train_val <- rbind(grids_train, grids_valid)

write.csv(catalog_train_val, 
          'data/intermid/catalog_guess_zone5_train_val.csv',
          row.names = F)
```

#### Generate labels images
In order to save the resources for deep learning, we re-defined the class index to be continuous. So:

```
id          name
1       Cropland
2       Forest
3       Grassland
4       Shrubland
5       Urban/Built up (8)
6       Water
```

```{r labels_img}
library(glue)

# Make the script consistent
tiles <- st_read('data/intermid/tiles_grids_256.geojson',
                 quiet = T)
lc_labels <- rast('data/intermid/lc_labels.tif')

plt_path <- '/Volumes/elephant/plt_nicfi'
plt_nms <- list.files(plt_path, full.names = T)
labels_path <- '/Volumes/elephant/labels_guess_zone5'

mclapply(unique(catalog_train_val$tile),
         function(tile_nm){
  tiles_each <- catalog_train_val %>% 
    filter(tile == tile_nm)
  lc_labels_each <- crop(lc_labels, tiles %>% 
                           filter(tile == tile_nm) %>% 
                           st_union() %>% 
                           st_buffer(0.01) %>% 
                           st_sf() %>% vect())
  nm <- grep(tile_nm, plt_nms, value = TRUE)[1]
  temp <- rast(nm)[[1]] %>% 
    aggregate(fact = 4096/width_chips)
  vals <- matrix(1:(width_chips^2), 
                 nrow = width_chips, 
                 ncol = width_chips) %>% t()
  vals <- vals[nrow(vals):1, ]
  values(temp) <- vals
  lapply(1:nrow(tiles_each), function(n){
    tile_each <- tiles_each %>% slice(n)
    temp_each <- temp
    index <- tile_each$index
    temp_each[temp_each != index] <- NA
    temp_each <- terra::trim(temp_each) %>% 
      disaggregate(fact = 4096/width_chips)
    label_each <- resample(lc_labels_each, temp_each, method = 'near')
    # Remove wetland, bareland, tundra, snow/ice
    label_each[label_each %in% c(5, 7, 9, 10)] <- 0
    # re-define urban
    label_each[label_each == 8] <- 5

    # freq(label_each)[, 2]
    writeRaster(label_each, 
                file.path(labels_path, 
                          glue('labels_{tile_nm}_{index}.tif')),
                wopt = list(datatype = 'INT1U',
                        gdal=c("COMPRESS=LZW")))
    rm(tile_each, temp_each, label_each, index);gc()
  })
  rm(tiles_each, lc_labels_each, nm, temp, vals);gc()
}, mc.cores = 12)
```

## Make catalogs
### Catalog for guess training

```{r catalogs}
library(stringr)
library(parallel)

## PlanetScope quads
plt_quads_rain_season <- list.files('/Volumes/elephant/plt_nicfi',
                        full.names = T, pattern = '2017-12_2018-05') %>% 
  data.frame(dir_gs = .) %>% 
  mutate(tile = str_extract(str_extract(dir_gs, 
                                        '[0-9]+-[0-9]+.tif'), 
                            '[0-9]+-[0-9]+'))
plt_quads_dry_season <- list.files('/Volumes/elephant/plt_nicfi',
                        full.names = T, pattern = '2018-06_2018-11') %>% 
  data.frame(dir_os = .) %>% 
  mutate(tile = str_extract(str_extract(dir_os, 
                                        '[0-9]+-[0-9]+.tif'), 
                            '[0-9]+-[0-9]+'))

plts <- merge(plt_quads_rain_season, plt_quads_dry_season, by = 'tile')
rm(plt_quads_rain_season, plt_quads_dry_season)
## Labels
lc_labels <- list.files('/Volumes/elephant/labels_guess_zone5',
                        full.names = T, pattern = '.tif$') %>% 
    data.frame(dir_label = .) %>% 
    mutate(name = str_extract(dir_label, 
                              '[0-9]+-[0-9]+_[0-9]+')) %>% 
    tidyr::separate(name, c('tile', 'index'), '_')
imgs <- merge(lc_labels, plts, by = 'tile')
# rm(plts, lc_labels)

catalog_train_val <- read.csv('data/intermid/catalog_guess_zone5_train_val.csv',
                                  stringsAsFactors = F) %>% 
    merge(imgs, by = c('tile', 'index')) %>% 
    mutate(name = paste(tile, index, sep = '-')) %>% 
    dplyr::select(name, usage, dir_gs, dir_os, dir_label)
write.csv(catalog_train_val, 'data/intermid/catalog_zone5_DL_guess_train_val.csv',
          row.names = F)
```

### Catalog for guess prediction
We make the prediction on all relevant tiles, and extra 200 tiles in our areas. One thing need to mention is that in order to reduce the impacts of chip boundary and give a better vision for checkers in next stage to manually check the generated labels, we just generate the labels for the central 3840 * 3840 of the original 4096 * 4096.

```{r}
pred_catalog <- catalog_train_val %>% 
  mutate(tile = str_extract(str_extract(dir_gs, 
                                        '[0-9]+-[0-9]+.tif'), 
                            '[0-9]+-[0-9]+')) %>% 
  dplyr::select(tile, dir_gs, dir_os) %>% unique() %>% 
  filter(!tile %in% (urbans %>% dplyr::select(tile) %>% unique() %>% pull(tile)))
write.csv(pred_catalog, 'data/intermid/catalog_zone5_DL_guess_predict.csv',
          row.names = F)
```

### AWS based (Optional)

Some pre-work before model training:

- Upload files to our AWS S3 bucket.
- Make the data catalog.

#### Upload imagery
Upload the images and labels to AWS S3 bucket.

```{r upload}
library(aws.s3)
library(parallel)

## PlanetScope quads
plt_quads_rain_season <- list.files('/Volumes/elephant/plt_nicfi',
                        full.names = T, pattern = '2017-12_2018-05')
plt_quads_dry_season <- list.files('/Volumes/elephant/plt_nicfi',
                        full.names = T, pattern = '2018-06_2018-11')
## Labels
lc_labels <- list.files('/Volumes/elephant/labels_guess',
                        full.names = T, pattern = '.tif$')

## Upload function
s3_upload <- function(fnames, prefix, bucket){
    mclapply(fnames, function(src_path){
    put_object(file = src_path, 
           object = file.path(prefix, 
                              basename(src_path)), 
           bucket = bucket)
}, mc.cores = 6)}

## Upload
s3_upload(plt_quads_rain_season, 
          "tz_dl_data/planet_quads/rain", 
          'activemapper')
s3_upload(plt_quads_dry_season, 
          "tz_dl_data/planet_quads/dry", 
          'activemapper')
s3_upload(lc_labels, 
          "tz_dl_data/lc_labels", 
          'activemapper')
```

#### Make catalog

```{r catalog}
library(dplyr)
library(stringr)
library(tidyr)
library(aws.s3)

# Rain season
items <- get_bucket(bucket = 'activemapper', 
                    prefix = 'tz_dl_data/planet_quads/rain', 
                    max = Inf)
keys <- lapply(c(2:length(items)), function(i) {
    basename(items[[i]]$Key)
})
plts_rain <- unlist(keys) %>% 
    paste0('s3://activemapper/tz_dl_data/planet_quads/rain/', .) %>% 
    data.frame(dir_gs = .) %>% 
    mutate(tile = str_extract(str_extract(dir_gs, 
                                          '[0-9]+-[0-9]+.tif'), 
                              '[0-9]+-[0-9]+'))

# Dry season
items <- get_bucket(bucket = 'activemapper', 
                    prefix = 'tz_dl_data/planet_quads/dry', 
                    max = Inf)
keys <- lapply(c(2:length(items)), function(i) {
    basename(items[[i]]$Key)
})
plts_dry <- unlist(keys) %>% 
    paste0('s3://activemapper/tz_dl_data/planet_quads/dry/', .) %>% 
    data.frame(dir_os = .) %>% 
    mutate(tile = str_extract(str_extract(dir_os, 
                                          '[0-9]+-[0-9]+.tif'), 
                              '[0-9]+-[0-9]+'))
plts <- merge(plts_rain, plts_dry, by = 'tile')
rm(plts_rain, plts_dry)

# Labels
items <- get_bucket(bucket = 'activemapper', 
                    prefix = 'tz_dl_data/lc_labels', 
                    max = Inf)
keys <- lapply(c(2:length(items)), function(i) {
    basename(items[[i]]$Key)
})
lc_labels <- unlist(keys) %>% 
    paste0('s3://activemapper/tz_dl_data/lc_labels/', .) %>% 
    data.frame(dir_label = .) %>% 
    mutate(name = str_extract(dir_label, 
                              '[0-9]+-[0-9]+_[0-9]+')) %>% 
    tidyr::separate(name, c('tile', 'index'), '_')
imgs <- merge(lc_labels, plts, by = 'tile')
rm(plts, lc_labels)

catalog_train_val_test <- read.csv('data/intermid/catalog_guess_train_val.csv',
                                  stringsAsFactors = F) %>% 
    merge(imgs, by = c('tile', 'index')) %>% 
    mutate(name = paste(tile, index, sep = '-')) %>% 
    dplyr::select(name, usage, dir_gs, dir_os, dir_label)
write.csv(catalog_train_val_test, 'data/intermid/catalog_DL_guess_train_val.csv',
          row.names = F)
put_object(file = 'data/intermid/catalog_DL_guess_train_val.csv', 
           object = 'tz_dl_data/catalogs/catalog_DL_guess_train_val.csv', 
           bucket = 'activemapper')
```

### 2021-03-06 docs/ensemble_labels_machine.Rmd
Some updates and applying OSM to clean labels

--- 2021-03-06 docs/ensemble_labels_local.Rmd
@@
 tiles <- vect('data/geoms/tiles_nicfi.geojson')
-```
-
-### TANSIS mask
-```{r}
-url_cp <- 'https://files.osf.io/v1/resources/yrj3h/providers/osfstorage/5c28365528af78001a63ee6d?action=download&direct&version=1'
-dir.create('data/tansis')
-download.file(url_cp, 'data/tansis/cp_pred.zip')
-unzip('data/tansis/cp_pred.zip', exdir = 'data/tansis')
 ```
@@
                 unique(fromglc_new), 
-                1)) # For GFSAD and TANSIS
+                1)) # For GFSAD
 lc_types <- lc_types %>% filter(id %in% ids)
@@
 
-tansis_mask <- rast(list.files('data/tansis', full.names = T, pattern = '.tif$'))
-tansis_mask <- tansis_mask$TZ__7
-tansis_mask[is.na(tansis_mask)] <- 0
-tansis_mask <- resample(tansis_mask != 0,
+gfsad_mask <- resample(gfsad_new == 0,
                        fromglc_new, 
                        method = 'near')
-
-gfsad_mask <- resample(gfsad_new != 0,
-                       fromglc_new, 
-                       method = 'near')
-crop_mask <- (tansis_mask + gfsad_mask) == 0
 lapply(1:nrow(lc_types), function(n){
@@
                     lc_lb_fromglc + 
-                    lc_lb_gfsad) >= 3
-    lc_lb_emb <- lc_lb_emb * crop_mask
+                    lc_lb_gfsad) == 3
     rm(lc_lb_esaglc, lc_lb_fromglc, lc_lb_gfsad); gc()
@@
                              method = 'near')
+    # gfsad_mask <- resample(gfsad_new == 0,
+    #                        lc_lb_fromglc, 
+    #                        method = 'near')
     lc_lb_emb <- (lc_lb_esaglc + 
                     lc_lb_fromglc) == 2
-    message('Skip the cropland area defined by gfsad and tansis.')
-    lc_lb_emb <- lc_lb_emb * crop_mask
-    # lc_lb_emb <- lc_lb_emb * gfsad_mask
+    message('Skip the cropland and water area from gfsad.')
+    lc_lb_emb <- lc_lb_emb * gfsad_mask
     rm(lc_lb_esaglc, lc_lb_fromglc); gc()
@@
 
-For Tanzania case, there is very tiny Tundra and Snow/Ice type if any because Tanzania is a tropical country. The only possible is on the Q mountain.
+For Tanzania case, there is no Tundra and Snow/Ice type because Tanzania is a tropical country.
 
@@
 fn <- file.path(dst_path, 'lc_labels.tif')
-writeRaster(labels, fn, overwrite = TRUE,
+writeRaster(labels, fn, 
               wopt = list(datatype = 'INT1U',
@@
 fn <- file.path(dst_path, 'labels_extent.tif')
-writeRaster(labels_ext, fn, overwrite = TRUE,
+writeRaster(labels_ext, fn, 
               wopt = list(datatype = 'INT1U',
@@
 #### Select out sub-grids
+Because of the under representation of classes: Bareland, Wetland, and Built-up, so gather them together as others class to ensure the good classification result.
+In general, we selected grids under three groups:
+- Group 1: Relatively pure class grids (400 * 6 = 2400).
+- Group 2: Highlighted areas such as cities and rivers (random 300)
+- Group 3: Random grids across the consensus label areas (random 300)
 
-Start-up zone: zone 5
-
+##### Group 1
 ```{r g1}
@@
                  quiet = T) %>% dplyr::select(tile)
-ecozones <- st_read('data/intermid/clusters_final.geojson',
+ecozones <- st_read('data/geoms/ecozones_simple.geojson',
                     quiet = T)
@@
            index = c(1:(width_chips^2)))
+  do.call(rbind, lapply(1:nrow(tiles_grids), function(m){
+    tile <- tiles_grids %>% slice(m)
+    ids <- st_intersects(tile, ecozones) %>% unlist()
+    tile %>% mutate(ecozone = ids[1])
+  }))
 }, mc.cores = 12))
+tiles <- tiles %>% filter(!is.na(ecozone))
 st_write(tiles, 'data/intermid/tiles_grids_ecozones_256.geojson')
@@
 
-tiles <- st_read('data/intermid/tiles_grids_ecozones_256.geojson')
-tiles <- tiles %>% dplyr::select(-ecozone) %>% unique()
-st_write(tiles, 'data/intermid/tiles_grids_256.geojson')
-
-ecozones <- st_read('data/intermid/clusters_final.geojson',
-                    quiet = T)
-ecozone_5 <- ecozones %>% filter(region == 5)
-tiles_zone5 <- tiles %>% 
-    filter(st_intersects(ecozone_5, tiles, sparse = F)) %>% 
-    vect()
-st_write(tiles_zone5, 'data/intermid/tiles_grids_zone5.geojson')
-
-# lc_types <- lc_types %>% filter(!id %in% c(5, 7, 9, 10))
-tiles_labels_zone5 <- mclapply(1:nrow(tiles_zone5), function(n){
-    labels_each <- crop(lc_labels, tiles_zone5[n, ])
-    lb <- freq(labels_each) %>% data.frame() %>% 
-        filter(value != 0) %>%
-        mutate(count = count / (dim(labels_each)[1] * dim(labels_each)[2])) %>%
-        left_join(., lc_types, by = c('value' = 'id')) %>%
-        dplyr::select(-c(value, layer)) %>%
-        pivot_wider(names_from = name, values_from = count) %>%
-        mutate(tile = tiles_zone5[n, ]$tile,
-               index = tiles_zone5[n, ]$index)
-    if (nrow(lb) > 0) lb
-}, mc.cores = 8) %>% bind_rows()
-
-tiles_labels_zone5 <- tiles_labels_zone5 %>%
-    dplyr::select(-c('Wetland', 'Bareland', 'Tundra'))
-
-class_nm <- c('Cropland', 'Forest', 'Grassland', 
-              'Shrubland', 'Water')
-grids_pure_zone5 <- do.call(rbind, 
+class_nm <- c('Cropland', 'Forest', 'Grassland', 'Shrubland', 
+              'Wetland', 'Water', 'Urban/Built up', 'Bareland')
+tiles_grids_pure <- do.call(rbind, 
                             lapply(class_nm, 
@@
     message(nm)
-                                tile_select <- tiles_labels_zone5 %>% 
+    # Ensure the enough amount of labels,
+    # use different threshold to choose labels,
+    # even though the labels might not be perfect.
+    # Bareland, the most corrupted, so use 0.4
+    # Shrubland and Cropland, use 0.7
+    # Grassland, Forest, and water are probably the 
+    # easiest classes.
+    if (nm %in% c('Bareland', 'Wetland', 'Urban/Built up')) {
+      tile_select <- tiles_labels %>% 
+        dplyr::select(tile, index, all_of(nm)) %>% 
+        filter(!is.na(!!rlang::sym(nm))) %>% 
+        filter((!!rlang::sym(nm)) >= 0.6)
+    } else {
+      tile_select <- tiles_labels %>% 
           dplyr::select(tile, index, all_of(nm)) %>% 
@@
           filter((!!rlang::sym(nm)) >= 0.9)
+    }
     data.frame(name = nm, 
                tile = tile_select$tile, 
-                                            index = tile_select$index,
-                                            purity = tile_select %>% 
-                                                dplyr::select((!!rlang::sym(nm))) %>% 
-                                                pull)
+               index = tile_select$index)
 }))
 
-grids_pure_count <- grids_pure_zone5 %>% 
+grids_pure_count <- tiles_grids_pure %>% 
   group_by(name) %>% summarize(n = n()) %>% 
   arrange(n)
+write.csv(grids_pure_count, 'data/intermid/pure_grids_count.csv',
+          row.names = F)
+```
 
-# This area covers most of the LC types, only miss enough built-up.
-# Fortunately, built-up has very obvious and relatively same feature across the whole regions.
-# so we could get some from other regions.
+```{r, eval=T, echo=F, message=F, warning=F}
+grids_pure_count <- read.csv(here('data/intermid/pure_grids_count.csv'),
+                             stringsAsFactors = F)
+
+# Based on the table, the first three minor classes 
+grids_pure_count %>%
+  kbl(caption = "Pure label grids summary") %>%
+  kable_classic(full_width = F, html_font = "Cambria")
+```
+
+```{r g1_sample}
 set.seed(123)
-grids_labels_zone5 <- grids_pure_zone5 %>% 
+grids_common_class <- tiles_grids_pure %>% 
+  mutate(name = ifelse(name %in% c('Bareland', 'Wetland', 
+                                   'Urban/Built up'), 'Other', 
+                       name)) %>% 
   group_by(name) %>% 
-    sample_n(250) %>% 
+  sample_n(500) %>% 
   ungroup()
+```
 
-# built-up
-tile_select <- tiles_labels %>% 
-    dplyr::select(tile, index, all_of('Urban/Built up')) %>% 
+##### Group 2
+```{r g2}
+# choose cities based on the consensus built-up
+nm <- 'Urban/Built up'
+cities <- tiles_labels %>% 
+        dplyr::select(tile, index, all_of(nm)) %>% 
         filter(!is.na(!!rlang::sym(nm))) %>% 
-    filter((!!rlang::sym(nm)) >= 0.5)
-urbans <- data.frame(name = nm, 
-           tile = tile_select$tile, 
-           index = tile_select$index,
-           purity = tile_select %>% 
-               dplyr::select((!!rlang::sym(nm))) %>% 
-               pull)
-grids_labels_zone5 <- rbind(grids_labels_zone5, urbans)
-grids_labels_zone5_json <- st_read('data/intermid/tiles_grids_256.geojson') %>% 
-    right_join(grids_labels_zone5, by = c('tile', 'index'))
-st_write(grids_labels_zone5_json, 'data/intermid/grids_labels_zone5.geojson')
+        filter((!!rlang::sym(nm)) >= 0.2) %>%
+  anti_join(grids_common_class, by = c('tile', 'index'))
+
+# choose tiles overlapped with rivers
+tiles <- st_read('data/intermid/tiles_grids_ecozones_256.geojson')
+rivers <- st_read('data/geoms/gis_osm_waterways_free_1.shp') %>% 
+  filter(fclass == 'river')
+set.seed(160)
+tiles_rivers <- tiles %>% 
+  slice(unique(unlist(st_intersects(rivers, tiles)))) %>% 
+  anti_join(grids_common_class, by = c('tile', 'index')) %>% 
+  anti_join(cities, by = c('tile', 'index')) %>% 
+  sample_n(1000 - nrow(cities))
+cities_rivers <- rbind(cities %>% dplyr::select(tile, index),
+                       tiles_rivers %>% dplyr::select(tile, index) %>% 
+                         st_drop_geometry()) %>%
+  unique() %>% mutate(name = 'Special')
+```
+
+##### Group 3
+```{r g3}
+g1_g2 <- rbind(grids_common_class, cities_rivers)
+tiles <- tiles %>% anti_join(g1_g2, by = c('tile', 'index'))
+
+# Only keep the grids with labels
+target_vars <- setdiff(names(tiles_labels), 
+                       c('ecozone', 'tile', 'index'))
+tiles_full <- tiles_labels %>% 
+  mutate(ratio = rowSums(.[target_vars], na.rm = TRUE)) %>% 
+  filter(ratio > 0.8)
+tiles <- tiles %>% right_join(tiles_full, by = c('tile', 'index'))
+
+set.seed(170)
+random_sites <- tiles %>% sample_n(1000) %>% 
+  dplyr::select(tile, index) %>% 
+  st_drop_geometry() %>% 
+  mutate(name = 'random')
+```
+
+##### All grids
+
+```{r g123}
+grids_selected <- rbind(g1_g2, random_sites)
+rm(g1_g2, random_sites, cities, rivers, tiles_rivers, cities_rivers);gc()
 ```
@@
 set.seed(100)
-grids_train <- grids_labels_zone5 %>% 
-  group_by(name) %>% sample_frac(0.71) %>% 
+grids_train <- grids_selected %>% 
+  group_by(name) %>% sample_frac(0.7) %>% 
   ungroup() %>% dplyr::select(-name) %>% 
@@
 
-grids_valid <- grids_labels_zone5 %>% 
+grids_valid <- grids_selected %>% 
   anti_join(grids_train, 
@@
 # We re-arrange the sites among train and validate
-# Train 1020, so 1020 / 30 could be without remainder.
-# Validate 410, so 410 / 10 could be without remainder.
+# Train 3510, so 3510 / 30 could be without remainder.
+# Validate 1470, so 1470 / 10 could be without remainder.
 set.seed(678)
 ids <- sample(1:nrow(grids_valid), 
-              size = (nrow(grids_valid) - (1020 - nrow(grids_train))) %% 10)
+              size = (nrow(grids_valid) - (3510 - nrow(grids_train))) %% 10)
 grids_valid <- grids_valid %>% slice(-ids)
@@
 set.seed(568)
-ids <- sample(1:nrow(grids_valid), size = 1020 - nrow(grids_train))
+ids <- sample(1:nrow(grids_valid), size = 3510 - nrow(grids_train))
 grids_valid$usage[ids] <- 'train'
@@
 write.csv(catalog_train_val, 
-          'data/intermid/catalog_guess_zone5_train_val.csv',
+          'data/intermid/catalog_guess_train_val.csv',
           row.names = F)
@@
 4       Shrubland
-5       Urban/Built up (8)
+5       Other (Wetland 5, Urban/Built up 8, Bareland 9)
 6       Water
@@
 # Make the script consistent
-tiles <- st_read('data/intermid/tiles_grids_256.geojson',
+tiles <- st_read('data/intermid/tiles_grids_ecozones_256.geojson',
                  quiet = T)
@@
 plt_nms <- list.files(plt_path, full.names = T)
-labels_path <- '/Volumes/elephant/labels_guess_zone5'
+labels_path <- '/Volumes/elephant/labels_guess'
 
@@
     label_each <- resample(lc_labels_each, temp_each, method = 'near')
-    # Remove wetland, bareland, tundra, snow/ice
-    label_each[label_each %in% c(5, 7, 9, 10)] <- 0
-    # re-define urban
-    label_each[label_each == 8] <- 5
+    label_each[label_each %in% c(8, 9)] <- 5
+    label_each[label_each %in% c(7, 10)] <- 0
 
@@
 ## Labels
-lc_labels <- list.files('/Volumes/elephant/labels_guess_zone5',
+lc_labels <- list.files('/Volumes/elephant/labels_guess',
                         full.names = T, pattern = '.tif$') %>% 
@@
 
-catalog_train_val <- read.csv('data/intermid/catalog_guess_zone5_train_val.csv',
+catalog_train_val <- read.csv('data/intermid/catalog_guess_train_val.csv',
                                   stringsAsFactors = F) %>% 
@@
     dplyr::select(name, usage, dir_gs, dir_os, dir_label)
-write.csv(catalog_train_val, 'data/intermid/catalog_zone5_DL_guess_train_val.csv',
+write.csv(catalog_train_val, 'data/intermid/catalog_DL_guess_train_val.csv',
           row.names = F)
@@
 ```{r}
-pred_catalog <- catalog_train_val %>% 
+pred_labeled <- catalog_train_val %>% 
   mutate(tile = str_extract(str_extract(dir_gs, 
@@
   dplyr::select(tile, dir_gs, dir_os) %>% unique() %>% 
-  filter(!tile %in% (urbans %>% dplyr::select(tile) %>% unique() %>% pull(tile)))
-write.csv(pred_catalog, 'data/intermid/catalog_zone5_DL_guess_predict.csv',
+  mutate(with_label = 1)
+
+set.seed(320)
+pred_unlabeled <- st_read('data/geoms/tiles_nicfi.geojson') %>% 
+  filter(!tile %in% pred_labeled$tile) %>% 
+  sample_n(200) %>% 
+  merge(plts, by = 'tile') %>% 
+  st_drop_geometry() %>% 
+  dplyr::select(tile, dir_gs, dir_os) %>% 
+  mutate(with_label = 0)
+
+pred_catalog <- rbind(pred_labeled, pred_unlabeled)
+rm(pred_labeled, pred_unlabeled)
+write.csv(pred_catalog, 'data/intermid/catalog_DL_guess_predict.csv',
           row.names = F)

### 2021-03-06 docs/learn_dl_ensemble.Rmd
Some updates and applying OSM to clean labels

--- 2021-01-16 docs/run_dl_aws.Rmd
@@
 ---
-title: "Run deep learning on AWS instance"
+title: "Learn from ensemble labels"
 author: "Lei Song"
@@
 
-## Launch instance
+## Set up GPU environment
+### AWS based method
+#### Launch AWS instance
+If you decide to use AWS instance, here are some basic steps.
 The information of instance that we used:
@@
 chmod 777 ./aws_tools/create_spot_instance.sh
-./aws_tools/create_spot_instance.sh ami-0643df3b347740189 g3.8xlarge sg-0a8bbc91697d6a76b lc_tz persistent 2021-01-20T23:00:00 lsong-keypair
+./aws_tools/create_spot_instance.sh ami-0643df3b347740189 g3.16xlarge sg-0a8bbc91697d6a76b lc_dl_tz persistent 2021-01-22T23:00:00 lsong-keypair
 ```
 
-## Parameters setting
+#### Parameters setting
 After successfully launched the instance, then it is ready to get into the instance to work.
@@
 
-## Result visualization
+### Google Colab
+In general, we mean to use Google Colab to run the model.
+For this case, it is more convenient to read the data locally and pickle them.
+Then directly load the pickles into Google Colab and just use the GPU environment to run the models.
+
+## Experiemnts
+###candidate models
+
+- U-net, which has simple architecture and is friendly to small dataset. This model is especially suitable for guess training.
+
+- Deeplab3plus with ResNet as backbone.
+This architecture can consider the global context and have skip connections to ensure the complex structure still could get coverage.
+This model is super useful for the final train with manually corrected labels.
+
+### Label smoothing
+The general loss is higher than classic cross entropy loss.
+But it do help to reduce the gaps between train and validate.
+So it might be a promising method to use for our case.
+There is one general parameter "smooth rate".
+Based on the experiments, a higher smooth rate could help to reduce the gap between train and validate more.
+0.5 is a safe choice.

### 2021-03-06 docs/work_log.Rmd
Some updates and applying OSM to clean labels

---
title: "Work log"
author: "Lei Song"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown:
    highlight: pygments
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Workflow 1
I tried to generate ensemble labels based on multiple land cover products with high quality. Choose 3000 "pure" grids, 1000 special grids for river regions and cities, and 1000 extra random grids across the whole region.

The train process is smooth, which has good loss and overall accuracy. However, because of the wideness of the country, global spatial generalization reduce the classification accuracy dramatically for any specific tile.

So this method is not ideal for now. But the workflow could be found in [here](ensemble_labels_machine.Rmd)

## Workflow 2
We decided to try another method, which use regional spatial generalization. We also plan to ensemble more prior knowledge such as TANSIS project.
- Use zone 5, train a U-net with 1500 epochs with cross entropy
- Use zone 5, train a Deeplab with 1500 epochs wit cross entropy
- Compare these two models, try to use co-training.
- Define the final version of modeling in one zone.
- Contagious to other areas.

The results shows that

### 2021-03-06 scripts/global_regional_local_coguess.R

@@ -1,0 +1,205 @@
+library(parallel)
+library(terra)
+library(sf)
+library(raster)
+library(dplyr)
+library(tidyr)
+
+dst_path <- 'data/zone5'
+
+## Get tiles
+select <- dplyr::select
+tiles <- st_read('data/geoms/tiles_nicfi.geojson')
+ecozones <- st_read('data/intermid/clusters_final.geojson',
+                    quiet = T)
+tiles <- do.call(rbind, mclapply(1:nrow(ecozones), function(n){
+    ecozone <- ecozones %>% slice(n)
+    ids <- st_intersects(ecozone, tiles) %>% unlist()
+    tiles %>% slice(ids) %>% 
+        select(tile) %>% 
+        mutate(ecozone = ecozone$region)
+}, mc.cores = 12))
+tiles <- tiles %>% na.omit()
+tiles_zone5 <- tiles %>% filter(ecozone == 5)
+st_write(tiles_zone5, file.path(dst_path, 'tiles_zone5.geojson'))
+
+## Sample global labels
+lc_labels <- rast('data/intermid/lc_labels.tif')
+n_labels <- freq(lc_labels)
+# set NA flag
+NAflag(lc_labels) <- 0
+
+# Get balanced samples
+set.seed(10)
+samples_global <- sampleStratified(raster(lc_labels), 
+                            size = min(30000, 
+                                       min(n_labels[, 'count'])),
+                            na.rm = T, sp = T) %>% 
+    st_as_sf() %>% mutate(landcover = sum) %>% select(landcover)
+
+
+## Sample regional labels
+### Get the labels for zone5
+tiles_zone5_vect <- vect(tiles_zone5)
+lc_labels_zone5 <- mask(crop(lc_labels, 
+                             tiles_zone5_vect), 
+                        tiles_zone5_vect)
+rm(lc_labels, tiles_zone5_vect); gc()
+
+# Tundra is basically a mis-classification around water bodies,
+# and urban class makes significant confusion with other classes,
+# so we just mask out these two classes for the guessing stage.
+n_labels <- freq(lc_labels_zone5)
+lc_labels_zone5[lc_labels_zone5 == 7] <- 0
+lc_labels_zone5[lc_labels_zone5 == 8] <- 0
+
+# ## Urban
[…]

### 2021-03-06 scripts/guess_model.R

@@ -1,0 +1,114 @@
+# an experiment
+# run RF model on one tile to get the results, and ensemble the RF results.
+## get tiles with high diversity
+library(parallel)
+library(terra)
+library(sf)
+library(dplyr)
+library(tidyr)
+select <- dplyr::select
+tiles <- st_read('data/geoms/tiles_nicfi.geojson')
+ecozones <- st_read('data/intermid/clusters_final.geojson',
+                    quiet = T)
+tiles <- do.call(rbind, mclapply(1:nrow(ecozones), function(n){
+    ecozone <- ecozones %>% slice(n)
+    ids <- st_intersects(ecozone, tiles) %>% unlist()
+    tiles %>% slice(ids) %>% 
+        select(tile) %>% 
+        mutate(ecozone = ecozone$region)
+}, mc.cores = 12))
+tiles <- tiles %>% na.omit()
+tiles_zone5 <- tiles %>% filter(ecozone == 5)
+
+# Get diversity
+lc_types <- data.frame(id = seq(1, 10),
+                       name = c('Cropland', 'Forest', 'Grassland', 
+                                'Shrubland', 'Wetland', 'Water', 
+                                'Tundra', 'Urban/Built up',
+                                'Bareland', 'Snow/Ice'))
+lc_types <- lc_types %>% slice(-10)
+tiles_zone5_vect <- vect(tiles_zone5)
+lc_labels <- rast('data/intermid/lc_labels.tif')
+tiles_labels_zone5 <- mclapply(1:nrow(tiles_zone5), function(n){
+    labels_each <- crop(lc_labels, tiles_zone5_vect[n, ])
+    lb <- freq(labels_each) %>% data.frame() %>% 
+        filter(value != 0) %>%
+        mutate(count = count / (dim(labels_each)[1] * dim(labels_each)[2])) %>%
+        left_join(., lc_types, by = c('value' = 'id')) %>%
+        dplyr::select(-c(value, layer)) %>%
+        # filter(count >= 0.2) %>% 
+        pivot_wider(names_from = name, values_from = count) %>%
+        mutate(ratio = rowSums(.),
+               diversity = ncol(.),
+               evenness = sd(.),
+               tile = tiles_zone5_vect[n, ]$tile)
+    if (nrow(lb) > 0) lb
+}, mc.cores = 8) %>% bind_rows()
+
+tiles_labels_zone5 <- tiles_labels_zone5 %>% 
[…]

### 2021-03-06 scripts/sampling.R

@@ -1,0 +1,165 @@
+# Title     : Script to get samples for RF
+# Objective : To sample landcover types to run 
+#             a random forest model.
+# Created by: Lei Song
+# Created on: 02/24/21
+
+#######################
+##  Step 1: Setting  ##
+#######################
+## Load packages
+library(terra)
+library(parallel)
+library(sf)
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(rgrass7)
+
+#############################################
+##  Step 2: Sampling from ensemble labels  ##
+#############################################
+# Read the OSM-masked ensemble labels
+lc_labels <- rast('data/north/lc_labels_north_mask.tif')
+n_labels <- freq(lc_labels)
+sum(n_labels[, 3]) * 0.01 / nrow(n_labels)
+
+## Use GRASS GIS to sample
+gisBase <- '/Applications/GRASS-7.9.app/Contents/Resources'
+initGRASS(gisBase = gisBase,
+          home = tempdir(),
+          gisDbase = tempdir(),  
+          mapset = 'PERMANENT', 
+          location = 'lc_types', 
+          override = TRUE)
+execGRASS("g.proj", flags = "c", 
+          proj4="+proj=longlat +datum=WGS84 +no_defs")
+execGRASS('r.in.gdal', flags = c("o", "overwrite"),
+          input = 'data/north/lc_labels_north_mask.tif',
+          band = 1,
+          output = "lc_types")
+execGRASS("g.region", raster = "lc_types")
+execGRASS('r.sample.category', flags = c("overwrite"),
+          parameters = list(input = 'lc_types', 
+                            output = 'lc_samples',
+                            npoints = c(rep(2e5, 4), rep(1e5, 2)), # roughly ncells * 0.01
+                            random_seed = 10))
+
+use_sf()
+samples_esm <- readVECT('lc_samples') %>% 
+    mutate(landcover = lc_types) %>% 
+    dplyr::select(landcover)
+save(samples_esm, file = 'data/north/samples_esm.rda')
+
+#########################################
+##  Step 3: Sampling from OSM dataset  ##
+#########################################
+## Get sample numbers
+nums <- samples_esm %>% 
+    group_by(landcover) %>% 
+    summarise(n = n())
+# save(nums, file = 'data/north/nums.rda')
+
+## Bareland
[…]

### 2021-03-06 scripts/train_guess_model.R

@@ -1,0 +1,180 @@
+# Title     : Script to build LC guess model
+# Objective : To tune and train random forest 
+#             land cover guesser.
+# Created by: Lei Song
+# Created on: 02/24/21
+
+#######################
+##  Step 1: Setting  ##
+#######################
+## Load packages
+library(dplyr)
+library(ramify)
+library(ranger)
+library(parsnip)
+library(tidymodels)
+library(vip)
+library(dials)
+library(tune)
+library(ggplot2)
+
+#############################
+##  Step 2: Load training  ##
+#############################
+## Get training
+load(file.path('data/north', 'training.rda'))
+training <- training %>% 
+    arrange(landcover) %>% 
+    mutate(landcover = as.factor(landcover))
+
+##############################
+##  Step 3: Tune the model  ##
+##############################
+## Remove NAs and get subset of training to tune
+set.seed(123)
+training <- training %>% na.omit() %>% 
+    sample_frac(size = 0.1)
+
+## Importance of features
+### We want to reduce the number of S1 to mitigate
+### the impacts of low resolution.
+set.seed(785)
+forest_vip <- rand_forest() %>%
+    set_engine("ranger", 
+               importance = "impurity_corrected") %>%
+    set_mode("classification") %>% 
+    fit(landcover ~ ., data = training)
+save(forest_vip, file = 'data/north/forest_vip.rda')
+
+## Plot
+vip(forest_vip, num_features = ncol(training) - 1,
+    aesthetics = list(color = "transparent", 
+                      fill = "red")) +
+    theme_light()
+
+## Based on the figure above, we decide to get rid of 
+## vv (3, 5, 6) and vh(3, 5, 6) variables. Because they
+## are the least important features, and they have coarse
+## spatial resolution.
+
+## Subset the features based on importance
+### Reload training
+load(file.path('data/north', 'training.rda'))
+training <- training %>% 
+    arrange(landcover) %>% 
+    mutate(landcover = as.factor(landcover))
+training <- training %>% 
+    dplyr::select(-c(paste0('vv', c(3, 5, 6)),
+                     paste0('vh', c(3, 5, 6))))
+
+## Define the cross validation folds
+set.seed(123)
+training_split <- initial_split(training, prop = 0.80)
+lc_train <- training(training_split)
[…]

### 2021-03-23 scripts/1_ensemble_labels.R
Pack all scripts related to guess model

@@ -1,0 +1,329 @@
+# Title     : Script to ensemble landcover labels
+# Objective : To ensemble multiple land cover products to make LC labels.
+# Created by: Lei Song
+# Created on: 03/22/21
+
+#######################
+##  Step 1: Setting  ##
+#######################
+message('Step1: Setting')
+
+## Load libraries
+library(dplyr)
+library(terra)
+library(sf)
+library(here)
+
+############################################
+##  Step 2: Mosaic and clip the products  ##
+############################################
+message('Step 2: Mosaic and clip the products')
+
+# Tiles
+tiles <- vect(here('data/geoms/tiles_nicfi_north.geojson'))
+
+# Data directory
+ext_dir <- '/Volumes/elephant/landcovers'
+
+# FROM_GLC
+message('--FROM_GLC')
+fnames <- list.files(file.path(ext_dir, 
+                               'FROM_GLC_2017'),
+                     full.names = T)
+fromglc <- do.call(merge, lapply(fnames, function(fname){
+    rast(fname)
+})) %>% crop(tiles) %>% mask(tiles)
+
+# GFSAD30AFCE
+message('--GFSAD30AFCE')
+fnames <- list.files(file.path(ext_dir, 
+                               'GFSAD30AFCE_2015'),
+                     full.names = T,
+                     pattern = 'tif$')
+gfsad <- do.call(merge, lapply(fnames, function(fname){
+    rast(fname)
+})) %>% crop(tiles) %>% mask(tiles)
+
+# ESAGLC
+message('--ESAGLC')
+fnames <- list.files(file.path(ext_dir, 
+                               'ESA_GLC_2018'),
+                     full.names = T)
+esaglc <- do.call(merge, lapply(fnames, function(fname){
+    rast(fname)
+})) %>% crop(tiles) %>% mask(tiles)
+
+# Get TANSIS mask
+message('--TANSIS')
+url_cp <- paste0('https://files.osf.io/v1/resources/',
+                 'yrj3h/providers/osfstorage/5c283655',
+                 '28af78001a63ee6d?action=download&di',
+                 'rect&version=1')
+dir.create(here('data/tansis'))
+download.file(url_cp, here('data/tansis/cp_pred.zip'))
+unzip(here('data/tansis/cp_pred.zip'), exdir = here('data/tansis'))
+
+#########################################
+##  Step 3: Redefine land cover types  ##
+#########################################
[…]

### 2021-03-23 scripts/2_get_osm.R

@@ -7,8 +7,10 @@
 #######################
 ##  Step 1: Setting  ##
 #######################
+message('Step1: Setting')
 
 ## Load libraries
+library(here)
 library(stringr)
 library(parallel)
 library(sf)
@@ -16,28 +18,32 @@ library(dplyr)
 library(tidyr)
 
 ## Define the destination folder
-dst_path <- 'data/north'
+dst_path <- here('data/north')
 
 ######################################
 ##  Step 2: Load and download data  ##
 ######################################
+message('Step 2: Load and download data')
+
 ## Get tiles
 select <- dplyr::select
-tiles_north <- st_read('data/geoms/tiles_nicfi_north.geojson')
+tiles_north <- st_read(here('data/geoms/tiles_nicfi_north.geojson'))
 
 ## Get OSM
 osm_link <- file.path('https://download.geofabrik.de/africa', 
                       'tanzania-latest-free.shp.zip')
-download.file(osm_link, 'data/tanzania_osm.zip')
-dir.create('data/temp', showWarnings = F)
-unzip('data/tanzania_osm.zip', exdir = 'data/temp')
+download.file(osm_link, here('data/tanzania_osm.zip'))
+dir.create(here('data/temp'), showWarnings = F)
+unzip(here('data/tanzania_osm.zip'), exdir = here('data/temp'))
 
 ###########################################
 ##  Step 3: Crop the data to study area  ##
 ###########################################
+message('Step 3: Crop the data to study area')
+
 ## Subset the vectors
 tiles_north <- tiles_north %>% st_union()
-fnames <- list.files('data/temp', pattern = '.shp', full.names = T)
+fnames <- list.files(here('data/temp'), pattern = '.shp', full.names = T)
 
 rivers <- st_read(fnames[str_detect(fnames, 'waterways', )]) %>% 
     st_intersection(tiles_north) %>% 
@@ -76,14 +82,14 @@ buildings <- do.call(rbind,
     st_collection_extract('POLYGON')
 
 ## Save out the processed vectors
-dir.create('data/osm')
-st_write(rivers, 'data/osm/rivers.geojson')
-st_write(waterbodies, 'data/osm/waterbodies.geojson')
-st_write(wetlands, 'data/osm/wetlands.geojson')
-st_write(roads, 'data/osm/roads.geojson')
-st_write(big_roads, 'data/osm/big_roads.geojson')
[…]

### 2021-03-23 scripts/5_get_training.R

@@ -7,7 +7,10 @@
 #######################
 ##  Step 1: Setting  ##
 #######################
+message('Step1: Setting')
+
 ## Load packages
+library(here)
 library(terra)
 library(parallel)
 library(sf)
@@ -19,11 +22,13 @@ library(rgrass7)
 ####################################
 ##  Step 2: Load related dataset  ##
 ####################################
+message('Step 2: Load related dataset')
+
 ## Get samples
-samples <- st_read('data/north/samples_all.geojson')
-tiles_north <- st_read('data/geoms/tiles_nicfi_north.geojson')
+samples <- st_read(here('data/north/samples_all.geojson'))
+tiles_north <- st_read(here('data/geoms/tiles_nicfi_north.geojson'))
 samples <- st_join(samples, tiles_north)
-save(samples, file = 'data/north/samples.rda')
+save(samples, file = here('data/north/samples.rda'))
 
 ## Read file names
 plt_path <- '/Volumes/elephant/plt_nicfi'
@@ -34,6 +39,8 @@ s1_nms <- list.files(s1_path, full.names = T)
 ####################################
 ##  Step 3: Prepare image stacks  ##
 ####################################
+message('Step 3: Prepare image stacks')
+
 ## Define the function to make image stacks
 get_img_wdist <- function(tile_nm, tiles_north,
                     rivers_all, roads_all, 
@@ -41,7 +48,7 @@ get_img_wdist <- function(tile_nm, tiles_north,
     message(tile_nm)
     
     # read Planet images
-    message('Planet basemap.')
+    message('--Planet basemap')
     plt_nms_tile <- grep(tile_nm, plt_nms, value = TRUE)
     plt_os <- rast(grep('2017-12_2018-05', 
                         plt_nms_tile, value = TRUE)) %>% 
@@ -71,7 +78,7 @@ get_img_wdist <- function(tile_nm, tiles_north,
     rm(plt_os, plt_gs); gc()
     
     # Read S1 images
-    message('Sentinel-1 images.')
+    message('--Sentinel-1 images')
     s1_nms_tile <- grep(tile_nm, s1_nms, value = TRUE)
     s1_vv <- rast(grep('VV', s1_nms_tile, value = TRUE))
     s1_vv <- resample(s1_vv, plts$os_band1)
@@ -81,7 +88,7 @@ get_img_wdist <- function(tile_nm, tiles_north,
     names(s1_vh) <- paste0('vh', 1:6)
     
[…]

### 2021-03-23 scripts/7_pred_guess_model.R

@@ -1,0 +1,62 @@
+# Title     : Script to make guess labels
+# Objective : To use random forest guesser
+#             to get new labels.
+# Created by: Lei Song
+# Created on: 02/24/21
+
+#######################
+##  Step 1: Setting  ##
+#######################
+message('Step1: Setting')
+
+library(here)
+library(terra)
+library(dplyr)
+library(ramify)
+library(ranger)
+library(parsnip)
+library(tidymodels)
+library(stringr)
+library(glue)
+
+#############################
+###  Step 2: Preparation  ###
+#############################
+message('Step 2: Preparation')
+
+# Load model
+message("--Load model")
+load(here('data/north/guess_rf_md.rda'))
+
+# Define function to do prediction
+make_pred <- function(img_path,
+                      dst_path = 'results/north/prediction'){
+    id <- str_extract(img_path, '[0-9]+-[0-9]+')
+    message(paste0('--', id))
+    imgs <- rast(img_path) %>%
+        subset(setdiff(names(.),
+                       c('rivers_dist', 'buildings_dist',
+                         'roads_dist')))
+    
+    ## Predict scores and classes
+    scores <- predict(imgs, guess_rf_md, type = "prob")
+    writeRaster(scores, here(glue('{dst_path}/scores_{id}.tif')))
+    pred <- argmax(values(scores))
+    classes <- scores[[1]]
+    values(classes) <- pred
+    writeRaster(classes, here(glue('{dst_path}/classed_{id}.tif')))
+}
+
+#############################
+#  Step 3: Make prediction  #
+#############################
+message('Step 3: Make prediction')
+
+# Read image stack
+dst_path <- '/Volumes/elephant'
+fnames <- list.files(
+    file.path(dst_path, 'pred_stack'),
+                     full.names = T)
+set.seed(456)
+fnames <- sample(fnames, size = 200)
+lapply(fnames, make_pred)

### 2021-03-23 scripts/global_regional_local_coguess.R

@@ -1,205 +1,0 @@
-library(parallel)
-library(terra)
-library(sf)
-library(raster)
-library(dplyr)
-library(tidyr)
-
-dst_path <- 'data/zone5'
-
-## Get tiles
-select <- dplyr::select
-tiles <- st_read('data/geoms/tiles_nicfi.geojson')
-ecozones <- st_read('data/intermid/clusters_final.geojson',
-                    quiet = T)
-tiles <- do.call(rbind, mclapply(1:nrow(ecozones), function(n){
-    ecozone <- ecozones %>% slice(n)
-    ids <- st_intersects(ecozone, tiles) %>% unlist()
-    tiles %>% slice(ids) %>% 
-        select(tile) %>% 
-        mutate(ecozone = ecozone$region)
-}, mc.cores = 12))
-tiles <- tiles %>% na.omit()
-tiles_zone5 <- tiles %>% filter(ecozone == 5)
-st_write(tiles_zone5, file.path(dst_path, 'tiles_zone5.geojson'))
-
-## Sample global labels
-lc_labels <- rast('data/intermid/lc_labels.tif')
-n_labels <- freq(lc_labels)
-# set NA flag
-NAflag(lc_labels) <- 0
-
-# Get balanced samples
-set.seed(10)
-samples_global <- sampleStratified(raster(lc_labels), 
-                            size = min(30000, 
-                                       min(n_labels[, 'count'])),
-                            na.rm = T, sp = T) %>% 
-    st_as_sf() %>% mutate(landcover = sum) %>% select(landcover)
-
-
-## Sample regional labels
-### Get the labels for zone5
-tiles_zone5_vect <- vect(tiles_zone5)
-lc_labels_zone5 <- mask(crop(lc_labels, 
-                             tiles_zone5_vect), 
-                        tiles_zone5_vect)
-rm(lc_labels, tiles_zone5_vect); gc()
-
-# Tundra is basically a mis-classification around water bodies,
-# and urban class makes significant confusion with other classes,
-# so we just mask out these two classes for the guessing stage.
-n_labels <- freq(lc_labels_zone5)
-lc_labels_zone5[lc_labels_zone5 == 7] <- 0
-lc_labels_zone5[lc_labels_zone5 == 8] <- 0
-
-# ## Urban
[…]

### 2021-03-25 scripts/8_refine_guess_labels.R
Add scripts to refine labels and other changes

@@ -1,0 +1,210 @@
+# Title     : Script to refine guess labels
+# Objective : To apply a few steps to refine 
+#             the guess labels generated by random forest.
+# Created by: Lei Song
+# Created on: 03/23/21
+
+####################### 
+##  Step 1: Setting  ##
+#######################
+message('Step 1: Setting')
+
+library(glue)
+library(here)
+library(terra)
+library(ramify)
+library(sf)
+library(rgrass7)
+library(dplyr)
+library(stringr)
+library(tidyverse)
+library(parallel)
+
+###############################
+###  Step 2: Refine labels  ###
+###############################
+message('Step 2: Refine labels')
+
+# Define function to refine the labels
+## Step 0: Reduce the weight of predicted buildings.
+## Step 1: Add roads, waterbodies, and buildings. (No rivers)
+## Step 2: Split a whole tile into 512 * 512 (or 256 * 256).
+refine_label <- function(tile_id, src_dir, img_dir, 
+                         labels_dir, tiles, roads, 
+                         waterbodies, buildings, 
+                         size_sub_tile = 512){
+    message('------Modify classses')
+    # Read images
+    scores <- rast(file.path(src_dir, glue('scores_{tile_id}.tif')))
+    
+    # Reduce the weight of predicted buildings
+    scores$.pred_8 <- scores$.pred_8 * 0.2
+    pred <- argmax(values(scores))
+    classes <- scores[[1]]
+    values(classes) <- pred
+    rm(scores, pred); rm()
+    # So here:
+    # 1: cropland
+    # 2: forest
+    # 3: grassland
+    # 4: shrubland
+    # 5: water
+    # 6: Urban
+    # 7: bareland
+    
+    # Set up GRASS GIS
+    message('------Add OSM layers')
+    gisBase <- '/Applications/GRASS-7.8.app/Contents/Resources'
+    initGRASS(gisBase = gisBase,
+              home = tempdir(),
+              gisDbase = tempdir(),  
+              mapset = 'PERMANENT', 
+              location = 'segments', 
+              override = TRUE)
+    execGRASS("g.proj", flags = "c", 
+              proj4 = crs(rast(
+                  file.path(src_dir, glue('scores_{tile_id}.tif'))),
+                  proj4 = T))
+    execGRASS('r.in.gdal', flags = c("o", "overwrite"),
+              input = file.path(src_dir, glue('scores_{tile_id}.tif')),
+              band = 1,
+              output = "score")
[…]

### 2021-03-25 scripts/9_human_check_labels.R

@@ -1,0 +1,27 @@
+# Title     : Script for human checking
+# Objective : To automatically generate leaflet map
+#             for human checking the refined guess labels.
+# Created by: Lei Song
+# Created on: 03/24/21
+
+#######################
+##  Step 1: Setting  ##
+#######################
+message('Step1: Setting')
+
+library(glue)
+library(here)
+library(sf)
+library(dplyr)
+library(stringr)
+
+################################
+##  Step 2: Define functions  ##
+################################
+message('Step 2: Define functions')
+
+
+####################################
+##  Step 3: Pop tiles one by one  ##
+####################################
+message('Step 3: Pop tiles one by one')

### 2021-03-25 scripts/generate_validation.R

@@ -1,0 +1,49 @@
+# Title     : Script to generate validation dataset
+# Objective : To randomly select dataset roughly balanced between types
+#             for manually check.
+# Created by: Lei Song
+# Created on: 03/23/21
+
+#######################
+##  Step 1: Setting  ##
+#######################
+message('Step1: Setting')
+
+library(raster)
+library(dplyr)
+library(here)
+library(rgrass7)
+
+#################################
+###  Step 2: Generate points  ###
+#################################
+message('Step 2: Generate points')
+
+## Use GRASS GIS to sample
+gisBase <- '/Applications/GRASS-7.8.app/Contents/Resources'
+initGRASS(gisBase = gisBase,
+          home = tempdir(),
+          gisDbase = tempdir(),  
+          mapset = 'PERMANENT', 
+          location = 'lc_types', 
+          override = TRUE)
+execGRASS("g.proj", flags = "c", 
+          proj4="+proj=longlat +datum=WGS84 +no_defs")
+execGRASS('r.in.gdal', flags = c("o", "overwrite"),
+          input = here('data/north/lc_labels_north.tif'),
+          band = 1,
+          output = "lc_types")
+execGRASS("g.region", raster = "lc_types")
+## Install r.sample.category addon
+# execGRASS("g.extension", extension = "r.sample.category")
+# execGRASS("g.gisenv", set = "GRASS_ADDON_BASE='~/.grass7/addons'")
+# Sys.setenv("GRASS_ADDON_BASE" = '~/.grass7/addons') 
+execGRASS('r.sample.category', flags = c("overwrite"),
+          parameters = list(input = 'lc_types', 
+                            output = 'lc_samples',
+                            npoints = c(280, rep(100, 4), 20, rep(100, 3)),
+                            random_seed = 10))
+use_sf()
+samples <- readVECT('lc_samples') %>% 
+    dplyr::select(lc_types)
+st_write(samples, here('data/north/samples_validation.geojson'))

### 2021-04-21 docs/report_apr16.Rmd
Add script to generate data for DL

---
title: "Dissertation progress report"
author: Lei Song
output:
  xaringan::moon_reader:
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = FALSE)
```

## Big picture

**Land cover map**
- Output: method-based paper in remote sensing
  - Before summer: finish experiment
  - Summer: writing manuscript
- Following work

  - Landscape structure analysis
     - Output: analysis-based paper in ecology
       - Summer: do experiment
  - Habitat suitability and animal movement
  - *+ segmentation -> Cropland field splitting*
  - *Yield estimation*

**Species distribution modeling**
- Output: method-based paper in ecological method
  - Summer: re-framing manuscript

---

## Land cover map

North of Tanzania

Steps:
1. Ensemble labels based on multiple LC products
2. Use ensemble labels to train a RF LC model
3. Randomly select tiles to run RF LC model to generate guessing labels
4. <ins>Use guessing labels to train DL model</ins>

---

## Land cover map

Ensemble labels

```{r, echo=F, warning=F, message=F}
library(tmap)
library(raster)
library(here)
esm <- stack(here('data/north/lc_labels_north.tif'),
             here('data/north/lc_labels_north_mask.tif'))
esm$lc_labels_north[esm$lc_labels_north == 0] <- NA
tmap_mode("view")
tm_basemap("Esri.WorldImagery") +
  tm_shape(esm, name = c("Ensemble labels", "Masked ensemble labels")) +
  tm_raster(style = "cat", 
            labels = c("Cropland", "Forest", "Grassland", 
                       "Shrubland", "Wetland", "Water", 
                       "Urban", "Bareland"),
            palette = c("darkorange", 'darkolivegreen', 
                        'darkseagreen1', 'goldenrod3', 
                        'darkorchid1', 'deepskyblue', 
                        'brown', 'darkgrey'),
            title = c("LC")) +
  tm_facets(sync = TRUE, ncol = 2) +
  tm_layout(title = c("Ensemble labels", "Masked ensemble labels"))
```

---

## Images

```{r, echo=F, warning=F, message=F}
library(ranger)
library(parsnip)
library(tidymodels)
library(vip)
library(dials)
load(here('data/north/forest_vip.rda'))
vip(forest_vip, num_features = forest_vip$fit$num.independent.variables,
    aesthetics = list(color = "transparent", 
                      fill = "red")) +
    theme_light()
```

---

## RF result example

```{r, echo=F, warning=F, message=F}
id <- '1227-1005_53'
fnames <- list.files(here('results/north/guess_labels'), pattern = id,
                     full.names = T)
label <- raster(fnames)
tmap_mode("view")
tm_basemap("Esri.WorldImagery") +
  tm_shape(label, name = c("label")) +
  tm_raster(style = "cat", 
            labels = c("Cropland", "Forest", "Grassland", 
                       "Shrubland", "Water", 
                       "Urban", "Bareland"),
            palette = c("darkorange", 'darkolivegreen', 
                        'darkseagreen1', 'goldenrod3', 
                        'deepskyblue', 
                        'brown', 'darkgrey'),
            title = c("LC"))
```

### 2021-04-21 scripts/6_train_guess_model.R

@@ -57,7 +57,8 @@ forest_vip <- rand_forest() %>%
 save(forest_vip, file = here('data/north/forest_vip.rda'))
 
 ## Plot
-vip(forest_vip, num_features = ncol(training) - 1,
+vip(forest_vip, 
+    num_features = forest_vip$fit$num.independent.variables,
     aesthetics = list(color = "transparent", 
                       fill = "red")) +
     theme_light()

### 2021-05-04 docs/notebook_learn_dl_ensemble.Rmd
Clean up documents

--- 2021-03-06 docs/learn_dl_ensemble.Rmd
@@
 ---
-title: "Learn from ensemble labels"
+title: "Notebook of learning from ensemble labels"
 author: "Lei Song"
@@
 
-- AMI ID: `ami-0643df3b347740189`, which is our customized deep learning AWS instance.
-- Instance type: `g3.8xlarge`.
+- AMI ID: `ami-0643df3b347740189`, which is our customized deep learning AWS instance. Or this one `ami-005050e76c11b3b16`, which includes datasets already.
+- Instance type: a few instance could use based on different needs.
+
+  - `g3.8xlarge`, 2 GPU, 16G GPU memory, $0.684/hr for SPOT instance.
+  - `g3.16xlarge`, 4 GPU, 32G GPU memory, $1.368/hr for SPOT instance.
+  - `g4dn.8xlarge`, 1 GPU, 16G GPU memory, $0.6528/hr for SPOT instance.
+  - `g4dn.12xlarge`, 4 GPU, 64G GPU memory, $1.1819/hr for SPOT instance.
+
 - Security group: `labeller-security`.
 
-Before start, install `jq`.
-Then use the scripts in `pytorch_planet/aws_tools/create_spot_instance.sh` using the template:
+Before run this script, do the following steps. Just need step one for Linux machine. Didn't test Windows machine.
+
+1. `brew install awscli`, then `aws configure` to configure AWS credential.
+2. `brew install jq`
+3. `brew install coreutils`. to use gdata on macOS.
+
+Then:
 ```
-cd /path/to/pytorch_planet/folder
-chmod 777 ./aws_tools/create_spot_instance.sh
-./aws_tools/create_spot_instance.sh <ami_id> <instance_type> <security_group_id> <new_instance_name> <spot_type> <valid_until> <key_name>
+cd tools
+chmod 777 create_spot_instance.sh
+create_spot_instance.sh <ami_id> <instance_type> <security_group_id> <new_instance_name> <spot_type> <valid_until> <key_name> <volume_size>
 ```
@@
 ```
-cd /path/to/pytorch_planet/folder
-chmod 777 ./aws_tools/create_spot_instance.sh
-./aws_tools/create_spot_instance.sh ami-0643df3b347740189 g3.16xlarge sg-0a8bbc91697d6a76b lc_dl_tz persistent 2021-01-22T23:00:00 lsong-keypair
+cd tools
+chmod 777 create_spot_instance.sh
+create_spot_instance.sh ami-0643df3b347740189 g3.16xlarge sg-0a8bbc91697d6a76b lc_dl_tz persistent 2021-01-22T23:00:00 lsong-keypair 200
 ```
@@
 
-## Experiemnts
-###candidate models
+## Methodology
+### Candidate models
 
@@
 
-### Label smoothing
+### Strategies to deal with noisy labels
+#### Label smoothing
 The general loss is higher than classic cross entropy loss.
@@
 0.5 is a safe choice.
+
+#### Co-teaching and co-teaching-plus
+
+#### JoCoR
+
+## Experiments
+
+### Single model
+Before any tests related to strategies to deal with noisy labels, we will build up a baseline model only using "pure" labels generated by human checking.
+
+#### Hyper-parameters
+
+- Learning rate and learning rate scheduler
+- Batch size
+- Transform methods (if necessary)
+
+### Double model

### 2021-05-07 docs/notebook_learn_dl_ensemble.Rmd
Update dataset class

@@
 
+#### Tensorboard
+
+If download log file to local machine, then it is easy to check the training loss curves.
+
+`tensorboard --logdir='./tensorboard_dirs' --port=16007`
+
+Do the following steps to use the tensorboard on a remote server (reference: https://blog.yyliu.net/remote-tensorboard/):
+
+1. You need to start SSH with transfer the remote server’s port to your local PC:
+
+    (on your local PC) `ssh -L 16007:127.0.0.1:16007 username@server_ip`
+
+2. Then you may start the tensorboard on the remote server with the specific port we want to transfer:
+
+    (on the remote server) `tensorboard --logdir='./tensorboard_dirs' --port=16007`
+
 ### Google Colab
@@
 - Batch size
+- Optimizer
+- Model (Unet or Deeplab)
 - Transform methods (if necessary)
 
+#### Tuning plans
+
+- Unet
+
+  - Batch size = 32 (Maximum value fit into `g4dn.12xlarge`)
+  - Initial learning rate = [0.1, 0.01, 0.001]
+
+    - 0.1 is too large
+    - 0.01 and 0.001 works similarly.
+
+  - Optimizer: we plan to try some more recent optimizer such as AdaBound, AdamP, AdamW, etc.
+Because SGD could make model have higher generalization while Adam can train the model faster.
+So if we could use an optimizer that has both advantages, it would be ideal.
+Since our research is not about the improvement of DL algorithm, so we just pick up the most right one at the moment.
+
+  - Scheduler: 0 - 50 use 0.01, 50 - 150 use a decayed cyclic scheduler (0.01 - 0.001), last 50: 0.001 with a tiny cycle range.
+
 ### Double model

### 2021-05-07 hrlcm/fit.py

@@ -223,14 +223,11 @@ def main():
                                      amsgrad=True)
 
     # Define scheduler
-    scheduler = torch.optim.lr_scheduler.CyclicLR(
-        optimizer, mode='exp_range',
-        step_size_up=4 * len(train_loader),
-        base_lr=args.base_lr,
-        max_lr=args.max_lr,
-        gamma=args.clr_gamma,
-        cycle_momentum=False
-    )
+    lr_scheduler_1 = torch.optim.lr_scheduler.CosineAnnealingLR(optimizer, T_max=20, eta_min=0.001)
+    lr_scheduler_2 = torch.optim.lr_scheduler.CyclicLR(optimizer, base_lr=0.001, max_lr=0.05,
+                                                       step_size_up=1, step_size_down=3,
+                                                       gamma=0.96, cycle_momentum=False,
+                                                       mode='exp_range')
 
     # Set up tensorboard logging
     writer = SummaryWriter(log_dir=args.logs_dir)
@@ -251,13 +248,18 @@ def main():
             trainer.validate(model, validate_loader, step, loss_fn, writer)
 
             # Update learning rate
-            scheduler.step()
+            if epoch <= lr_scheduler_1.T_max:
+                lr_scheduler_1.step()
+            else:
+                lr_scheduler_2.step()
 
             # Save checkpoint
             if epoch % args.save_freq == 0:
                 trainer.export_model(model, optimizer=optimizer, step=step)
 
             # Update pbar
+            pbar.set_description("[Epoch] lr: {:.4f}".format(
+                round(optimizer.param_groups[0]["lr"], 4)))
             pbar.update()
 
         # Export final set of weights

### 2021-05-07 tools/create_spot_instance.sh

@@ -116,5 +116,5 @@ NEWIID=$(aws ec2 describe-instances \
 
 echo $NEWIID
 
-# ./tools/create_spot_instance.sh ami-0643df3b347740189 g4dn.8xlarge \
-# sg-0a8bbc91697d6a76b tzlcm persistent 2021-05-04T23:00:00 lsong-keypair 180
+# ./tools/create_spot_instance.sh ami-0833ca42c91eb4a58 g4dn.12xlarge \
+# sg-0a8bbc91697d6a76b tzlcms persistent 2021-05-15T23:00:00 lsong-keypair 200

### 2021-05-09 docs/notebook_learn_dl_ensemble.Rmd
Update evaluate

@@
 ### Strategies to deal with noisy labels
+
+#### Add noisy labels to fine tune
+
+After the initial 200 epochs with perfect labels, adding more noisy labels to "adapt" the model.
+
 #### Label smoothing
+
 The general loss is higher than classic cross entropy loss.
@@
 
-#### Tuning plans
+#### Baseline
 
@@
     - 0.1 is too large
-    - 0.01 and 0.001 works similarly.
+    - 0.01 and 0.001 works similarly, but 0.001 works slightly better for multiple optimizer.
 
-  - Optimizer: we plan to try some more recent optimizer such as AdaBound, AdamP, AdamW, etc.
+  - Optimizer: we plan to try some more recent optimizer such as AdaBound, AdamP, etc.
 Because SGD could make model have higher generalization while Adam can train the model faster.
 So if we could use an optimizer that has both advantages, it would be ideal.
+AdaBound is such kind of optimizer.
 Since our research is not about the improvement of DL algorithm, so we just pick up the most right one at the moment.
 
-  - Scheduler: 0 - 50 use 0.01, 50 - 150 use a decayed cyclic scheduler (0.01 - 0.001), last 50: 0.001 with a tiny cycle range.
+    - AdaBound does obviously better than Adam or AdamW at least in the first 20 epochs.
+    - AdamP performs similar to AdaBound, that are much better than other traditional ones. But validate loss is a lit higher than AdaBound.
+
+  - Scheduler: we decided to use a compose scheduler to have dynamic learning rate.
+Even though Adam-based optimizer uses dynamic learning rate already, but experiments prove that using both dynamic learning rate and Adam together could have better performance.
+So we chose to use 0.001 for the first 30 epochs, to use a decayed cyclic scheduler (0.0008 - 0.0012) for epoch 30 - 120, and use another decayed cyclic scheduler (0.0004 - 0.0006) for last 80 epochs.
 

### 2021-05-13 docs/notebook_learn_dl_ensemble.Rmd

@@
 
-### Single model
+### Start up (Baseline)
+
 Before any tests related to strategies to deal with noisy labels, we will build up a baseline model only using "pure" labels generated by human checking.
@@
 
-#### Baseline
-
-- Unet
+##### Unet
 
@@
 - Scheduler: we decided to use a compose scheduler to have dynamic learning rate.
-Even though Adam-based optimizer uses dynamic learning rate already, but experiments prove that using both dynamic learning rate and Adam together could have better performance.
+Even though Adam-based optimizer uses dynamic learning rate already, but experiments prove that using both dynamic learning rate and Adam-based optimizer together could have better performance.
 So we chose to use 0.001 for the first 30 epochs, to use a decayed cyclic scheduler (0.0008 - 0.0012) for epoch 30 - 120, and use another decayed cyclic scheduler (0.0004 - 0.0006) for last 80 epochs.
 
-### Double model
+###### DeepLab
+
+  [TO BE CONTINUE]
+
+### Resume
+
+#### Single model
+
+#### Double model

### 2021-05-20 hrlcm/dataset.py
Update code to run in command line

@@ -116,8 +116,9 @@ class NFSEN1LC(Dataset):
 
     def __init__(self, data_dir,
                  usage='train',
+                 highest_score=10,
                  lowest_score=9,
-                 noise_ratio=0.2,
+                 noise_ratio=0.3,
                  label_offset=1,
                  sync_transform=None,
                  img_transform=None,
@@ -158,6 +159,7 @@ class NFSEN1LC(Dataset):
         # Check inputs
         assert usage in ['train', 'validate', 'predict']
         assert lowest_score in [8, 9, 10]
+        assert highest_score in [8, 9, 10]
         assert os.path.exists(data_dir)
 
         # Read catalog
@@ -174,13 +176,14 @@ class NFSEN1LC(Dataset):
         # Shrink the catalog based on noise ratio
         if self.usage == 'train':
             # Initialize values
+            self.highest_score = highest_score
             self.lowest_score = lowest_score
             self.noise_ratio = noise_ratio
 
             # Subset catalog based on score
-            catalog = catalog_full.loc[catalog_full['score'] >= self.lowest_score]
+            catalog = catalog_full.loc[self.lowest_score <= catalog_full['score'] <= self.highest_score]
 
-            if self.lowest_score < 10:
+            if self.lowest_score < 10 & self.highest_score == 10:
                 # Subset catalog based on noise_ratio
                 catalog_perfect = catalog.loc[catalog['score'] == 10]
                 catalog_rest = catalog.loc[catalog['score'] < 10]

### 2021-05-20 hrlcm/fit.py

@@ -34,6 +34,8 @@ def main():
                         help='path to dataset')
     parser.add_argument('--out_dir', type=str, default="models",
                         help='path to output dir (default: ./models)')
+    parser.add_argument('--highest_score', type=int, default=10,
+                        help='highest score to subset train dataset (default: 10)')
     parser.add_argument('--lowest_score', type=int, default=10,
                         help='lowest score to subset train dataset (default: 10)')
     parser.add_argument('--noise_ratio', type=float, default=None,
@@ -57,12 +59,12 @@ def main():
                         help='the gpu devices to use (default: None) (format: 1, 2)')
 
     # Training hyper-parameters
-    parser.add_argument('--base_lr', type=float, default=0.001,
-                        help='initial learning rate or a constant learning rate.')
-    parser.add_argument('--max_lr', type=float, default=0.01,
-                        help='maximum learning rate.')
-    parser.add_argument('--final_lr', type=float, default=0.01,
-                        help='final learning rate for AdaBound or AmsBound')
+    parser.add_argument('--base_lr', type=float, default=0.0001,
+                        help='base learning rate for scheduler.')
+    parser.add_argument('--max_lr', type=float, default=0.001,
+                        help='maximum learning rate for scheduler.')
+    parser.add_argument('--gamma_lr', type=float, default=0.97,
+                        help='gamma for learning rate.')
     parser.add_argument('--optimizer_name', type=str,
                         choices=['AdaBound', 'AmsBound', 'AdamP'],
                         default="AmsBound",
@@ -77,8 +79,8 @@ def main():
                         help='batch size for training (default: 16)')
     parser.add_argument('--val_batch_size', type=int, default=32,
                         help='batch size for validation (default: 16)')
-    parser.add_argument('--epochs', type=int, default=100,
-                        help='number of training epochs (default: 100)')
+    parser.add_argument('--epochs', type=int, default=300,
+                        help='number of training epochs (default: 300)')
     parser.add_argument('--resume', '-r', type=str, default=None,
                         help='path to the pretrained weights file', )
 
@@ -140,6 +142,7 @@ def main():
     # Get train dataset
     train_dataset = NFSEN1LC(data_dir=args.data_dir,
                              usage='train',
+                             highest_score=args.highest_score,
[…]

### 2021-05-20 hrlcm/train.py

@@ -155,7 +155,7 @@ class Trainer:
         model2.train()
 
         # Training loop
-        pbar = tqdm(total=len(train_loader), desc="[Train]")
+        pbar = tqdm(total=len(train_loader), desc="[Train]", ncols='100%')
         loss1_total = 0
         loss2_total = 0
         for i, (image, target, indexes) in enumerate(train_loader):

### 2021-05-20 tools/create_spot_instance.sh

@@ -149,5 +149,5 @@ NEWIID=$(aws ec2 describe-instances \
 
 echo $NEWIID
 
-# ./tools/create_spot_instance.sh ami-0833ca42c91eb4a58 g4dn.12xlarge \
-# sg-0a8bbc91697d6a76b tzlcms persistent 2021-05-15T23:00:00 lsong-keypair 200
+# ./tools/create_spot_instance.sh ami-0b7965e0f45fe2f1d g4dn.12xlarge \
+# sg-0a8bbc91697d6a76b tzlcm one-time 2021-05-15T23:00:00 lsong-keypair 200

### 2021-05-21 docs/notebook_learn_dl_ensemble.Rmd
Update code to run in command line

@@
 
-#### Parameters setting
+#### Instance setting
 After successfully launched the instance, then it is ready to get into the instance to work.
@@
   replace the private IP with the public IP to open it in browser. If you can log in without issues, then it is ready to go.
+
+#### Run experiments
+
+```
+python hrlcm/fit.py --exp_name unet_single --data_dir 'results/north' --out_dir 'results/dl' --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200
+```
 
@@
 
-###### DeepLab
+##### DeepLab
 

### 2021-05-23 hrlcm/fit.py
Use resume

@@ -236,8 +236,25 @@ def main():
 
     # Start train
     step = 0
+    epoch = 0
+    # Resume model based on settings
+    if args.resume:
+        if os.path.isfile(args.resume):
+            print("Load checkpoint '{}'".format(args.resume))
+            checkpoint = torch.load(args.resume)
+
+            if checkpoint['step'] > step:
+                step = checkpoint['step']
+                epoch = floor(step / floor(len(train_dataset) / args.train_batch_size)) + 1
+            model.load_state_dict(checkpoint['model_state_dict'])
+            optimizer.load_state_dict(checkpoint['optimizer_state_dict'])
+            print("Loaded checkpoint '{}' (epoch {})".format(args.resume, epoch))
+        else:
+            print("No checkpoint found at '{}'".format(args.resume))
+
+    # Do loop
     trainer = Trainer(args)
-    for epoch in range(args.epochs):
+    for epoch in range(epoch, args.epochs):
         # Update info
         print("[Epoch {}] lr: {}".format(
             epoch, optimizer.param_groups[0]["lr"]))

### 2021-05-23 hrlcm/fit.py
Modify resume a bit

@@ -240,21 +240,21 @@ def main():
     # Resume model based on settings
     if args.resume:
         if os.path.isfile(args.resume):
-            print("Load checkpoint '{}'".format(args.resume))
             checkpoint = torch.load(args.resume)
 
+            # Get step and epoch
             if checkpoint['step'] > step:
                 step = checkpoint['step']
-                epoch = floor(step / floor(len(train_dataset) / args.train_batch_size)) + 1
+                epoch = floor(step / floor(len(train_dataset) / args.train_batch_size))
             model.load_state_dict(checkpoint['model_state_dict'])
             optimizer.load_state_dict(checkpoint['optimizer_state_dict'])
-            print("Loaded checkpoint '{}' (epoch {})".format(args.resume, epoch))
+            print("Load checkpoint '{}' (epoch {})".format(args.resume, epoch))
         else:
             print("No checkpoint found at '{}'".format(args.resume))
 
     # Do loop
     trainer = Trainer(args)
-    for epoch in range(epoch, args.epochs):
+    for epoch in range(epoch + 1, args.epochs):
         # Update info
         print("[Epoch {}] lr: {}".format(
             epoch, optimizer.param_groups[0]["lr"]))

### 2021-05-24 tools/parse_logs.sh
Modify the tools

@@ -5,19 +5,25 @@
 # Get input parameters
 DNS=$1
 if [ -z "$DNS" ]; then
-    echo "`date`: Usage: $0 <Public_IPv4_DNS> <experiment_name> <download_dir>"
+    echo "`date`: Usage: $0 <Public_IPv4_DNS> <experiment_name> <download_dir> <sleep_sec>"
     exit 1
 fi
 ENAME=$2
 if [ -z "$ENAME" ]; then
-    echo "`date`: Usage: $0 <Public_IPv4_DNS> <experiment_name> <download_dir>"
+    echo "`date`: Usage: $0 <Public_IPv4_DNS> <experiment_name> <download_dir> <sleep_sec>"
     exit 1
 fi
 DIR=$3
 if [ -z "$DIR" ]; then
-    echo "`date`: Usage: $0 <Public_IPv4_DNS> <experiment_name> <download_dir>"
+    echo "`date`: Usage: $0 <Public_IPv4_DNS> <experiment_name> <download_dir> <sleep_sec>"
+    exit 1
+fi
+STIME=$4
+if [ -z "$STIME" ]; then
+    echo "`date`: Usage: $0 <Public_IPv4_DNS> <experiment_name> <download_dir> <sleep_sec>"
     exit 1
 fi
 
+
 # Download files in loop
-while true; do scp -r ubuntu@$DNS:~/hrlcm/results/dl/$ENAME $DIR; sleep 2000; done
+while true; do scp -r ubuntu@$DNS:~/hrlcm/results/dl/$ENAME $DIR; sleep $STIME; done

### 2021-06-01 docs/notebook_learn_dl_ensemble.Rmd
Use resume
Modify resume a bit
Modify the tools

@@
 ```
-python hrlcm/fit.py --exp_name unet_single --data_dir 'results/north' --out_dir 'results/dl' --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200
+python hrlcm/fit.py --exp_name unet_compose_lr --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200
+```
+
+```
+python hrlcm/fit.py --exp_name unet_compose_lr --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200 --resume 'results/dl/resume/interim.pth' --save_freq 5
 ```
@@
   - 0.01 and 0.001 works similarly, but 0.001 works slightly better for multiple optimizer.
+  - Learning rate smaller than 0.0001 might be too small for this case.
 

### 2021-06-01 docs/notebook_learn_dl_ensemble.Rmd
Modify the default params for coteaching

@@
 ```
-python hrlcm/fit.py --exp_name unet_compose_lr --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200 --resume 'results/dl/resume/interim.pth' --save_freq 5
+python hrlcm/fit.py --exp_name unet_compose_lr --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200 --save_freq 5 --resume 'results/dl/resume/interim.pth'
 ```

### 2021-06-01 hrlcm/fit_compose_lr.py

@@ -8,7 +8,6 @@ Maintainer: Lei Song (lsong@clarku.edu)
 import argparse
 from augmentation import *
 from dataset import *
-from tqdm import tqdm  # use tqdm.auto for notebook
 from torch.utils.data import DataLoader
 from torch.utils.tensorboard import SummaryWriter
 import pickle as pkl

### 2021-06-01 hrlcm/fit_coteaching.py

@@ -35,9 +35,9 @@ def main():
                         help='path to output dir (default: results/dl)')
     parser.add_argument('--highest_score', type=int, default=10,
                         help='highest score to subset train dataset (default: 10)')
-    parser.add_argument('--lowest_score', type=int, default=10,
+    parser.add_argument('--lowest_score', type=int, default=9,
                         help='lowest score to subset train dataset (default: 10)')
-    parser.add_argument('--noise_ratio', type=float, default=None,
+    parser.add_argument('--noise_ratio', type=float, default=0.3,
                         help='ratio of noise to subset train dataset (default: None)')
     parser.add_argument('--label_offset', type=int, default=1,
                         help='offset value to minus from label in order to start from 0 (default: 1)')
@@ -62,8 +62,6 @@ def main():
                         help='minimum or last learning rate for scheduler.')
     parser.add_argument('--max_lr', type=float, default=0.001,
                         help='maximum or initial learning rate for scheduler.')
-    parser.add_argument('--step_size', type=int, default=5,
-                        help='step size for scheduler.')
     parser.add_argument('--gamma_lr', type=float, default=0.9,
                         help='gamma for learning rate.')
     parser.add_argument('--optimizer_name', type=str,

### 2021-06-09 docs/notebook_learn_dl_ensemble.Rmd
A few updates for test

--- 2021-05-21 docs/notebook_learn_dl_ensemble.Rmd
@@
 ```
-python hrlcm/fit.py --exp_name unet_single --data_dir 'results/north' --out_dir 'results/dl' --num_workers 32 --gpu_devices '0,1,2,3' --epochs 200
+python hrlcm/fit_coteaching_compare.py --exp_name unet_cot_argue --num_workers 32 --gpu_devices '0,1,2,3' --epochs 30
+```
+
+```
+python hrlcm/fit_coteaching.py --exp_name unet_cot_da --num_workers 32 --gpu_devices '0,1,2,3' --save_freq 5 --resume1 'results/dl/unet_cot_da/model1_final.pth' --resume2 'results/dl/unet_cot_da/model2_final.pth'
 ```
@@
 
+Based on the original papers and their GitHub repos, we combined these two logic into one function and adapted it for image segmentation.
+
+- The first version is image based, which means it takes each image as a whole thing.
+If the label of one image is "perfect", then use the whole image, otherwise only use pixels with small loss to update the models.
+  - Under "argue" mode, use disagreement to update the models.
+  - Under "discuss" mode, do not use disagreement.
+
+- The second version is batch based, which means it only use pixels with small loss from the whole batch to update the models. Mode works similarly as the first version.
+
 #### JoCoR
+Since the original paper is about image classification rather than image segmentation, it is harder to adapt this method into image segmentation with good performance.
+
+[NEED MORE EXPERIMENTS]
 
@@
 
-- Learning rate and learning rate scheduler
+- <input type="checkbox" checked> Learning rate and learning rate scheduler</input>
 - Batch size
 - Optimizer
-- Model (Unet or Deeplab)
+- Model (U-net or Deeplab)
 - Transform methods (if necessary)
@@
 
-### Resume
+### Co-teaching
 
-#### Single model
+We first use constant parameters, 0.001 learning rate, AmsBound optimizer, and 30 epochs, to run the models.
 
-#### Double model
+- Co_teaching_batch doesn't fit multi-classes classification task. It might be good for binary classification. Because based on the curves, co_teaching_batch give up the minorities.
+
+- Co_teaching works good. "Discuss" mode works slightly better than "argue" mode.

### 2021-06-09 hrlcm/fit_coteaching.py

@@ -15,7 +15,7 @@ from models.deeplab import DeepLab
 from models.unet import UNet
 from train import Trainer
 import torch_optimizer as optim
-from loss import BalancedCrossEntropyLoss, loss_colearning, loss_colearning_batch, loss_jocor
+from loss import BalancedCrossEntropyLoss, loss_colearning
 
 
 def main():
@@ -77,9 +77,9 @@ def main():
                         help='batch size for training (default: 16)')
     parser.add_argument('--val_batch_size', type=int, default=16,
                         help='batch size for validation (default: 16)')
-    parser.add_argument('--epochs', type=int, default=50,
-                        help='number of training epochs (default: 50). '
-                             'NOTE: The scheduler is designed best for 50.')
+    parser.add_argument('--epochs', type=int, default=30,
+                        help='number of training epochs (default: 30). '
+                             'NOTE: The scheduler is designed best for 30.')
     parser.add_argument('--start_epoch', type=int, default=0,
                         help='the start epoch for resume (default: 0).')
     parser.add_argument('--resume1', '-r1', type=str, default=None,

### 2021-06-09 hrlcm/fit_coteaching_compare.py

@@ -15,7 +15,7 @@ from models.deeplab import DeepLab
 from models.unet import UNet
 from train import Trainer
 import torch_optimizer as optim
-from loss import BalancedCrossEntropyLoss, loss_colearning, loss_colearning_batch, loss_jocor
+from loss import BalancedCrossEntropyLoss, loss_colearning, loss_colearning_batch
 
 
 def main():
@@ -215,7 +215,7 @@ def main():
         model2 = model2.cuda()
 
     # Define loss function
-    loss_fn = loss_colearning_batch
+    loss_fn = loss_colearning
     loss_fn_val = BalancedCrossEntropyLoss()
 
     # Define optimizer

### 2021-06-11 hrlcm/fit_cyclic_lr.py
Update some details

@@ -1,274 +1,0 @@
-"""
-This is a script of fitting DL model.
-Reference: https://github.com/lukasliebel/dfc2020_baseline/blob/master/code/train.py
-Author: Lei Song
-Maintainer: Lei Song (lsong@clarku.edu)
-"""
-
-import argparse
-from augmentation import *
-from dataset import *
-from torch.utils.data import DataLoader
-from torch.utils.tensorboard import SummaryWriter
-import pickle as pkl
-from models.deeplab import DeepLab
-from models.unet import UNet
-from train import Trainer
-import torch_optimizer as optim
-from loss import BalancedCrossEntropyLoss
-
-
-def main():
-    # Get in-line arguments
-    # define and parse arguments
-    parser = argparse.ArgumentParser()
-
-    # config
-    parser.add_argument('--exp_name', type=str, default="experiment",
-                        help='experiment name that will be used in path names '
-                             'for logs and checkpoints (default: experiment)')
-
-    # dataset
-    parser.add_argument('--data_dir', type=str, default='results/north',
-                        help='path to dataset (default: results/north)')
-    parser.add_argument('--out_dir', type=str, default="results/dl",
-                        help='path to output dir (default: results/dl)')
-    parser.add_argument('--highest_score', type=int, default=10,
-                        help='highest score to subset train dataset (default: 10)')
-    parser.add_argument('--lowest_score', type=int, default=10,
-                        help='lowest score to subset train dataset (default: 10)')
-    parser.add_argument('--noise_ratio', type=float, default=None,
-                        help='ratio of noise to subset train dataset (default: None)')
-    parser.add_argument('--label_offset', type=int, default=1,
-                        help='offset value to minus from label in order to start from 0 (default: 1)')
-    parser.add_argument('--rg_rotate', type=str, default='-90, 90',
-                        help='ratio of noise to subset train dataset (default: -90, 90)')
-    parser.add_argument('--trans_prob', type=float, default=0.5,
-                        help='probability to do data transformation (default:0.5)')
-    parser.add_argument('--num_workers', type=int, default=0,
-                        help='number of worker(s) to load dataset (default: 0)')
-
-    # Network
-    parser.add_argument('--model', type=str, choices=['unet', 'deeplab'],
-                        default="unet",
-                        help='network architecture (default: unet)')
-    parser.add_argument('--out_stride', type=int, default=8,
[…]

### 2021-06-11 hrlcm/fit_step_lr.py

@@ -182,7 +182,7 @@ def main():
     # Train network
     # Define model
     if args.model == "deeplab":
-        # TODO Not test yet
+        # TODO Not test fully yet
         model = DeepLab(num_classes=args.n_classes,
                         backbone='resnet',
                         pretrained_backbone=False,

### 2021-07-03 docs/manuscript_figures.Rmd
Add some updates

---
title: "Manuscript figures"
author: "Lei Song"
date: "6/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Introduction

This is just a markdown to record the script to generate figures for the paper.

## Study area

Study area figure should include a overall view of study area in a bigger background, a zoom-in view of the study area (northern of Tanzania), the ecozones, the NICFI tiling system and the following sub-tiling system,

```{r}
library(here)
library(sf)
library(nngeo)
library(ggplot2)
library(ggspatial)
library(RColorBrewer)
library(dplyr)
library(rnaturalearth)

# Read boundaries
tz_bry <- read_sf(here('data/geoms/tanzania.geojson'))
study_area <- read_sf(here('data/geoms/study_area.geojson')) %>% 
    st_remove_holes()
nicfi_tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson')) %>% 
    mutate(`NICFI tile` = 1)
ecozones <- read_sf(here('data/geoms/ecozones.geojson')) %>% 
    st_intersection(study_area) %>% 
    rename(Ecozone = zone)

# The overview of study area in the whole country at the left corner
# Get the surrounding countries
countries <- ne_countries(type = 'countries', scale = 'large',
                          returnclass = 'sf') %>% 
    st_intersection(., st_bbox(tz_bry) %>% 
                        st_as_sfc() %>% 
                        st_buffer(5, joinStyle = 'MITRE') %>% 
                        st_bbox(tz_bry) %>% # Get he squared one
                        st_as_sfc())

# Make overview
xlim <- c(st_bbox(countries)[1] + 3, st_bbox(countries)[3] - 3)
ylim <- c(st_bbox(countries)[2] + 3, st_bbox(countries)[4] - 3)
overview <- ggplotGrob(ggplot(tz_bry) +
    geom_sf(fill = 'lightblue', color = 'grey') +
    geom_sf_text(aes(label = geounit), size = 4) +
    geom_sf(data = countries, fill = NA, color = 'grey') +
    geom_sf(data = study_area, fill = 'red', color = 'grey') +
    coord_sf(xlim = xlim, ylim = ylim) +
    theme_bw() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          plot.margin = unit(rep(0, 4), "cm")))

# Make the main figure
main_fg <- ggplot(ecozones) +
    geom_sf(aes(fill = Ecozone), 
            color = 'grey') +
    scale_fill_brewer(palette = 'Accent') +
    geom_sf(data = nicfi_tiles, fill = NA, 
            aes(color = "black", lty = "dotted"), 
            lwd = 0.4) +
    geom_sf(data = study_area, fill = NA, 
            aes(color = 'red', lty = 'solid')) +
    scale_color_identity(name = '',
                         breaks = c('black', 'red'),
                         labels = c('NICFI tiles', 'Study area'),
                         guide = 'legend') +
    scale_linetype_identity(name = '',
                            breaks = c('dotted', 'solid'),
                            labels = c('NICFI tiles', 'Study area'),
                            guide = 'legend') +
    annotation_custom(grob = overview, 
                      xmin = 36.5, xmax = 38.5,
                      ymin = -2.3, ymax = -0.5) +
    annotation_scale(location = 'br', text_cex = 1) +
    annotation_north_arrow(which_north = "true", location = 'tl') +
    theme_minimal() + 
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          legend.text = element_text(size = 12),
          plot.margin = unit(rep(0, 4),"cm"))

ggsave(here('docs/figures/study_area.png'),
       main_fg,
       width = 10, height = 5.7, dpi = 600)
main_fg
```

## Satellite images

This figure will provide an example of satellite images including NICFI images with two seasons, and the harmonic regression of Sentinel-1 images.

```{r}
library(sf)
library(raster)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(tidyr)
library(RStoolbox)

# Read example images
# tile 1227-1002, 
# this tile has a few different land cover types and obvious characteristics
# so it could be a good example tile.
tile_id <- '1227-1002'
fnames_nicfi <- list.files(here('data/plts_nicfi'),
                           pattern = tile_id,
                           full.names = T)
nicfi_s1 <- stack(fnames_nicfi[1]) %>% subset(1:4)
nicfi_s2 <- stack(fnames_nicfi[2]) %>% subset(1:4)
rm(fnames_nicfi)

# Define example points
pts_example <- read_sf(here('data/north/pts_example.shp')) %>% 
    st_cast('POINT')

# NICFI
# Transform points
pts_nicfi <- pts_example %>% 
    st_transform(crs = crs(nicfi_s1))

# Define colors
cols_lc <- tibble(cols = c('#ff7f00', '#074702', '#b2df8a',
                           '#33a02c', '#3347f9', '#5a6057',
                           '#fdbf6f'),
                  `Land cover type` = c("Cropland", 'Forest', "Grassland", 
                                        'Shrubland',  "Water", "Built-up",
                                        'Bareland'),
                  ids = as.factor(1:7))

# Image of season 1
s1_fg <- ggRGB(nicfi_s1, r = 4, g = 3, b = 2, 
               scale = max(values(nicfi_s1)[, 2:4]), 
               stretch = 'hist') +
    geom_sf(data = pts_nicfi,
            color = 'black',
            size = 3) +
    geom_sf(data = pts_nicfi,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    theme_minimal() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))

# Image of season 2
s2_fg <- ggRGB(nicfi_s2, r = 4, g = 3, b = 2, 
               scale = max(values(nicfi_s2)[, 2:4]), 
               stretch = 'lin') +
    geom_sf(data = pts_nicfi,
            color = 'black',
            size = 3) +
    geom_sf(data = pts_nicfi,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    theme_minimal() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))

# Spectral signature of examples
# Extract values
pts_nicfi_s1 <- raster::extract(nicfi_s1, pts_nicfi) %>% 
    t() %>% data.frame() %>% 
    `names<-`(pts_nicfi$type) %>% 
    `rownames<-`(1:nrow(.)) %>% 
    mutate(`Band name` = c('Blue', 'Green', 'Red', 'NIR'),
           Band = 1:4) %>% 
    pivot_longer(cols = names(.)[1:(ncol(.) - 2)], 
                 names_to = 'Land cover type',
                 values_to = 'Reflectance') %>% 
    mutate(`Land cover type` = as.factor(`Land cover type`),
           Season = 'Season 1')
pts_nicfi_s2 <- raster::extract(nicfi_s2, pts_nicfi) %>% 
    t() %>% data.frame() %>% 
    `names<-`(pts_nicfi$type) %>% 
    `rownames<-`(1:nrow(.)) %>% 
    mutate(`Band name` = c('Blue', 'Green', 'Red', 'NIR'),
           Band = 1:4) %>% 
    pivot_longer(cols = names(.)[1:(ncol(.) - 2)], 
                 names_to = 'Land cover type',
                 values_to = 'Reflectance') %>% 
    mutate(`Land cover type` = as.factor(`Land cover type`),
           Season = 'Season 2')
pts_nicfi_all <- rbind(pts_nicfi_s1, pts_nicfi_s2)
rm(pts_nicfi_s1, pts_nicfi_s2)

# Figure
pts_nicfi_all <- merge(pts_nicfi_all, cols_lc[, 2:3])
ref_epl <- ggplot(pts_nicfi_all,
                  aes(x = Band, y = Reflectance / 1000,
                      color = ids)) +
    geom_point() + geom_line(show.legend = 'line') +
    ylab(bquote('Reflectance'~(10^3))) + 
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    scale_x_discrete(limit = 1:4,
                     labels = unique(pts_nicfi_all$`Band name`)) +
    theme_bw() +
    theme(axis.title.x = element_blank()) +
    facet_wrap(~ Season, nrow = 2, 
               scales = "free_y",
               strip.position = "right")

nicfi_fg <- ggarrange(
    ggarrange(s1_fg, s2_fg,
              labels = c('Season 1', 'Season 2'),
              font.label = list(size = 12),
              vjust = 3,
              ncol = 2), 
    ref_epl, ncol = 2)
ggsave(here('docs/figures/nicfi_image.png'),
       nicfi_fg,
       width = 8, height = 2.7, dpi = 300)

# Sentinel-1 harmonic coefficient regression
fnames_s1 <- list.files(here('data/s1_harmonic'),
                        pattern = tile_id,
                        full.names = T)
vv_coefs <- stack(fnames_s1[str_detect(fnames_s1, 'VV')])
vh_coefs <- stack(fnames_s1[str_detect(fnames_s1, 'VH')])

# Image of VV
# Slope, Cos(x), Intercept
vv_fg <- ggRGB(vv_coefs, r = 2, g = 4, b = 1, 
               scale = max(values(vv_coefs)[, c(2, 4, 1)]), 
               stretch = 'hist') +
    geom_sf(data = pts_example,
            color = 'white',
            size = 3) +
    geom_sf(data = pts_example,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    theme_minimal() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))

# Image of VH
# Slope, Cos(x), Intercept
vh_fg <- ggRGB(vh_coefs, r = 2, g = 4, b = 1, 
               scale = max(values(vh_coefs)[, c(1, 2, 4)]), 
               stretch = 'lin') +
    geom_sf(data = pts_example,
            color = 'white',
            size = 3) +
    geom_sf(data = pts_example,
            aes(color = factor(id)),
            size = 2,
            show.legend = F) +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    theme_minimal() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))

# Time series and harmonic fitting of examples
# out = cos((2 * pi * n0 * t) / freq - (n % 2) * pi / 2)
# n_0 = {0,1,1,2,2}
# n = {0,1,2,3,4}
# freq = 365
# Band1: intercept
# Band2: slope
# Band3: sin(x)
# Band4: cos(x)
# Band5: sin(2x)
# Band6: cos(2x)

# Real time series
## Images
vv_ts <- stack(
    list.files(here('data/s1_timeseries_example/temp_ard_1227-1002'),
               pattern = 'VV',
               full.names = T)) 
vh_ts <- stack(
    list.files(here('data/s1_timeseries_example/temp_ard_1227-1002'),
               pattern = 'VH',
               full.names = T))

# DOY
doy <- c(0,   9,  12,  21,  33,  45,  48,  57,  69,  81,  93, 105, 117,
       129, 141, 153, 165, 177, 189, 201, 213, 225, 237, 249, 261, 273,
       285, 288, 293, 297, 300, 305, 309, 312, 317, 321, 324, 329, 333,
       336, 345, 348, 357, 360)

# Extract values
pts_vv_ts <- raster::extract(vv_ts, pts_example) %>% 
    t() %>% data.frame() %>% 
    `names<-`(pts_example$type) %>% 
    mutate(date = rownames(.)) %>% 
    `rownames<-`(1:nrow(.)) %>% 
    mutate(date = str_extract(date, '[0-9]{8}')) %>% 
    arrange(date) %>% 
    mutate(DOY = doy, polarization = 'VV',
           type = 'Real value')

pts_vh_ts <- raster::extract(vh_ts, pts_example) %>% 
    t() %>% data.frame() %>% 
    `names<-`(pts_example$type) %>% 
    mutate(date = rownames(.)) %>% 
    `rownames<-`(1:nrow(.)) %>% 
    mutate(date = str_extract(date, '[0-9]{8}')) %>% 
    arrange(date) %>% 
    mutate(DOY = doy, polarization = 'VH',
           type = 'Real value')

pts_ts <- rbind(pts_vv_ts, pts_vh_ts) %>% 
    dplyr::select(-date) %>% 
    pivot_longer(names(.)[1:7], 
                 names_to = "Land cover type", 
                 values_to = "dB")
rm(pts_vv_ts, pts_vh_ts)

# Harmonic coefficients
pts_vv <- raster::extract(vv_coefs, pts_example) %>% 
    t() %>% data.frame() %>% 
    `names<-`(pts_example$type) %>% 
    `rownames<-`(1:nrow(.)) %>% 
    mutate(`Band name` = c('Intersept', 'Slope', 
                           'Sin(x)', 'Cos(x)', 
                           'Sin(2x)', "Cos(2x)"), Band = 1:6)

pts_vv_fit <- do.call(cbind, lapply(names(pts_vv)[1:7], function(typ){
    coefs <- pts_vv %>% pull(typ)
    data.frame(val = coefs[1] + coefs[2] * doy +
    coefs[3] * sin(2 * pi * doy /365) + 
    coefs[4] * cos(2 * pi * doy /365) + 
    coefs[5] * sin(4 * pi * doy /365) + 
    coefs[6] * cos(4 * pi * doy /365))
})) %>% `names<-`(names(pts_vv)[1:7]) %>% 
    mutate(DOY = doy) %>% 
    mutate(polarization = 'VV',
           type = 'Harmoic regression')

pts_vh <- raster::extract(vh_coefs, pts_example) %>% 
    t() %>% data.frame() %>% 
    `names<-`(pts_example$type) %>% 
    `rownames<-`(1:nrow(.)) %>% 
    mutate(`Band name` = c('Intersept', 'Slope', 
                           'Sin(x)', 'Cos(x)', 
                           'Sin(2x)', "Cos(2x)"), Band = 1:6)

pts_vh_fit <- do.call(cbind, lapply(names(pts_vh)[1:7], function(typ){
    coefs <- pts_vh %>% pull(typ)
    data.frame(val = coefs[1] + coefs[2] * doy +
    coefs[3] * sin(2 * pi * doy /365) + 
    coefs[4] * cos(2 * pi * doy /365) + 
    coefs[5] * sin(4 * pi * doy /365) + 
    coefs[6] * cos(4 * pi * doy /365))
})) %>% `names<-`(names(pts_vh)[1:7]) %>% 
    mutate(DOY = doy) %>% 
    mutate(polarization = 'VH',
           type = 'Harmoic regression')

pts_fit <- rbind(pts_vv_fit, pts_vh_fit) %>% 
    pivot_longer(names(.)[1:7], 
                 names_to = "Land cover type", 
                 values_to = "dB")
rm(pts_vv_ts, pts_vh_ts)

# Make figure
pts_ts <- merge(pts_ts, cols_lc[, 2:3])
pts_fit <- merge(pts_fit, cols_lc[, 2:3])
ts_epl <- ggplot() + 
    geom_point(data = pts_ts, 
               aes(x = DOY, y = `dB`, 
                   color = factor(ids)),
               size = 0.6) +
    geom_line(data = pts_fit,
               aes(x = DOY, y = `dB`, 
                   color = factor(ids))) +
    facet_wrap(~polarization, 
               scales = 'free_y', nrow = 2,
               strip.position = "right") +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    theme_bw()

s1_fg <- ggarrange(
    ggarrange(vv_fg, vh_fg,
              labels = c('VV', 'VH'),
              font.label = list(size = 12),
              vjust = 3,
              ncol = 2), 
    ts_epl, ncol = 2)

ggsave(here('docs/figures/s1_image.png'),
       s1_fg,
       width = 8, height = 2.7, dpi = 300)
```

## Samples for Random forest and U-Net

This figure will provide the selected 200 tiles for RF to predict, the sub-tiling system for human checking, and the distribution of sub-tiles (chips) with score higher than 7.

```{r}
library(sf)
library(rasterVis)
library(ggnewscale)
library(cowplot)

# Read tiles
guess_tiles <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
    pull(tile) %>% unique()
nicfi_tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson')) %>% 
    mutate(guess = ifelse(tile %in% guess_tiles, 1, 0))
samples <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
    filter(score > 7)
sample_quality <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
    filter(tile == '1228-999' & score > 7)

# Sub-tiling
indices <- matrix(1:64, 8, 8)
indices <- indices[, ncol(indices):1]
sub_tiling <- nicfi_tiles %>% 
    filter(tile == '1228-999') %>% 
    st_make_grid(n = c(8, 8)) %>% 
        st_sf() %>% 
        mutate(index = as.vector(indices))

# Weak labels
labels_esb <- raster(here('data/north/lc_labels_north_mask.tif')) %>% 
    crop( nicfi_tiles %>% filter(tile == '1228-999'))
labels_guess <- raster(
    here('results/north/prediction/classed_1228-999.tif'))

# Sub-tiling figure
sub_tiling_fg <- ggplot(sub_tiling) + 
    geom_sf(color = 'blue', fill = NA, lwd = 0.3) + 
    geom_sf_text(aes(label = index), size = 2.5) +
    theme_minimal() +
    labs(title = 'B') +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.title = element_text(hjust = -0.15, vjust = -6),
          plot.margin = unit(rep(0, 4),"cm"))

# Weak ensemble labels
r_df <- as.data.frame(labels_esb, xy = TRUE) %>%
    rename(`Weak ensemble label` = lc_labels_north_mask) %>% 
    mutate(`Weak ensemble label` = factor(`Weak ensemble label`)) %>% 
    na.omit()
weak_lb_fg <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = `Weak ensemble label`)) +
    scale_fill_manual(
        values = c('#ff7f00', '#33a02c', '#b2df8a',
                   '#074702', '#0ea591'), 
        breaks = c(1, 4, 3, 2, 5),
        labels = c("Cropland", "Shrubland", 
                   "Grassland", "Forest", 'Wetland')) +
    geom_sf(data = sub_tiling, color = 'blue', 
            fill = NA, lty = 'dotted', lwd = 0.4) +
    theme_minimal() +
    theme(legend.position = 'none',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))

# RF guessed labels
r_df <- as.data.frame(labels_guess, xy = TRUE) %>%
    rename(`RF guess label` = classed_1228.999) %>% 
    mutate(`RF guess label` = factor(`RF guess label`)) %>% 
    na.omit()
guess_lb_fg <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = `RF guess label`)) +
    scale_fill_manual(
        values = c('#ff7f00', '#074702', '#b2df8a',
                   '#33a02c', '#3347f9', '#5a6057',
                   '#fdbf6f'), 
        breaks = 1:7,
        labels = c("Cropland", 'Forest', "Grassland", 
                   'Shrubland',  "Water", "Urban/Built-up",
                   'Bareland')) +
    geom_sf(data = sub_tiling %>% 
                st_transform(crs(labels_guess)), 
            color = 'blue', 
            fill = NA, lty = 'dotted', lwd = 0.4) +
    theme_minimal() +
    theme(legend.position = 'none',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))

# Sample distribution
legend_lc <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = `RF guess label`)) +
    scale_fill_manual('Land cover',
        values = c('#ff7f00', '#074702', '#b2df8a',
                   '#33a02c', '#3347f9', '#5a6057',
                   '#fdbf6f'), 
        breaks = 1:7,
        labels = c("Cropland", 'Forest', "Grassland", 
                   'Shrubland',  "Water", "Built-up",
                   'Bareland')) +
    geom_sf(data = sub_tiling %>% 
                st_transform(crs(labels_guess)), 
            color = 'blue', 
            fill = NA, lty = 'dotted', lwd = 0.4) +
    theme_minimal() +
    theme(legend.position = 'left',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))
legend_lc <- get_legend(legend_lc)

samples_fg <- ggplot() + 
    geom_sf(data = nicfi_tiles,
            aes(color = factor(guess),
                lty = factor(guess)), 
            fill = 'white', lwd = 0.4) +
    scale_linetype_manual('Usage', values = c('solid', 'solid'),
                          labels = c('Others', 'Guessed tile')) +
    scale_color_manual('Usage', values = c("grey", "blue"),
                       labels = c('Others', 'Guessed tile')) +
    geom_sf(data = samples, aes(fill = factor(score)), color = NA) +
    scale_fill_manual('Lable score', 
                      values = c("#00AFBB", "#E7B800", "#FC4E07")) +
    annotation_custom(grob = ggplotGrob(sub_tiling_fg), 
                      xmin = 35.8, xmax = 38.2,
                      ymin = -2.2, ymax = -0.1) +
    labs(title = 'A') +
    theme_minimal() +
    theme(legend.position = 'bottom',
          legend.box = "vertical",
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(-20, 2, 2, 2),
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.title = element_text(vjust = -6),
          plot.margin = unit(c(0, 0, 0, 0.2),"cm"))
    # guides(fill = guide_legend(nrow = 2, byrow = TRUE),
    #        color = guide_legend(nrow = 2, byrow = TRUE),
    #        linetype = guide_legend(nrow = 2, byrow = TRUE))

samples_fg <- ggarrange(samples_fg, legend_lc, 
                        nrow = 1, widths = c(1, 0.2))
imgs <- ggarrange(weak_lb_fg, guess_lb_fg, 
                  nrow = 2, labels = c('C', 'D'),
                  font.label = list(face = "plain"),
                  hjust = 0, vjust = 2)
sample_imgs <- ggarrange(samples_fg, imgs, 
                         ncol = 2,
                         widths = c(2.5, 1))
ggsave(here('docs/figures/samples_distribution.png'),
       sample_imgs,
       width = 8, height = 4.5, dpi = 600)
```

## Workflow

This figure will provide an overall flowchart of methods.

### 2021-07-03 docs/notebook_learn_dl_ensemble.Rmd
Update some details
Add some updates

@@
 ```
-python hrlcm/fit_coteaching_compare.py --exp_name unet_cot_argue --num_workers 32 --gpu_devices '0,1,2,3' --epochs 30
+python hrlcm/fit_coteaching.py --exp_name unet_cot_noisy8_40 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3' --num_gradual 10
+```
+
+```
+python hrlcm/fit_compose_lr.py --exp_name dpl_compose_lr --num_workers 32 --model deeplab --gpu_devices '0,1,2,3' --train_batch_size 16 --val_batch_size 16
 ```

### 2021-07-03 tools/generate_predict_catalog.R

@@ -1,0 +1,52 @@
+###############################################################
+## Part 1: predict all validate tiles to compare all methods ##
+############## Have instant image stack to use ################
+###############################################################
+
+# Get tile ids
+library(here)
+library(dplyr)
+library(stringr)
+library(terra)
+library(parallel)
+tile_valid <- read.csv(here('results/north/dl_catalog_valid.csv'),
+                       stringsAsFactors = F) %>% 
+    pull(tile) %>% unique()
+
+# Prepare satellite image stack for each tile
+load(here('data/north/forest_vip.rda'))
+var_selected <- data.frame(var = names(forest_vip$fit$variable.importance),
+                           imp = forest_vip$fit$variable.importance) %>% 
+    filter(str_detect(var, c('band')) | # remove indices
+               str_detect(var, c('vv')) |
+               str_detect(var, c('vh'))) %>% 
+    filter(imp > 1000) # remove less important ones
+
+img_from <- '/Volumes/elephant/pred_stack'
+img_to <- here('results/north/dl_valid_full')
+cp_img <- lapply(tile_valid, function(tile_id){
+    message(tile_id)
+    sat <- rast(
+        file.path(
+            img_from, paste0(tile_id, '.tif')
+        ))
+    sat <- subset(sat, var_selected$var)
+    writeRaster(
+        sat, 
+        file.path(
+            img_to, 
+            paste0(tile_id, '.tif')))
+})
+
+# Generate catalog
+dl_catalog_pred <- data.frame(tile_id = tile_valid) %>% 
+    mutate(img = file.path('dl_valid_full', 
+                           paste0(tile_id, '.tif')))
+write.csv(dl_catalog_pred, 
+          here('results/north/dl_catalog_valid_full.csv'),
+          row.names = F)
+
+###################################################
+## Part 2: predict all tiles over the study area ##
+###### Need to generate image stack to use ########
+###################################################

### 2021-07-03 tools/reorganize_datasets.R

@@ -76,18 +76,18 @@ write.csv(catalog_train_8, file.path(dst_dir, 'dl_catalog_train_noisy8_40.csv'),
           row.names = F)
 
 # # Fixed perfect sample numbers
-# catalog_train <- catalog_train %>% filter(score == 9) %>% 
+# catalog_train <- catalog_train %>% filter(score == 9) %>%
 #     sample_n(nrow(sample_perfect) * noise_ratio / (1 - noise_ratio))
 
 # # Copy files
 # dir.create(file.path(dst_dir, 'dl_train'), showWarnings = F)
 # dir.create(file.path(dst_dir, 'dl_valid'), showWarnings = F)
 # mclapply(1:nrow(catalog_train), function(n){
-#     ctg_n <- catalog_train %>% 
+#     ctg_n <- catalog_train %>%
 #         slice(n)
-#     file.copy(here(file.path(src_dir, ctg_n$img)), 
+#     file.copy(here(file.path(src_dir, ctg_n$img)),
 #               file.path(dst_dir, ctg_n$img))
-#     file.copy(here(file.path(src_dir, ctg_n$label)), 
+#     file.copy(here(file.path(src_dir, ctg_n$label)),
 #               file.path(dst_dir, ctg_n$label))
 # }, mc.cores = 6)
 

### 2021-07-03 docs/notebook_learn_dl_ensemble.Rmd
Add an argument of predict catalog to predict.py
Add another argument to predict

@@
   ```
-  git clone git@github.com:agroimpacts/pytorch_planet.git
+  git clone git@github.com:LLeiSong/hrlcm.git
   ```
@@
     (on the remote server) `tensorboard --logdir='./tensorboard_dirs' --port=16007`
+
+#### Prediction
+
+```
+python hrlcm/predict.py --args_path 'results/dl/resume/args.pkl' --checkpoint_file 'results/dl/resume/final.pth' --fname_predict 'results/north/dl_catalog_valid_full.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+```
 
@@
 
-  [TO BE CONTINUE]
+  Our experiments proved that architecture of DeepLab family has worse performance.
 

### 2021-07-03 hrlcm/predict.py

@@ -34,6 +34,8 @@ def main():
                         help='path to dataset')
     parser.add_argument('--out_dir', type=str, default="prediction",
                         help='path to output dir (default: ./prediction)')
+    parser.add_argument('--stats_dir', type=str, default="norm_stats",
+                        help='path of normalization params (default: ./norm_stats)')
     parser.add_argument('--num_workers', type=int, default=0,
                         help='number of worker(s) to load dataset (default: 0)')
 

### 2021-07-03 docs/notebook_learn_dl_ensemble.Rmd
Make some changes

--- 2021-07-03 docs/notebook_learn_dl_ensemble.Rmd
@@
     (on the remote server) `tensorboard --logdir='./tensorboard_dirs' --port=16007`
+
+#### Prediction
+
+```
+python hrlcm/predict.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --fname_predict 'results/north/dl_catalog_valid_full.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+```
 

### 2021-07-03 hrlcm/dataset.py

@@ -254,9 +254,9 @@ class NFSEN1LC(Dataset):
             img = self.img_ls[index]
             if self.img_transform is not None:
                 img = self.img_transform(img)
-            index = self.index_ls[index]
+            ind = self.index_ls[index]
 
-            return img, index
+            return img, ind
 
     def __len__(self):
         """Get number of samples in the dataset

### 2021-07-03 hrlcm/predict.py

@@ -60,6 +60,13 @@ def main():
 
     # Create output dir
     os.makedirs(args.out_dir, exist_ok=True)
+    # Set and create paths
+    score_path = os.path.join(args.out_dir, 'score')
+    class_path = os.path.join(args.out_dir, 'class')
+    if not os.path.isdir(score_path):
+        os.mkdir(score_path)
+    if not os.path.isdir(class_path):
+        os.mkdir(class_path)
 
     # Set flags for GPU processing if available
     args.use_gpu = torch.cuda.is_available()
@@ -123,14 +130,6 @@ def main():
                                     shuffle=False,
                                     drop_last=False)
 
-        # Set and crate paths
-        score_path = os.path.join(args.out_dir, 'score')
-        class_path = os.path.join(args.out_dir, 'class')
-        if not os.path.isdir(score_path):
-            os.mkdir(score_path)
-        if not os.path.isdir(class_path):
-            os.mkdir(class_path)
-
         # File names
         name_score = os.path.join(score_path, 'score_{}'.format(tile_id))
         name_class = os.path.join(class_path, 'class_{}.tif'.format(tile_id))
@@ -182,6 +181,8 @@ def main():
         for n in range(n_class):
             with rasterio.open('{}_class{}.tif'.format(name_score, n), 'w', **meta) as dst:
                 dst.write(canvas_score_ls[n])
+
+        del predict_dataset, predict_loader
 
 
 if __name__ == "__main__":

### 2021-07-04 docs/notebook_learn_dl_ensemble.Rmd
Coteaching is ready to use at the moment, update document a bit

--- 2021-07-03 docs/notebook_learn_dl_ensemble.Rmd
@@
     (on the remote server) `tensorboard --logdir='./tensorboard_dirs' --port=16007`
+
+#### Prediction
+
+```
+python hrlcm/predict.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+```
+
+```
+python hrlcm/predict.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/model2_final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction2' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+```
+
+#### Evaluation
+
+```
+python hrlcm/evaluate.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+```
+
+```
+python hrlcm/evaluate.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/model1_final.pth' --data_dir 'results/north' --out_dir 'results/evaluation1' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+```
 

### 2021-07-04 docs/notebook_learn_dl_ensemble.Rmd
Update documentation :memo:

@@
 
-### Google Colab
-In general, we mean to use Google Colab to run the model.
-For this case, it is more convenient to read the data locally and pickle them.
-Then directly load the pickles into Google Colab and just use the GPU environment to run the models.
+#### Other useful commands
+
+##### Check disk space and clean trash
+
+```bash
+df -H
+cd .local/share/Trash/
+rm -rf *
+```
+##### Check the RAM usage in M
+
+```bash
+free -m
+```
 
@@
 
-- U-net, which has simple architecture and is friendly to small dataset. This model is especially suitable for guess training.
+- U-net, which has simple architecture and is friendly to small dataset.
 
-- Deeplab3plus with ResNet as backbone.
-This architecture can consider the global context and have skip connections to ensure the complex structure still could get coverage.
-This model is super useful for the final train with manually corrected labels.
+- Deeplab3plus with ResNet as backbone. This architecture can consider the global context and have skip connections to ensure the complex structure still could get coverage.
 
-### Strategies to deal with noisy labels
+### Possible strategies to deal with noisy labels
 
@@
 
-[NEED MORE EXPERIMENTS]
+So after all experiments, we decide to stick with co-teaching & co-teaching-plus.
 
@@
 - <input type="checkbox" checked> Learning rate and learning rate scheduler</input>
-- Batch size
-- Optimizer
-- Model (U-net or Deeplab)
+- <input type="checkbox" checked> Batch size</input>
+- <input type="checkbox" checked> Optimizer</input>
+- <input type="checkbox" checked> Model (U-net or Deeplab)</input>
 - Transform methods (if necessary)
@@
 
-- Co_teaching works good. "Discuss" mode works slightly better than "argue" mode.
+- Co_teaching works good.
+"Discuss" mode works slightly better than "argue" mode.
+Since "argue" mode use the disagreement between two models, we assume this method would be helpful to transfer a model to other areas.
+Of course, this assumption needs more test.

### 2021-07-06 docs/notebook_learn_dl_ensemble.Rmd
Update catalogs

@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name dpl_compose_lr --num_workers 32 --model deeplab --gpu_devices '0,1,2,3' --train_batch_size 16 --val_batch_size 16
-```
-
-```
-python hrlcm/fit_coteaching.py --exp_name unet_cot_da --num_workers 32 --gpu_devices '0,1,2,3' --save_freq 5 --resume1 'results/dl/unet_cot_da/model1_final.pth' --resume2 'results/dl/unet_cot_da/model2_final.pth'
+python hrlcm/fit_compose_lr.py --exp_name unet_single_noisy8_40 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3'
 ```

### 2021-07-06 guess_model/10_generate_catalogs.R

@@ -107,7 +107,7 @@ message('Step 3: Get train dataset')
 # All other tiles with different levels of quality
 tiles_train <- st_read(here('results/north/label_check_catalog.geojson')) %>% 
     filter(pass == 'yes') %>% 
-    filter(score > 7) %>% 
+    filter(score > 5) %>% 
     mutate(id = paste0(tile, index)) %>% 
     filter(!id %in% paste0(tiles_validate$tile, tiles_validate$index)) %>% 
     dplyr::select(-id)

### 2021-07-14 docs/manuscript_figures.Rmd
Merge some files

@@
 This figure will provide an overall flowchart of methods.
+
+## Scalars
+
+```{r}
+# Single U-Net model with step learning rate
+# Get file names
+fns <- list.files('results/scalars/single_step_lr', 
+                  pattern = 'step_lr',
+                  full.names = T)
+
+# Learning rate
+step_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
+    mutate(Step = Step / 113)
+
+# Scalars
+fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
+unet_step_lr_scalars <- lapply(fns, function(fn){
+    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
+        mutate(Step = Step / 113) %>% 
+        select(-Wall.time)
+})
+names(unet_step_lr_scalars) <- gsub(
+    '.csv', "", 
+    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+
+# Single U-Net model with compose learning rate
+# Get file names
+fns <- list.files('results/scalars/single_compose_lr', 
+                  pattern = 'compose_lr',
+                  full.names = T)
+
+# Learning rate
+compose_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
+    mutate(Step = Step / 113)
+
+# Scalars
+fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
+unet_compose_lr_scalars <- lapply(fns, function(fn){
+    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
+        mutate(Step = Step / 113) %>% 
+        select(-Wall.time)
+})
+names(unet_compose_lr_scalars) <- gsub(
+    '.csv', "", 
+    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+
+# Coteaching + single U-Net model
+nms <- gsub(
+    '.csv', "", 
+    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+fns_cot <- list.files('results/scalars/cot_single/cot', 
+                  full.names = T)
+stages <- c('8_5_1', '8_5_2', '9_5_1', '9_5_2')
+
+cot_scalars <- lapply(nms, function(nm){
+    fns1 <- fns_cot[str_detect(fns_cot, paste0(nm, "1"))]
+    fns2 <- fns_cot[str_detect(fns_cot, paste0(nm, "2"))]
+    scalar1 <- do.call(rbind, lapply(stages, function(stage){
+        fns <- fns1[str_detect(fns1, stage)]
+        if (stage == '8_5_2') {
+            read.csv(fns) %>%
+                mutate(Step = Step/min(Step) + 5)
+        } else if (stage == '9_5_1'){
+            read.csv(fns) %>%
+                mutate(Step = Step/min(Step) + 10)
+        } else if (stage == '9_5_2'){
+            read.csv(fns) %>%
+                mutate(Step = Step/min(Step) + 15)
+        } else{
+            read.csv(fns) %>%
+                mutate(Step = Step/min(Step))
+        }
+    }))
+    scalar2 <- do.call(rbind, lapply(stages, function(stage){
+        fns <- fns2[str_detect(fns2, stage)]
+        if (stage == '8_5_2') {
+            read.csv(fns) %>%
+                mutate(Step = Step/min(Step) + 5)
+        } else if (stage == '9_5_1'){
+            read.csv(fns) %>%
+                mutate(Step = Step/min(Step) + 10)
+        } else if (stage == '9_5_2'){
+            read.csv(fns) %>%
+                mutate(Step = Step/min(Step) + 15)
+        } else{
+            read.csv(fns) %>%
+                mutate(Step = Step/min(Step))
+        }
+    }))
+    scalar1 %>% select(-Wall.time) %>% 
+        rename(Value_m1 = Value) %>% 
+        merge(scalar2 %>% select(-Wall.time) %>% 
+                  rename(Value_m2 = Value),
+              by = 'Step')
+})
+names(cot_scalars) <- nms
+
+fns <- list.files('results/scalars/cot_single/single_ctn', 
+                  full.names = T)
+fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
+cot_ctn_scalars <- lapply(fns, function(fn){
+    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
+        mutate(Step = Step / 113 + 20) %>% 
+        select(-Wall.time)
+})
+names(cot_ctn_scalars) <- gsub(
+    '.csv', "", 
+    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+
+cot_single_scalars <- lapply(nms, function(nm){
+    cot_scalars[[nm]] %>% 
+        select(Step, Value_m2) %>% 
+        rename(Value = Value_m2) %>% 
+        rbind(cot_ctn_scalars[[nm]])
+})
+names(cot_single_scalars) <- nms
+
+# Plot
+
+aa <- merge(unet_compose_lr_scalars$Water, 
+            cot_single_scalars$Water, 
+            by = 'Step') %>% 
+    rename(Compose = Value.x, Cot = Value.y) %>% 
+    pivot_longer(cols = c(Compose, Cot),
+                 names_to = 'type', values_to = 'value')
+ggplot(aa, aes(x = Step, y = value)) +
+    geom_line(aes(color = type, lty = type)) +
+    # geom_smooth(aes(color = type)) +
+    theme_bw()
+```

### 2021-07-14 docs/notebook_learn_dl_ensemble.Rmd
Merge some files

@@
 
+Prepare work:
+
 ```
-python hrlcm/fit_coteaching.py --exp_name unet_cot_noisy8_40 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3' --num_gradual 10
+scp -r /Volumes/wildebeest/dl_train ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
+
+scp -r /Volumes/wildebeest/dl_valid ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
+
+scp -r /Users/pinot/Dropbox/research/hrlcm/results/north/norm_stats ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
+
+scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train.csv ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
+
+scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_valid.csv ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
+```
+
+Run models:
+
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_single_gl --lowest_score 9 --num_workers 32 --gpu_devices '0,1,2,3'
 ```
@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_single_noisy8_40 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3'
+python hrlcm/fit_coteaching.py --exp_name unet_cot_gl_blind --lowest_score 9 --num_workers 32 --gpu_devices '0,1,2,3'
+```
+
+```
+python hrlcm/fit_coteaching.py --exp_name unet_cot_8 --highest_score 8 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3'
 ```
@@
 df -H
-cd .local/share/Trash/
+cd ~/.local/share/Trash/
 rm -rf *

### 2021-07-14 guess_model/10_generate_catalogs.R

@@ -30,44 +30,44 @@ message('Step 2: Select validate dataset')
 
 # Get perfect tiles
 tiles_perfect <- st_read(here('results/north/label_check_catalog.geojson')) %>% 
-    filter(pass == 'yes') %>% 
-    filter(score == 10)
+  filter(pass == 'yes') %>% 
+  filter(score == 10)
 
 # Make summary of these tiles
 tiles_summary <- mclapply(1:nrow(tiles_perfect), function(n){
-    tile_row <- tiles_perfect %>% slice(n)
-    label_nm <- paste0('refine_', tile_row$tile, 
-                       "_", tile_row$index, '.tif')
-    label <- rast(here(file.path('results/north/guess_labels',
-                                 label_nm)))
-    freq(label) %>% data.frame() %>% 
-        filter(value != 0) %>%
-        dplyr::select(-layer) %>%
-        pivot_wider(names_from = value, values_from = count) %>% 
-        mutate(tile = tile_row$tile,
-               index = tile_row$index) %>% 
-        dplyr::select(tile, index, setdiff(names(.), c('tile', 'index')))
+  tile_row <- tiles_perfect %>% slice(n)
+  label_nm <- paste0('refine_', tile_row$tile, 
+                     "_", tile_row$index, '.tif')
+  label <- rast(here(file.path('results/north/guess_labels',
+                               label_nm)))
+  freq(label) %>% data.frame() %>% 
+    filter(value != 0) %>%
+    dplyr::select(-layer) %>%
+    pivot_wider(names_from = value, values_from = count) %>% 
+    mutate(tile = tile_row$tile,
+           index = tile_row$index) %>% 
+    dplyr::select(tile, index, setdiff(names(.), c('tile', 'index')))
 }, mc.cores = 6) %>% bind_rows()
 
 # Select out validation dataset
 tiles_valid <- lapply(as.character(1:7), function(ind){
-    if (ind %in% 6:7){
-        set.seed(10)
-        tiles_summary %>% 
-            dplyr::select(tile, index, all_of(ind)) %>% 
-            na.omit() %>% arrange(desc(across(ind))) %>% 
-            slice(1:(nrow(.) / 2)) %>% 
-            sample_n(400)
-    } else{
-        tiles_summary %>% 
-            dplyr::select(tile, index, all_of(ind)) %>% 
-            na.omit() %>% arrange(desc(across(ind))) %>% 
-            slice(1:100)
-    }
+  if (ind %in% 6:7){
+    set.seed(10)
[…]

### 2021-07-16 docs/manuscript_figures.Rmd
Stage 1 :bookmark:

--- 2021-07-03 docs/manuscript_figures.Rmd
@@
 library(tidyr)
+library(stringr)
 library(RStoolbox)
@@
                        labels = cols_lc$`Land cover type`) +
-    scale_x_discrete(limit = 1:4,
+    scale_x_discrete(limit = factor(1:4),
                      labels = unique(pts_nicfi_all$`Band name`)) +
@@
                scales = "free_y",
-               strip.position = "right")
+               strip.position = "top")
 
@@
                scales = 'free_y', nrow = 2,
-               strip.position = "right") +
+               strip.position = "top") +
     scale_color_manual("Land cover type",
@@
     filter(score > 7)
-sample_quality <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
-    filter(tile == '1228-999' & score > 7)
 
@@
 This figure will provide an overall flowchart of methods.
+
+## Metrics
+
+```{r}
+# Get file names
+fns <- list.files(here('results/scalars/single_compose_lr'), 
+                  pattern = 'compose_lr',
+                  full.names = T)
+
+# Metrics
+fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
+metrics_last10 <- do.call(cbind, lapply(fns, function(fn){
+    read.csv(fn, stringsAsFactors = F) %>% 
+        dplyr::select(-c(Wall.time, Step)) %>% 
+        tail(10)
+}))
+names(metrics_last10) <- gsub(
+    '.csv', "", 
+    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+
+# Calculate mean and sd
+items <- c('AA', 'IoU', 'Cropland', 'Forest', 
+           'Grassland', 'Shrubland', 'Water', 
+           'Urban', 'Bareland')
+options(digits = 3)
+tb <- do.call(rbind, lapply(items, function(item){
+    vals <- metrics_last10 %>% pull(all_of(item))
+    if (item == 'Urban') item <- 'Built-up'
+    data.frame(mean = mean(vals),
+               sd = sd(vals)) %>% 
+        mutate(metric = item)
+}))
+```
+
+## Scalars
+
+```{r}
+library(here)
+
+# Single U-Net model with step learning rate
+# Get file names
+fns <- list.files(here('results/scalars/single_step_lr'), 
+                  pattern = 'step_lr',
+                  full.names = T)
+
+# Learning rate
+step_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
+    mutate(Step = Step / 113)
+
+# Scalars
+fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
+unet_step_lr_scalars <- lapply(fns, function(fn){
+    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
+        mutate(Step = Step / 113) %>% 
+        dplyr::select(-Wall.time)
+})
+names(unet_step_lr_scalars) <- gsub(
+    '.csv', "", 
+    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+
+# Single U-Net model with compose learning rate
+# Get file names
+fns <- list.files(here('results/scalars/single_compose_lr'), 
+                  pattern = 'compose_lr',
+                  full.names = T)
+
+# Learning rate
+compose_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
+    mutate(Step = Step / 113)
+
+# Scalars
+fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
+unet_compose_lr_scalars <- lapply(fns, function(fn){
+    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
+        mutate(Step = Step / 113) %>% 
+        dplyr::select(-Wall.time)
+})
+names(unet_compose_lr_scalars) <- gsub(
+    '.csv', "", 
+    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+
+# Plot
+aa <- merge(unet_compose_lr_scalars$AA, 
+            unet_step_lr_scalars$AA, 
+            by = 'Step') %>% 
+    rename(Compose = Value.x, Cot = Value.y) %>% 
+    pivot_longer(cols = c(Compose, Cot),
+                 names_to = 'type', values_to = 'value')
+ggplot(aa, aes(x = Step, y = value)) +
+    geom_line(aes(color = type, lty = type)) +
+    geom_smooth(aes(color = type)) +
+    theme_bw()
+```

### 2021-07-16 guess_model/5_get_training.R

@@ -213,9 +213,7 @@ get_img_wdist <- function(tile_nm, tiles_north,
     imgs
 }
 
-get_img <- function(tile_nm, tiles_north,
-                          rivers_all, roads_all, 
-                          buildings_all){
+get_img <- function(tile_nm){
     message(tile_nm)
     
     # read Planet images

### 2021-07-16 tools/generate_predict_catalog.R

@@ -4,6 +4,7 @@
 ###############################################################
 
 # Get tile ids
+library(sf)
 library(here)
 library(dplyr)
 library(stringr)
@@ -21,6 +22,7 @@ var_selected <- data.frame(var = names(forest_vip$fit$variable.importance),
                str_detect(var, c('vv')) |
                str_detect(var, c('vh'))) %>% 
     filter(imp > 1000) # remove less important ones
+rm(forest_vip)
 
 img_from <- '/Volumes/elephant/pred_stack'
 img_to <- here('results/north/dl_valid_full')
@@ -39,10 +41,10 @@ cp_img <- lapply(tile_valid, function(tile_id){
 })
 
 # Generate catalog
-dl_catalog_pred <- data.frame(tile_id = tile_valid) %>% 
+dl_catalog_valid_full <- data.frame(tile_id = tile_valid) %>% 
     mutate(img = file.path('dl_valid_full', 
                            paste0(tile_id, '.tif')))
-write.csv(dl_catalog_pred, 
+write.csv(dl_catalog_valid_full, 
           here('results/north/dl_catalog_valid_full.csv'),
           row.names = F)
 
@@ -50,3 +52,83 @@ write.csv(dl_catalog_pred,
 ## Part 2: predict all tiles over the study area ##
 ###### Need to generate image stack to use ########
 ###################################################
+tiles_pred_left <- read_sf(
+    here('data/geoms/tiles_nicfi_north.geojson')) %>% 
+    filter(!tile %in% dl_catalog_valid_full$tile_id)
+
+# Function to make raster stack
+get_img_imp <- function(tile_nm) {
+  message(tile_nm)
+
+  # read Planet images
+  message("--Planet basemap")
+  plt_nms_tile <- grep(tile_nm, plt_nms, value = TRUE)
+  plt_os <- rast(grep("2017-12_2018-05",
+    plt_nms_tile,
+    value = TRUE
+  )) %>%
+    subset(1:4)
+  names(plt_os) <- paste0("band", 1:4)
+  plt_gs <- rast(grep("2018-06_2018-11",
+    plt_nms_tile,
+    value = TRUE
+  )) %>%
+    subset(1:4)
+  names(plt_gs) <- paste0("band", 1:4)
[…]

### 2021-07-18 docs/notebook_learn_dl_ensemble.Rmd
Update for new format

@@
 ```
-python hrlcm/fit_coteaching.py --exp_name unet_cot_gl_blind --lowest_score 9 --num_workers 32 --gpu_devices '0,1,2,3'
-```
-
-```
 python hrlcm/fit_coteaching.py --exp_name unet_cot_8 --highest_score 8 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3'
@@
 
-```
-python hrlcm/predict.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/model2_final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction2' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
-```
-
 #### Evaluation
@@
 python hrlcm/evaluate.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
-```
-
-```
-python hrlcm/evaluate.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/model1_final.pth' --data_dir 'results/north' --out_dir 'results/evaluation1' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
 ```
@@
 
-- Deeplab3plus with ResNet as backbone. This architecture can consider the global context and have skip connections to ensure the complex structure still could get coverage.
-
 ### Possible strategies to deal with noisy labels
-
 #### Add noisy labels to fine tune
@@
 #### JoCoR
+
 Since the original paper is about image classification rather than image segmentation, it is harder to adapt this method into image segmentation with good performance.
@@
 Of course, this assumption needs more test.
+
+So now, I have a clear idea is that the "wrong" guess labels are actually the hard ones. So instead of dumping them, we should take advantage of them.
+
+- Randomly get 8 out of 64 for each tile, 6 for train, and 2 for validate.
+- For these sub-tiles, score them and also correct the wrong part. The scores will be used as weight to calculate loss. The lower the score is, the higher weight it is.

### 2021-07-18 guess_model/11_generate_holdout.R

@@ -1,0 +1,67 @@
+# Title     : Script to generate validation dataset
+# Objective : To randomly select dataset roughly balanced between types
+#             for manually check.
+# Created by: Lei Song
+# Created on: 03/23/21
+
+#######################
+##  Step 1: Setting  ##
+#######################
+message('Step1: Setting')
+
+library(sf)
+library(dplyr)
+library(here)
+
+################################################
+###  Step 2: Sampling for independent check  ###
+################################################
+message('Step 2: Sampling for independent check')
+
+# Sample
+set.seed(10)
+samples_check <- read_sf(
+    here('data/geoms/tiles_nicfi_north.geojson')) %>% 
+    st_sample(rep(2, nrow(.))) %>% 
+    st_buffer(5 %>% units::set_units("m")) %>% 
+    st_sf() %>% 
+    mutate(landcover = '', 
+           source = 'humancheck',
+           valid = TRUE)
+
+# Convert to use square
+samples_check <- do.call(
+    rbind, 
+    lapply(1:nrow(samples_check), function(n){
+        samples_check %>% slice(n) %>% 
+            mutate(geometry = st_make_grid(
+                geometry, n = 1))
+}))
+
+st_write(samples_check, 
+         here('data/north/plys_holdout_check.geojson'))
+
+#######################################################
+###  Step 3: Add samples from other public datasets ###
+#######################################################
+# Full polygon field, use centroid as evaluation
+samples_mappingafrica <- read_sf(
+    here('data/references/user_maps_tz.geojson')) %>% 
+    st_make_valid() %>% 
+    st_centroid() %>% 
+    st_sf() %>% 
+    mutate(landcover = 1, source = 'mappingafrica') %>%
+    dplyr::select(landcover, source)
+
+# Polygon samples inside of field, use centroid as evaluation
+samples_mlhub <- read_sf(
+    here('data/references/ref_crops.geojson')) %>% 
+    st_make_valid() %>% 
+    st_centroid() %>% 
+    st_sf() %>% 
+    mutate(landcover = 1, source = 'mlhub') %>%
+    dplyr::select(landcover, source)
+    
+samples_pts <- rbind(samples_mappingafrica, samples_mlhub)
+rm(samples_mappingafrica, samples_mlhub); gc()
+st_write(samples_pts, here('data/north/pts_holdout.geojson'))

### 2021-07-18 guess_model/4_sampling.R

@@ -1,5 +1,5 @@
 # Title     : Script to get samples for RF
-# Objective : To sample landcover types to run 
+# Objective : To sample landcover types to run
 #             a random forest model.
 # Created by: Lei Song
 # Created on: 02/24/21
@@ -7,7 +7,7 @@
 #######################
 ##  Step 1: Setting  ##
 #######################
-message('Step1: Setting')
+message("Step1: Setting")
 
 ## Load packages
 library(here)
@@ -22,157 +22,183 @@ library(rgrass7)
 #############################################
 ##  Step 2: Sampling from ensemble labels  ##
 #############################################
-message('Step 2: Sampling from ensemble labels')
+message("Step 2: Sampling from ensemble labels")
 
 # Read the OSM-masked ensemble labels
-lc_labels <- rast(here('data/north/lc_labels_north_mask.tif'))
+lc_labels <- rast(here("data/north/lc_labels_north_mask.tif"))
 n_labels <- freq(lc_labels)
 sum(n_labels[, 3]) * 0.01 / nrow(n_labels)
 
 ## Use GRASS GIS to sample
-gisBase <- '/Applications/GRASS-7.9.app/Contents/Resources'
-initGRASS(gisBase = gisBase,
-          home = tempdir(),
-          gisDbase = tempdir(),  
-          mapset = 'PERMANENT', 
-          location = 'lc_types', 
-          override = TRUE)
-execGRASS("g.proj", flags = "c", 
-          proj4="+proj=longlat +datum=WGS84 +no_defs")
-execGRASS('r.in.gdal', flags = c("o", "overwrite"),
-          input = here('data/north/lc_labels_north_mask.tif'),
-          band = 1,
-          output = "lc_types")
+gisBase <- "/Applications/GRASS-7.8.app/Contents/Resources"
+initGRASS(
+  gisBase = gisBase,
+  home = tempdir(),
+  gisDbase = tempdir(),
+  mapset = "PERMANENT",
+  location = "lc_types",
+  override = TRUE
+)
+execGRASS("g.proj",
+  flags = "c",
+  proj4 = "+proj=longlat +datum=WGS84 +no_defs"
+)
+execGRASS("r.in.gdal",
+  flags = c("o", "overwrite"),
+  input = here("data/north/lc_labels_north_mask.tif"),
+  band = 1,
+  output = "lc_types"
+)
 execGRASS("g.region", raster = "lc_types")
-execGRASS('r.sample.category', flags = c("overwrite"),
[…]

### 2021-07-18 guess_model/5_get_training.R

@@ -1,5 +1,5 @@
 # Title     : Script to get training data
-# Objective : To extract satellite values  
+# Objective : To extract satellite values
 #             from a bunch of images.
 # Created by: Lei Song
 # Created on: 02/24/21
@@ -7,7 +7,7 @@
 #######################
 ##  Step 1: Setting  ##
 #######################
-message('Step1: Setting')
+message("Step1: Setting")
 
 ## Load packages
 library(here)
@@ -17,298 +17,139 @@ library(sf)
 library(dplyr)
 library(tidyr)
 library(stringr)
-library(rgrass7)
 
 ####################################
 ##  Step 2: Load related dataset  ##
 ####################################
-message('Step 2: Load related dataset')
+message("Step 2: Load related dataset")
 
 ## Get samples
-samples <- st_read(here('data/north/samples_all.geojson'))
-tiles_north <- st_read(here('data/geoms/tiles_nicfi_north.geojson'))
+samples <- read_sf(
+    here("data/north/samples_all.geojson"))
+tiles_north <- read_sf(
+    here("data/geoms/tiles_nicfi_north.geojson"))
 samples <- st_join(samples, tiles_north)
-save(samples, file = here('data/north/samples.rda'))
+save(samples, file = here("data/north/samples.rda"))
 
 ## Read file names
-plt_path <- '/Volumes/elephant/plt_nicfi'
+plt_path <- "/Volumes/elephant/plt_nicfi"
 plt_nms <- list.files(plt_path, full.names = T)
-s1_path <- '/Volumes/elephant/sentinel1_hr_coefs'
+s1_path <- "/Volumes/elephant/sentinel1_hr_coefs"
 s1_nms <- list.files(s1_path, full.names = T)
 
 ####################################
 ##  Step 3: Prepare image stacks  ##
 ####################################
-message('Step 3: Prepare image stacks')
+message("Step 3: Prepare image stacks")
 
-## Define the function to make image stacks
-get_img_wdist <- function(tile_nm, tiles_north,
-                    rivers_all, roads_all, 
-                    buildings_all){
-    message(tile_nm)
-    
-    # read Planet images
-    message('--Planet basemap')
-    plt_nms_tile <- grep(tile_nm, plt_nms, value = TRUE)
[…]

### 2021-07-18 guess_model/7_pred_guess_model.R

@@ -9,6 +9,7 @@
 #######################
 message('Step1: Setting')
 
+library(sf)
 library(here)
 library(terra)
 library(dplyr)
@@ -18,6 +19,8 @@ library(parsnip)
 library(tidymodels)
 library(stringr)
 library(glue)
+library(parallel)
+library(rgrass7)
 
 #############################
 ###  Step 2: Preparation  ###
@@ -29,23 +32,164 @@ message("--Load model")
 load(here('data/north/guess_rf_md.rda'))
 
 # Define function to do prediction
-make_pred <- function(img_path,
-                      dst_path = 'results/north/prediction'){
-    id <- str_extract(img_path, '[0-9]+-[0-9]+')
-    message(paste0('--', id))
-    imgs <- rast(img_path) %>%
-        subset(setdiff(names(.),
-                       c('rivers_dist', 'buildings_dist',
-                         'roads_dist')))
+make_pred <- function(tile_id,
+                      sample_tiles,
+                      tiles,
+                      size_sub_tile = 512,
+                      skip_class = 8,
+                      img_dir,
+                      dst_dir = 'results/north/guess_labels'){
+    message(paste0('--', tile_id))
     
-    ## Predict scores and classes
-    scores <- predict(imgs, guess_rf_md, type = "prob", na.rm = T)
-    writeRaster(scores, here(glue('{dst_path}/scores_{id}.tif')))
-    pred <- values(scores); pred[is.na(pred)] <- 0
-    pred <- argmax(pred)
-    classes <- scores[[1]]
-    values(classes) <- pred
-    writeRaster(classes, here(glue('{dst_path}/classed_{id}.tif')))
+    # Get image
+    imgs <- rast(file.path(img_dir, paste0(tile_id, '.tif')))
+    
+    # Subset vectors for whole tile
+    tile <- tiles %>% 
+        filter(tile == tile_id) %>% 
+        st_buffer(0.01)
+    sub_tiles <- sample_tiles %>% 
+        filter(tile == tile_id)
+    crs_mer <- crs(imgs)
+    road <- roads %>% 
+        st_intersection(tile) %>% 
+        st_cast('MULTILINESTRING') %>% 
+        st_transform(crs = crs_mer)
+    waterbody <- waterbodies %>% 
+        st_intersection(tile) %>% 
+        st_cast('MULTIPOLYGON') %>% 
+        st_transform(crs = crs_mer)
+    building <- buildings %>% 
[…]

### 2021-07-18 guess_model/8_refine_guess_labels.R

@@ -1,214 +1,0 @@
-# Title     : Script to refine guess labels
-# Objective : To apply a few steps to refine 
-#             the guess labels generated by random forest.
-# Created by: Lei Song
-# Created on: 03/23/21
-
-####################### 
-##  Step 1: Setting  ##
-#######################
-message('Step 1: Setting')
-
-library(glue)
-library(here)
-library(terra)
-library(ramify)
-library(sf)
-library(rgrass7)
-library(dplyr)
-library(stringr)
-library(tidyverse)
-library(parallel)
-
-###############################
-###  Step 2: Refine labels  ###
-###############################
-message('Step 2: Refine labels')
-
-# Define function to refine the labels
-## Step 2-0: Reduce the weight of predicted buildings.
-## Step 2-1: Add roads, waterbodies, and buildings. (No rivers)
-## Step 2-2: Split a whole tile into 512 * 512 (or 256 * 256).
-refine_label <- function(tile_id, src_dir, 
-                         labels_dir, tiles, roads, 
-                         waterbodies, buildings, 
-                         size_sub_tile = 512){
-    message('------Modify classses')
-    # Read images
-    scores <- rast(file.path(src_dir, glue('scores_{tile_id}.tif')))
-    
-    # Reduce the weight of predicted buildings
-    scores$.pred_8 <- scores$.pred_8 * 0.2
-    pred <- values(scores); pred[is.na(pred)] <- 0
-    pred <- argmax(pred)
-    classes <- scores[[1]]
-    values(classes) <- pred
-    rm(scores, pred); gc()
-    # So here:
-    # 1: cropland
-    # 2: forest
-    # 3: grassland
-    # 4: shrubland
-    # 5: water
-    # 6: Urban
-    # 7: bareland
-    
-    # Set up GRASS GIS
-    message('------Add OSM layers')
-    gisBase <- '/Applications/GRASS-7.9.app/Contents/Resources'
-    initGRASS(gisBase = gisBase,
-              home = tempdir(),
-              gisDbase = tempdir(),  
-              mapset = 'PERMANENT', 
-              location = 'segments', 
-              override = TRUE)
-    execGRASS("g.proj", flags = "c", 
-              proj4 = crs(rast(
-                  file.path(src_dir, glue('scores_{tile_id}.tif'))),
-                  proj4 = T))
-    execGRASS('r.in.gdal', flags = c("o", "overwrite"),
-              input = file.path(src_dir, glue('scores_{tile_id}.tif')),
-              band = 1,
[…]

### 2021-07-18 guess_model/8_refine_guess_labels_with_segments.R

@@ -1,255 +1,0 @@
-# Title     : Script to refine guess labels
-# Objective : To apply a few steps to refine 
-#             the guess labels generated by random forest.
-# Created by: Lei Song
-# Created on: 03/23/21
-
-#######################
-##  Step 1: Setting  ##
-#######################
-message('Step1: Setting')
-
-library(glue)
-library(here)
-library(terra)
-library(ramify)
-library(sf)
-library(rgrass7)
-library(dplyr)
-library(tidyverse)
-library(parellel)
-
-###############################
-###  Step 2: Refine labels  ###
-###############################
-message('Step 2: Refine labels')
-
-# Define function to refine the labels
-## Step 0: Remove predicted buildings.
-## Step 1: Apply zonal mode to objects that are over segmented.
-## Step 2: Add roads, waterbodies, and buildings. (No rivers)
-## Step 3: Split a whole tile into 512 * 512 (or 256 * 256).
-refine_label <- function(tile_id, src_dir, img_dir, tiles){
-    # tile_id <- '1208-996'
-    # src_dir <- here('results/north/prediction')
-    # img_dir <- here('data/plts_nicfi')
-    # tiles <- st_read('data/geoms/tiles_nicfi_north.geojson')
-    # roads <- st_read(here('data/osm/big_roads.geojson'))
-    # waterbodies <- st_read(here('data/osm/waterbodies.geojson'))
-    # buildings <- st_read(here('data/osm/buildings.geojson'))
-    # Read images
-    scores <- rast(file.path(src_dir, glue('scores_{tile_id}.tif')))
-    
-    # Remove predicted buildings
-    classes_path <- file.path(tempdir(), 'temp.tif')
-    scores <- subset(scores, c(1:5, 7))
-    pred <- argmax(values(scores))
-    classes <- scores[[1]]
-    values(classes) <- pred
-    writeRaster(classes, classes_path,
-                wopt = list(datatype = 'INT1U',
-                            gdal=c("COMPRESS=LZW")),
-                overwrite = T)
-    rm(scores, pred, classes); rm()
-    # So here:
-    # 1: cropland
-    # 2: forest
-    # 3: grassland
-    # 4: shrubland
-    # 5: water
-    # 6: bareland
-    
-    # Do segmentation
-    nicfi_prefix <- 'planet_medres_normalized_analytic'
-    s1_prefix <- '2017-12_2018-05'
[…]

### 2021-07-18 tools/download.hls.sh

@@ -1,0 +1,224 @@
+#!/bin/bash
+
+# Download all the HLS L30 and S30 files for a single tile ID or for all the tile IDs 
+# in a given file; a year can be specified as an option.
+#
+# version: 1.0
+#
+# Junchang Ju
+# Jul 26, 2017: Download for an entire test site.
+# Mar 16, 2018: Modified to work for a tile ID, or a file of tile IDs.
+# Oct 11, 2018: Delete any partially downloaded file on interruption, and
+# 		only download new files or newer files. 
+# Oct 25, 2018: Fix a bug reported by Tyler Anderson so that all years of S30 is now downloaded.
+
+tilePara=
+YEAR=			# Oct 25, 2018: change to uppercase because year is also used as a variable later.	
+outdir=
+if [ $# = 3 ] 
+then
+	# $1 is "-t"
+	tilePara=$2
+	OUTDIR=$3
+elif [ $# = 5 ] 
+then
+  	# $1 is "-t"
+        tilePara=$2
+        # $3 is "-y"
+        YEAR=$4
+        OUTDIR=$5
+else
+	echo "Example usage: $0 -t 11SPC /data/hls" >&2
+  	echo "               $0 -t 11SPC -y 2017 /data/hls " >&2
+  	echo "               $0 -t mytilelist -y 2017 /data/hls" >&2
+     	echo "in which " >&2
+     	echo "   11SPC is a 5-character tile ID " >&2
+     	echo "   /data/hls is the directory where to save the data" >&2
+	echo "   2017 indicates download for year 2017 only" >&2 
+     	echo "Alternatively, a text file (named mytilelist in this example) containing multiple, ">&2 
+	echo "white-space delimited tile IDs can be given in place of a single tile ID ">&2
+	echo "to download for multiple tiles." >&2
+     	exit 1
+fi
+
+set -u
+set -o pipefail
+
+### Determine wheter a tile ID is given or a file of tile IDs is given. Validate the parameters.
+case $tilePara in 
+  [0-6][0-9][A-Z][A-Z][A-Z]) all_tileids=$tilePara;;
+  *)   	if [ -f $tilePara ]
+	then
+		all_tileids=$(cat $tilePara)
+	else
+		echo "Parameter $tilePara is neither a tile ID nor a text file of tile IDs. exit" >&2
+		exit 1
+	fi
+	;;
+esac
+
+
+### wget or curl?
+which wget >/dev/null 2>&1
+WGET=$? 
[…]

### 2021-07-18 tools/filter_hls_tile.py

@@ -1,0 +1,15 @@
+import geopandas as gpd
+
+
+# Open KML support
+gpd.io.file.fiona.drvsupport.supported_drivers['KML'] = 'rw'
+
+# Filter out tiles
+tiles = gpd.read_file('data/geoms/hls_s2_tiles.kml')
+bry = gpd.read_file('data/geoms/tiles_nicfi.geojson').dissolve()
+tiles = gpd.overlay(tiles, bry, how='intersection')
+
+# Save out tiles as text
+tiles = tiles['Name']
+tiles.to_csv('data/HLS/tiles.txt',
+             header=False, sep='\t', index=False)

### 2021-07-27 docs/notebook_learn_dl_ensemble.Rmd
Fix parse dataset bug and modify a few parameters

@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_single_gl --lowest_score 9 --num_workers 32 --gpu_devices '0,1,2,3'
+python hrlcm/fit_step_lr.py --exp_name unet_slr --num_workers 32 --gpu_devices '0,1,2,3'
 ```
@@
 ```
-python hrlcm/fit_coteaching.py --exp_name unet_cot_8 --highest_score 8 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3'
+python hrlcm/fit_compose_lr.py --exp_name unet_clr --num_workers 32 --gpu_devices '0,1,2,3'
 ```

### 2021-07-27 hrlcm/utils/parse_dataset.sh

@@ -4,21 +4,12 @@
 # Parse inline input
 DIR=$1
 if [ -z "$DIR" ]; then
-    echo "`date`: Usage: $0 <Directory to download> <Type to download. \
-    {1: base dataset: validate and other necessary catalogs, \
-    2: perfect train, 3: train with quality score 9, \
-    4: train with quality score 8}>"
-    exit 1
-fi
-
-TYPE=$2
-if [ -z "$TYPE" ]; then
     echo "`date`: Usage: $0 <Directory to download>"
     exit 1
 fi
 
 echo "Download dataset to $DIR/dl_data.zip"
-curl -o "$DIR/north.zip" https://www.dropbox.com/s/bz3zcomjp6hkshw/dl_data.zip -L
+curl -o "$DIR/dl_data.zip" https://www.dropbox.com/s/bz3zcomjp6hkshw/dl_data.zip -L
 unzip $DIR/dl_data.zip -d $DIR
 rm -rf $DIR/dl_data.zip
 rm -rf $DIR/__MACOSX

### 2021-08-07 docs/manuscript_figures.Rmd
Add option to not predict scores

@@
 
+id_selected <- '1240-995'
 # Read tiles
-guess_tiles <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
-    pull(tile) %>% unique()
-nicfi_tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson')) %>% 
-    mutate(guess = ifelse(tile %in% guess_tiles, 1, 0))
-samples <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
-    filter(score > 7)
+nicfi_tiles <- read_sf(
+    here('data/geoms/tiles_nicfi_north.geojson'))
 
@@
 sub_tiling <- nicfi_tiles %>% 
-    filter(tile == '1228-999') %>% 
+    filter(tile == id_selected) %>% 
     st_make_grid(n = c(8, 8)) %>% 
@@
     mutate(index = as.vector(indices))
-
-# Weak labels
-labels_esb <- raster(here('data/north/lc_labels_north_mask.tif')) %>% 
-    crop( nicfi_tiles %>% filter(tile == '1228-999'))
-labels_guess <- raster(
-    here('results/north/prediction/classed_1228-999.tif'))
+trains_inside <- sub_tiling %>% 
+    filter(index %in% (read.csv(
+    here('results/north/dl_catalog_train.csv'),
+    stringsAsFactors = F) %>% 
+    filter(tile == id_selected) %>% 
+    pull(index))) %>% 
+    mutate(Usage = 'Train')
+valids_inside <- sub_tiling %>% 
+    filter(index %in% (read.csv(
+    here('results/north/dl_catalog_valid.csv'),
+    stringsAsFactors = F) %>% 
+    filter(tile == id_selected) %>% 
+    pull(index))) %>% 
+    mutate(Usage = 'Validate')
+# Labels of each sub-tile
+sub_tiles <- rbind(trains_inside, valids_inside) %>% 
+    arrange(index); rm(trains_inside, valids_inside)
 
@@
 sub_tiling_fg <- ggplot(sub_tiling) + 
+    geom_sf(data = sub_tiles, aes(fill = Usage),
+            color = 'blue', lwd = 0.3) +
+    scale_fill_manual(values = c('forestgreen', 'orangered')) +
     geom_sf(color = 'blue', fill = NA, lwd = 0.3) + 
@@
     theme_minimal() +
-    labs(title = 'B') +
-    theme(axis.title.x = element_blank(),
+    theme(legend.position = 'bottom',
+          axis.title.x = element_blank(),
           axis.text.x = element_blank(),
@@
 
-# Weak ensemble labels
-r_df <- as.data.frame(labels_esb, xy = TRUE) %>%
-    rename(`Weak ensemble label` = lc_labels_north_mask) %>% 
-    mutate(`Weak ensemble label` = factor(`Weak ensemble label`)) %>% 
+# Weak labels
+labels_esb <- lapply(1:nrow(sub_tiles), function(n){
+    raster(here('data/north/lc_labels_north_mask.tif')) %>% 
+        crop(sub_tiles %>% slice(n))
+}); names(labels_esb) <- sub_tiles$index
+
+labels_guess <- lapply(sub_tiles$index, function(id){
+    prefix <- glue('results/north/guess_labels/guess_{id_selected}')
+    raster(here(glue('{prefix}_{id}.tif')))
+}); names(labels_guess) <- sub_tiles$index
+
+labels_refine <- lapply(sub_tiles$index, function(id){
+    prefix <- glue('results/north/refine_labels/{id_selected}')
+    raster(here(glue('{prefix}_{id}_label.tif')))
+}); names(labels_refine) <- sub_tiles$index
+
+# Plot
+color_tb <- data.frame(
+    id = 1:7,
+    type = c("Cropland", "Forest", 
+             "Grassland", "Shrubland", 
+             "Water", 'Built-up', "Bareland"),
+    color = c('#ff7f00', '#074702', '#b2df8a',
+              '#33a02c', '#3347f9', '#5a6057',
+              '#fdbf6f'))
+plot_rst <- function(rst, bry){
+    r_df <- as.data.frame(rst, xy = TRUE) %>%
+        `colnames<-`(c('x', 'y', 'rst')) %>%
+        mutate(rst = as.factor(rst)) %>% 
         na.omit()
-weak_lb_fg <- ggplot() + 
+    colors <- color_tb %>% filter(id %in% unique(r_df$rst))
+
+    # plot
+    ggplot() + 
         geom_raster(
@@
             aes(x = x, y = y, 
-            fill = `Weak ensemble label`)) +
+                fill = rst)) +
         scale_fill_manual(
-        values = c('#ff7f00', '#33a02c', '#b2df8a',
-                   '#074702', '#0ea591'), 
-        breaks = c(1, 4, 3, 2, 5),
-        labels = c("Cropland", "Shrubland", 
-                   "Grassland", "Forest", 'Wetland')) +
-    geom_sf(data = sub_tiling, color = 'blue', 
-            fill = NA, lty = 'dotted', lwd = 0.4) +
+            values = colors %>% pull(color), 
+            breaks = colors %>% pull(id),
+            labels = colors %>% pull(type)) +
+        geom_sf(data = bry, 
+                color = 'blue', fill = NA,
+                lty = 'dotted', lwd = 0.4) +
         theme_minimal() +
@@
               plot.margin = unit(rep(0, 4),"cm"))
+}
 
-# RF guessed labels
-r_df <- as.data.frame(labels_guess, xy = TRUE) %>%
-    rename(`RF guess label` = classed_1228.999) %>% 
-    mutate(`RF guess label` = factor(`RF guess label`)) %>% 
-    na.omit()
-guess_lb_fg <- ggplot() + 
+plots_esb <- lapply(1:length(labels_esb), function(n) {
+    nm <- names(labels_guess)[n]
+    bry <- sub_tiles %>% filter(index == nm)
+    plot_rst(labels_esb[[n]], bry)
+})
+
+plots_guess <- lapply(1:length(labels_guess), function(n) {
+    nm <- names(labels_guess)[n]
+    bry <- sub_tiles %>% filter(index == nm) %>% 
+        st_transform(crs = crs(labels_guess[[n]]))
+    plot_rst(labels_guess[[n]], bry)
+})
+
+plots_refine <- lapply(1:length(labels_refine), function(n) {
+    nm <- names(labels_refine)[n]
+    bry <- sub_tiles %>% filter(index == nm) %>% 
+        st_transform(crs = crs(labels_refine[[n]]))
+    plot_rst(labels_refine[[n]], bry)
+})
+
+# Ensemble plots
+## Legend
+r_df <- data.frame(x = 1:7, 
+                   y = 1:7,
+                   rst = as.factor(1:7))
+legend_lc <- ggplot() + 
     geom_raster(
@@
         aes(x = x, y = y, 
-            fill = `RF guess label`)) +
-    scale_fill_manual(
+            fill = rst)) +
+    scale_fill_manual('Land cover',
                       values = c('#ff7f00', '#074702', '#b2df8a',
@@
                       labels = c("Cropland", 'Forest', "Grassland", 
-                   'Shrubland',  "Water", "Urban/Built-up",
+                                 'Shrubland',  "Water", "Built-up",
                                  'Bareland')) +
-    geom_sf(data = sub_tiling %>% 
-                st_transform(crs(labels_guess)), 
-            color = 'blue', 
-            fill = NA, lty = 'dotted', lwd = 0.4) +
     theme_minimal() +
-    theme(legend.position = 'none',
+    theme(legend.position = 'right',
           axis.title.x = element_blank(),
@@
           panel.grid.minor = element_blank(),
-          plot.margin = unit(rep(0, 4),"cm"))
+          plot.margin = unit(rep(0, 4),"cm"))+
+    guides(fill = guide_legend(ncol = 2))
 
-# Sample distribution
-legend_lc <- ggplot() + 
-    geom_raster(
-        data = r_df, 
-        aes(x = x, y = y, 
-            fill = `RF guess label`)) +
-    scale_fill_manual('Land cover',
-        values = c('#ff7f00', '#074702', '#b2df8a',
-                   '#33a02c', '#3347f9', '#5a6057',
-                   '#fdbf6f'), 
-        breaks = 1:7,
-        labels = c("Cropland", 'Forest', "Grassland", 
-                   'Shrubland',  "Water", "Built-up",
-                   'Bareland')) +
-    geom_sf(data = sub_tiling %>% 
-                st_transform(crs(labels_guess)), 
-            color = 'blue', 
-            fill = NA, lty = 'dotted', lwd = 0.4) +
-    theme_minimal() +
-    theme(legend.position = 'left',
-          axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(),
-          plot.margin = unit(rep(0, 4),"cm"))
 legend_lc <- get_legend(legend_lc)
+sub_tiling_fg <- ggarrange(NULL, sub_tiling_fg, legend_lc, NULL,
+                           nrow = 4, heights = c(0.3, 2, 1, 0.3))
 
-samples_fg <- ggplot() + 
-    geom_sf(data = nicfi_tiles,
-            aes(color = factor(guess),
-                lty = factor(guess)), 
-            fill = 'white', lwd = 0.4) +
-    scale_linetype_manual('Usage', values = c('solid', 'solid'),
-                          labels = c('Others', 'Guessed tile')) +
-    scale_color_manual('Usage', values = c("grey", "blue"),
-                       labels = c('Others', 'Guessed tile')) +
-    geom_sf(data = samples, aes(fill = factor(score)), color = NA) +
-    scale_fill_manual('Lable score', 
-                      values = c("#00AFBB", "#E7B800", "#FC4E07")) +
-    annotation_custom(grob = ggplotGrob(sub_tiling_fg), 
-                      xmin = 35.8, xmax = 38.2,
-                      ymin = -2.2, ymax = -0.1) +
-    labs(title = 'A') +
-    theme_minimal() +
-    theme(legend.position = 'bottom',
-          legend.box = "vertical",
-          legend.margin = margin(0, 0, 0, 0),
-          legend.box.margin = margin(-20, 2, 2, 2),
-          axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(),
-          plot.title = element_text(vjust = -6),
-          plot.margin = unit(c(0, 0, 0, 0.2),"cm"))
-    # guides(fill = guide_legend(nrow = 2, byrow = TRUE),
-    #        color = guide_legend(nrow = 2, byrow = TRUE),
-    #        linetype = guide_legend(nrow = 2, byrow = TRUE))
+esb_fg <- ggarrange(plotlist = plots_esb, ncol = 4,
+                    labels = sub_tiles$index, 
+                    hjust = -2.5)
+guess_fg <- ggarrange(plotlist = plots_guess, ncol = 4)
+refine_fg <- ggarrange(plotlist = plots_refine, ncol = 4)
+fgs <- ggarrange(esb_fg, guess_fg, refine_fg, nrow = 3,
+                 labels = c('A', 'B', 'C'),
+                 hjust = 0.4, vjust = 6,
+                 font.label = list(face = "plain"))
+labels_fg <- ggarrange(NULL, fgs, sub_tiling_fg, 
+                       ncol = 3, widths = c(0.1, 2, 1))
 
-samples_fg <- ggarrange(samples_fg, legend_lc, 
-                        nrow = 1, widths = c(1, 0.2))
-imgs <- ggarrange(weak_lb_fg, guess_lb_fg, 
-                  nrow = 2, labels = c('C', 'D'),
-                  font.label = list(face = "plain"),
-                  hjust = 0, vjust = 2)
-sample_imgs <- ggarrange(samples_fg, imgs, 
-                         ncol = 2,
-                         widths = c(2.5, 1))
-ggsave(here('docs/figures/samples_distribution.png'),
-       sample_imgs,
-       width = 8, height = 4.5, dpi = 600)
+ggsave(here('docs/figures/labels.png'),
+       labels_fg,
+       width = 8, height = 4, dpi = 300)
 ```
@@
 
-## Metrics
+## Results
+### Learning rate comparison
 
 ```{r}
+library(tidyverse)
+# Define function
+get_curves <- function(experiment_name,
+                       step = 59,
+                       path = here('results/scalar/compare_lr')){
     # Get file names
-fns <- list.files(here('results/scalars/single_compose_lr'), 
-                  pattern = 'compose_lr',
+    fns <- list.files(path, 
+                      pattern = experiment_name,
+                      full.names = T)
+    fns <- fns[str_detect(fns, 'Validate')]
+
+    # Process each csv
+    scalars <- lapply(fns, function(fn){
+        scalar <- read.csv(fn, stringsAsFactors = F) %>% 
+            mutate(Step = Step / step) %>% # step of each epoch
+            dplyr::select(-Wall.time)
+    })
+    names(scalars) <- gsub(
+        '.csv', "", 
+        str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+
+    scalars
+}
+
+# Clean scalar csvs
+curves_lr_01 <- get_curves('unet_lr_01')
+curves_lr_001 <- get_curves('unet_lr_001')
+curves_lr_0001 <- get_curves('unet_lr_0001')
+curves_lr_00001 <- get_curves('unet_lr_00001')
+curves_lr_000001 <- get_curves('unet_lr_000001')
+
+types <- c('AA', 'IoU', 'Cropland', 'Forest', 
+           'Grassland', 'Shrubland', 'Water', 
+           'Built-up', 'Bareland')
+content <- do.call(rbind, lapply(types, function(type){
+    if (type == 'Built-up') {
+        item <- 'Urban'
+        } else{item <- type}
+    list(curves_lr_01[[item]],
+         curves_lr_001[[item]],
+         curves_lr_0001[[item]],
+         curves_lr_00001[[item]],
+         curves_lr_000001[[item]]) %>% 
+        reduce(left_join, by = "Step") %>% 
+        `colnames<-`(c("Epoch", '0.1', '0.01', 
+                       '0.001', '0.0001', '0.00001')) %>% 
+        mutate(Item = type) %>% 
+        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
+                     names_to = 'Learning rate', 
+                     values_to = 'Value')
+})) %>% mutate(Item = factor(Item, levels = types))
+
+# Get final plot
+curves_lr <- ggplot(content, aes(x = Epoch, y = Value)) +
+    # geom_line(aes(color = `Learning rate`)) +
+    geom_smooth(aes(color = `Learning rate`), span = 0.2,
+                se = F, size = 0.6) +
+    scale_color_brewer(palette = "Set1") +
+    facet_wrap(~Item, scales = 'free_y') +
+    labs(y = 'Accuracy') +
+    theme_bw() +
+    theme(legend.position = 'top')
+ggsave(here('docs/figures/curves_lr.png'),
+       curves_lr,
+       width = 8, height = 5, dpi = 300)
+```
+
+### Overall results
+#### Metrics
+```{r}
+library(glue)
+# Get file names
+fns <- list.files(here(
+    file.path('results/scalar',
+              'unet_score08_hardiness20_epoch200')), 
     full.names = T)
@@
 # Metrics
-fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
+fns <- fns[str_detect(fns, 'Validate')]
 metrics_last10 <- do.call(cbind, lapply(fns, function(fn){
@@
     '.csv', "", 
-    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+    str_extract(fns, '[A-Z|a-z]{1}[A-Z|a-z]+.csv'))
 
 # Calculate mean and sd
-items <- c('AA', 'IoU', 'Cropland', 'Forest', 
+items <- c('loss', 'AA', 'mIoU', 'Cropland', 'Forest', 
            'Grassland', 'Shrubland', 'Water', 
            'Urban', 'Bareland')
-options(digits = 3)
+types <- c('Cropland', 'Forest', 
+           'Grassland', 'Shrubland', 'Water', 
+           'Built-up', 'Bareland', 'AA')
+
 tb <- do.call(rbind, lapply(items, function(item){
@@
     if (item == 'Urban') item <- 'Built-up'
+    if (item == 'loss') item <- 'Loss'
     data.frame(mean = mean(vals),
                sd = sd(vals)) %>% 
-        mutate(metric = item)
+        mutate(Metric = item)
 }))
+
+acc <- tb %>% filter(Metric %in% types) %>% 
+    mutate(mean = round(mean * 100, 2),
+           sd = round(sd * 100, 2),
+           Class = factor(Metric, levels = types),
+           Accuracy = glue(
+               paste0('{format(round(mean, digits = 2), nsmall = 2)}',
+                      '\u00B1{format(round(sd, digits = 2), nsmall = 2)} %'))) %>% 
+    dplyr::select(Class, Accuracy) %>% 
+    arrange(Class)
+write.csv(acc, here('docs/figures/acc_last10epoch.csv'),
+          row.names = F)
 ```
 
-## Scalars
+#### Scalars
 
@@
 library(here)
-
-# Single U-Net model with step learning rate
 # Get file names
-fns <- list.files(here('results/scalars/single_step_lr'), 
-                  pattern = 'step_lr',
+fns <- list.files(here(
+    file.path('results/scalar',
+              'unet_score08_hardiness20_epoch200')), 
     full.names = T)
 
+step <- 59
 # Learning rate
-step_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
-    mutate(Step = Step / 113)
+lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
+    mutate(Epoch = Step / step)
 
 # Scalars
-fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
-unet_step_lr_scalars <- lapply(fns, function(fn){
+fns <- fns[str_detect(fns, 'Validate|Train_lr')]
+final_mod_scalars <- lapply(fns, function(fn){
     scalar <- read.csv(fn, stringsAsFactors = F) %>% 
-        mutate(Step = Step / 113) %>% 
-        dplyr::select(-Wall.time)
+        mutate(Epoch = Step / step) %>% 
+        dplyr::select(-c(Wall.time, Step))
 })
-names(unet_step_lr_scalars) <- gsub(
+names(final_mod_scalars) <- gsub(
     '.csv', "", 
-    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+    str_extract(fns, '[A-Z|a-z]{1}[A-Z|a-z]+.csv'))
 
-# Single U-Net model with compose learning rate
-# Get file names
-fns <- list.files(here('results/scalars/single_compose_lr'), 
-                  pattern = 'compose_lr',
-                  full.names = T)
-
-# Learning rate
-compose_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
-    mutate(Step = Step / 113)
-
-# Scalars
-fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
-unet_compose_lr_scalars <- lapply(fns, function(fn){
-    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
-        mutate(Step = Step / 113) %>% 
-        dplyr::select(-Wall.time)
-})
-names(unet_compose_lr_scalars) <- gsub(
-    '.csv', "", 
-    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+types <- c('Learning rate', 'Loss', 'AA', 'mIoU', 'Cropland', 'Forest', 
+           'Grassland', 'Shrubland', 'Water', 
+           'Built-up', 'Bareland')
+lc <- c('Cropland', 'Forest', 
+        'Grassland', 'Shrubland', 'Water', 
+        'Built-up', 'Bareland', 'AA')
+content <- do.call(rbind, lapply(types, function(type){
+    if (type == 'Built-up') {
+        item <- 'Urban'
+    } else if (type == 'Loss'){
+        item <- 'loss'
+    } else if (type == 'Learning rate'){
+        item <- 'lr'
+    } else {item <- type}
+    final_mod_scalars[[item]] %>% 
+        mutate(Item = type)
+}))
 
 # Plot
-aa <- merge(unet_compose_lr_scalars$AA, 
-            unet_step_lr_scalars$AA, 
-            by = 'Step') %>% 
-    rename(Compose = Value.x, Cot = Value.y) %>% 
-    pivot_longer(cols = c(Compose, Cot),
-                 names_to = 'type', values_to = 'value')
-ggplot(aa, aes(x = Step, y = value)) +
-    geom_line(aes(color = type, lty = type)) +
-    geom_smooth(aes(color = type)) +
+curve_lr <- content %>% 
+    filter(Item == 'Learning rate') %>% 
+    mutate(Value = Value * 1000) %>% 
+    ggplot(., aes(x = Epoch, y = Value)) +
+    geom_line() +
+    labs(y = expression(Learning ~ rate ~ (10^-3)), x = '') +
     theme_bw()
+curve_loss <- content %>% 
+    filter(Item == 'Loss') %>% 
+    ggplot(., aes(x = Epoch, y = Value)) +
+    geom_line() +
+    labs(y = 'Loss', x = '') +
+    theme_bw()
+curve_iou <- content %>% 
+    filter(Item == 'mIoU') %>% 
+    ggplot(., aes(x = Epoch, y = Value)) +
+    geom_line() +
+    labs(y = 'mIoU', x = '') +
+    theme_bw()
+curves_acc <- content %>% 
+    filter(Item %in% lc) %>% 
+    mutate(Item = factor(Item, levels = lc)) %>% 
+    ggplot(aes(x = Epoch, y = Value)) +
+    geom_line() +
+    labs(y = 'Accuracy') +
+    facet_wrap(~Item, scales = 'free_y', 
+               nrow = 2, ncol = 4) +
+    theme_bw()
+curves <- ggarrange(
+    ggarrange(curve_lr, curve_loss, curve_iou, ncol = 3),
+    curves_acc, nrow = 2, heights = c(1, 1.6))
+
+ggsave(here('docs/figures/curves_final_mod.png'),
+       curves,
+       width = 8, height = 5, dpi = 300)
 ```
+
+## Sensitivity analysis
+### Quality weights
+#### Score factor
+```{r}
+# Clean scalar csvs
+curves_no_weight <- get_curves(
+    'unet_no_weight',
+    path = here('results/scalar/compare_score'))
+curves_score02 <- get_curves(
+    'unet_score_02',
+    path = here('results/scalar/compare_score'))
+curves_score08 <- get_curves(
+    'unet_score_08',
+    path = here('results/scalar/compare_score'))
+curves_score16 <- get_curves(
+    'unet_score_16',
+    path = here('results/scalar/compare_score'))
+curves_score32 <- get_curves(
+    'unet_score_32',
+    path = here('results/scalar/compare_score'))
+curves_score100 <- get_curves(
+    'unet_score_100',
+    path = here('results/scalar/compare_score'))
+
+types <- c('AA', 'IoU', 'Cropland', 'Forest', 
+           'Grassland', 'Shrubland', 'Water', 
+           'Built-up', 'Bareland')
+content <- do.call(rbind, lapply(types, function(type){
+    if (type == 'Built-up') {
+        item <- 'Urban'
+        } else{item <- type}
+    list(curves_no_weight[[item]],
+         curves_score02[[item]],
+         curves_score08[[item]],
+         curves_score16[[item]],
+         curves_score32[[item]],
+         curves_score100[[item]]) %>% 
+        reduce(left_join, by = "Step") %>% 
+        `colnames<-`(c("Epoch", '0', '0.2', '0.8', 
+                       '1.6', '3.2', '10')) %>% 
+        mutate(Item = type) %>% 
+        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
+                     names_to = 'Weight factor', 
+                     values_to = 'Value')
+})) %>% mutate(Item = factor(Item, levels = types),
+               `Weight factor` = factor(
+                   `Weight factor`, 
+                   levels = c('0', '0.2', '0.8', 
+                              '1.6', '3.2', '10')))
+
+# Get final plot
+curves_score <- ggplot(content, aes(x = Epoch, y = Value)) +
+    # geom_line(aes(color = `Weight factor`)) +
+    geom_smooth(aes(color = `Weight factor`), span = 0.2,
+                se = F, size = 0.6) +
+    scale_color_manual(
+        values = c('Black', 
+                   RColorBrewer::brewer.pal(5, "Dark2"))) +
+    # scale_color_brewer(palette = "Dark2") +
+    facet_wrap(~Item, scales = 'free_y') +
+    labs(y = 'Accuracy') +
+    theme_bw() +
+    theme(legend.position = 'top') +
+    guides(color = guide_legend(nrow = 1))
+ggsave(here('docs/figures/curves_score.png'),
+       curves_score,
+       width = 8, height = 5, dpi = 300)
+```
+
+#### Hardiness
+```{r}
+# Clean scalar csvs
+curves_score08_nohard <- get_curves(
+    'unet_score_08',
+    path = here('results/scalar/compare_score'))
+curves_hard2 <- get_curves(
+    'unet_score08_hardiness_2',
+    path = here('results/scalar/compare_score'))
+curves_hard4 <- get_curves(
+    'unet_score08_hardiness_4',
+    path = here('results/scalar/compare_score'))
+curves_hard6 <- get_curves(
+    'unet_score08_hardiness_6',
+    path = here('results/scalar/compare_score'))
+
+types <- c('AA', 'IoU', 'Cropland', 'Forest', 
+           'Grassland', 'Shrubland', 'Water', 
+           'Built-up', 'Bareland')
+content <- do.call(rbind, lapply(types, function(type){
+    if (type == 'Built-up') {
+        item <- 'Urban'
+        } else{item <- type}
+    list(curves_score08_nohard[[item]],
+         curves_hard2[[item]],
+         curves_hard4[[item]],
+         curves_hard6[[item]]) %>% 
+        reduce(left_join, by = "Step") %>% 
+        `colnames<-`(c("Epoch", '0', '2', '4', '6')) %>% 
+        mutate(Item = type) %>% 
+        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
+                     names_to = 'Weight scale', 
+                     values_to = 'Value')
+})) %>% mutate(Item = factor(Item, levels = types),
+               `Weight scale` = factor(
+                   `Weight scale`, 
+                   levels = c('0', '2', '4', '6')))
+
+# Get final plot
+curves_hard <- ggplot(content, aes(x = Epoch, y = Value)) +
+    geom_smooth(aes(color = `Weight scale`), span = 0.2,
+                se = F, size = 0.6) +
+    scale_color_manual(
+        values = c('Black', 
+                   RColorBrewer::brewer.pal(3, "Dark2"))) +
+    # scale_color_brewer(palette = "Dark2") +
+    facet_wrap(~Item, scales = 'free_y') +
+    labs(y = 'Accuracy') +
+    theme_bw() +
+    theme(legend.position = 'top') +
+    guides(color = guide_legend(nrow = 1))
+ggsave(here('docs/figures/curves_hard.png'),
+       curves_hard,
+       width = 8, height = 5, dpi = 300)
+```
+
+### Sampling
+
+```{r}
+
+```

### 2021-08-07 docs/notebook_learn_dl_ensemble.Rmd
Overfitting
Add option to not predict scores

@@
 
-scp -r /Users/pinot/Dropbox/research/hrlcm/results/north/norm_stats ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
-
-scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train.csv ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
-
-scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_valid.csv ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
+scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_1.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_1.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_2.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_2.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_34.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_random_34.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_67.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_random_67.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv
 ```
@@
 ```
-python hrlcm/fit_step_lr.py --exp_name unet_slr --num_workers 32 --gpu_devices '0,1,2,3'
+python hrlcm/fit_step_lr.py --exp_name unet_one_tile --num_workers 32 --gpu_devices '0,1,2,3'
 ```
@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_clr --num_workers 32 --gpu_devices '0,1,2,3'
+python hrlcm/fit_compose_lr.py --exp_name unet_score08_hardiness2_epoch300 --num_workers 32 --gpu_devices '0,1,2,3'
 ```
@@
 python hrlcm/predict.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+
+scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200
 ```
@@
 ```
+scp /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200/checkpoints/final.pth ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/dl/final.pth;
+scp /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200/checkpoints/args.pkl ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/dl/args.pkl
+
 python hrlcm/evaluate.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+
+scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/evaluation /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200
 ```

### 2021-08-07 guess_model/9_2_train_sampling.R

@@ -23,79 +23,102 @@ tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson'))
 trains <- read.csv(here('results/north/dl_catalog_train.csv'))
 valids <- read.csv(here('results/north/dl_catalog_valid.csv'))
 
-# Check number of tiles
-# The ratio is about 0.3, so we start test the sampling ratio from 0.4.
-nrow(valids) / nrow(trains)
+##############################
+##  Step 3: Sampling ratio  ##
+##############################
+# Reduce sub tile number within each tile
+# Still use all tiles over study area
 
-########################
-##  Step 3: Sampling  ##
-########################
+message('--One each tile')
+set.seed(10)
+trains_1 <- trains %>% 
+    group_by(tile) %>% 
+    do(sample_n(., 1)) %>% 
+    ungroup()
+write.csv(
+    trains_1, 
+    here('results/north/dl_catalog_train_1.csv'))
 
-# Random sampling
-message('--Random sampling')
-message('----Ratio 0.4')
+message('--Two each tile')
+set.seed(11)
+trains_2 <- trains %>% 
+    group_by(tile) %>% 
+    do(sample_n(., 2)) %>% 
+    ungroup()
+write.csv(
+    trains_2, 
+    here('results/north/dl_catalog_train_2.csv'))
 
+# Sample tiles, and select 3 sub-tiles from each
+# Sampling tiles is a bit faster to generate guess label
+# and maybe a bit faster for human checking
+# However, might be less representative.
+message('--Sampling tiles')
+
+# Comparing to one from each tile
+message('----Ratio 0.34')
 set.seed(10)
 tiles_selected <- tiles %>% 
-    sample_frac(0.4)
+    sample_frac(0.34)
 trains_selected <- trains %>% 
     filter(tile %in% tiles_selected$tile)
 write.csv(
     trains_selected, 
-    here('results/north/dl_catalog_train_random_04.csv'))
+    here('results/north/dl_catalog_train_random_34.csv'))
 
-message('----Ratio 0.6')
-
+# Comparing to two from each tile
+message('----Ratio 0.67')
 set.seed(11)
 tiles_selected <- tiles %>% 
-    sample_frac(0.6)
+    sample_frac(0.67)
 trains_selected <- trains %>% 
     filter(tile %in% tiles_selected$tile)
 write.csv(
     trains_selected, 
[…]

### 2021-08-07 hrlcm/dataset.py

@@ -4,6 +4,7 @@ Author: Lei Song
 Maintainer: Lei Song (lsong@clarku.edu)
 """
 
+import math
 import os
 import sys
 import itertools
@@ -11,6 +12,19 @@ import pandas as pd
 import rasterio
 from torch.utils.data import Dataset
 from rasterio.plot import reshape_as_image
+
+
+def logistic_scale(x, L=1, k=1.5, x0=2.5):
+    """Util function to scale data using logistic
+    Args:
+        x (numpy.ndarray): the array to scale
+        L (float): the curve's maximum value
+        k (float): logistic growth rate
+        x0 (float): the x value of the sigmoid midpoint
+    Returns:
+        numpy.ndarray: the array of image values
+    """
+    return L / (1 + math.e ** (-k * (x - x0)))
 
 
 def load_sat(path):
@@ -115,8 +129,8 @@ class NFSEN1LC(Dataset):
 
     def __init__(self, data_dir,
                  usage='train',
-                 score_factor=0.8,  # max score is 5, so 2.
-                 hardiness_max=2,
+                 score_k=1.5,
+                 hardiness_max=1.2,
                  random_state=1,
                  label_offset=1,
                  sync_transform=None,
@@ -127,12 +141,11 @@ class NFSEN1LC(Dataset):
         Args:
             data_dir (str): the directory of all data
             usage (str): Usage of the dataset : "train", "validate" or "predict"
-            score_factor (float): the ratio to multiply with score as weight for loss calculation.
-                E.g. score = 4, then weight = score * score_factor = 4 * 0.2 = 0.8.
+            score_k (float): the k param of logistic scale to calculate weight of score.
             hardiness_max (float): the rescaled max of hardiness as weight for loss calculation.
                 Must be larger than 1 to be effective, otherwise no weight affect.
-                E.g. score = 4, and hardiness = 3,
-                then weight = score * score_factor * ((hardiness_max - 1) * (hardiness - 1) / (max(hardiness) - 1) + 1)
+                E.g.hardiness = 3,
+                then weight = ((hardiness_max - 1) * (hardiness - 1) / (max(hardiness) - 1) + 1)
                 = 4 * 0.2 * ((2 - 1) * (4 - 1) / (5 - 1) + 1) = 1.4
             random_state (int): the random state for pandas sampling.
             label_offset (int): the offset of label to minus in order to fit into DL model.
@@ -146,7 +159,7 @@ class NFSEN1LC(Dataset):
[…]

### 2021-08-07 hrlcm/fit_step_lr.py

@@ -38,8 +38,9 @@ def main():
     parser.add_argument('--quality_weight', type=int, default=1,
                         help='whether to use quality as weight to calculate loss '
                              '(0 for no, 1 for yes). (default: 1)')
-    parser.add_argument('--score_factor', type=float, default=0.8,
-                        help='ratio to multiply with score, see details in dataset. (default: 0.8)')
+    parser.add_argument('--score_k', type=float, default=1.5,
+                        help='k param of logistic scale to calculate score weight, '
+                             'see details in dataset. (default: 1.5)')
     parser.add_argument('--hardiness_max', type=float, default=2,
                         help='ratio to multiply with hardiness, see details in dataset (default: 2)')
     parser.add_argument('--label_offset', type=int, default=1,
@@ -142,7 +143,7 @@ def main():
     # Get train dataset
     train_dataset = NFSEN1LC(data_dir=args.data_dir,
                              usage='train',
-                             score_factor=args.score_factor,
+                             score_k=args.score_k,
                              hardiness_max=args.hardiness_max,
                              label_offset=args.label_offset,
                              sync_transform=sync_transform,

### 2021-08-07 hrlcm/predict.py

@@ -39,6 +39,10 @@ def main():
                         help='number of worker(s) to load dataset (default: 0)')
     parser.add_argument('--label_offset', type=int, default=1,
                         help='offset value to minus from label in order to start from 0 (default: 1)')
+    parser.add_argument('--score_type', type=str, default='overall',
+                        help='format of score maps. ["overall", "each", "none"], '
+                             'overall, overall score map; each: score map of each class,'
+                             'none: no score map. (default: overall)')
 
     # Hyper-parameters of GPU
     parser.add_argument('--batch_size', type=int, default=16,
@@ -47,6 +51,8 @@ def main():
                         help='the gpu devices to use (default: None) (format: 1, 2)')
 
     args = parser.parse_args()
+    assert args.score_type in ["overall", "each", "none"]
+
     print("=" * 20, "PREDICTION CONFIG", "=" * 20)
     for arg in vars(args):
         print('{0:20}  {1}'.format(arg, getattr(args, arg)))
@@ -164,24 +170,30 @@ def main():
                     out_predict = out_predict.astype(np.int8)
                     canvas[:, index[0]: index[0] + sw, index[1]: index[1] + sh] = out_predict
 
-                    # scores for each non-background class
-                    for n in range(n_class):
-                        out_score = out[:, n, :, :].data[i][:, :].cpu().numpy() * 100
-                        out_score = np.expand_dims(out_score, axis=0).astype(np.int8)
-                        try:
-                            canvas_score_ls[n][:, index[0]: index[0] + sw, index[1]: index[1] + sh] = out_score
-                        except:
-                            canvas_score_single = np.zeros((1, meta['height'], meta['width']), dtype=meta['dtype'])
-                            canvas_score_single[:, index[0]: index[0] + sw, index[1]: index[1] + sh] = out_score
-                            canvas_score_ls.append(canvas_score_single)
+                    if args.score_type != 'none':
+                        # scores for each non-background class
+                        for n in range(n_class):
+                            out_score = out[:, n, :, :].data[i][:, :].cpu().numpy() * 100
+                            out_score = np.expand_dims(out_score, axis=0).astype(np.int8)
+                            try:
+                                canvas_score_ls[n][:, index[0]: index[0] + sw, index[1]: index[1] + sh] = out_score
+                            except:
[…]

### 2021-08-07 docs/notebook_learn_dl_ensemble.Rmd
Update dataset parse

@@
 python hrlcm/fit_compose_lr.py --exp_name unet_score08_hardiness2_epoch300 --num_workers 32 --gpu_devices '0,1,2,3'
+```
+
+- Learning rates
+
+```
+python hrlcm/fit_step_lr.py --exp_name unet_lr_01 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.1 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.01 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_0001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_00001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_000001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.00001 --gamma_lr 1 --epochs 51
 ```

### 2021-08-07 hrlcm/utils/parse_dataset.sh

@@ -9,7 +9,7 @@ if [ -z "$DIR" ]; then
 fi
 
 echo "Download dataset to $DIR/dl_data.zip"
-curl -o "$DIR/dl_data.zip" https://www.dropbox.com/s/bz3zcomjp6hkshw/dl_data.zip -L
+curl -o "$DIR/dl_data.zip" https://www.dropbox.com/s/u9ef5nb4a9htegc/dl_data.zip -L
 unzip $DIR/dl_data.zip -d $DIR
 rm -rf $DIR/dl_data.zip
 rm -rf $DIR/__MACOSX

### 2021-08-09 docs/notebook_learn_dl_ensemble.Rmd
Update scheduler

@@
 python hrlcm/fit_step_lr.py --exp_name unet_lr_01 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.1 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.01 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_0001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_00001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_000001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.00001 --gamma_lr 1 --epochs 51
+```
+
+```
+python hrlcm/predict.py --args_path 'results/dl/unet_lr_00001/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_lr_00001/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
 ```

### 2021-08-09 guess_model/7_pred_guess_model.R

@@ -1,6 +1,7 @@
 # Title     : Script to make guess labels
 # Objective : To use random forest guesser
-#             to get new labels.
+#             to get new labels. At this stage,
+#             we used Google Open Buildings as built-up label
 # Created by: Lei Song
 # Created on: 02/24/21
 
@@ -223,8 +224,30 @@ roads <- roads %>%
 roads <- st_join(roads, tiles)
 waterbodies <- read_sf(here('data/osm/waterbodies.geojson'))
 waterbodies <- st_join(waterbodies, tiles)
-buildings <- read_sf(here('data/osm/buildings.geojson'))
-buildings <- st_join(buildings, tiles)
+# buildings <- read_sf(here('data/osm/buildings.geojson'))
+# buildings <- st_join(buildings, tiles)
+# Change to use Open Buildings dataset
+### Follow the tutorial to download Google Open Buildings dataset 
+## https://sites.research.google/open-buildings/ 
+fn <- 'open_buildings_v1_polygons_ne_10m_TZA.csv'
+buildings <- st_read(here(file.path('data/open_buildings', fn)),
+                  int64_as_string = F,
+                  stringsAsFactors = F); rm(fn)
+buildings <- buildings %>% 
+    mutate(latitude = as.numeric(latitude),
+           longitude = as.numeric(longitude),
+           area_in_meters = as.numeric(area_in_meters),
+           confidence = as.numeric(confidence)) %>% 
+    # Buildings with area less than a pixel might not be representative
+    filter(confidence >= 0.75 & area_in_meters > 4.8^2) %>% 
+    mutate(geometry = st_as_sfc(geometry) %>% 
+               st_cast('MULTIPOLYGON')) %>% 
+    st_as_sf() %>% st_set_crs(4326) %>% 
+    st_make_valid()
+
+builds <- st_crop(builds, st_bbox(tiles))
+builds <- st_join(builds, tiles)
+# write_sf(buildings, here('data/open_buildings/buildings_tza.geojson'))
 
 # Cut the tiles and make 4 samples
 # 3 for train, 1 for validate

### 2021-08-09 hrlcm/fit_compose_lr.py

@@ -35,7 +35,7 @@ def main():
                         help='path to dataset (default: results/north)')
     parser.add_argument('--out_dir', type=str, default="results/dl",
                         help='path to output dir (default: results/dl)')
-    parser.add_argument('--quality_weight', type=int, default=1,
+    parser.add_argument('--quality_weight', type=int, default=0,
                         help='whether to use quality as weight to calculate loss '
                              '(0 for no, 1 for yes). (default: 1)')
     parser.add_argument('--score_k', type=float, default=1.5,
@@ -77,9 +77,9 @@ def main():
                         help='batch size for training (default: 16)')
     parser.add_argument('--val_batch_size', type=int, default=32,
                         help='batch size for validation (default: 16)')
-    parser.add_argument('--epochs', type=int, default=300,
-                        help='number of training epochs (default: 300). '
-                             'NOTE: The scheduler is designed best for 300.')
+    parser.add_argument('--epochs', type=int, default=400,
+                        help='number of training epochs (default: 400). '
+                             'NOTE: The scheduler is designed best for 400.')
     parser.add_argument('--resume', '-r', type=str, default=None,
                         help='path to the pretrained weights file')
 
@@ -255,7 +255,7 @@ def main():
     if args.quality_weight == 1:
         weight = torch.from_numpy(train_dataset.weight)
     else:
-        weight = torch.from_numpy(np.ones(len(train_dataset.weight)))
+        weight = None
     for epoch in range(epoch + 1, args.epochs):
         # Update info
         print("[Epoch {}] lr: {}".format(

### 2021-08-09 hrlcm/fit_step_lr.py

@@ -257,7 +257,7 @@ def main():
     if args.quality_weight == 1:
         weight = torch.from_numpy(train_dataset.weight)
     else:
-        weight = torch.from_numpy(np.ones(len(train_dataset.weight)))
+        weight = None
     for epoch in range(epoch + 1, args.epochs):
         # Update info
         print("[Epoch {}] lr: {}".format(

### 2021-08-09 hrlcm/lr_scheduler.py

@@ -2,7 +2,7 @@ import torch
 import torch_optimizer as optim
 
 
-def get_compose_lr(model, epochs, min_lr=0.0001, max_lr=0.001, stage1=30, stage2=130, stage3=170):
+def get_compose_lr(model, epochs, min_lr=0.0001, max_lr=0.001, stage1=60, stage2=260, stage3=340):
     """Util function to customize a learning rate scheduler.
     Note: not a perfect function, user could customize this function based on needs.
         Args:

### 2021-08-09 docs/notebook_learn_dl_ensemble.Rmd
Weighted loss seems to have an issue, not a big deal though

--- 2021-08-07 docs/notebook_learn_dl_ensemble.Rmd
@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_score08_hardiness2_epoch300 --num_workers 32 --gpu_devices '0,1,2,3'
+python hrlcm/fit_compose_lr.py --exp_name unet_no_weight_epoch400 --num_workers 32 --gpu_devices '0,1,2,3'
 ```
@@
 python hrlcm/fit_step_lr.py --exp_name unet_lr_01 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.1 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.01 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_0001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_00001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_000001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.00001 --gamma_lr 1 --epochs 51
+```
+
+```
+python hrlcm/predict.py --args_path 'results/dl/unet_no_weight_epoch400/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_no_weight_epoch400/checkpoints/interim.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
 ```

### 2021-08-09 hrlcm/loss.py

@@ -65,8 +65,8 @@ def weighted_loss(predict, target, weights=None):
             # An arbitrary way to set dims
             loss_each = loss_fn(torch.unsqueeze(predict[i, :, :, :], 0),
                                 torch.unsqueeze(target[i, :, :], 0))
-            loss_each = loss_each * weights[i]
+            loss_each *= weights[i]
             loss_total += loss_each
-        loss = loss_total / len(weights)
+        loss = loss_total / sum(weights)
 
     return loss

### 2021-08-09 hrlcm/lr_scheduler.py

@@ -2,7 +2,7 @@ import torch
 import torch_optimizer as optim
 
 
-def get_compose_lr(model, epochs, min_lr=0.0001, max_lr=0.001, stage1=60, stage2=260, stage3=340):
+def get_compose_lr(model, epochs, min_lr=0.0001, max_lr=0.001, stage1=60, stage2=150, stage3=200):
     """Util function to customize a learning rate scheduler.
     Note: not a perfect function, user could customize this function based on needs.
         Args:

### 2021-08-10 docs/notebook_learn_dl_ensemble.Rmd
Finalize the weighted loss

--- 2021-08-07 docs/notebook_learn_dl_ensemble.Rmd
@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_score08_hardiness2_epoch300 --num_workers 32 --gpu_devices '0,1,2,3'
+python hrlcm/fit_compose_lr.py --exp_name unet_no_weight_epoch400 --num_workers 32 --gpu_devices '0,1,2,3'
 ```
 
-- Learning rates
+- Weights
 
 ```
-python hrlcm/fit_step_lr.py --exp_name unet_lr_01 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.1 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.01 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_0001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_00001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_000001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.00001 --gamma_lr 1 --epochs 51
+python hrlcm/fit_step_lr.py --exp_name unet_k05_only --quality_weight 1 --score_k 0.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k15_only --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k3_only --quality_weight 1 --score_k 3.0 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
+```
+
+```
+python hrlcm/fit_step_lr.py --exp_name unet_k15_only --quality_weight 1 --score_k 1.5 --hardiness_max 1.1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k15_only --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k15_only --quality_weight 1 --score_k 1.5 --hardiness_max 1.4 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
+```
+
+```
+python hrlcm/predict.py --args_path 'results/dl/unet_k3_only/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k3_only/checkpoints/interim.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
 ```

### 2021-08-10 hrlcm/dataset.py

@@ -198,10 +198,10 @@ class NFSEN1LC(Dataset):
 
             # Set score, hardiness and loss weights
             self.score = self.catalog['score'].to_numpy()
-            self.score_weight = logistic_scale(self.score, self.score_k)
+            self.score_weight = logistic_scale(self.score, k=self.score_k)
             self.hardiness = self.catalog['hardiness'].to_numpy()
             self.hardiness_weight = (self.hardiness_max - 1) * (self.hardiness - 1) / (max(self.hardiness) - 1) + 1
-            self.weight = self.score * self.score_weight * self.hardiness_weight
+            self.weight = self.score_weight * self.hardiness_weight
         elif self.usage == 'validate':
             self.catalog = catalog_full
         # Prediction

### 2021-08-10 hrlcm/loss.py

@@ -75,10 +75,9 @@ def weighted_loss(predict, target, weights=None, ignore_index=-100):
         loss_fn = BalancedCrossEntropyLoss(ignore_index=ignore_index, reduction='none')
         
         loss = loss_fn(predict, target)
-        # Mean through classes
-        loss = torch.sum(loss, (1, 2)) / lossWeight.sum()
-        # Mean through image
-        loss = (loss * weights) / weights.sum()
-        loss = loss.mean()
+        # Multiply image weights
+        loss = torch.sum(loss, (1, 2)) * weights
+        # Mean through batch
+        loss = loss.sum() / (lossWeight * unique_counts).sum()
 
     return loss

### 2021-08-12 docs/notebook_learn_dl_ensemble.Rmd
Milestone mark

--- 2021-08-09 docs/notebook_learn_dl_ensemble.Rmd
@@
 scp -r /Volumes/wildebeest/dl_valid ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
-
-scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_1.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_1.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_2.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_2.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_34.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_random_34.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_67.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_random_67.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv
 ```
@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_score08_hardiness2_epoch300 --num_workers 32 --gpu_devices '0,1,2,3'
+python hrlcm/fit_compose_lr.py --exp_name unet_k15_hard12_clr_200epc --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
 ```
 
-- Learning rates
+- Weights
 
+Score
 ```
-python hrlcm/fit_step_lr.py --exp_name unet_lr_01 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.1 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.01 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_0001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_00001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 51; python hrlcm/fit_step_lr.py --exp_name unet_lr_000001 --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.00001 --gamma_lr 1 --epochs 51
+python hrlcm/fit_step_lr.py --exp_name unet_no_weight --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k05_only --quality_weight 1 --score_k 0.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k15_only --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k3_only --quality_weight 1 --score_k 3.0 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
+```
+
+Hardiness
+```
+python hrlcm/fit_step_lr.py --exp_name unet_k15_hard11 --quality_weight 1 --score_k 1.5 --hardiness_max 1.1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k15_hard12 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k15_hard14 --quality_weight 1 --score_k 1.5 --hardiness_max 1.4 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
 ```
@@
 ```
-python hrlcm/predict.py --args_path 'results/dl/unet_lr_00001/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_lr_00001/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+python hrlcm/predict.py --args_path 'results/dl/unet_k3_only/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k3_only/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+```
+
+- Sampling
+
+```
+scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_1.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_2.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_34.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_67.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
+```
+
+```
+python hrlcm/fit_step_lr.py --exp_name unet_one_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_2.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_two_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
 ```
@@
 ```
-python hrlcm/predict.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
 
@@
 
-python hrlcm/evaluate.py --args_path 'results/dl/args.pkl' --checkpoint_file 'results/dl/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+python hrlcm/evaluate.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
 

### 2021-08-12 guess_model/9_2_train_sampling.R

@@ -15,6 +15,7 @@ library(here)
 library(sf)
 library(dplyr)
 library(stringr)
+library(tidyverse)
 
 ##########################
 ##  Step 2: Read files  ##

### 2021-08-12 docs/notebook_learn_dl_ensemble.Rmd
Try replicate pad

@@
 
+#### Test
+
+```
+python hrlcm/predict.py --args_path 'results/dl/unet_no_weight/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_no_weight/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_no_weight' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+
+python hrlcm/predict.py --args_path 'results/dl/unet_k05_only/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k05_only/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k05_only' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+
+python hrlcm/predict.py --args_path 'results/dl/unet_k15_only/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_only/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_only' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+
+python hrlcm/predict.py --args_path 'results/dl/unet_k3_only/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k3_only/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k3_only' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+
+python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard11/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard11/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard11' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+
+python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard12' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+
+python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard14/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard14/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard14' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+```
+
 #### Evaluation

### 2021-08-12 hrlcm/models/utils/unet_parts.py

@@ -14,10 +14,12 @@ class DoubleConv(nn.Module):
     def __init__(self, in_channels, out_channels):
         super().__init__()
         self.double_conv = nn.Sequential(
-            nn.Conv2d(in_channels, out_channels, kernel_size=3, padding=1),
+            nn.Conv2d(in_channels, out_channels, kernel_size=3,
+                      padding=1, padding_mode='replicate'),
             nn.BatchNorm2d(out_channels),
             nn.ReLU(inplace=True),
-            nn.Conv2d(out_channels, out_channels, kernel_size=3, padding=1),
+            nn.Conv2d(out_channels, out_channels, kernel_size=3,
+                      padding=1, padding_mode='replicate'),
             nn.BatchNorm2d(out_channels),
             nn.ReLU(inplace=True)
         )

### 2021-08-14 docs/notebook_learn_dl_ensemble.Rmd
Revert back to regular unet

@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_k15_hard12_clr_200epc --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
+python hrlcm/fit_compose_lr.py --exp_name unet_k15_hard12_clr_rep_pad_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 221 --tain_batch_size 16
 ```
@@
 python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard14/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard14/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard14' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+
+python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12_clr_rep_pad_220epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_rep_pad_220epc/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard14' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
 ```

### 2021-08-16 docs/notebook_learn_dl_ensemble.Rmd
Remove an assert check

@@
 
-Prepare work:
+Parse dataset:
 
 ```
-scp -r /Volumes/wildebeest/dl_train ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
-
-scp -r /Volumes/wildebeest/dl_valid ubuntu@ec2-3-19-239-231.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
+./hrlcm/utils/parse_dataset.sh results/north
 ```
@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_k15_hard12_clr_rep_pad_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 221 --tain_batch_size 16
+python hrlcm/fit_compose_lr.py --exp_name unet_k15_hard12_clr_rep_pad_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
 ```
@@
 python hrlcm/fit_step_lr.py --exp_name unet_k15_hard11 --quality_weight 1 --score_k 1.5 --hardiness_max 1.1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k15_hard12 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k15_hard14 --quality_weight 1 --score_k 1.5 --hardiness_max 1.4 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
-```
-
-```
-python hrlcm/predict.py --args_path 'results/dl/unet_k3_only/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k3_only/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
 ```
@@
 
-scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200
+scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/dl
 ```
@@
 
-python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12_clr_rep_pad_220epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_rep_pad_220epc/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard14' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard12_clr_200epc' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
 ```
@@
 ```
-scp /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200/checkpoints/final.pth ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/dl/final.pth;
-scp /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200/checkpoints/args.pkl ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/dl/args.pkl
-
 python hrlcm/evaluate.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'

### 2021-08-17 docs/notebook_learn_dl_ensemble.Rmd
Some updates due to former changes

@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_k15_hard12_clr_rep_pad_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
+python hrlcm/fit_compose_lr.py --exp_name unet_k15_only_clr_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
 ```
@@
 ```
-scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_1.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_2.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_34.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_67.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv ubuntu@ec2-3-16-90-184.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
+scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_1.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_2.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_34.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_67.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
 ```
@@
 ```
-python hrlcm/fit_step_lr.py --exp_name unet_one_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_2.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_two_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
+mv results/north/dl_catalog_train.csv results/north/dl_catalog_train_full.csv; mv results/north/dl_catalog_train_1.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_one_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_2.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_two_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
 ```

### 2021-08-17 hrlcm/predict.py

@@ -203,6 +203,8 @@ def main():
                 dst.write(canvas_score)
 
         del predict_dataset, predict_loader
+        # for fname in catalog.loc[catalog['tile_id'] == tile_id]['tiles_relate'].item().split(','):
+        #     os.remove(os.path.join(args.data_path, fname))
 
 
 if __name__ == "__main__":

### 2021-08-17 tools/generate_predict_catalog.R

@@ -73,11 +73,11 @@ write.csv(dl_catalog_full,
           row.names = F)
 
 # A test dataset
-set.seed(10)
+set.seed(123)
 tiles_test <- read.csv(here('results/north/dl_catalog_valid.csv'),
                        stringsAsFactors = F) %>% 
   group_by(hardiness) %>% 
-  sample_n(4)
+  sample_n(3)
 dl_catalog_test <- dl_catalog_full %>% 
   filter(tile_id %in% tiles_test$tile)
 write.csv(dl_catalog_test, 

### 2021-10-08 docs/manuscript_figures.Rmd
Update docs for manuscript and tools to get final produ ct

@@
 ## Results
-### Learning rate comparison
+### Random forest evaluation
+#### Holdout validate
 
 ```{r}
-library(tidyverse)
-# Define function
-get_curves <- function(experiment_name,
-                       step = 59,
-                       path = here('results/scalar/compare_lr')){
-    # Get file names
-    fns <- list.files(path, 
-                      pattern = experiment_name,
-                      full.names = T)
-    fns <- fns[str_detect(fns, 'Validate')]
-
-    # Process each csv
-    scalars <- lapply(fns, function(fn){
-        scalar <- read.csv(fn, stringsAsFactors = F) %>% 
-            mutate(Step = Step / step) %>% # step of each epoch
-            dplyr::select(-Wall.time)
+load(here("data/north/final_res.rda"))
+cf <- confusionMatrix(data = final_res$.predictions[[1]]$.pred_class, 
+                      reference = final_res$.predictions[[1]]$landcover)
+save(cf, file = here('docs/figures/rf_holdout_conf.rda'))
+
+conf <- cf$table
+# row is truth, column is predict
+# match with python sklearn
+conf <- matrix(as.numeric(conf), nrow = nrow(conf), ncol = ncol(conf))
+conf <- t(conf)
+
+# Calculate producer's accuracy
+prac <- sapply(1:7, function(n){
+  conf[n, n] / rowSums(conf)[n]
 })
-    names(scalars) <- gsub(
-        '.csv', "", 
-        str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
-
-    scalars
-}
-
-# Clean scalar csvs
-curves_lr_01 <- get_curves('unet_lr_01')
-curves_lr_001 <- get_curves('unet_lr_001')
-curves_lr_0001 <- get_curves('unet_lr_0001')
-curves_lr_00001 <- get_curves('unet_lr_00001')
-curves_lr_000001 <- get_curves('unet_lr_000001')
-
-types <- c('AA', 'IoU', 'Cropland', 'Forest', 
-           'Grassland', 'Shrubland', 'Water', 
-           'Built-up', 'Bareland')
-content <- do.call(rbind, lapply(types, function(type){
-    if (type == 'Built-up') {
-        item <- 'Urban'
-        } else{item <- type}
-    list(curves_lr_01[[item]],
-         curves_lr_001[[item]],
-         curves_lr_0001[[item]],
-         curves_lr_00001[[item]],
-         curves_lr_000001[[item]]) %>% 
-        reduce(left_join, by = "Step") %>% 
-        `colnames<-`(c("Epoch", '0.1', '0.01', 
-                       '0.001', '0.0001', '0.00001')) %>% 
-        mutate(Item = type) %>% 
-        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
-                     names_to = 'Learning rate', 
-                     values_to = 'Value')
-})) %>% mutate(Item = factor(Item, levels = types))
-
-# Get final plot
-curves_lr <- ggplot(content, aes(x = Epoch, y = Value)) +
-    # geom_line(aes(color = `Learning rate`)) +
-    geom_smooth(aes(color = `Learning rate`), span = 0.2,
-                se = F, size = 0.6) +
-    scale_color_brewer(palette = "Set1") +
-    facet_wrap(~Item, scales = 'free_y') +
-    labs(y = 'Accuracy') +
-    theme_bw() +
-    theme(legend.position = 'top')
-ggsave(here('docs/figures/curves_lr.png'),
-       curves_lr,
-       width = 8, height = 5, dpi = 300)
+
+acc_test <- data.frame(class = 1:7,
+                       producer_acc = prac)
+write.csv(acc_test, here('docs/figures/rf_holdout_acc.csv'),
+          row.names = F)
+```
+
+#### Independent test
+
+```{r}
+library(terra)
+library(parallel)
+library(ramify)
+library(ranger)
+library(parsnip)
+library(tidymodels)
+library(caret)
+
+tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson'))
+imgs <- rast(file.path(
+        "/Volumes/elephant/pred_stack",
+        paste0(tiles$tile[1], ".tif")))
+sample_test <- read_sf(here('data/north/plys_holdout_check.geojson')) %>% 
+  st_join(tiles) %>% st_transform(crs = crs(imgs)) %>% 
+  vect(); rm(imgs)
+
+test_rf_features <- do.call(
+  rbind,
+  mclapply(unique(sample_test$tile),
+    function(tile_nm) {
+      # Get imgs
+      imgs <- rast(file.path(
+        "/Volumes/elephant/pred_stack",
+        paste0(tile_nm, ".tif")
+      ))
+
+      # get samples
+      samples_this <- sample_test[sample_test$tile == tile_nm, ]
+      trainings_this <- do.call(
+          rbind, 
+          lapply(1:nrow(samples_this), function(n){
+          sample_n <- samples_this[n, ]
+          terra::extract(
+              imgs, sample_n) %>%
+              mutate(landcover = sample_n$landcover) %>%
+              dplyr::select(-ID)
+      }))
+      rm(imgs, samples_this)
+      gc()
+      trainings_this
+    }, mc.cores = 4)
+)
+save(test_rf_features, 
+     file = file.path(here("data/north"), 
+                      "test_rf_features.rda"))
+
+load(here("data/north/guess_rf_md.rda"))
+test_rf_features <- test_rf_features %>% na.omit()
+pred <- predict(guess_rf_md$fit, 
+                test_rf_features %>% select(-landcover))
+pred <- argmax(pred$predictions)
+pred <- data.frame(predict = pred,
+                   test = test_rf_features$landcover)
+lc_types <- data.frame(id = 1:7,
+                       type = c('cropland', 'forest', 'grassland',
+                                'shrubland', 'water', 'built-up',
+                                'bareland'))
+pred_eval <- left_join(pred, lc_types, 
+                       by = c('test' = 'type')) %>% 
+    dplyr::select(-test) %>% 
+    rename(test = id) %>% 
+    mutate(predict = as.factor(predict),
+           test = as.factor(test))
+
+cf <- confusionMatrix(data = pred_eval$predict, 
+                      reference = pred_eval$test)
+save(cf, file = here('docs/figures/rf_test_conf.rda'))
+
+acc_test <- cf$byClass
+write.csv(acc_test, here('docs/figures/rf_test_acc.csv'),
+          row.names = F)
+```
+
+#### Human checking
+```{r}
+library(sf)
+library(glue)
+library(here)
+
+tile_nm <- 'catalog_sample_tiles_update.geojson'
+tiles <- here(glue('results/north/{tile_nm}')) %>% 
+  read_sf(); rm(tile_nm)
+tiles <- tiles %>% 
+  mutate(quality = glue("({score}, {hardiness})")) %>% 
+  st_drop_geometry() %>% 
+  mutate(quality = factor(quality))
+
+ggplot(tiles, aes(quality)) +
+  geom_bar(color = 'black',fill = 'cyan3') +
+  xlab('Quality (correctness, difficulty)') +
+  ylab('Count') +
+  theme_bw()
+
+quality_fig <- ggplot(
+  tiles,
+  aes(fill = factor(hardiness), x = score)) + 
+  geom_bar(position = "stack") +
+  scale_fill_brewer('Difficulty', palette = "Dark2") +
+  xlab('Correctness') +
+  ylab('Count') +
+  theme_bw()
+
+ggplot(
+  tiles,
+  aes(fill = factor(hardiness), x = score)) + 
+  geom_bar(position = "stack") +
+  coord_polar("x") +
+  theme_bw()
+
+ggsave(here('docs/figures/humancheck_quality.png'),
+       quality_fig,
+       width = 4, height = 4, dpi = 300)
 ```
@@
 library(glue)
+library(stringr)
+library(caret)
+
+# Validate
 # Get file names
 fns <- list.files(here(
-    file.path('results/scalar',
-              'unet_score08_hardiness20_epoch200')), 
+    'results/scalar/full_runs'), 
+    pattern = 'unet_k15_only_nopad_clr_200epc',
     full.names = T)
@@
     arrange(Class)
-write.csv(acc, here('docs/figures/acc_last10epoch.csv'),
+write.csv(acc, here('docs/figures/k15_only_acc_last10epoch.csv'),
+          row.names = F)
+
+# Test
+sample_test <- read_sf(here('data/north/plys_holdout_check.geojson'))
+pred <- rast(here(file.path('results/dl/prediction',
+                            'unet_k15_only_clr_200epc',
+                            'landcover_north.tif')))
+sample_test <- vect(sample_test %>% st_transform(crs = crs(pred)))
+pred_eval <- terra::extract(pred, sample_test, list = T)
+pred_eval <- do.call(rbind, lapply(1:length(pred_eval), function(n){
+    rst_vals <- pred_eval[[n]][[1]]
+    data.frame(predict = rst_vals,
+               test = sample_test[n, ]$landcover)
+}))
+
+lc_types <- data.frame(id = 1:7,
+                       type = c('cropland', 'forest', 'grassland',
+                                'shrubland', 'water', 'built-up',
+                                'bareland'))
+pred_eval <- left_join(pred_eval, lc_types, by = c('test' = 'type')) %>% 
+    dplyr::select(-test) %>% 
+    rename(test = id) %>% 
+    mutate(predict = as.factor(predict),
+           test = as.factor(test))
+cf <- confusionMatrix(data=pred_eval$predict, reference = pred_eval$test)
+save(cf, file = here('docs/figures/test_conf.rda'))
+
+acc_test <- cf$byClass
+write.csv(acc_test, here('docs/figures/test_acc.csv'),
           row.names = F)
@@
 library(here)
+library(ggplot2)
+library(ggpubr)
+
 # Get file names
 fns <- list.files(here(
-    file.path('results/scalar',
-              'unet_score08_hardiness20_epoch200')), 
+    'results/scalar/full_runs'), 
+    pattern = 'unet_k15_only_nopad_clr_200epc', 
     full.names = T)
@@
 
-ggsave(here('docs/figures/curves_final_mod.png'),
+ggsave(here('docs/figures/curves_k15_only_final_mod.png'),
        curves,
@@
 
+#### Prediction examples
+
+Provide some prediction examples of different LC types. Then provide an overall map. Could put them together.
+
+```{r, eval=FALSE}
+library(glue)
+
+pred_path <- here(file.path('results/dl/prediction',
+                            'unet_k15_only_clr_200epc',
+                            'landcover_north_withwl.tif'))
+score_path <- here(file.path('results/dl/prediction',
+                             'unet_k15_only_clr_200epc',
+                             'landcover_confidence_north_withwl.tif'))
+# Partial GRASS command to get standard deviation
+execGRASS('r.in.gdal', flags = c("o", "overwrite"),
+          input = score_path,
+          band = 1,
+          output = "score")
+execGRASS('r.in.gdal', flags = c("o", "overwrite"),
+          input = pred_path,
+          band = 1,
+          output = "pred")
+execGRASS("g.region", raster = "score")
+execGRASS('r.stats.zonal', flags = c('overwrite'),
+          base = 'pred',
+          cover = 'score',
+          method = 'stddev',
+          output = 'class_stddev')
+dst_path <- here(file.path('results/dl/prediction',
+                             'unet_k15_only_clr_200epc',
+                             'class_stddev.tif'))
+execGRASS('r.out.gdal', flags = c("overwrite"),
+          parameters = list(input = 'class_stddev', 
+                            output = dst_path,
+                            createopt = "COMPRESS=LZW"))
+
+pred_path <- here(file.path('results/dl/prediction',
+                            'unet_k15_only_clr_200epc',
+                            'landcover_north_withwl.tif'))
+score_path <- here(file.path('results/dl/prediction',
+                             'unet_k15_only_clr_200epc',
+                             'landcover_confidence_north_withwl.tif'))
+pred <- rast(pred_path)
+score <- rast(score_path)
+std <- rast(dst_path)
+means <- zonal(score, pred, "mean", na.rm = TRUE)
+stds <- zonal(std, pred, "mean", na.rm = TRUE)
+
+mean_std <- data.frame(means) %>% 
+  left_join(data.frame(stds)) %>% 
+  `colnames<-`(c('landcover', 'mean', 'std')) %>% 
+  mutate(Confidence = glue(
+               paste0('{format(round(mean, digits = 2), nsmall = 2)}',
+                      '\u00B1{format(round(std, digits = 2), nsmall = 2)}'))) %>% 
+  left_join(color_tb %>% select(id, type), by = c('landcover' = 'id')) %>% 
+  rename(Landcover = type) %>% select(Landcover, Confidence)
+save(mean_std, file = here('docs/figures/conf_mean_std.rda'))
+```
+
+```{r}
+library(terra)
+library(stars)
+library(tmap)
+library(ggpubr)
+library(gridExtra)
+
+load(here('docs/figures/conf_mean_std.rda'))
+pred_path <- here(file.path('results/dl/prediction',
+                           'unet_k15_only_clr_200epc',
+                           'landcover_north_withwl.tif'))
+color_tb <- data.frame(
+    id = 1:8,
+    type = c("Cropland", "Forest", 
+             "Grassland", "Shrubland", 
+             "Water", 'Built-up', "Bareland", 
+             'Wetland'),
+    color = c('#ff7f00', '#074702', '#b2df8a',
+              '#33a02c', '#3347f9', '#5a6057',
+              '#fdbf6f', '#0ea591'))
+# pred <- read_stars(pred_path)
+pred <- rast(pred_path)
+setCats(pred, value = color_tb$type, index = color_tb$id)
+pred <- st_as_stars(pred)
+
+# plot
+# Get examples
+tiles <- read_sf('data/geoms/tiles_nicfi_north.geojson')
+id_selected <- c('1226-1012', '1227-1005', '1209-997', '1219-1017',
+                 '1234-992', '1211-1008', '1236-1007','1220-995')
+tiles <- tiles %>% filter(tile %in% id_selected) %>% 
+    st_transform(crs = crs(rast(pred_path))) %>% 
+    mutate(id = 1:nrow(.))
+rst_tiles <- lapply(1:nrow(tiles), function(n){
+    tm <- st_crop(pred, tiles %>% slice(n)) %>% 
+        tm_shape() + 
+        tm_raster("landcover_north", 
+              n = 8, style = 'cat',
+              labels = color_tb$type,
+              palette = color_tb$color) +
+        tm_layout(frame = F,
+                  legend.show = F,
+                  title.position = c(0, 0.9),
+                  title = tiles %>% slice(n) %>% pull(id))
+     tmap_grob(tm)
+})
+plot_left <- ggarrange(
+    rst_tiles[[1]], rst_tiles[[2]], rst_tiles[[3]], 
+    rst_tiles[[4]], ncol = 1, nrow = 4)
+plot_right <- ggarrange(
+    rst_tiles[[5]], rst_tiles[[6]], rst_tiles[[7]],
+    rst_tiles[[8]], ncol = 1, nrow = 4)
+
+tmap_mode("plot")
+pred_final <- tm_shape(pred) +
+    tm_raster("landcover_north", 
+              title = "Land cover types",
+              n = 8, style = 'cat',
+              labels = color_tb$type,
+              palette = color_tb$color) +
+    tm_shape(tiles) +
+    tm_borders("black", lwd = 1.2) +
+    tm_text("id", col = 'black', fontface = "bold", size = 0.8) +
+    tm_layout(frame = F,
+              legend.show = F,
+              outer.margins = c(0.02, 0.01, 0, 0.01),
+              inner.margins = 0)
+pred_final <- tmap_grob(pred_final)
+
+# Get legend
+r_df <- data.frame(x = 1:8, 
+                   y = 1:8,
+                   rst = as.factor(1:8))
+legend_lc <- ggplot() + 
+    geom_raster(
+        data = r_df, 
+        aes(x = x, y = y, 
+            fill = rst)) +
+    scale_fill_manual('Land cover',
+                      values = color_tb$color, 
+                      breaks = 1:8,
+                      labels = color_tb$type) +
+    theme_minimal() +
+    theme(legend.position = 'right',
+          axis.title.x = element_blank(),
+          axis.text.x = element_blank(),
+          axis.ticks.x = element_blank(),
+          axis.title.y = element_blank(),
+          axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(),
+          plot.margin = unit(rep(0, 4),"cm"))+
+    guides(fill = guide_legend(ncol = 2))
+legend_lc <- get_legend(legend_lc)
+
+tbl_theme <- gridExtra::ttheme_default(
+    core = list(fg_params=list(cex = 0.6),
+                bg_params = list(fill = 'gray95')),
+    colhead = list(fg_params=list(cex = 0.7)),
+    rowhead = list(fg_params=list(cex = 0.7)))
+tbl_conf <- tableGrob(mean_std, rows = NULL, theme = tbl_theme)
+legend_lc <- ggarrange(NA, tbl_conf, NA, legend_lc, NA,
+                       ncol = 5, widths = c(1, 2, 1, 2, 1))
+
+pred_final_plt <- ggarrange(pred_final, legend_lc, NA,
+                        nrow = 3, heights = c(5, 1, 0.6))
+pred_example <- ggarrange(plot_left, pred_final_plt, plot_right,
+          ncol = 3, widths = c(1, 3, 1))
+ggsave(here('docs/figures/pred_example.png'),
+       pred_example,
+       width = 7, height = 6, dpi = 300)
+```
+
 ## Sensitivity analysis
 ### Quality weights
-#### Score factor
+#### Correctness
 ```{r}
+library(tidyverse)
+library(gridExtra)
+
+# Define function
+get_curves <- function(experiment_name,
+                       step = 59,
+                       path = here('results/scalar/compare_score')){
+    # Get file names
+    fns <- list.files(path, 
+                      pattern = experiment_name,
+                      full.names = T)
+    fns <- fns[str_detect(fns, 'Validate')]
+
+    # Process each csv
+    scalars <- lapply(fns, function(fn){
+        scalar <- read.csv(fn, stringsAsFactors = F) %>% 
+            mutate(Step = Step / step) %>% # step of each epoch
+            dplyr::select(-Wall.time)
+    })
+    names(scalars) <- gsub(
+        '.csv', "", 
+        str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+
+    scalars
+}
+
 # Clean scalar csvs
@@
     path = here('results/scalar/compare_score'))
-curves_score02 <- get_curves(
-    'unet_score_02',
+curves_k05 <- get_curves(
+    'unet_k05_only',
     path = here('results/scalar/compare_score'))
-curves_score08 <- get_curves(
-    'unet_score_08',
+curves_k15 <- get_curves(
+    'unet_k15_only',
     path = here('results/scalar/compare_score'))
-curves_score16 <- get_curves(
-    'unet_score_16',
+curves_k30 <- get_curves(
+    'unet_k3_only',
     path = here('results/scalar/compare_score'))
-curves_score32 <- get_curves(
-    'unet_score_32',
-    path = here('results/scalar/compare_score'))
-curves_score100 <- get_curves(
-    'unet_score_100',
-    path = here('results/scalar/compare_score'))
-
-types <- c('AA', 'IoU', 'Cropland', 'Forest', 
+
+types <- c('AA', 'mIoU', 'Cropland', 'Forest', 
            'Grassland', 'Shrubland', 'Water', 
@@
         item <- 'Urban'
-        } else{item <- type}
+    } else if (type == 'mIoU'){
+        item <- 'IoU'
+    } else {item <- type}
     list(curves_no_weight[[item]],
-         curves_score02[[item]],
-         curves_score08[[item]],
-         curves_score16[[item]],
-         curves_score32[[item]],
-         curves_score100[[item]]) %>% 
+         curves_k05[[item]],
+         curves_k15[[item]],
+         curves_k30[[item]]) %>% 
         reduce(left_join, by = "Step") %>% 
-        `colnames<-`(c("Epoch", '0', '0.2', '0.8', 
-                       '1.6', '3.2', '10')) %>% 
+        `colnames<-`(c("Epoch", '0', '0.5', '1.5', '3.0')) %>% 
         mutate(Item = type) %>% 
         pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
-                     names_to = 'Weight factor', 
+                     names_to = 'k of logistic function', 
                      values_to = 'Value')
 })) %>% mutate(Item = factor(Item, levels = types),
-               `Weight factor` = factor(
-                   `Weight factor`, 
-                   levels = c('0', '0.2', '0.8', 
-                              '1.6', '3.2', '10')))
+               `k of logistic function` = factor(
+                   `k of logistic function`, 
+                   levels = c('0', '0.5', '1.5', '3.0')))
+
+# Calculate mean and sd of last 10 epochs
+content_plot <- content %>% 
+  filter(Epoch >= 21) %>% 
+  filter(Item %in% c('AA', 'mIoU')) %>% 
+  group_by(Item, `k of logistic function`) %>% 
+  summarise(Mean = mean(Value), 
+            sd = sd(Value))
 
 # Get final plot
-curves_score <- ggplot(content, aes(x = Epoch, y = Value)) +
-    # geom_line(aes(color = `Weight factor`)) +
-    geom_smooth(aes(color = `Weight factor`), span = 0.2,
-                se = F, size = 0.6) +
-    scale_color_manual(
-        values = c('Black', 
-                   RColorBrewer::brewer.pal(5, "Dark2"))) +
-    # scale_color_brewer(palette = "Dark2") +
+curves_corr <- ggplot(
+  content_plot, 
+  aes(x = `k of logistic function`, y = Mean)) + 
+  geom_point() +
+  geom_errorbar(aes(ymin = Mean - sd, ymax = Mean + sd), width=.2,
+                position = position_dodge(0.05)) +
   facet_wrap(~Item, scales = 'free_y') +
-    labs(y = 'Accuracy') +
-    theme_bw() +
-    theme(legend.position = 'top') +
-    guides(color = guide_legend(nrow = 1))
-ggsave(here('docs/figures/curves_score.png'),
-       curves_score,
-       width = 8, height = 5, dpi = 300)
+  labs(y = 'Value', x = expression(paste(k, ' of logistic function'))) +
+  theme_bw()
+# ggsave(here('docs/figures/sa_correctness.png'),
+#        curves_corr,
+#        width = 6.5, height = 2, dpi = 300)
 ```
@@
 # Clean scalar csvs
-curves_score08_nohard <- get_curves(
-    'unet_score_08',
+curves_k15_nohard <- get_curves(
+    'unet_k15_only',
     path = here('results/scalar/compare_score'))
-curves_hard2 <- get_curves(
-    'unet_score08_hardiness_2',
+curves_k15_h11 <- get_curves(
+    'unet_k15_hard11',
     path = here('results/scalar/compare_score'))
-curves_hard4 <- get_curves(
-    'unet_score08_hardiness_4',
+curves_k15_h12 <- get_curves(
+    'unet_k15_hard12',
     path = here('results/scalar/compare_score'))
-curves_hard6 <- get_curves(
-    'unet_score08_hardiness_6',
+curves_k15_h14 <- get_curves(
+    'unet_k15_hard14',
     path = here('results/scalar/compare_score'))
 
-types <- c('AA', 'IoU', 'Cropland', 'Forest', 
+types <- c('AA', 'mIoU', 'Cropland', 'Forest', 
            'Grassland', 'Shrubland', 'Water', 
@@
         item <- 'Urban'
-        } else{item <- type}
-    list(curves_score08_nohard[[item]],
-         curves_hard2[[item]],
-         curves_hard4[[item]],
-         curves_hard6[[item]]) %>% 
+    } else if (type == 'mIoU'){
+        item <- 'IoU'
+    } else {item <- type}
+    list(curves_k15_nohard[[item]],
+         curves_k15_h11[[item]],
+         curves_k15_h12[[item]],
+         curves_k15_h14[[item]]) %>% 
         reduce(left_join, by = "Step") %>% 
-        `colnames<-`(c("Epoch", '0', '2', '4', '6')) %>% 
+        `colnames<-`(c("Epoch", '1', '1.1', '1.2', '1.4')) %>% 
         mutate(Item = type) %>% 
@@
                    `Weight scale`, 
-                   levels = c('0', '2', '4', '6')))
+                   levels = c('1', '1.1', '1.2', '1.4')))
+
+# Calculate mean and sd of last 10 epochs
+content_plot <- content %>% 
+  filter(Epoch >= 21) %>% 
+  filter(Item %in% c('AA', 'mIoU')) %>% 
+  group_by(Item, `Weight scale`) %>% 
+  summarise(Mean = mean(Value), 
+            sd = sd(Value))
 
 # Get final plot
-curves_hard <- ggplot(content, aes(x = Epoch, y = Value)) +
-    geom_smooth(aes(color = `Weight scale`), span = 0.2,
-                se = F, size = 0.6) +
-    scale_color_manual(
-        values = c('Black', 
-                   RColorBrewer::brewer.pal(3, "Dark2"))) +
-    # scale_color_brewer(palette = "Dark2") +
+curves_diff <- ggplot(
+  content_plot, 
+  aes(x = `Weight scale`, y = Mean)) + 
+  geom_point() +
+  geom_errorbar(aes(ymin = Mean - sd, ymax = Mean + sd), width=.2,
+                position = position_dodge(0.05)) +
   facet_wrap(~Item, scales = 'free_y') +
-    labs(y = 'Accuracy') +
-    theme_bw() +
-    theme(legend.position = 'top') +
-    guides(color = guide_legend(nrow = 1))
-ggsave(here('docs/figures/curves_hard.png'),
-       curves_hard,
-       width = 8, height = 5, dpi = 300)
+  labs(y = 'Value', x = expression(s[max])) +
+  theme_bw()
+# ggsave(here('docs/figures/sa_difficulty.png'),
+#        curves_diff,
+#        width = 6.5, height = 2, dpi = 300)
+
+params_cost <- ggarrange(curves_corr, curves_diff,
+                        nrow = 2)
+ggsave(here('docs/figures/sa_loss_params.png'),
+       params_cost,
+       width = 6.5, height = 4, dpi = 300)
 ```
@@
 ```{r}
-
-```
+# Clean scalar csvs
+curves_full <- get_curves(
+    'unet_k15_only',
+    path = here('results/scalar/compare_score'))
+curves_one_tile <- get_curves(
+    step = 19, 
+    'unet_one_tile',
+    path = here('results/scalar/compare_sampling'))
+curves_random_34 <- get_curves(
+    step = 19,
+    'unet_random_34',
+    path = here('results/scalar/compare_sampling'))
+curves_hori_strip_34 <- get_curves(
+    step = 19,
+    'unet_hori_strip_34',
+    path = here('results/scalar/compare_sampling'))
+curves_vert_strip_34 <- get_curves(
+    step = 18,
+    'vert_strip_34',
+    path = here('results/scalar/compare_sampling'))
+curves_two_tile <- get_curves(
+    step = 39, 
+    'unet_two_tile',
+    path = here('results/scalar/compare_sampling'))
+curves_random_67 <- get_curves(
+    step = 39,
+    'unet_random_67',
+    path = here('results/scalar/compare_sampling'))
+curves_hori_strip_67 <- get_curves(
+    step = 39,
+    'unet_hori_strip_67',
+    path = here('results/scalar/compare_sampling'))
+curves_vert_strip_67 <- get_curves(
+    step = 39,
+    'vert_strip_67',
+    path = here('results/scalar/compare_sampling'))
+
+types <- c('AA', 'mIoU', 'Cropland', 'Forest', 
+           'Grassland', 'Shrubland', 'Water', 
+           'Built-up', 'Bareland')
+content <- do.call(rbind, lapply(types, function(type){
+    if (type == 'Built-up') {
+        item <- 'Urban'
+    } else if (type == 'mIoU'){
+        item <- 'IoU'
+    } else {item <- type}
+    list(curves_full[[item]],
+         curves_one_tile[[item]],
+         curves_random_34[[item]],
+         curves_hori_strip_34[[item]],
+         curves_vert_strip_34[[item]],
+         curves_two_tile[[item]],
+         curves_random_67[[item]],
+         curves_hori_strip_67[[item]],
+         curves_vert_strip_67[[item]]) %>% 
+        reduce(left_join, by = "Step") %>% 
+        `colnames<-`(c("Epoch", '3 samples/tile', '1 sample/tile', '34% (randomly)', 
+                       '34% (Hori-strip)', '34% (Vert-strip)',
+                       '2 samples/tile', '67% (randomly)', 
+                       '67% (Hori-strip)', '67% (Vert-strip)')) %>% 
+        mutate(Item = type) %>% 
+        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
+                     names_to = 'Sampling method', 
+                     values_to = 'Value')
+})) %>% mutate(Item = factor(Item, levels = types),
+               `Sampling method` = factor(
+                   `Sampling method`, 
+                   levels = c('3 samples/tile', '1 sample/tile', '34% (randomly)', 
+                       '34% (Hori-strip)', '34% (Vert-strip)',
+                       '2 samples/tile', '67% (randomly)', 
+                       '67% (Hori-strip)', '67% (Vert-strip)')))
+
+# Calculate mean and sd of last 10 epochs
+content_plot <- content %>% 
+  filter(Epoch >= 21) %>% 
+  filter(`Sampling method` %in% 
+           c('1 sample/tile', '34% (randomly)',
+             '2 samples/tile', '67% (randomly)',
+             '3 samples/tile')) %>% 
+  filter(Item %in% c('AA', 'mIoU')) %>% 
+  rename(`Sampling strategy` = `Sampling method`) %>% 
+  group_by(Item, `Sampling strategy`) %>% 
+  summarise(Mean = mean(Value), 
+            sd = sd(Value))
+
+# Get final plot
+curves_sampling <- ggplot(
+  content_plot, aes(x = `Sampling strategy`, y = Mean)) + 
+  geom_point() +
+  geom_errorbar(aes(ymin = Mean - sd, ymax = Mean + sd), 
+                width =.2,
+                position = position_dodge(0.05)) +
+  facet_wrap(~Item, scales = 'free_y') +
+  labs(y = 'Value') +
+  scale_x_discrete(guide = guide_axis(angle = 45)) +
+  NULL + theme_bw()
+ggsave(here('docs/figures/sa_sampling.png'),
+       curves_sampling,
+       width = 6.5, height = 2.5, dpi = 300)
+```
+
+## Appendix
+### Evaluation of LC products
+
+Use our independent test dataset to evaluate the quality of LC products used in this study.
+
+```{r}
+library(here)
+library(sf)
+library(terra)
+library(caret)
+
+sample_test <- vect(here('data/north/plys_holdout_check.geojson'))
+lc_types <- data.frame(id = 1:10,
+                       type = c('cropland', 'forest', 'grassland',
+                                'shrubland', 'wetland', 'water', 
+                                "tundra", 'built-up',
+                                'bareland', 'snow/ice'))
+tiles <- read_sf(
+    here('data/geoms/tiles_nicfi_north.geojson'),
+    stringsAsFactors = F) %>% vect()
+
+# ESA LC
+esaglc <- rast(here('data/landcovers/esaglc_rcl.tif'))
+esaglc_eval <- terra::extract(esaglc, sample_test, list = T, touches = T)
+esaglc_eval <- do.call(rbind, lapply(1:length(esaglc_eval), function(n){
+    rst_vals <- esaglc_eval[[n]][[1]]
+    data.frame(product = rst_vals,
+               test = sample_test[n, ]$landcover)
+}))
+
+esaglc_eval <- left_join(esaglc_eval, lc_types, 
+                       by = c('test' = 'type')) %>% 
+    dplyr::select(-test) %>% 
+    rename(test = id) %>% 
+    filter(product != 5) %>% 
+    mutate(product = as.factor(product),
+           test = as.factor(test))
+cf <- confusionMatrix(data=esaglc_eval$product, reference = esaglc_eval$test)
+save(cf, file = here('docs/figures/esaglc_test_conf.rda'))
+
+acc_test <- cf$byClass
+write.csv(acc_test, here('docs/figures/esaglc_test_acc.csv'),
+          row.names = F)
+
+# fromglc
+fromglc <- rast(here('data/landcovers/fromglc_rcl.tif'))
+fromglc_eval <- terra::extract(fromglc, sample_test, list = T, touches = T)
+fromglc_eval <- do.call(rbind, lapply(1:length(fromglc_eval), function(n){
+    rst_vals <- fromglc_eval[[n]][[1]]
+    data.frame(product = rst_vals,
+               test = sample_test[n, ]$landcover)
+}))
+
+fromglc_eval <- left_join(fromglc_eval, lc_types, 
+                       by = c('test' = 'type')) %>% 
+    dplyr::select(-test) %>% 
+    rename(test = id) %>% 
+    filter(product != 5) %>% 
+    mutate(product = as.factor(product),
+           test = as.factor(test))
+cf <- confusionMatrix(data=fromglc_eval$product, reference = fromglc_eval$test)
+save(cf, file = here('docs/figures/fromglc_test_conf.rda'))
+
+acc_test <- cf$byClass
+write.csv(acc_test, here('docs/figures/fromglc_test_acc.csv'),
+          row.names = F)
+
+# gfsad
+gfsad <- rast(here('data/landcovers/gfsad_rcl.tif'))
+gfsad_eval <- terra::extract(gfsad, sample_test, list = T, touches = T)
+gfsad_eval <- do.call(rbind, lapply(1:length(gfsad_eval), function(n){
+    rst_vals <- gfsad_eval[[n]][[1]]
+    data.frame(product = rst_vals,
+               test = sample_test[n, ]$landcover)
+}))
+
+gfsad_eval <- left_join(gfsad_eval, lc_types, 
+                       by = c('test' = 'type')) %>% 
+    dplyr::select(-test) %>% 
+    rename(test = id) %>% 
+    mutate(test = ifelse(test == 6, 6, ifelse(test == 1, 1, 0))) %>% 
+    mutate(product = as.factor(product),
+           test = as.factor(test))
+cf <- confusionMatrix(data = gfsad_eval$product, reference = gfsad_eval$test)
+save(cf, file = here('docs/figures/gfsad_test_conf.rda'))
+
+acc_test <- cf$byClass
+write.csv(acc_test, here('docs/figures/gfsad_test_acc.csv'),
+          row.names = F)
+
+# Tansis
+tansis <- rast(list.files(here('data/tansis'), 
+                          full.names = T, pattern = '.tif$'))
+tansis <- tansis$TZ__7
+tansis <- project(tansis, crs(sample_test), method = 'near')
+tansis[is.na(tansis)] <- 0
+
+tansis_eval <- terra::extract(tansis, sample_test, list = T, touches = T)
+tansis_eval <- do.call(rbind, lapply(1:length(tansis_eval), function(n){
+    rst_vals <- tansis_eval[[n]][[1]]
+    data.frame(product = rst_vals,
+               test = sample_test[n, ]$landcover)
+}))
+
+tansis_eval <- left_join(tansis_eval, lc_types, 
+                         by = c('test' = 'type')) %>% 
+  dplyr::select(-test) %>% 
+  rename(test = id) %>% 
+  mutate(test = ifelse(test == 1, 1, 0)) %>% 
+  na.omit() %>% 
+  mutate(product = as.factor(product),
+         test = as.factor(test))
+cf <- confusionMatrix(data = tansis_eval$product, 
+                      reference = tansis_eval$test,
+                      positive = "1")
+save(cf, file = here('docs/figures/tansis_test_conf.rda'))
+
+acc_test <- cf$byClass
+write.csv(acc_test, here('docs/figures/tansis_test_acc.csv'))
+```
+
+### RF tuning
+
+```{r}
+library(here)
+library(dplyr)
+library(ramify)
+library(ranger)
+library(parsnip)
+library(tidymodels)
+library(vip)
+library(dials)
+library(ggplot2)
+library(ggpubr)
+
+load("~/Dropbox/research/hrlcm/data/north/forest_vip.rda")
+vip_figure <- vip(forest_vip, 
+    num_features = forest_vip$fit$num.independent.variables,
+    aesthetics = list(color = "transparent", 
+                      fill = "red")) +
+    theme_light()
+
+load("~/Dropbox/research/hrlcm/data/north/tune_res.rda")
+tune_figure <- tune_res %>%
+    collect_metrics() %>%
+    filter(.metric == "accuracy") %>%
+    mutate(min_n = factor(min_n)) %>%
+    ggplot(aes(mtry, mean, color = min_n)) +
+    geom_line() + geom_point() +
+    scale_color_brewer(palette = "Dark2") +
+    labs(y = "Accuracy") +
+    theme_light()
+
+params_fig <- ggarrange(vip_figure, tune_figure,
+                        ncol = 2, widths = c(1, 1.5))
+ggsave(here('docs/figures/rf_tuning.png'),
+       params_fig,
+       width = 8, height = 4, dpi = 300)
+```
+
+### Confusion matrix heatmap for RF
+
+```{r}
+cm <- pred_eval %>% 
+    conf_mat(truth = test, 
+             estimate = predict)
+cm_figure <- autoplot(cm, type = 'heatmap')
+ggsave(here('docs/figures/rf_cm_heatmap.png'),
+       cm_figure,
+       width = 4, height = 3, dpi = 300)
+```
+
+### Confusion matrix heatmap for U-Net
+```{r}
+cm <- pred_eval %>% 
+    conf_mat(truth = test, 
+             estimate = predict)
+cm_figure <- autoplot(cm, type = 'heatmap')
+ggsave(here('docs/figures/unet_cm_heatmap.png'),
+       cm_figure,
+       width = 4, height = 3, dpi = 300)
+```
+
+### Land cover classification confidence
+```{r}
+library(stars)
+library(tmap)
+library(tmaptools)
+
+pred_path <- here(file.path('results/dl/prediction',
+                            'unet_k15_only_clr_200epc',
+                            'landcover_confidence_north_withwl.tif'))
+pred <- read_stars(pred_path)
+conf_fig <- tm_shape(pred) +
+    tm_raster("landcover_confidence_north_withwl.tif", 
+              title = "Confidence",
+              style = 'cont',
+              palette = rev(
+                  get_brewer_pal('Greys', 
+                                 plot = F, 
+                                 contrast=c(.25, 1)))) +
+    tm_layout(frame = F,
+              legend.position = c(0.8, 0.7))
+tmap_save(conf_fig, 
+          here('docs/figures/conf_figure.png'), 
+          width = 4, height = 4, units = 'in',
+          dpi = 300)
+```

### 2022-01-04 docs/nasa_meeting_poster.Rmd
Add meeting poster

--- 2021-08-07 docs/manuscript_figures.Rmd
@@
 ---
-title: "Manuscript figures"
-author: "Lei Song"
-date: "6/17/2021"
-output: html_document
+title: "Land cover mapping in data-sparse regions"
+subtitle: Northern Tanzania
+author: Lei Song, Lyndon Estes, Boka Luo, Anna Estes
+output:
+  xaringan::moon_reader:
+    lib_dir: libs
+    css: ["default", "lucy", "middlebury-fonts", "theme.css"]
+    nature:
+      highlightStyle: github
+      countIncrementalSlides: false
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
+knitr::opts_chunk$set(echo = F)
+library(here)
 ```
 
-## Introduction
+```{r, eval = FALSE, include=FALSE}
+library(here)
+library(terra)
+library(stars)
+library(tmap)
+library(ggpubr)
+library(gridExtra)
 
-This is just a markdown to record the script to generate figures for the paper.
+pred_path <- here(file.path('results/dl/prediction',
+                           'unet_k15_only_clr_200epc',
+                           'landcover_north_withwl.tif'))
+color_tb <- data.frame(
+    id = 1:8,
+    type = c("Cropland", "Forest", 
+             "Grassland", "Shrubland", 
+             "Water", 'Built-up', "Bareland", 
+             'Wetland'),
+    color = c('#ff7f00', '#074702', '#b2df8a',
+              '#33a02c', '#3347f9', '#5a6057',
+              '#fdbf6f', '#0ea591'))
+# pred <- read_stars(pred_path)
+pred <- rast(pred_path)
+setCats(pred, value = color_tb$type, index = color_tb$id)
+pred <- st_as_stars(pred)
 
-## Study area
+# plot
+tmap_mode("plot")
+pred_final <- tm_shape(pred) +
+    tm_raster("landcover_north", 
+              title = "Land cover types",
+              n = 8, style = 'cat',
+              labels = color_tb$type,
+              palette = color_tb$color) +
+    tm_layout(frame = F,
+              legend.show = F,
+              outer.margins = c(0.02, 0.01, 0, 0.01),
+              inner.margins = 0,
+              bg.color = 'black')
+pred_final <- tmap_grob(pred_final)
 
-Study area figure should include a overall view of study area in a bigger background, a zoom-in view of the study area (northern of Tanzania), the ecozones, the NICFI tiling system and the following sub-tiling system,
-
-```{r}
-library(here)
-library(sf)
-library(nngeo)
-library(ggplot2)
-library(ggspatial)
-library(RColorBrewer)
-library(dplyr)
-library(rnaturalearth)
-
-# Read boundaries
-tz_bry <- read_sf(here('data/geoms/tanzania.geojson'))
-study_area <- read_sf(here('data/geoms/study_area.geojson')) %>% 
-    st_remove_holes()
-nicfi_tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson')) %>% 
-    mutate(`NICFI tile` = 1)
-ecozones <- read_sf(here('data/geoms/ecozones.geojson')) %>% 
-    st_intersection(study_area) %>% 
-    rename(Ecozone = zone)
-
-# The overview of study area in the whole country at the left corner
-# Get the surrounding countries
-countries <- ne_countries(type = 'countries', scale = 'large',
-                          returnclass = 'sf') %>% 
-    st_intersection(., st_bbox(tz_bry) %>% 
-                        st_as_sfc() %>% 
-                        st_buffer(5, joinStyle = 'MITRE') %>% 
-                        st_bbox(tz_bry) %>% # Get he squared one
-                        st_as_sfc())
-
-# Make overview
-xlim <- c(st_bbox(countries)[1] + 3, st_bbox(countries)[3] - 3)
-ylim <- c(st_bbox(countries)[2] + 3, st_bbox(countries)[4] - 3)
-overview <- ggplotGrob(ggplot(tz_bry) +
-    geom_sf(fill = 'lightblue', color = 'grey') +
-    geom_sf_text(aes(label = geounit), size = 4) +
-    geom_sf(data = countries, fill = NA, color = 'grey') +
-    geom_sf(data = study_area, fill = 'red', color = 'grey') +
-    coord_sf(xlim = xlim, ylim = ylim) +
-    theme_bw() +
-    theme(axis.title.x = element_blank(),
+# Get legend
+r_df <- data.frame(x = 1:8, 
+                   y = 1:8,
+                   rst = as.factor(1:8))
+legend_lc <- ggplot() + 
+    geom_raster(
+        data = r_df, 
+        aes(x = x, y = y, 
+            fill = rst)) +
+    scale_fill_manual('Land cover',
+                      values = color_tb$color, 
+                      breaks = 1:8,
+                      labels = color_tb$type) +
+    theme_minimal() +
+    theme(legend.position = 'right',
+          legend.text = element_text(color = 'white'),
+          axis.title.x = element_blank(),
           axis.text.x = element_blank(),
@@
           axis.ticks.y = element_blank(),
-          plot.margin = unit(rep(0, 4), "cm")))
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(),
+          plot.margin = unit(rep(0, 4),"cm"),
+          plot.background = element_rect(fill = "black"))+
+    guides(fill = guide_legend(ncol = 4))
+legend_lc <- get_legend(legend_lc)
+pred_final_plt <- ggarrange(pred_final, legend_lc, NA,
+                        nrow = 3, heights = c(5, 1, 0.6))
+ggsave(here('docs/figures/nasa_poster_result_img.png'),
+       pred_final_plt, bg = 'black',
+       width = 6, height = 6, dpi = 300)
+ggsave(here('docs/figures/nasa_poster_title_img.png'),
+       ggarrange(pred_final, bg = 'black',
+       width = 6, height = 6, dpi = 300)
+```
+
+## Introductions
+
+We proposed a method to make timely and accurate land cover maps in data-sparse regions, such as Tanzania.
+The main motivation of this project is that land cover products over Sub-Saharan Africa, including Tanzania, have poor quality.
+
+For instance, the following is the evaluation of some LC products in Northern Tanzania based on our test dataset.
+
+```{r}
+library(tibble)
+library(kableExtra)
+lc_products <- tibble(
+  `Product name` = c('CGLS_LC100m', 'FROM-GLC 2017v1', 'GFSAD30', 'TanSIS'),
+  `Product type` = c('Land cover', 'Land cover', 'Crop mask', 'Crop mask'),
+  Year = c(2018, 2017, 2015, 2018),
+  Resolution = c('100 m', '30 m', '30 m', '250 m'),
+  `Overall accuracy` = c('67.70%', '60.13%', '82.93%', '82.39%'))
+lc_products %>%
+  kbl() %>%
+  kable_paper("striped", full_width = F) %>%
+  row_spec(0, bold = T) %>% 
+  row_spec(0:4, color = "white", background = 'black')
+```
+
+---
+
+## Methodology
+
+Stage 1: We extracted the consensus of multiple existing land cover products to generate fragmented pixel-wise training labels.
+
+Stage 2: We translated pixel-wise training labels to image-wise labels using the random forest as a guessing model and satellite images.
+
+Stage 3: We fine-tuned a U-Net network based upon these image-wise labels using Sentinel-1 time series and raw bands of NICFI basemaps as image features.
+
+```{r, fig.align='center', out.width = "60%"}
+knitr::include_graphics("figures/hrlcm_flowchart.png")
+```
+
+---
+
+## Sub-tiling system and different types of label
+
+```{r, eval=F}
+library(raster)
+library(glue)
+library(here)
+library(sf)
+library(nngeo)
+library(ggplot2)
+library(RColorBrewer)
+library(dplyr)
+library(sf)
+library(rasterVis)
+library(ggnewscale)
+library(cowplot)
+library(ggpubr)
+
+# Read boundaries
+study_area <- read_sf(here('data/geoms/study_area.geojson')) %>% 
+    st_remove_holes()
+nicfi_tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson')) %>% 
+    mutate(`NICFI tile` = 1)
 
 # Make the main figure
-main_fg <- ggplot(ecozones) +
-    geom_sf(aes(fill = Ecozone), 
-            color = 'grey') +
-    scale_fill_brewer(palette = 'Accent') +
-    geom_sf(data = nicfi_tiles, fill = NA, 
+main_fg <- ggplot(nicfi_tiles) +
+    geom_sf(fill = NA, 
             aes(color = "black", lty = "dotted"), 
@@
                             guide = 'legend') +
-    annotation_custom(grob = overview, 
-                      xmin = 36.5, xmax = 38.5,
-                      ymin = -2.3, ymax = -0.5) +
-    annotation_scale(location = 'br', text_cex = 1) +
-    annotation_north_arrow(which_north = "true", location = 'tl') +
     theme_minimal() + 
-    theme(axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          legend.text = element_text(size = 12),
-          plot.margin = unit(rep(0, 4),"cm"))
-
-ggsave(here('docs/figures/study_area.png'),
-       main_fg,
-       width = 10, height = 5.7, dpi = 600)
-main_fg
-```
-
-## Satellite images
-
-This figure will provide an example of satellite images including NICFI images with two seasons, and the harmonic regression of Sentinel-1 images.
-
-```{r}
-library(sf)
-library(raster)
-library(ggplot2)
-library(ggpubr)
-library(dplyr)
-library(tidyr)
-library(stringr)
-library(RStoolbox)
-
-# Read example images
-# tile 1227-1002, 
-# this tile has a few different land cover types and obvious characteristics
-# so it could be a good example tile.
-tile_id <- '1227-1002'
-fnames_nicfi <- list.files(here('data/plts_nicfi'),
-                           pattern = tile_id,
-                           full.names = T)
-nicfi_s1 <- stack(fnames_nicfi[1]) %>% subset(1:4)
-nicfi_s2 <- stack(fnames_nicfi[2]) %>% subset(1:4)
-rm(fnames_nicfi)
-
-# Define example points
-pts_example <- read_sf(here('data/north/pts_example.shp')) %>% 
-    st_cast('POINT')
-
-# NICFI
-# Transform points
-pts_nicfi <- pts_example %>% 
-    st_transform(crs = crs(nicfi_s1))
-
-# Define colors
-cols_lc <- tibble(cols = c('#ff7f00', '#074702', '#b2df8a',
-                           '#33a02c', '#3347f9', '#5a6057',
-                           '#fdbf6f'),
-                  `Land cover type` = c("Cropland", 'Forest', "Grassland", 
-                                        'Shrubland',  "Water", "Built-up",
-                                        'Bareland'),
-                  ids = as.factor(1:7))
-
-# Image of season 1
-s1_fg <- ggRGB(nicfi_s1, r = 4, g = 3, b = 2, 
-               scale = max(values(nicfi_s1)[, 2:4]), 
-               stretch = 'hist') +
-    geom_sf(data = pts_nicfi,
-            color = 'black',
-            size = 3) +
-    geom_sf(data = pts_nicfi,
-            aes(color = factor(id)),
-            size = 2,
-            show.legend = F) +
-    scale_color_manual("Land cover type",
-                       values = cols_lc$cols, 
-                       breaks = cols_lc$ids,
-                       labels = cols_lc$`Land cover type`) +
-    theme_minimal() +
-    theme(axis.title.x = element_blank(),
+    theme(legend.position = 'none',
+          axis.title.x = element_blank(),
           axis.text.x = element_blank(),
@@
           plot.margin = unit(rep(0, 4),"cm"))
-
-# Image of season 2
-s2_fg <- ggRGB(nicfi_s2, r = 4, g = 3, b = 2, 
-               scale = max(values(nicfi_s2)[, 2:4]), 
-               stretch = 'lin') +
-    geom_sf(data = pts_nicfi,
-            color = 'black',
-            size = 3) +
-    geom_sf(data = pts_nicfi,
-            aes(color = factor(id)),
-            size = 2,
-            show.legend = F) +
-    scale_color_manual("Land cover type",
-                       values = cols_lc$cols, 
-                       breaks = cols_lc$ids,
-                       labels = cols_lc$`Land cover type`) +
-    theme_minimal() +
-    theme(axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          plot.margin = unit(rep(0, 4),"cm"))
-
-# Spectral signature of examples
-# Extract values
-pts_nicfi_s1 <- raster::extract(nicfi_s1, pts_nicfi) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_nicfi$type) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(`Band name` = c('Blue', 'Green', 'Red', 'NIR'),
-           Band = 1:4) %>% 
-    pivot_longer(cols = names(.)[1:(ncol(.) - 2)], 
-                 names_to = 'Land cover type',
-                 values_to = 'Reflectance') %>% 
-    mutate(`Land cover type` = as.factor(`Land cover type`),
-           Season = 'Season 1')
-pts_nicfi_s2 <- raster::extract(nicfi_s2, pts_nicfi) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_nicfi$type) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(`Band name` = c('Blue', 'Green', 'Red', 'NIR'),
-           Band = 1:4) %>% 
-    pivot_longer(cols = names(.)[1:(ncol(.) - 2)], 
-                 names_to = 'Land cover type',
-                 values_to = 'Reflectance') %>% 
-    mutate(`Land cover type` = as.factor(`Land cover type`),
-           Season = 'Season 2')
-pts_nicfi_all <- rbind(pts_nicfi_s1, pts_nicfi_s2)
-rm(pts_nicfi_s1, pts_nicfi_s2)
-
-# Figure
-pts_nicfi_all <- merge(pts_nicfi_all, cols_lc[, 2:3])
-ref_epl <- ggplot(pts_nicfi_all,
-                  aes(x = Band, y = Reflectance / 1000,
-                      color = ids)) +
-    geom_point() + geom_line(show.legend = 'line') +
-    ylab(bquote('Reflectance'~(10^3))) + 
-    scale_color_manual("Land cover type",
-                       values = cols_lc$cols, 
-                       breaks = cols_lc$ids,
-                       labels = cols_lc$`Land cover type`) +
-    scale_x_discrete(limit = factor(1:4),
-                     labels = unique(pts_nicfi_all$`Band name`)) +
-    theme_bw() +
-    theme(axis.title.x = element_blank()) +
-    facet_wrap(~ Season, nrow = 2, 
-               scales = "free_y",
-               strip.position = "top")
-
-nicfi_fg <- ggarrange(
-    ggarrange(s1_fg, s2_fg,
-              labels = c('Season 1', 'Season 2'),
-              font.label = list(size = 12),
-              vjust = 3,
-              ncol = 2), 
-    ref_epl, ncol = 2)
-ggsave(here('docs/figures/nicfi_image.png'),
-       nicfi_fg,
-       width = 8, height = 2.7, dpi = 300)
-
-# Sentinel-1 harmonic coefficient regression
-fnames_s1 <- list.files(here('data/s1_harmonic'),
-                        pattern = tile_id,
-                        full.names = T)
-vv_coefs <- stack(fnames_s1[str_detect(fnames_s1, 'VV')])
-vh_coefs <- stack(fnames_s1[str_detect(fnames_s1, 'VH')])
-
-# Image of VV
-# Slope, Cos(x), Intercept
-vv_fg <- ggRGB(vv_coefs, r = 2, g = 4, b = 1, 
-               scale = max(values(vv_coefs)[, c(2, 4, 1)]), 
-               stretch = 'hist') +
-    geom_sf(data = pts_example,
-            color = 'white',
-            size = 3) +
-    geom_sf(data = pts_example,
-            aes(color = factor(id)),
-            size = 2,
-            show.legend = F) +
-    scale_color_manual("Land cover type",
-                       values = cols_lc$cols, 
-                       breaks = cols_lc$ids,
-                       labels = cols_lc$`Land cover type`) +
-    theme_minimal() +
-    theme(axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          plot.margin = unit(rep(0, 4),"cm"))
-
-# Image of VH
-# Slope, Cos(x), Intercept
-vh_fg <- ggRGB(vh_coefs, r = 2, g = 4, b = 1, 
-               scale = max(values(vh_coefs)[, c(1, 2, 4)]), 
-               stretch = 'lin') +
-    geom_sf(data = pts_example,
-            color = 'white',
-            size = 3) +
-    geom_sf(data = pts_example,
-            aes(color = factor(id)),
-            size = 2,
-            show.legend = F) +
-    scale_color_manual("Land cover type",
-                       values = cols_lc$cols, 
-                       breaks = cols_lc$ids,
-                       labels = cols_lc$`Land cover type`) +
-    theme_minimal() +
-    theme(axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          plot.margin = unit(rep(0, 4),"cm"))
-
-# Time series and harmonic fitting of examples
-# out = cos((2 * pi * n0 * t) / freq - (n % 2) * pi / 2)
-# n_0 = {0,1,1,2,2}
-# n = {0,1,2,3,4}
-# freq = 365
-# Band1: intercept
-# Band2: slope
-# Band3: sin(x)
-# Band4: cos(x)
-# Band5: sin(2x)
-# Band6: cos(2x)
-
-# Real time series
-## Images
-vv_ts <- stack(
-    list.files(here('data/s1_timeseries_example/temp_ard_1227-1002'),
-               pattern = 'VV',
-               full.names = T)) 
-vh_ts <- stack(
-    list.files(here('data/s1_timeseries_example/temp_ard_1227-1002'),
-               pattern = 'VH',
-               full.names = T))
-
-# DOY
-doy <- c(0,   9,  12,  21,  33,  45,  48,  57,  69,  81,  93, 105, 117,
-       129, 141, 153, 165, 177, 189, 201, 213, 225, 237, 249, 261, 273,
-       285, 288, 293, 297, 300, 305, 309, 312, 317, 321, 324, 329, 333,
-       336, 345, 348, 357, 360)
-
-# Extract values
-pts_vv_ts <- raster::extract(vv_ts, pts_example) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_example$type) %>% 
-    mutate(date = rownames(.)) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(date = str_extract(date, '[0-9]{8}')) %>% 
-    arrange(date) %>% 
-    mutate(DOY = doy, polarization = 'VV',
-           type = 'Real value')
-
-pts_vh_ts <- raster::extract(vh_ts, pts_example) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_example$type) %>% 
-    mutate(date = rownames(.)) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(date = str_extract(date, '[0-9]{8}')) %>% 
-    arrange(date) %>% 
-    mutate(DOY = doy, polarization = 'VH',
-           type = 'Real value')
-
-pts_ts <- rbind(pts_vv_ts, pts_vh_ts) %>% 
-    dplyr::select(-date) %>% 
-    pivot_longer(names(.)[1:7], 
-                 names_to = "Land cover type", 
-                 values_to = "dB")
-rm(pts_vv_ts, pts_vh_ts)
-
-# Harmonic coefficients
-pts_vv <- raster::extract(vv_coefs, pts_example) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_example$type) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(`Band name` = c('Intersept', 'Slope', 
-                           'Sin(x)', 'Cos(x)', 
-                           'Sin(2x)', "Cos(2x)"), Band = 1:6)
-
-pts_vv_fit <- do.call(cbind, lapply(names(pts_vv)[1:7], function(typ){
-    coefs <- pts_vv %>% pull(typ)
-    data.frame(val = coefs[1] + coefs[2] * doy +
-    coefs[3] * sin(2 * pi * doy /365) + 
-    coefs[4] * cos(2 * pi * doy /365) + 
-    coefs[5] * sin(4 * pi * doy /365) + 
-    coefs[6] * cos(4 * pi * doy /365))
-})) %>% `names<-`(names(pts_vv)[1:7]) %>% 
-    mutate(DOY = doy) %>% 
-    mutate(polarization = 'VV',
-           type = 'Harmoic regression')
-
-pts_vh <- raster::extract(vh_coefs, pts_example) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_example$type) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(`Band name` = c('Intersept', 'Slope', 
-                           'Sin(x)', 'Cos(x)', 
-                           'Sin(2x)', "Cos(2x)"), Band = 1:6)
-
-pts_vh_fit <- do.call(cbind, lapply(names(pts_vh)[1:7], function(typ){
-    coefs <- pts_vh %>% pull(typ)
-    data.frame(val = coefs[1] + coefs[2] * doy +
-    coefs[3] * sin(2 * pi * doy /365) + 
-    coefs[4] * cos(2 * pi * doy /365) + 
-    coefs[5] * sin(4 * pi * doy /365) + 
-    coefs[6] * cos(4 * pi * doy /365))
-})) %>% `names<-`(names(pts_vh)[1:7]) %>% 
-    mutate(DOY = doy) %>% 
-    mutate(polarization = 'VH',
-           type = 'Harmoic regression')
-
-pts_fit <- rbind(pts_vv_fit, pts_vh_fit) %>% 
-    pivot_longer(names(.)[1:7], 
-                 names_to = "Land cover type", 
-                 values_to = "dB")
-rm(pts_vv_ts, pts_vh_ts)
-
-# Make figure
-pts_ts <- merge(pts_ts, cols_lc[, 2:3])
-pts_fit <- merge(pts_fit, cols_lc[, 2:3])
-ts_epl <- ggplot() + 
-    geom_point(data = pts_ts, 
-               aes(x = DOY, y = `dB`, 
-                   color = factor(ids)),
-               size = 0.6) +
-    geom_line(data = pts_fit,
-               aes(x = DOY, y = `dB`, 
-                   color = factor(ids))) +
-    facet_wrap(~polarization, 
-               scales = 'free_y', nrow = 2,
-               strip.position = "top") +
-    scale_color_manual("Land cover type",
-                       values = cols_lc$cols, 
-                       breaks = cols_lc$ids,
-                       labels = cols_lc$`Land cover type`) +
-    theme_bw()
-
-s1_fg <- ggarrange(
-    ggarrange(vv_fg, vh_fg,
-              labels = c('VV', 'VH'),
-              font.label = list(size = 12),
-              vjust = 3,
-              ncol = 2), 
-    ts_epl, ncol = 2)
-
-ggsave(here('docs/figures/s1_image.png'),
-       s1_fg,
-       width = 8, height = 2.7, dpi = 300)
-```
-
-## Samples for Random forest and U-Net
-
-This figure will provide the selected 200 tiles for RF to predict, the sub-tiling system for human checking, and the distribution of sub-tiles (chips) with score higher than 7.
-
-```{r}
-library(sf)
-library(rasterVis)
-library(ggnewscale)
-library(cowplot)
+save(main_fg, file = 'figures/nasa_tiling.rda')
 
@@
                        ncol = 3, widths = c(0.1, 2, 1))
-
-ggsave(here('docs/figures/labels.png'),
-       labels_fg,
-       width = 8, height = 4, dpi = 300)
+fg <- ggarrange(main_fg, labels_fg, ncol = 2, widths = c(1, 1.8))
+ggsave(here('docs/figures/nasa_poster_exp_img.png'),
+       fg, bg = 'white', width = 10, height = 4, dpi = 300)
 ```
 
-## Workflow
+- We used NICFI basemap tiling system to manage the whole study area. 
+- We split each tile into 8 * 8 sub-tiles. Within each tile, we randomly selected 4 sub-tiles (3 for training and 1 for validation) to make image-wise training labels with quality information.
 
-This figure will provide an overall flowchart of methods.
+```{r, fig.align='center', warning=F, message=F, fig.width=10, fig.height=4, fig.cap = "A: fragmented consensus labels, B: Image-wise RF guessed label, C: Human refined label"}
+knitr::include_graphics("figures/nasa_poster_exp_img.png")
+```
+
+---
+
+## U-Net training
+
+```{r, fig.align='center', out.width = "90%"}
+knitr::include_graphics("figures/curves_k15_only_final_mod.png")
+```
+---
 
 ## Results
-### Learning rate comparison
 
-```{r}
-library(tidyverse)
-# Define function
-get_curves <- function(experiment_name,
-                       step = 59,
-                       path = here('results/scalar/compare_lr')){
-    # Get file names
-    fns <- list.files(path, 
-                      pattern = experiment_name,
-                      full.names = T)
-    fns <- fns[str_detect(fns, 'Validate')]
-
-    # Process each csv
-    scalars <- lapply(fns, function(fn){
-        scalar <- read.csv(fn, stringsAsFactors = F) %>% 
-            mutate(Step = Step / step) %>% # step of each epoch
-            dplyr::select(-Wall.time)
-    })
-    names(scalars) <- gsub(
-        '.csv', "", 
-        str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
-
-    scalars
-}
-
-# Clean scalar csvs
-curves_lr_01 <- get_curves('unet_lr_01')
-curves_lr_001 <- get_curves('unet_lr_001')
-curves_lr_0001 <- get_curves('unet_lr_0001')
-curves_lr_00001 <- get_curves('unet_lr_00001')
-curves_lr_000001 <- get_curves('unet_lr_000001')
-
-types <- c('AA', 'IoU', 'Cropland', 'Forest', 
-           'Grassland', 'Shrubland', 'Water', 
-           'Built-up', 'Bareland')
-content <- do.call(rbind, lapply(types, function(type){
-    if (type == 'Built-up') {
-        item <- 'Urban'
-        } else{item <- type}
-    list(curves_lr_01[[item]],
-         curves_lr_001[[item]],
-         curves_lr_0001[[item]],
-         curves_lr_00001[[item]],
-         curves_lr_000001[[item]]) %>% 
-        reduce(left_join, by = "Step") %>% 
-        `colnames<-`(c("Epoch", '0.1', '0.01', 
-                       '0.001', '0.0001', '0.00001')) %>% 
-        mutate(Item = type) %>% 
-        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
-                     names_to = 'Learning rate', 
-                     values_to = 'Value')
-})) %>% mutate(Item = factor(Item, levels = types))
-
-# Get final plot
-curves_lr <- ggplot(content, aes(x = Epoch, y = Value)) +
-    # geom_line(aes(color = `Learning rate`)) +
-    geom_smooth(aes(color = `Learning rate`), span = 0.2,
-                se = F, size = 0.6) +
-    scale_color_brewer(palette = "Set1") +
-    facet_wrap(~Item, scales = 'free_y') +
-    labs(y = 'Accuracy') +
-    theme_bw() +
-    theme(legend.position = 'top')
-ggsave(here('docs/figures/curves_lr.png'),
-       curves_lr,
-       width = 8, height = 5, dpi = 300)
+```{r, fig.align='center', out.width = "80%"}
+knitr::include_graphics("figures/nasa_poster_result_img.png")
 ```
 
-### Overall results
-#### Metrics
-```{r}
-library(glue)
-# Get file names
-fns <- list.files(here(
-    file.path('results/scalar',
-              'unet_score08_hardiness20_epoch200')), 
-    full.names = T)
+---
 
-# Metrics
-fns <- fns[str_detect(fns, 'Validate')]
-metrics_last10 <- do.call(cbind, lapply(fns, function(fn){
-    read.csv(fn, stringsAsFactors = F) %>% 
-        dplyr::select(-c(Wall.time, Step)) %>% 
-        tail(10)
-}))
-names(metrics_last10) <- gsub(
-    '.csv', "", 
-    str_extract(fns, '[A-Z|a-z]{1}[A-Z|a-z]+.csv'))
+## Results
 
-# Calculate mean and sd
-items <- c('loss', 'AA', 'mIoU', 'Cropland', 'Forest', 
-           'Grassland', 'Shrubland', 'Water', 
-           'Urban', 'Bareland')
-types <- c('Cropland', 'Forest', 
-           'Grassland', 'Shrubland', 'Water', 
-           'Built-up', 'Bareland', 'AA')
-
-tb <- do.call(rbind, lapply(items, function(item){
-    vals <- metrics_last10 %>% pull(all_of(item))
-    if (item == 'Urban') item <- 'Built-up'
-    if (item == 'loss') item <- 'Loss'
-    data.frame(mean = mean(vals),
-               sd = sd(vals)) %>% 
-        mutate(Metric = item)
-}))
-
-acc <- tb %>% filter(Metric %in% types) %>% 
-    mutate(mean = round(mean * 100, 2),
-           sd = round(sd * 100, 2),
-           Class = factor(Metric, levels = types),
-           Accuracy = glue(
-               paste0('{format(round(mean, digits = 2), nsmall = 2)}',
-                      '\u00B1{format(round(sd, digits = 2), nsmall = 2)} %'))) %>% 
-    dplyr::select(Class, Accuracy) %>% 
-    arrange(Class)
-write.csv(acc, here('docs/figures/acc_last10epoch.csv'),
-          row.names = F)
+```{r, fig.align='center', out.width = "90%", warning=F, message=F}
+knitr::include_graphics("figures/nasa_poster_eval.png")
+load(here('docs/figures/conf_mean_std.rda'))
+mean_std %>% 
+  dplyr::filter(Landcover != 'Wetland') %>% 
+  t() %>% 
+  kbl() %>%
+  kable_paper("striped", full_width = F, font_size = 16) %>%
+  column_spec(1, bold = T) %>% 
+  row_spec(1:2, color = "white", background = 'black')
 ```
-
-#### Scalars
-
-```{r}
-library(here)
-# Get file names
-fns <- list.files(here(
-    file.path('results/scalar',
-              'unet_score08_hardiness20_epoch200')), 
-    full.names = T)
-
-step <- 59
-# Learning rate
-lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
-    mutate(Epoch = Step / step)
-
-# Scalars
-fns <- fns[str_detect(fns, 'Validate|Train_lr')]
-final_mod_scalars <- lapply(fns, function(fn){
-    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
-        mutate(Epoch = Step / step) %>% 
-        dplyr::select(-c(Wall.time, Step))
-})
-names(final_mod_scalars) <- gsub(
-    '.csv', "", 
-    str_extract(fns, '[A-Z|a-z]{1}[A-Z|a-z]+.csv'))
-
-types <- c('Learning rate', 'Loss', 'AA', 'mIoU', 'Cropland', 'Forest', 
-           'Grassland', 'Shrubland', 'Water', 
-           'Built-up', 'Bareland')
-lc <- c('Cropland', 'Forest', 
-        'Grassland', 'Shrubland', 'Water', 
-        'Built-up', 'Bareland', 'AA')
-content <- do.call(rbind, lapply(types, function(type){
-    if (type == 'Built-up') {
-        item <- 'Urban'
-    } else if (type == 'Loss'){
-        item <- 'loss'
-    } else if (type == 'Learning rate'){
-        item <- 'lr'
-    } else {item <- type}
-    final_mod_scalars[[item]] %>% 
-        mutate(Item = type)
-}))
-
-# Plot
-curve_lr <- content %>% 
-    filter(Item == 'Learning rate') %>% 
-    mutate(Value = Value * 1000) %>% 
-    ggplot(., aes(x = Epoch, y = Value)) +
-    geom_line() +
-    labs(y = expression(Learning ~ rate ~ (10^-3)), x = '') +
-    theme_bw()
-curve_loss <- content %>% 
-    filter(Item == 'Loss') %>% 
-    ggplot(., aes(x = Epoch, y = Value)) +
-    geom_line() +
-    labs(y = 'Loss', x = '') +
-    theme_bw()
-curve_iou <- content %>% 
-    filter(Item == 'mIoU') %>% 
-    ggplot(., aes(x = Epoch, y = Value)) +
-    geom_line() +
-    labs(y = 'mIoU', x = '') +
-    theme_bw()
-curves_acc <- content %>% 
-    filter(Item %in% lc) %>% 
-    mutate(Item = factor(Item, levels = lc)) %>% 
-    ggplot(aes(x = Epoch, y = Value)) +
-    geom_line() +
-    labs(y = 'Accuracy') +
-    facet_wrap(~Item, scales = 'free_y', 
-               nrow = 2, ncol = 4) +
-    theme_bw()
-curves <- ggarrange(
-    ggarrange(curve_lr, curve_loss, curve_iou, ncol = 3),
-    curves_acc, nrow = 2, heights = c(1, 1.6))
-
-ggsave(here('docs/figures/curves_final_mod.png'),
-       curves,
-       width = 8, height = 5, dpi = 300)
-```
-
-## Sensitivity analysis
-### Quality weights
-#### Score factor
-```{r}
-# Clean scalar csvs
-curves_no_weight <- get_curves(
-    'unet_no_weight',
-    path = here('results/scalar/compare_score'))
-curves_score02 <- get_curves(
-    'unet_score_02',
-    path = here('results/scalar/compare_score'))
-curves_score08 <- get_curves(
-    'unet_score_08',
-    path = here('results/scalar/compare_score'))
-curves_score16 <- get_curves(
-    'unet_score_16',
-    path = here('results/scalar/compare_score'))
-curves_score32 <- get_curves(
-    'unet_score_32',
-    path = here('results/scalar/compare_score'))
-curves_score100 <- get_curves(
-    'unet_score_100',
-    path = here('results/scalar/compare_score'))
-
-types <- c('AA', 'IoU', 'Cropland', 'Forest', 
-           'Grassland', 'Shrubland', 'Water', 
-           'Built-up', 'Bareland')
-content <- do.call(rbind, lapply(types, function(type){
-    if (type == 'Built-up') {
-        item <- 'Urban'
-        } else{item <- type}
-    list(curves_no_weight[[item]],
-         curves_score02[[item]],
-         curves_score08[[item]],
-         curves_score16[[item]],
-         curves_score32[[item]],
-         curves_score100[[item]]) %>% 
-        reduce(left_join, by = "Step") %>% 
-        `colnames<-`(c("Epoch", '0', '0.2', '0.8', 
-                       '1.6', '3.2', '10')) %>% 
-        mutate(Item = type) %>% 
-        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
-                     names_to = 'Weight factor', 
-                     values_to = 'Value')
-})) %>% mutate(Item = factor(Item, levels = types),
-               `Weight factor` = factor(
-                   `Weight factor`, 
-                   levels = c('0', '0.2', '0.8', 
-                              '1.6', '3.2', '10')))
-
-# Get final plot
-curves_score <- ggplot(content, aes(x = Epoch, y = Value)) +
-    # geom_line(aes(color = `Weight factor`)) +
-    geom_smooth(aes(color = `Weight factor`), span = 0.2,
-                se = F, size = 0.6) +
-    scale_color_manual(
-        values = c('Black', 
-                   RColorBrewer::brewer.pal(5, "Dark2"))) +
-    # scale_color_brewer(palette = "Dark2") +
-    facet_wrap(~Item, scales = 'free_y') +
-    labs(y = 'Accuracy') +
-    theme_bw() +
-    theme(legend.position = 'top') +
-    guides(color = guide_legend(nrow = 1))
-ggsave(here('docs/figures/curves_score.png'),
-       curves_score,
-       width = 8, height = 5, dpi = 300)
-```
-
-#### Hardiness
-```{r}
-# Clean scalar csvs
-curves_score08_nohard <- get_curves(
-    'unet_score_08',
-    path = here('results/scalar/compare_score'))
-curves_hard2 <- get_curves(
-    'unet_score08_hardiness_2',
-    path = here('results/scalar/compare_score'))
-curves_hard4 <- get_curves(
-    'unet_score08_hardiness_4',
-    path = here('results/scalar/compare_score'))
-curves_hard6 <- get_curves(
-    'unet_score08_hardiness_6',
-    path = here('results/scalar/compare_score'))
-
-types <- c('AA', 'IoU', 'Cropland', 'Forest', 
-           'Grassland', 'Shrubland', 'Water', 
-           'Built-up', 'Bareland')
-content <- do.call(rbind, lapply(types, function(type){
-    if (type == 'Built-up') {
-        item <- 'Urban'
-        } else{item <- type}
-    list(curves_score08_nohard[[item]],
-         curves_hard2[[item]],
-         curves_hard4[[item]],
-         curves_hard6[[item]]) %>% 
-        reduce(left_join, by = "Step") %>% 
-        `colnames<-`(c("Epoch", '0', '2', '4', '6')) %>% 
-        mutate(Item = type) %>% 
-        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
-                     names_to = 'Weight scale', 
-                     values_to = 'Value')
-})) %>% mutate(Item = factor(Item, levels = types),
-               `Weight scale` = factor(
-                   `Weight scale`, 
-                   levels = c('0', '2', '4', '6')))
-
-# Get final plot
-curves_hard <- ggplot(content, aes(x = Epoch, y = Value)) +
-    geom_smooth(aes(color = `Weight scale`), span = 0.2,
-                se = F, size = 0.6) +
-    scale_color_manual(
-        values = c('Black', 
-                   RColorBrewer::brewer.pal(3, "Dark2"))) +
-    # scale_color_brewer(palette = "Dark2") +
-    facet_wrap(~Item, scales = 'free_y') +
-    labs(y = 'Accuracy') +
-    theme_bw() +
-    theme(legend.position = 'top') +
-    guides(color = guide_legend(nrow = 1))
-ggsave(here('docs/figures/curves_hard.png'),
-       curves_hard,
-       width = 8, height = 5, dpi = 300)
-```
-
-### Sampling
-
-```{r}
-
-```

### 2022-01-24 docs/tanzania_full_map.Rmd
Routine save

---
title: "Make the full map of Tanzania"
author: "Lei Song"
date: "1/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Introduction

This document is to record steps for making the full map of Tanzania.

- Generate guessing labels (done)
- Random select and manually check validate dataset
- Fine tune a U-Net model for the whole country

### Validate dataset generation
#### Check the quality of labels
```{r}
tiles <- read_sf("results/tanzania/catalog_sample_tiles.geojson")
library(tidyr)
# Check labels
stats_guess_labels <- do.call(
    rbind, 
    lapply(unique(tiles$tile), 
           function(tile_id){
               sub_tiles <- tiles %>% filter(tile == tile_id) %>% 
                   st_drop_geometry() %>% 
                   mutate(surfix = paste(tile, index, sep = '_')) %>% 
                   mutate(score_path = file.path(here('results/tanzania/guess_labels'),
                                                 sprintf('score_%s.tif', surfix)))
               do.call(rbind, lapply(sub_tiles$surfix, function(sur) {
                   pth <- sub_tiles %>% filter(surfix == sur) %>% 
                       pull(score_path)
                   scores <- values(rast(pth))
                   na_ratio <- sum(is.na(scores))/ length(scores)
                   data.frame(surfix = sur,
                              hasna = any(is.na(scores)), 
                              na_ratio = na_ratio,
                              mean = mean(scores, na.rm = T),
                              sd = sd(scores, na.rm = T),
                              min = min(scores, na.rm = T),
                              max = max(scores, na.rm = T))}))
               }
           )
    )
save(stats_guess_labels, file = 'results/tanzania/stats_guess_labels.rda')
err_labels <- stats_guess_labels %>% filter(hasna == TRUE) %>% 
    separate(col = surfix, into = c('tile', 'index'), sep = "_")
```

#### Check the quality of images

```{r}
# Check images
stack_dir <- '/Volumes/elephant/pred_stack'
img_quality <- do.call(
    rbind, 
    mclapply(unique(tiles$tile), 
             function(tile_id){
                 imgs <- rast(file.path(stack_dir, paste0(tile_id, '.tif')))
                 nas <- is.na(imgs)
                 zeros <- imgs == 0
                 rm(imgs)
                 nas <- freq(nas) %>% as.data.frame() %>% 
                     mutate(count = count / (dim(nas)[1] * dim(nas)[2])) %>% 
                     rename(na_ratio = count) %>% 
                     mutate(tile_id = tile_id) %>% 
                     filter(value == 1) %>% select(-value)
                 zeros <- freq(zeros) %>% as.data.frame() %>% 
                     mutate(count = count / (dim(zeros)[1] * dim(zeros)[2])) %>% 
                     rename(zero_ratio = count) %>% 
                     mutate(tile_id = tile_id) %>% 
                     filter(value == 1) %>% select(-value)
                 gc()
                 full_join(nas, zeros, by = c('tile_id', 'layer')) %>% 
                     select(tile_id, layer, na_ratio, zero_ratio)
             }, mc.cores = 6))

imgs <- rast(file.path(stack_dir, paste0(tiles$tile[1], '.tif')))
layers <- data.frame(layer_name = names(imgs)) %>% 
    mutate(layer = 1:nrow(.))
img_quality <- left_join(img_quality, layers, by = 'layer') %>% 
    select(tile_id, layer_name, na_ratio, zero_ratio); rm(imgs, layers)
save(img_quality, file = 'results/tanzania/img_quality.rda')
img_withna <- img_quality %>% filter(!is.na(na_ratio)) %>% 
    pull(tile_id) %>% unique()
img_withzero <- img_quality %>% filter(zero_ratio > 0.3) %>% 
    filter(!grepl("vv|vh", layer_name)) %>% 
    pull(tile_id) %>% unique()
```

There are a few problematic images

```{r}
# 1192-988, water, missing partial image
# 1207-971, land, missing half image
# 1229-975, land, seems weird
# 1234-957, land, missing the whole image
# 1246-962, land, missing the whole image
# VH
# 1200-974, land and water, seems weird
# 1199-1018, land, seems weird
# 1245-974, land, a small fragment seems weird
```

#### Get candidate validation

Get one sub tile from each tile randomly as validation. Not all of them will be used. After manually checking, low quality ones that cannot be fixed easily would be excluded.

Why random ones rather than good ones? To optimize the cooperation of random forest and U-Net. Because if selecting good ones, the results might be biased to easy-to-model instances.
```{r}
skip_tile <- err_labels %>% pull(tile) %>% unique()
stats_guess_labels <- stats_guess_labels %>% 
    separate(col = surfix, into = c('tile', 'index'), sep = "_") %>% 
    filter(!tile %in% skip_tile)
set.seed(124)
validate_labels <- stats_guess_labels %>% 
    group_by(tile) %>% 
    sample_n(1) %>% ungroup() %>% 
    dplyr::select(tile, index) %>% 
    mutate(index = as.integer(index))

# Check the validate
# 1 is TRUE, 0 is FALSE
tiles_validate <- right_join(tiles, validate_labels, by = c("tile", "index")) %>% 
    mutate(use = 1, modify = 0)
plot(tiles_validate$geometry)
write_sf(tiles_validate, "results/tanzania/catalog_tiles_validate.geojson")
```

Next, the author manually checked these validation sub-tiles. Only the good ones would be used for validation.

First, move these validation candidate into a separate folder.

```{r}
copy_from <- here("results/tanzania/guess_labels")
copy_to <- here('results/tanzania/temp')
if (!dir.exists(copy_to)) dir.create(copy_to)
tiles_validate <- tiles_validate %>% 
    mutate(tile_id = paste(tile, index, sep = "_"))
cp <- lapply(tiles_validate$tile_id, function(tile_move) {
    fnames_from <- sprintf("%s/%s_%s.tif", 
                           copy_from, c("guess", "scores", "score"), tile_move)
    fnames_to <- sprintf("%s/%s_%s.tif", 
                         copy_to, c("guess", "scores", "score"), tile_move)
    file.copy(from = fnames_from, 
              to = fnames_to)
})
```

Next step is to check and fix other labels

```{r}
tile_index_val <- tiles_validate %>% 
    mutate(tile_index = paste(tile, index, sep = "_")) %>% 
    pull(tile_index)
tile_index_train <- stats_guess_labels %>% 
    mutate(index = as.integer(index)) %>% 
    mutate(tile_index = paste(tile, index, sep = "_")) %>% 
    filter(!tile_index %in% tile_index_val) %>% 
    dplyr::select(tile, index)
tiles_train <- right_join(tiles, tile_index_train, by = c("tile", "index")) %>% 
    mutate(use = 1, modify = 0, comment = NA)
write_sf(tiles_train, "results/tanzania/catalog_tiles_train.geojson")
```

### 2022-01-24 guess_model/8_human_refine.R

@@ -171,31 +171,55 @@ refine_scores <- function(tile_sf,
 # 9: bareland
 
 # Read vectors
-tiles <- read_sf('results/north/catalog_sample_tiles.geojson')
-tiles_big <- read_sf('data/geoms/tiles_nicfi_north.geojson')
-roads_all <- read_sf(here('data/osm/roads.geojson'))
-roads_all <- st_join(roads_all, tiles_big)
-waterbodies_all <- read_sf(here('data/osm/waterbodies.geojson'))
-waterbodies_all <- st_join(waterbodies_all, tiles_big)
-buildings_all <- read_sf(here('data/osm/buildings.geojson'))
-buildings_all <- st_join(buildings_all, tiles_big)
+tiles <- read_sf('results/tanzania/catalog_tiles_train.geojson')
+tiles_big <- read_sf('data/geoms/tiles_nicfi_others.geojson')
+roads_all <- read_sf(here('data/vct_tanzania/roads.geojson'))
+roads_all <- roads_all %>%
+    filter(fclass %in% c('primary', 'secondary', 'tertiary',
+                         'trunk', 'primary_link', 'secondary_link',
+                         'tertiary_link', 'rail'))
+roads_all <- st_join(roads_all, tiles_big) %>% 
+    filter(!is.na(tile))
+gc()
+waterbodies_all <- read_sf(here('data/vct_tanzania/waterbodies.geojson'))
+waterbodies_all <- st_join(waterbodies_all, tiles_big) %>% 
+    filter(!is.na(tile))
+gc()
+fn <- 'open_buildings_v1_polygons_ne_10m_TZA.csv'
+buildings_all <- st_read(here(file.path('data/open_buildings', fn)),
+                     int64_as_string = F,
+                     stringsAsFactors = F); rm(fn)
+buildings_all <- buildings_all %>% 
+    mutate(latitude = as.numeric(latitude),
+           longitude = as.numeric(longitude),
+           area_in_meters = as.numeric(area_in_meters),
+           confidence = as.numeric(confidence)) %>% 
+    # Buildings with area less than a pixel might not be representative
+    filter(confidence >= 0.75 & area_in_meters > 4.8^2) %>% 
+    mutate(geometry = st_as_sfc(geometry) %>% 
+               st_cast('MULTIPOLYGON')) %>% 
+    st_as_sf() %>% st_set_crs(4326) %>% 
+    st_make_valid()
[…]

### 2022-01-24 guess_model/9_2_train_sampling.R

@@ -1,125 +1,0 @@
-# Title     : Script of sampling
-# Objective : To test the impact of sampling ratio and methods.
-# Created by: Lei Song
-# Created on: 07/31/21
-# alias Rscript='/Library/Frameworks/R.framework/Resources/bin/Rscript'
-
-#######################
-##  Step 1: Setting  ##
-#######################
-message('Step 1: Setting')
-
-## Load packages
-library(glue)
-library(here)
-library(sf)
-library(dplyr)
-library(stringr)
-library(tidyverse)
-
-##########################
-##  Step 2: Read files  ##
-##########################
-tiles <- read_sf(here('data/geoms/tiles_nicfi.geojson'))
-trains <- read.csv(here('results/tanzania/dl_catalog_train.csv'))
-valids <- read.csv(here('results/tanzania/dl_catalog_valid.csv'))
-
-##############################
-##  Step 3: Sampling ratio  ##
-##############################
-# Reduce sub tile number within each tile
-# Still use all tiles over study area
-
-message('--One each tile')
-set.seed(10)
-trains_1 <- trains %>% 
-    group_by(tile) %>% 
-    do(sample_n(., 1)) %>% 
-    ungroup()
-write.csv(
-    trains_1, 
-    here('results/north/dl_catalog_train_1.csv'))
-
-message('--Two each tile')
-set.seed(11)
-trains_2 <- trains %>% 
-    group_by(tile) %>% 
-    do(sample_n(., 2)) %>% 
-    ungroup()
-write.csv(
-    trains_2, 
-    here('results/north/dl_catalog_train_2.csv'))
-
-# Sample tiles, and select 3 sub-tiles from each
-# Sampling tiles is a bit faster to generate guess label
-# and maybe a bit faster for human checking
-# However, might be less representative.
-message('--Sampling tiles')
-
-# Comparing to one from each tile
-message('----Ratio 0.34')
-set.seed(10)
-tiles_selected <- tiles %>% 
-    sample_frac(0.34)
-trains_selected <- trains %>% 
-    filter(tile %in% tiles_selected$tile)
-write.csv(
-    trains_selected, 
-    here('results/north/dl_catalog_train_random_34.csv'))
-
-# Comparing to two from each tile
-message('----Ratio 0.67')
-set.seed(11)
-tiles_selected <- tiles %>% 
-    sample_frac(0.67)
[…]

### 2022-01-24 docs/ecrs_2022_poster_imgs.Rmd
Add poster for ECRS 2022

---
title: "ecrs_2022_poster"
author: "Lei Song"
date: "1/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(terra)
library(stars)
library(tmap)
library(ggpubr)
library(gridExtra)

pred_path <- here(file.path('results/dl/prediction',
                           'unet_k15_only_clr_200epc',
                           'landcover_north_withwl.tif'))
color_tb <- data.frame(
    id = 1:8,
    type = c("Cropland", "Forest", 
             "Grassland", "Shrubland", 
             "Water", 'Built-up', "Bareland", 
             'Wetland'),
    color = c('#ff7f00', '#074702', '#b2df8a',
              '#33a02c', '#3347f9', '#5a6057',
              '#fdbf6f', '#0ea591'))
pred <- read_stars(pred_path)

# plot
tmap_mode("plot")
pred_final <- tm_shape(pred) +
    tm_raster("landcover_north_withwl.tif", 
              title = "Land cover types",
              n = 8, style = 'cat',
              labels = color_tb$type,
              palette = color_tb$color) +
    tm_layout(frame = F,
              legend.show = F,
              outer.margins = c(0.02, 0.01, 0, 0.01),
              inner.margins = 0,
              bg.color = 'transparent')
pred_final <- tmap_grob(pred_final)

# Get legend
r_df <- data.frame(x = 1:8, 
                   y = 1:8,
                   rst = as.factor(1:8))
legend_lc <- ggplot() + 
    geom_raster(
        data = r_df, 
        aes(x = x, y = y, 
            fill = rst)) +
    scale_fill_manual('Land cover',
                      values = color_tb$color, 
                      breaks = 1:8,
                      labels = color_tb$type) +
    theme_minimal() +
    theme(legend.position = 'right',
          legend.text = element_text(color = 'black'),
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"),
          plot.background = element_rect(fill = "transparent"))+
    guides(fill = guide_legend(ncol = 1))
legend_lc <- get_legend(legend_lc)
pred_final_plt <- ggarrange(pred_final, legend_lc, NA,
                        ncol = 3, widths = c(5, 1, 2))
ggsave(here('docs/figures/ecrs_results.png'),
       pred_final_plt, 
       width = 8, height = 6, dpi = 600)
```

```{r}
library(raster)
library(glue)
library(here)
library(sf)
library(nngeo)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(sf)
library(rasterVis)
library(ggnewscale)
library(cowplot)
library(ggpubr)

# Read boundaries
study_area <- read_sf(here('data/geoms/study_area.geojson')) %>% 
    st_remove_holes()
nicfi_tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson')) %>% 
    mutate(`NICFI tile` = 1)

# Make the main figure
main_fg <- ggplot(nicfi_tiles) +
    geom_sf(fill = NA, 
            aes(color = "grey"), 
            lwd = 0.5) +
    geom_sf(data = study_area, fill = NA, 
            aes(color = 'red', lty = 'solid')) +
  scale_color_identity(name = '',
                         breaks = c('black', 'red'),
                         labels = c('NICFI tiles', 'Study area'),
                         guide = 'legend') +
    scale_linetype_identity(name = '',
                            breaks = c('dotted', 'solid'),
                            labels = c('NICFI tiles', 'Study area'),
                            guide = 'legend') +
    theme_minimal() + 
    theme(legend.position = 'none',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))
ggsave(here('docs/figures/ecrs_tiling.png'),
       main_fg, 
       width = 6, height = 6, dpi = 600)

id_selected <- '1226-999'
# Read tiles
nicfi_tiles <- read_sf(
    here('data/geoms/tiles_nicfi_north.geojson'))

# Sub-tiling
indices <- matrix(1:64, 8, 8)
indices <- indices[, ncol(indices):1]
sub_tiling <- nicfi_tiles %>% 
    filter(tile == id_selected) %>% 
    st_make_grid(n = c(8, 8)) %>% 
    st_sf() %>% 
    mutate(index = as.vector(indices))
trains_inside <- sub_tiling %>% 
    filter(index %in% (read.csv(
    here('results/north/dl_catalog_train.csv'),
    stringsAsFactors = F) %>% 
    filter(tile == id_selected) %>% 
    pull(index))) %>% 
    mutate(Usage = 'Train')
valids_inside <- sub_tiling %>% 
    filter(index %in% (read.csv(
    here('results/north/dl_catalog_valid.csv'),
    stringsAsFactors = F) %>% 
    filter(tile == id_selected) %>% 
    pull(index))) %>% 
    mutate(Usage = 'Validate')
# Labels of each sub-tile
sub_tiles <- rbind(trains_inside, valids_inside) %>% 
    arrange(index); rm(trains_inside, valids_inside)

# Sub-tiling figure
sub_tiling_fg <- ggplot(sub_tiling) + 
    geom_sf(data = sub_tiles, aes(fill = Usage),
            color = 'black', lwd = 0.3) +
    scale_fill_manual(values = c('forestgreen', 'orangered')) +
    geom_sf(color = 'black', fill = NA, lwd = 0.3) + 
    geom_sf_text(aes(label = index), size = 10) +
    theme_minimal() +
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          legend.text = element_text(size = 30),
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          plot.title = element_text(hjust = -0.15, vjust = -6),
          plot.margin = unit(rep(0, 4),"cm"))

ggsave(here('docs/figures/ecrs_subtiling.png'),
       sub_tiling_fg, 
       width = 6, height = 6, dpi = 600)

sub_tiles <- sub_tiles %>% filter(index == 12)

# Weak labels
labels_esb <- raster(here('data/north/lc_labels_north_mask.tif')) %>% 
        crop(sub_tiles)

labels_guess <- lapply(sub_tiles$index, function(id){
    prefix <- glue('results/north/guess_labels/guess_{id_selected}')
    raster(here(glue('{prefix}_{id}.tif')))
})[[1]]

labels_refine <- lapply(sub_tiles$index, function(id){
    prefix <- glue('results/north/refine_labels/{id_selected}')
    raster(here(glue('{prefix}_{id}_label.tif')))
})[[1]]

labels_dl <- st_crop(pred, st_transform(sub_tiles, 
                                        crs = st_crs(pred)))

# Plot
color_tb <- data.frame(
    id = 1:7,
    type = c("Cropland", "Forest", 
             "Grassland", "Shrubland", 
             "Water", 'Built-up', "Bareland"),
    color = c('#ff7f00', '#074702', '#b2df8a',
              '#33a02c', '#3347f9', '#5a6057',
              '#fdbf6f'))
plot_rst <- function(rst, bry){
    r_df <- as.data.frame(rst, xy = TRUE) %>%
        `colnames<-`(c('x', 'y', 'rst')) %>%
        mutate(rst = as.factor(rst)) %>% 
        na.omit()
    colors <- color_tb %>% filter(id %in% unique(r_df$rst))

    # plot
    ggplot() + 
        geom_raster(
            data = r_df, 
            aes(x = x, y = y, 
                fill = rst)) +
        scale_fill_manual(
            values = colors %>% pull(color), 
            breaks = colors %>% pull(id),
            labels = colors %>% pull(type)) +
        geom_sf(data = bry, 
                color = 'blue', fill = NA,
                lty = 'dotted', lwd = 0.4) +
        theme_minimal() +
        theme(legend.position = 'none',
              axis.title.x = element_blank(),
              axis.text.x = element_blank(),
              axis.ticks.x = element_blank(),
              axis.title.y = element_blank(),
              axis.text.y = element_blank(),
              axis.ticks.y = element_blank(),
              panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(),
              plot.margin = unit(rep(0, 4),"cm"))
}

plots_esb <- plot_rst(labels_esb, sub_tiles)

plots_guess <- plot_rst(labels_guess, 
                        sub_tiles %>% 
                            st_transform(crs = crs(labels_guess)))

plots_refine <- plot_rst(labels_refine, 
                        sub_tiles %>% 
                            st_transform(crs = crs(labels_refine)))
plots_dl <- plot_rst(labels_dl, sub_tiles %>% 
                            st_transform(crs = st_crs(labels_dl)))

# Ensemble plots
labels_fg <- ggarrange(plots_esb, plots_guess, plots_refine, 
                       plots_dl, ncol = 4)
ggsave(here('docs/figures/exrs_exp_labels.png'),
       labels_fg, width = 10, height = 4, dpi = 300)
```

```{r}
id_selected <- '1226-1002'
# Read tiles
nicfi_tiles <- read_sf(
    here('data/geoms/tiles_nicfi_north.geojson'))

# Sub-tiling
indices <- matrix(1:64, 8, 8)
indices <- indices[, ncol(indices):1]
sub_tiles <- nicfi_tiles %>% 
    filter(tile == id_selected) %>% 
    st_make_grid(n = c(8, 8)) %>% 
    st_sf() %>% 
    mutate(index = as.vector(indices)) %>% 
    filter(index == 44)
fnames_nicfi <- list.files("/Volumes/elephant/plt_nicfi",
                           pattern = id_selected,
                           full.names = T)
nicfi_s1 <- stack(fnames_nicfi[1]) %>% subset(1:4)
nicfi_s1 <-  nicfi_s1%>% 
    crop(sub_tiles %>% st_transform(crs = crs(nicfi_s1)))

s1_fg <- ggRGB(nicfi_s1, r = 4, g = 3, b = 2, 
               scale = max(values(nicfi_s1)[, 2:4]), 
               stretch = 'hist') +
    theme_minimal() +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          plot.margin = unit(rep(0, 4),"cm"))
```

### 2022-02-21 docs/tanzania_full_map.Rmd
Finish all work before training

@@
 - Generate guessing labels (done)
-- Random select and manually check validate dataset
-- Fine tune a U-Net model for the whole country
+- Manually check labels (done)
+- Train U-Net model for the whole country
 
-### Validate dataset generation
+## Steps
+### Generate guessing labels
+
+Prepare the needed datasets and install necessary software (e.g. GRASS GIS) and libraries. Run the following scripts under guess_model to get the guessed labels:
+
+- 0_set_up.R
+- 1_ensemble_labels.R
+- 2_get_osm.R
+- 3_update_lc_labels_osm.R
+- 4_sampling.R
+- 5_get_training.R
+- 6_train_guess_model.R
+- 7_pred_guess_model.R
+
+### Manually check labels
+
+Analyze the reliability of labels based on the score of guessed label and the quality of satellite images.
+
 #### Check the quality of labels
+
 ```{r}
@@
 
-There are a few problematic images
+[*NOTE:*] There are a few problematic images. Skip them for now. These tiles can be fixed after segmentation.
 
@@
 
-#### Get candidate validation
+#### Get candidate validation and train
 
@@
 Why random ones rather than good ones? To optimize the cooperation of random forest and U-Net. Because if selecting good ones, the results might be biased to easy-to-model instances.
+
 ```{r}
+# Validation
 skip_tile <- err_labels %>% pull(tile) %>% unique()
@@
 
-Next, the author manually checked these validation sub-tiles. Only the good ones would be used for validation.
-
-First, move these validation candidate into a separate folder.
-
 ```{r}
-copy_from <- here("results/tanzania/guess_labels")
-copy_to <- here('results/tanzania/temp')
-if (!dir.exists(copy_to)) dir.create(copy_to)
-tiles_validate <- tiles_validate %>% 
-    mutate(tile_id = paste(tile, index, sep = "_"))
-cp <- lapply(tiles_validate$tile_id, function(tile_move) {
-    fnames_from <- sprintf("%s/%s_%s.tif", 
-                           copy_from, c("guess", "scores", "score"), tile_move)
-    fnames_to <- sprintf("%s/%s_%s.tif", 
-                         copy_to, c("guess", "scores", "score"), tile_move)
-    file.copy(from = fnames_from, 
-              to = fnames_to)
-})
-```
-
-Next step is to check and fix other labels
-
-```{r}
+# Train
 tile_index_val <- tiles_validate %>% 
@@
 ```
+
+#### Manually check
+
+Next, the author manually checked sub-tiles of validation and train. Script `8_human_refine.R` can help to do this step.
+
+#### Add existing labels of north to use
+
+Add to catalogs
+
+```{r}
+# Get labels from north
+## Randomly get 50% tiles
+## Get two for training
+
+# Read train labels
+num_tiles <- read_sf(here("data/geoms/tiles_nicfi_north.geojson")) %>% nrow()
+north_train <- read.csv(here("results/north/dl_catalog_train.csv"),
+  stringsAsFactors = F)
+
+# Keep two for each tile
+north_train <- do.call(
+  rbind,
+  lapply(
+    unique(north_train$tile),
+    function(this_tile) {
+      north_train %>%
+        filter(tile == this_tile) %>%
+        arrange(desc(score)) %>%
+        slice(1:2)}))
+
+# Read validate labels
+north_valid <- read.csv(here("results/north/dl_catalog_valid.csv"),
+  stringsAsFactors = F)
+
+# Randomly select 50% of tile to use
+set.seed(10)
+tile_to_use <- north_train %>%
+  group_by(tile) %>%
+  summarise(score = sum(score)) %>%
+  filter(score == 10) %>%
+  sample_n(round(num_tiles * 0.5)) %>%
+  pull(tile)
+
+# Finalize train and validate
+train_path <- 'train'
+valid_path <- 'validation'
+north_train <- north_train %>%
+  filter(tile %in% tile_to_use) %>%
+    mutate(
+    label = file.path(
+      train_path,
+      paste0(tile, "_", index, "_label.tif")
+    ),
+    img = file.path(
+      train_path,
+      paste0(tile, "_", index, "_img.tif")
+    )) %>% 
+  dplyr::select(tile_id, tile, index, label, img)
+north_valid <- north_valid %>%
+  filter(tile %in% tile_to_use) %>%
+    mutate(
+    label = file.path(
+      valid_path,
+      paste0(tile, "_", index, "_label.tif")
+    ),
+    img = file.path(
+      valid_path,
+      paste0(tile, "_", index, "_img.tif")
+    )) %>% 
+  dplyr::select(tile_id, tile, index, label, img)
+
+# Add to catalog of full country
+catalog_train <- read.csv(here("results/tanzania/dl_catalog_train.csv"),
+                          stringsAsFactors = FALSE) %>% 
+    rbind(north_train)
+catalog_validate <- read.csv(here("results/tanzania/dl_catalog_valid.csv"),
+                             stringsAsFactors = FALSE) %>% 
+    rbind(north_valid)
+write.csv(catalog_train, 
+          here('results/tanzania/dl_catalog_train.csv'),
+          row.names = F)
+write.csv(catalog_validate, 
+          here('results/tanzania/dl_catalog_valid.csv'),
+          row.names = F)
+```
+
+Double check
+
+```{r}
+catalog_train <- read.csv(here("results/tanzania/dl_catalog_train.csv"),
+                          stringsAsFactors = FALSE)
+files_should <- c(catalog_train$label, catalog_train$img)
+files_have <- file.path("train", list.files(here("results/tanzania/train")))
+setdiff(files_should, files_have)
+
+catalog_validate <- read.csv(here("results/tanzania/dl_catalog_valid.csv"),
+                             stringsAsFactors = FALSE)
+files_should <- c(catalog_validate$label, catalog_validate$img)
+files_have <- file.path("validation", list.files(here("results/tanzania/validation")))
+setdiff(files_should, files_have)
+```
+
+Move images
+
+```{r}
+move_train <- lapply(1:nrow(north_train), function(n) {
+    things_to <- unlist(north_train[n, c("label", 'img')])
+    things_from <- gsub("train", "dl_train", things_to)
+    things_to <- file.path(here("results/tanzania"), things_to)
+    things_from <- file.path(here("results/north"), things_from)
+    file.copy(things_from, things_to)
+})
+
+move_valid <- lapply(1:nrow(north_valid), function(n) {
+    things_to <- unlist(north_valid[n, c("label", 'img')])
+    things_from <- gsub("validation", "dl_valid", things_to)
+    things_to <- file.path(here("results/tanzania"), things_to)
+    things_from <- file.path(here("results/north"), things_from)
+    file.copy(things_from, things_to)
+})
+```
+
+### Train U-Net model for the whole country
+
+The scripts used for training U-Net are under directory hrlcm.

### 2022-02-21 guess_model/8_human_refine.R

@@ -205,21 +205,23 @@ buildings_all <- st_join(buildings_all, tiles_big) %>%
 gc()
 
 guess_dir <- here('results/tanzania/guess_labels')
+# refine_dir <- here('results/tanzania/validation')
 refine_dir <- here('results/tanzania/train')
+
 if (!dir.exists(refine_dir)) dir.create(refine_dir)
 
 # Change the parameters correspondingly
-tile_id <- '1221-989'
-tile_index <- '13'
+tile_id <- '1236-956'
+tile_index <- '41'
 convert <- F
 convert_class <- c(1)
-to_class <- c(3)
+to_class <- c(7)
 touch_scores <- T
 big_road <- F
 apply_mask <- T
 apply_line_mask <- F
-reduce_class <- c(4)
-reduce_ratio <- c(4)
+reduce_class <- c(1)
+reduce_ratio <- c(0)
 reduce_class <- c(reduce_class, 8)
 reduce_ratio <- c(reduce_ratio, 0)
 
@@ -361,14 +363,14 @@ if (apply_mask){
                             gdal=c("COMPRESS=LZW")))
 }
 
-# After all checks finished, run these lines to 
-# all tiles
-tiles_all <- here('results/tanzania/catalog_tiles_validate.geojson') %>% 
+# After all checks finished, run these lines to all tiles
+## Change validate/validation to train for train labels.
+tiles_all <- here('results/tanzania/catalog_tiles_train.geojson') %>% 
     read_sf() %>% 
     mutate(name_temp = paste(tile, index, sep = '_'))
 
 # Tiles get modified
-refine_tiles <- list.files(here('results/tanzania/validation')) %>% 
+refine_tiles <- list.files(here('results/tanzania/train')) %>% 
     str_extract(., '[0-9]+-[0-9]+_[0-9]+')
 
 # modify tiles
@@ -388,7 +390,7 @@ lapply(tiles_all$name_temp, function(tile_nm){
 
 # Remove abandoned ones
 tile_throw <- tiles_all %>% 
-    filter(use ==0)
+    filter(use == 0)
 lapply(tile_throw$name_temp, function(tile_nm){
     copy_to <- file.path(here('results/tanzania/validation'), 
                          glue('{tile_nm}_label.tif'))

### 2022-02-24 docs/tanzania_full_map.Rmd
Update python scripts for full country

@@
 The scripts used for training U-Net are under directory hrlcm.
+
+#### Preparation
+
+**[Launch AWS instance]** a few instance could be used for different needs.
+
+  - `g3.8xlarge`, 2 GPU, 16G GPU memory, $0.684/hr for SPOT instance.
+  - `g3.16xlarge`, 4 GPU, 32G GPU memory, $1.368/hr for SPOT instance.
+  - `g4dn.8xlarge`, 1 GPU, 16G GPU memory, $0.6528/hr for SPOT instance.
+  - `g4dn.12xlarge`, 4 GPU, 64G GPU memory, $1.1819/hr for SPOT instance.
+
+**[Clean and organize directories]** pull branch `full_country` of `hrlcm` to the instance, and create relative folders for dataset.
+
+**[Parse dataset from Dropbox]** run script `hrlcm/utils/parse_dataset.sh` to parse dataset into the instance.
+
+The instance should be ready to run training for now.
+
+#### Training
+
+Multiple type of models will be trained:
+- Using all bands and image standardization
+- Using all bands without image standardization
+- Using only NICFI bands with image standardization
+- Using only NICFI bands without image standardization
+
+Run models:
+
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_clr_200epc --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
+```
+
+Evaluation:
+
+```
+python hrlcm/evaluate.py --args_path 'results/tanzania/unet_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/tanzania/unet_clr_200epc/checkpoints/final.pth' --data_dir 'results/tanzania' --out_dir 'results/tanzania/evaluation' --stats_dir 'results/tanzania/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+
+scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/evaluation /Users/pinot/Dropbox/research/hrlcm/results/tanzania/unet_clr_200epc
+```
+
+Prediction
+
+```
+python hrlcm/predict.py --args_path 'results/tanzania/unet_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/tanzania/unet_clr_200epc/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/tanzania' --out_dir 'results/tanzania/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+
+scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/tanzania
+```
+
+#### Tensorboard
+
+If download log file to local machine, then it is easy to check the training loss curves.
+
+`tensorboard --logdir='./tensorboard_dirs' --port=16007`
+
+Do the following steps to use the tensorboard on a remote server (reference: https://blog.yyliu.net/remote-tensorboard/):
+
+1. You need to start SSH with transfer the remote server’s port to your local PC:
+
+    (on your local PC) `ssh -L 16007:127.0.0.1:16007 username@server_ip`
+
+2. Then you may start the tensorboard on the remote server with the specific port we want to transfer:
+
+    (on the remote server) `tensorboard --logdir='./tensorboard_dirs' --port=16007`

### 2022-02-24 hrlcm/dataset.py

@@ -4,7 +4,6 @@ Author: Lei Song
 Maintainer: Lei Song (lsong@clarku.edu)
 """
 
-import math
 import copy
 import os
 import sys
@@ -14,19 +13,6 @@ import pandas as pd
 import rasterio
 from torch.utils.data import Dataset
 from rasterio.plot import reshape_as_image
-
-
-def logistic_scale(x, L=1, k=1.5, x0=2.5):
-    """Util function to scale data using logistic
-    Args:
-        x (numpy.ndarray): the array to scale
-        L (float): the curve's maximum value
-        k (float): logistic growth rate
-        x0 (float): the x value of the sigmoid midpoint
-    Returns:
-        numpy.ndarray: the array of image values
-    """
-    return L / (1 + math.e ** (-k * (x - x0)))
 
 
 def load_sat(path):
@@ -174,8 +160,6 @@ class NFSEN1LC(Dataset):
 
     def __init__(self, data_dir,
                  usage='train',
-                 score_k=1.5,
-                 hardiness_max=1.2,
                  random_state=1,
                  label_offset=1,
                  chip_buffer=64,
@@ -187,12 +171,6 @@ class NFSEN1LC(Dataset):
         Args:
             data_dir (str): the directory of all data
             usage (str): Usage of the dataset : "train", "validate" or "predict"
-            score_k (float): the k param of logistic scale to calculate weight of score.
-            hardiness_max (float): the rescaled max of hardiness as weight for loss calculation.
-                Must be larger than 1 to be effective, otherwise no weight affect.
-                E.g.hardiness = 3,
-                then weight = ((hardiness_max - 1) * (hardiness - 1) / (max(hardiness) - 1) + 1)
-                = 4 * 0.2 * ((2 - 1) * (4 - 1) / (5 - 1) + 1) = 1.4
             random_state (int): the random state for pandas sampling.
             label_offset (int): the offset of label to minus in order to fit into DL model.
             chip_buffer (int): buffer value to read images.
@@ -206,8 +184,6 @@ class NFSEN1LC(Dataset):
         super(NFSEN1LC, self).__init__()
         self.data_dir = data_dir
         self.usage = usage
-        self.score_k = score_k
-        self.hardiness_max = hardiness_max
         self.random_state = random_state
         self.label_offset = label_offset
         self.chip_buffer = chip_buffer
@@ -243,13 +219,6 @@ class NFSEN1LC(Dataset):
         # Shrink the catalog based on noise ratio
[…]

### 2022-02-24 hrlcm/fit_compose_lr.py

@@ -35,14 +35,6 @@ def main():
                         help='path to dataset (default: results/north)')
     parser.add_argument('--out_dir', type=str, default="results/dl",
                         help='path to output dir (default: results/dl)')
-    parser.add_argument('--quality_weight', type=int, default=0,
-                        help='whether to use quality as weight to calculate loss '
-                             '(0 for no, 1 for yes). (default: 1)')
-    parser.add_argument('--score_k', type=float, default=1.5,
-                        help='k param of logistic scale to calculate score weight, '
-                             'see details in dataset. (default: 1.5)')
-    parser.add_argument('--hardiness_max', type=float, default=2,
-                        help='ratio to multiply with hardiness, see details in dataset (default: 2)')
     parser.add_argument('--label_offset', type=int, default=1,
                         help='offset value to minus from label in order to start from 0 (default: 1)')
     parser.add_argument('--rg_rotate', type=str, default='-90, 90',
@@ -142,8 +134,6 @@ def main():
     # Get train dataset
     train_dataset = NFSEN1LC(data_dir=args.data_dir,
                              usage='train',
-                             score_k=args.score_k,
-                             hardiness_max=args.hardiness_max,
                              label_offset=args.label_offset,
                              sync_transform=sync_transform,
                              img_transform=img_transform,
@@ -252,10 +242,6 @@ def main():
 
     # Do loop
     trainer = Trainer(args)
-    if args.quality_weight == 1:
-        weight = torch.from_numpy(train_dataset.weight)
-    else:
-        weight = None
     for epoch in range(epoch + 1, args.epochs):
         # Update info
         print("[Epoch {}] lr: {}".format(
@@ -263,8 +249,7 @@ def main():
 
         # Run training for one epoch
         model, step = trainer.train(model, train_loader, loss_fn,
-                                    optimizer, writer, step=step,
-                                    weights=weight)
+                                    optimizer, writer, step=step)
         # Run validation
         trainer.validate(model, validate_loader, step, loss_fn_valid, writer)
 

### 2022-02-24 hrlcm/loss.py

@@ -53,6 +53,7 @@ def weighted_loss(predict, target, weights=None, ignore_index=-100):
     :param predict: predicts
     :param target: validate
     :param weights: weights array
+    :param ignore_index: the ignored index in labels
     :return: mean loss
     """
     # Calculate weighted mean loss

### 2022-02-24 hrlcm/train.py

@@ -15,14 +15,13 @@ class Trainer:
     def __init__(self, args):
         self.args = args
 
-    def train(self, model, train_loader, loss_fn, optimizer, writer, step, weights=None):
+    def train(self, model, train_loader, loss_fn, optimizer, writer, step):
         """Train a single model
 
         :param model: the model to train
         :param train_loader: train Dataloader
         :param loss_fn: loss function
         :param optimizer: optimizer for training
-        :param weights: the weights to calculate loss
         :param writer: defined writer for statistics
         :param step: global step so far
         :return: updated model and global step
@@ -36,12 +35,6 @@ class Trainer:
         for i, (image, target, indexes) in enumerate(train_loader):
             # Shrink target
             target = target[:, 4:-4, 4:-4]
-
-            # Get weights
-            if weights is not None:
-                weights_batch = weights[indexes]
-            else:
-                weights_batch = None
             
             # Add replicate padding
             # image = F.pad(image, (4, 4, 4, 4), 'replicate')
@@ -49,12 +42,10 @@ class Trainer:
             # Move data to gpu if model is on gpu
             if self.args.use_gpu:
                 image, target = image.cuda(), target.cuda()
-                if weights_batch is not None:
-                    weights_batch = weights_batch.cuda()
 
             # Forward pass
             prediction = model(image)
-            loss = loss_fn(prediction, target, weights_batch)
+            loss = loss_fn(prediction, target)
             loss_total += loss.item()
 
             # Backward pass

### 2022-02-24 hrlcm/utils/get_mean_sd_norm.py

@@ -15,15 +15,17 @@ from torch.utils.data import DataLoader
 # Define a dummy args for testing
 class args_dummy:
     def __init__(self):
-        self.data_dir = 'results/north'
+        self.data_dir = '/Volumes/elephant'
         self.catalog = 'dl_catalog_predict.csv'
 
 
 class full_tile(Dataset):
     def __init__(self,
                  catalog,
+                 data_dir,
                  img_transform=None):
         self.catalog = catalog
+        self.data_dir = data_dir
         self.img_transform = img_transform
 
     def __len__(self):
@@ -32,7 +34,7 @@ class full_tile(Dataset):
     def __getitem__(self, idx):
         # import
         path = self.catalog.iloc[idx]['img']
-        img = load_sat(path)
+        img = load_sat(os.path.join(self.data_dir, path))
 
         # augmentations
         if self.img_transform is not None:
@@ -55,6 +57,7 @@ transform = ComposeImg([
     ImgToTensor()
 ])
 train_set = full_tile(catalog=full_catalog,
+                      data_dir=args.data_dir,
                       img_transform=transform)
 
 # Fast way with enough RAM
@@ -67,14 +70,14 @@ loader = DataLoader(train_set, batch_size=1,
                     shuffle=False, num_workers=0)
 
 # Initialize
-mean = torch.zeros(14)
-std = torch.zeros(14)
+mean = torch.zeros(12)
+std = torch.zeros(12)
 num_pixel = 4096 * 4096
 num_img = len(train_set)
 
 # Mean
 for data in tqdm(loader):
-    mean += data.squeeze(0).sum((1, 2)) / num_pixel
+    mean += data.squeeze(0).nansum((1, 2)) / num_pixel
 mean /= num_img
 print(mean)
 pkl.dump(mean.detach().cpu().tolist(),
@@ -83,7 +86,7 @@ pkl.dump(mean.detach().cpu().tolist(),
 # SD
 mean = mean.unsqueeze(1).unsqueeze(2)
 for data in tqdm(loader):
-    std += ((data.squeeze(0) - mean) ** 2).sum((1, 2)) / num_pixel
+    std += ((data.squeeze(0) - mean) ** 2).nansum((1, 2)) / num_pixel
 std /= num_img
 std = std.sqrt()
 print(std)

### 2022-02-24 hrlcm/utils/parse_dataset.sh

@@ -8,9 +8,9 @@ if [ -z "$DIR" ]; then
     exit 1
 fi
 
-echo "Download dataset to $DIR/dl_data.zip"
-curl -o "$DIR/dl_data.zip" https://www.dropbox.com/s/ghlssjk7ojoj6ob/dl_train_valid.zip -L
-unzip $DIR/dl_data.zip -d $DIR
-rm -rf $DIR/dl_data.zip
+echo "Download dataset to $DIR/tanzania_train_valid.zip"
+curl -o "$DIR/tanzania_train_valid.zip" https://www.dropbox.com/s/1xvtyyx2a6jdovi/tanzania_train_valid.zip -L
+unzip $DIR/tanzania_train_valid.zip -d $DIR
+rm -rf $DIR/tanzania_train_valid.zip
 rm -rf $DIR/__MACOSX
 

### 2022-02-24 tools/generate_predict_catalog.R

@@ -12,12 +12,10 @@ library(stringr)
 library(terra)
 library(parallel)
 
-tile_valid <- read.csv(here('results/north/dl_catalog_valid.csv'),
-                       stringsAsFactors = F) %>% 
-    pull(tile) %>% unique()
+tiles <- read_sf(here('data/geoms/tiles_nicfi.geojson')) %>% select(tile)
 
 # Prepare satellite image stack for each tile
-load(here('data/north/forest_vip.rda'))
+load(here('data/tanzania/forest_vip.rda'))
 var_selected <- data.frame(var = names(forest_vip$fit$variable.importance),
                            imp = forest_vip$fit$variable.importance) %>% 
     filter(str_detect(var, c('band')) | # remove indices
@@ -27,10 +25,10 @@ var_selected <- data.frame(var = names(forest_vip$fit$variable.importance),
 rm(forest_vip)
 
 img_from <- '/Volumes/elephant/pred_stack'
-img_to <- here('results/north/dl_predict')
+img_to <- here('/Volumes/elephant/predict')
 if (!dir.exists(img_to)) dir.create(img_to)
 
-cp_img <- lapply(tile_valid, function(tile_id){
+cp_img <- mclapply(tiles$tile, function(tile_id){
     message(tile_id)
     sat <- rast(
         file.path(
@@ -42,14 +40,13 @@ cp_img <- lapply(tile_valid, function(tile_id){
         file.path(
             img_to, 
             paste0(tile_id, '.tif')))
-})
+}, mc.cores = 11)
 
 # Generate catalog
-dl_catalog_full <- data.frame(tile_id = tile_valid) %>% 
-    mutate(img = file.path('dl_predict', 
+dl_catalog_full <- data.frame(tile_id = tiles$tile) %>% 
+    mutate(img = file.path('predict', 
                            paste0(tile_id, '.tif')))
-tiles <- read_sf(
-  here('data/geoms/tiles_nicfi_north.geojson'))
+
 dl_catalog_full <- do.call(rbind, lapply(dl_catalog_full$tile_id, function(id){
   tile_this <- tiles %>% filter(tile == id)
   col <- as.integer(unlist(strsplit(tile_this$tile, '-'))[1])
@@ -62,109 +59,23 @@ dl_catalog_full <- do.call(rbind, lapply(dl_catalog_full$tile_id, function(id){
[…]

### 2022-02-24 tools/reorganize_datasets.R

@@ -1,109 +1,0 @@
-#### Just a internal used script to subset datasets for experiments ####
-### PART 1: Do the experiment of co-teaching using noisy labels. ###
-##        - The same number of training labels, but
-##          - 80 % perfect labels + 20 % noisy labels (8 or 9)
-##          - 60 % perfect labels + 40 % noisy labels (8 or 9)
-### PART 2: Get a random prediction catalog for testing. ###
-
-# Libraries
-library(here)
-library(stringr)
-library(dplyr)
-library(parallel)
-src_dir <- 'results/north'
-dst_dir <- 'results/north'
-
-### PART 1: Do the experiment of co-teaching using noisy labels. ###
-catalog_train <- read.csv(file.path(src_dir, 'dl_catalog_train.csv'))
-num_train <- (catalog_train %>% filter(score == 10) %>% nrow() %/% 32) * 32
-
-### 80 % perfect labels + 20 % noisy labels (8 or 9) ###
-noise_ratio <- 0.2
-num_perfect <- round(num_train * (1 - noise_ratio), 0)
-num_noisy <- num_train - num_perfect
-
-# Noisy with 9
-set.seed(10)
-sample_perfect <- catalog_train %>% filter(score == 10) %>% 
-    sample_n(num_perfect)
-set.seed(10)
-catalog_train_9 <- catalog_train %>% filter(score == 9) %>% 
-    sample_n(num_noisy) %>% rbind(sample_perfect)
-rm(sample_perfect)
-
-write.csv(catalog_train_9, file.path(dst_dir, 'dl_catalog_train_noisy9_20.csv'),
-          row.names = F)
-
-# Noisy with 8
-set.seed(10)
-sample_perfect <- catalog_train %>% filter(score == 10) %>% 
-    sample_n(num_perfect)
-set.seed(10)
-catalog_train_8 <- catalog_train %>% filter(score == 8) %>% 
-    sample_n(num_noisy) %>% rbind(sample_perfect)
-rm(sample_perfect)
-
-write.csv(catalog_train_8, file.path(dst_dir, 'dl_catalog_train_noisy8_20.csv'),
-          row.names = F)
-
-### 60 % perfect labels + 40 % noisy labels (8 or 9) ###
-noise_ratio <- 0.4
-num_perfect <- round(num_train * (1 - noise_ratio), 0)
-num_noisy <- num_train - num_perfect
-
-# Noisy with 9
-set.seed(10)
[…]

### 2022-02-24 docs/run_experiments.Rmd
Update documents

--- 2021-08-17 docs/notebook_learn_dl_ensemble.Rmd
@@
 ---
-title: "Notebook of learning from ensemble labels"
+title: "Introduction of using AWS instance to run experiments"
 author: "Lei Song"
@@
 
-#### Run experiments
+### Other cloud computing platform
 
-Parse dataset:
+The users could set up the deep learning environment with similar steps used on AWS. For example, Colab can be used as long as the GPU power is enough for your computation.
+
+## Run experiments
+
+### Parse dataset
 
 ```
-./hrlcm/utils/parse_dataset.sh results/north
+cd path/of/hrlcm
+./hrlcm/utils/parse_dataset.sh path/to/save
 ```
 
-Run models:
+### Run models
 
+```
+cd path/of/hrlcm
+python hrlcm/fit_step_lr.py --arg arg_value
+```
+Check arguments:
+```
+python hrlcm/fit_step_lr.py --help
+```
+
+For example:
 ```
@@
 
-- Weights
-
-Score
-```
-python hrlcm/fit_step_lr.py --exp_name unet_no_weight --quality_weight 0 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k05_only --quality_weight 1 --score_k 0.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k15_only --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k3_only --quality_weight 1 --score_k 3.0 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
-```
-
-Hardiness
-```
-python hrlcm/fit_step_lr.py --exp_name unet_k15_hard11 --quality_weight 1 --score_k 1.5 --hardiness_max 1.1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k15_hard12 --quality_weight 1 --score_k 1.5 --hardiness_max 1.2 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; python hrlcm/fit_step_lr.py --exp_name unet_k15_hard14 --quality_weight 1 --score_k 1.5 --hardiness_max 1.4 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
-```
-
-- Sampling
-
-```
-scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_1.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_2.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_34.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_random_67.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_34.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_hori_strip_67.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_34.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north;scp /Users/pinot/Dropbox/research/hrlcm/results/north/dl_catalog_train_vert_strip_67.csv ubuntu@ec2-18-188-227-35.us-east-2.compute.amazonaws.com:~/hrlcm/results/north
-```
-
-```
-mv results/north/dl_catalog_train.csv results/north/dl_catalog_train_full.csv; mv results/north/dl_catalog_train_1.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_one_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_34.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_34 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_2.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_two_tile --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_random_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_random_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_hori_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_hori_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31; rm results/north/dl_catalog_train.csv; mv results/north/dl_catalog_train_vert_strip_67.csv results/north/dl_catalog_train.csv; python hrlcm/fit_step_lr.py --exp_name unet_vert_strip_67 --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --max_lr 0.0001 --gamma_lr 1 --epochs 31
-```
-
-#### Tensorboard
+### Tensorboard
 
@@
 
-#### Prediction
+### Prediction
 
+```
+cd path/of/hrlcm
+python hrlcm/predict.py --arg arg_value
+```
+Check arguments:
+```
+python hrlcm/predict.py --help
+```
+
+For example:
 ```
@@
 
-#### Test
+### Evaluation
 
 ```
-python hrlcm/predict.py --args_path 'results/dl/unet_no_weight/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_no_weight/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_no_weight' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
-
-python hrlcm/predict.py --args_path 'results/dl/unet_k05_only/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k05_only/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k05_only' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
-
-python hrlcm/predict.py --args_path 'results/dl/unet_k15_only/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_only/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_only' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
-
-python hrlcm/predict.py --args_path 'results/dl/unet_k3_only/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k3_only/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k3_only' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
-
-python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard11/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard11/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard11' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
-
-python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard12' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
-
-python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard14/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard14/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard14' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
-
-python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/north' --out_dir 'results/test/unet_k15_hard12_clr_200epc' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+cd path/of/hrlcm
+python hrlcm/evaluate.py --arg arg_value
+```
+Check arguments:
+```
+python hrlcm/evaluate.py --help
 ```
 
-#### Evaluation
-
+For example:
 ```
@@
 
-#### Other useful commands
+## Other useful commands
 
-##### Check disk space and clean trash
+### Check disk space and clean trash
 
@@
 ```
-##### Check the RAM usage in M
+### Check the RAM usage in M
 
@@
 ```
-
-## Methodology
-### Candidate models
-
-- U-net, which has simple architecture and is friendly to small dataset.
-
-### Possible strategies to deal with noisy labels
-#### Add noisy labels to fine tune
-
-After the initial 200 epochs with perfect labels, adding more noisy labels to "adapt" the model.
-
-#### Label smoothing
-
-The general loss is higher than classic cross entropy loss.
-But it do help to reduce the gaps between train and validate.
-So it might be a promising method to use for our case.
-There is one general parameter "smooth rate".
-Based on the experiments, a higher smooth rate could help to reduce the gap between train and validate more.
-0.5 is a safe choice.
-
-#### Co-teaching and co-teaching-plus
-
-Based on the original papers and their GitHub repos, we combined these two logic into one function and adapted it for image segmentation.
-
-- The first version is image based, which means it takes each image as a whole thing.
-If the label of one image is "perfect", then use the whole image, otherwise only use pixels with small loss to update the models.
-  - Under "argue" mode, use disagreement to update the models.
-  - Under "discuss" mode, do not use disagreement.
-
-- The second version is batch based, which means it only use pixels with small loss from the whole batch to update the models. Mode works similarly as the first version.
-
-#### JoCoR
-
-Since the original paper is about image classification rather than image segmentation, it is harder to adapt this method into image segmentation with good performance.
-
-So after all experiments, we decide to stick with co-teaching & co-teaching-plus.
-
-## Experiments
-
-### Start up (Baseline)
-
-Before any tests related to strategies to deal with noisy labels, we will build up a baseline model only using "pure" labels generated by human checking.
-
-#### Hyper-parameters
-
-- <input type="checkbox" checked> Learning rate and learning rate scheduler</input>
-- <input type="checkbox" checked> Batch size</input>
-- <input type="checkbox" checked> Optimizer</input>
-- <input type="checkbox" checked> Model (U-net or Deeplab)</input>
-- Transform methods (if necessary)
-
-##### Unet
-
-- Batch size = 32 (Maximum value fit into `g4dn.12xlarge`)
-- Initial learning rate = [0.1, 0.01, 0.001]
-
-  - 0.1 is too large
-  - 0.01 and 0.001 works similarly, but 0.001 works slightly better for multiple optimizer.
-  - Learning rate smaller than 0.0001 might be too small for this case.
-
-- Optimizer: we plan to try some more recent optimizer such as AdaBound, AdamP, etc.
-Because SGD could make model have higher generalization while Adam can train the model faster.
-So if we could use an optimizer that has both advantages, it would be ideal.
-AdaBound is such kind of optimizer.
-Since our research is not about the improvement of DL algorithm, so we just pick up the most right one at the moment.
-
-  - AdaBound does obviously better than Adam or AdamW at least in the first 20 epochs.
-  - AdamP performs similar to AdaBound, that are much better than other traditional ones. But validate loss is a lit higher than AdaBound.
-
-- Scheduler: we decided to use a compose scheduler to have dynamic learning rate.
-Even though Adam-based optimizer uses dynamic learning rate already, but experiments prove that using both dynamic learning rate and Adam-based optimizer together could have better performance.
-So we chose to use 0.001 for the first 30 epochs, to use a decayed cyclic scheduler (0.0008 - 0.0012) for epoch 30 - 120, and use another decayed cyclic scheduler (0.0004 - 0.0006) for last 80 epochs.
-
-##### DeepLab
-
-  Our experiments proved that architecture of DeepLab family has worse performance.
-
-### Co-teaching
-
-We first use constant parameters, 0.001 learning rate, AmsBound optimizer, and 30 epochs, to run the models.
-
-- Co_teaching_batch doesn't fit multi-classes classification task. It might be good for binary classification. Because based on the curves, co_teaching_batch give up the minorities.
-
-- Co_teaching works good.
-"Discuss" mode works slightly better than "argue" mode.
-Since "argue" mode use the disagreement between two models, we assume this method would be helpful to transfer a model to other areas.
-Of course, this assumption needs more test.
-
-So now, I have a clear idea is that the "wrong" guess labels are actually the hard ones. So instead of dumping them, we should take advantage of them.
-
-- Randomly get 8 out of 64 for each tile, 6 for train, and 2 for validate.
-- For these sub-tiles, score them and also correct the wrong part. The scores will be used as weight to calculate loss. The lower the score is, the higher weight it is.

### 2022-02-24 docs/tanzania_full_map.Rmd
Update documents

--- 2022-02-21 docs/tanzania_full_map.Rmd
@@
 ---
-title: "Make the full map of Tanzania"
+title: "Make the full map of Tanzania land cover"
 author: "Lei Song"
@@
 
-The scripts used for training U-Net are under directory hrlcm.
+The scripts used for training U-Net are under directory hrlcm. Multiple type of models will be trained:
+
+- Using all bands and image standardization
+- Using all bands without image standardization
+- Using only NICFI bands with image standardization
+- Using only NICFI bands without image standardization
+
+Please reference to tutorial [Introduction of using AWS instance to run experiments](run_experiments.Rmd) for how to run experiments.

### 2022-02-27 docs/tanzania_full_map.Rmd
Subset images for North

@@
 ```{r}
+library(terra)
+# Select features
+load(here('data/tanzania/forest_vip.rda'))
+var_selected <- data.frame(var = names(forest_vip$fit$variable.importance),
+                           imp = forest_vip$fit$variable.importance) %>% 
+  filter(str_detect(var, c('band')) | # remove indices
+           str_detect(var, c('vv')) |
+           str_detect(var, c('vh'))) %>% 
+  filter(imp > 1000) # remove less important ones
+
 move_train <- lapply(1:nrow(north_train), function(n) {
-    things_to <- unlist(north_train[n, c("label", 'img')])
+    # Label, directly copy
+    things_to <- north_train[n, 'label']
     things_from <- gsub("train", "dl_train", things_to)
@@
     file.copy(things_from, things_to)
+
+    # Image, subset it
+    things_to <- north_train[n, 'img']
+    things_from <- gsub("train", "dl_train", things_to)
+    things_to <- file.path(here("results/tanzania"), things_to)
+    things_from <- file.path(here("results/north"), things_from)
+
+    sat <- rast(things_from)
+    sat <- subset(sat, var_selected$var)
+    writeRaster(sat, things_to, overwrite = TRUE)
 })
@@
 move_valid <- lapply(1:nrow(north_valid), function(n) {
-    things_to <- unlist(north_valid[n, c("label", 'img')])
+    # Label, directly copy
+    things_to <- north_valid[n, "label"]
     things_from <- gsub("validation", "dl_valid", things_to)
@@
     file.copy(things_from, things_to)
+
+    # Image, subset it
+    things_to <- north_valid[n, "img"]
+    things_from <- gsub("validation", "dl_valid", things_to)
+    things_to <- file.path(here("results/tanzania"), things_to)
+    things_from <- file.path(here("results/north"), things_from)
+    sat <- rast(things_from)
+    sat <- subset(sat, var_selected$var)
+    writeRaster(sat, things_to, overwrite = TRUE)
 })

### 2022-03-02 docs/run_experiments.Rmd
Update some default values

@@
 
-  - `g3.8xlarge`, 2 GPU, 16G GPU memory, $0.684/hr for SPOT instance.
-  - `g3.16xlarge`, 4 GPU, 32G GPU memory, $1.368/hr for SPOT instance.
-  - `g4dn.8xlarge`, 1 GPU, 16G GPU memory, $0.6528/hr for SPOT instance.
-  - `g4dn.12xlarge`, 4 GPU, 64G GPU memory, $1.1819/hr for SPOT instance.
+  - `g3.8xlarge`, 2 GPU, 16G GPU memory, 32 CPUs, 244 GB CPU memory, $0.684/hr for SPOT instance.
+  - `g3.16xlarge`, 4 GPU, 32G GPU memory, 64 CPUs, 488 GB CPU memory, $1.368/hr for SPOT instance.
+  - `g4dn.8xlarge`, 1 GPU, 16G GPU memory, 32 CPUs, 128 GB CPU memory, $0.6528/hr for SPOT instance.
+  - `g4dn.12xlarge`, 4 GPUs, 64G GPU memory, 48 CPUs, 192 GB CPU memory, $1.1819/hr for SPOT instance.
+  - `g5.xlarge`, 1 GPU, 24 GPU memory, 4 CPUs, 16 GB CPU memory (on-demand $1.212/hr, spot 0.3018/hr).
+  - `g5.2xlarge`, 1 GPU, 24 GPU memory, 8 CPUs, 32 GB CPU memory (on-demand $1.624/hr, spot 0.3636/hr).
+  - `g5.4xlarge`, 1 GPU, 24 GPU memory, 16 CPUs, 64 GB CPU memory (on-demand $2.448/hr, spot 0.4872/hr).
+  - `g5.8xlarge`, 1 GPU, 24 GPU memory, 32 CPUs, 128 GB CPU memory (on-demand $4.096/hr, spot 0.967/hr).
+  - `g5.12xlarge`, 4 GPUs, 96 GPU memory, 48 CPUs, 192 GB CPU memory (on-demand $5.672/hr, 1.7016/hr).
 

### 2022-03-02 hrlcm/fit_compose_lr.py

@@ -31,13 +31,14 @@ def main():
                              'for logs and checkpoints (default: experiment)')
 
     # dataset
-    parser.add_argument('--data_dir', type=str, default='results/north',
-                        help='path to dataset (default: results/north)')
+    parser.add_argument('--data_dir', type=str, default='results/tanzania',
+                        help='path to dataset (default: results/tanzania)')
     parser.add_argument('--out_dir', type=str, default="results/dl",
                         help='path to output dir (default: results/dl)')
     parser.add_argument('--label_offset', type=int, default=1,
                         help='offset value to minus from label in order to start from 0 (default: 1)')
     parser.add_argument('--img_bands', type=str, choices=['all', 'nicfi'],
+                        default='all',
                         help='bands of satellite images to use. \
                         all means all bands, including RGB, NIR of NICFI tiles, intercept,  \
                         cos(2t) of VV and VH. (default: all)')

### 2022-03-02 hrlcm/fit_step_lr.py

@@ -30,13 +30,14 @@ def main():
                              'for logs and checkpoints (default: experiment)')
 
     # dataset
-    parser.add_argument('--data_dir', type=str, default='results/north',
-                        help='path to dataset (default: results/north)')
+    parser.add_argument('--data_dir', type=str, default='results/tanzania',
+                        help='path to dataset (default: results/tanzania)')
     parser.add_argument('--out_dir', type=str, default="results/dl",
                         help='path to output dir (default: results/dl)')
     parser.add_argument('--label_offset', type=int, default=1,
                         help='offset value to minus from label in order to start from 0 (default: 1)')
     parser.add_argument('--img_bands', type=str, choices=['all', 'nicfi'],
+                        default='all',
                         help='bands of satellite images to use. \
                               all means all bands, including RGB, NIR of NICFI tiles, intercept,  \
                               cos(2t) of VV and VH. (default: all)')

### 2022-03-03 docs/run_experiments.Rmd
Update some default args

@@
 
+Before official running, test a bit about the largest values of `num_worker`, `train_batch_size`, `val_batch_size` that could be used. For `g5.12xlarge`, these values could be:
+
+- `num_worker`:48
+- `train_batch_size`: 32 (could be a bit bigger, but it is recommended to use $2^n$)
+- `val_batch_size`: 32
+
+Also, test the optimal learning rate and scheduler to use:
+
+- 0.1 is too large.
+- 0.01 is too large.
+- 0.001 is a good start point.
+- 0.00001 is a good end point.
+
+`final_lr` for `optim.AdaBound`:
+
+- 0.01 still works fine.
+
+Syntax:
+
 ```
@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_k15_only_clr_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
+python hrlcm/fit_compose_lr.py --exp_name unet_all_norm_200 --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.000001 --max_lr 0.00001 --save_freq 20 --epochs 201
 ```

### 2022-03-03 hrlcm/fit_compose_lr.py

@@ -71,12 +71,12 @@ def main():
                         help='training state will be saved every save_freq \
                         batches during training')
     parser.add_argument('--train_batch_size', type=int, default=32,
-                        help='batch size for training (default: 16)')
+                        help='batch size for training (default: 32)')
     parser.add_argument('--val_batch_size', type=int, default=32,
-                        help='batch size for validation (default: 16)')
-    parser.add_argument('--epochs', type=int, default=400,
-                        help='number of training epochs (default: 400). '
-                             'NOTE: The scheduler is designed best for 400.')
+                        help='batch size for validation (default: 32)')
+    parser.add_argument('--epochs', type=int, default=201,
+                        help='number of training epochs (default: 200). '
+                             'NOTE: The scheduler is designed best for 200.')
     parser.add_argument('--resume', '-r', type=str, default=None,
                         help='path to the pretrained weights file')
 

### 2022-03-03 hrlcm/fit_step_lr.py

@@ -58,11 +58,11 @@ def main():
                         help='the gpu devices to use (default: None) (format: 1, 2)')
 
     # Training hyper-parameters
-    parser.add_argument('--max_lr', type=float, default=0.0001,
+    parser.add_argument('--max_lr', type=float, default=0.001,
                         help='maximum or initial learning rate for scheduler.')
     parser.add_argument('--step_size', type=int, default=10,
                         help='step size for scheduler.')
-    parser.add_argument('--gamma_lr', type=float, default=0.9,
+    parser.add_argument('--gamma_lr', type=float, default=0.8,
                         help='gamma for learning rate.')
     parser.add_argument('--optimizer_name', type=str,
                         choices=['AdaBound', 'AmsBound', 'AdamP'],
@@ -72,11 +72,11 @@ def main():
                         help='training state will be saved every save_freq \
                         batches during training')
     parser.add_argument('--train_batch_size', type=int, default=32,
-                        help='batch size for training (default: 16)')
+                        help='batch size for training (default: 32)')
     parser.add_argument('--val_batch_size', type=int, default=32,
-                        help='batch size for validation (default: 16)')
-    parser.add_argument('--epochs', type=int, default=300,
-                        help='number of training epochs (default: 300)')
+                        help='batch size for validation (default: 32)')
+    parser.add_argument('--epochs', type=int, default=201,
+                        help='number of training epochs (default: 200)')
     parser.add_argument('--resume', '-r', type=str, default=None,
                         help='path to the pretrained weights file')
 

### 2022-03-05 docs/run_experiments.Rmd
Add more normalization options

--- 2022-03-02 docs/run_experiments.Rmd
@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_k15_only_clr_220epc --quality_weight 1 --score_k 1.5 --hardiness_max 1 --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
+python hrlcm/fit_compose_lr.py --exp_name unet_all_norm_200 --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 201
 ```
@@
 
+### Hyperparameter tunning
+#### Network parameter
+
+Before official running, test a bit about the largest values of `num_worker`, `train_batch_size`, `val_batch_size` that could be used. For `g5.12xlarge`, these values can be:
+
+- `num_worker`:48 (CPU cores)
+- `train_batch_size`: 32 (could be a bit bigger, but it is recommended to use $2^n$)
+- `val_batch_size`: 32
+
+#### Learning rate
+Also, test the optimal learning rate and scheduler to use:
+
+- 0.001 is a good start point.
+- 0.00001 is a good end point with middle value of 0.0001.
+
+`final_lr` for `optim.AdaBound`:
+
+- 0.01 still works fine. The default value is robust for many cases.
+
+#### Augmentation
+
+- Random scale
+- Random flip (always use)
+- Random center rotate
+- Normalization
+    - Dataset based standardization
+    - Image based standardization
+    - Image based min-max scaler
+
 ### Prediction
@@
 ```
-python hrlcm/predict.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+python hrlcm/predict.py --args_path 'results/dl/unet_all_norm_200/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_all_norm_200/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
 
@@
 ```
-python hrlcm/evaluate.py --args_path 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_k15_hard12_clr_200epc/checkpoints/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'
+python hrlcm/evaluate.py --args_path 'results/dl/unet_all_norm_200/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_all_norm_200/checkpoints/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
 

### 2022-03-05 hrlcm/augmentation.py

@@ -259,7 +259,7 @@ class LabelToTensor(object):
 
 
 class ImgNorm(object):
-    """Normalize image layers."""
+    """Dataset based normalize image layers. This indicates a general standardization."""
 
     def __init__(self, bands_mean, bands_std):
         """Initialize the object.
@@ -273,9 +273,9 @@ class ImgNorm(object):
     def __call__(self, img):
         """Define the call.
         Params:
-            img (numpy.ndarray): Concatenated variables or brightness value with a dimension of (H, W, C)
+            img (torch.tensor): Concatenated variables or brightness value with a dimension of (H, W, C)
         Returns:
-            (numpy.ndarray) tuple of rescaled image, and label.
+            (torch.tensor) tensor of rescaled image, and label.
         """
         for t, m, s in zip(img, self.mean, self.std):
             t.sub_(m).div_(s)
@@ -283,3 +283,40 @@ class ImgNorm(object):
         # img /= self.std
 
         return img
+
+
+class SingleImgNorm(object):
+    """Image-based normalize image layers. This indicates a general standardization."""
+
+    def __call__(self, img):
+        """Define the call.
+        Params:
+            img (torch.tensor): Concatenated variables or brightness value with a dimension of (H, W, C)
+        Returns:
+            (torch.tensor) tensor of rescaled image, and label.
+        """
+        means = torch.mean(img, dim=(1, 2))
+        stds = torch.std(img, dim=(1, 2))
+        for t, m, s in zip(img, means, stds):
+            t.sub_(m).div_(s)
+
+        return img
+
+
+class ImgMinMaxScaler(object):
+    """Normalize image layers. This indicates a general normalization."""
+
+    def __call__(self, img):
+        """Define the call.
+        Params:
+            img (torch.tensor): Concatenated variables or brightness value with a dimension of (H, W, C)
+        Returns:
+            (torch.tensor) tensor of rescaled image, and label.
+        """
+        max_bands = torch.amax(img, dim=(1, 2))
+        min_bands = torch.amin(img, dim=(1, 2))
+        for t, a, b in zip(img, max_bands, min_bands):
+            t.sub_(b).div_(a.sub_(b))
+
+        return img
+

### 2022-03-06 docs/run_experiments.Rmd
Ready to run

@@
 
+- Random flip (always use)
 - Random scale
-- Random flip (always use)
 - Random center rotate
-- Normalization
-    - Dataset based standardization
-    - Image based standardization
-    - Image based min-max scaler
+- Normalization: Dataset based standardization.
+*Among dataset-based standardization, image-based standardization, image-based normalization, and no such transformation, dataset-based standardization works the best because the U-Net learned much faster.*
+
+#### Hierachical training
+
+- Train a big model using the whole dataset over the whole area.
+- Fine tune (or transfer) the model into 5 sub zones.
+
+Records:
+
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_all_norm_200 --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 201
+```
 

### 2022-03-06 docs/tanzania_full_map.Rmd
Ready to run

@@
 
-- Using all bands and image standardization
-- Using all bands without image standardization
-- Using only NICFI bands with image standardization
-- Using only NICFI bands without image standardization
+- Using all bands with image augmentation including image standardization
+- Using only NICFI bands with image augmentation including image standardization （* This provides option of prediction for other years, it is much faster to prepare satellite images).
 

### 2022-03-06 hrlcm/fit_step_lr.py

@@ -113,10 +113,10 @@ def main():
 
     # synchronize transform for train dataset
     sync_transform = Compose([
-        # RandomScale(prob=args.trans_prob),
+        RandomScale(prob=args.trans_prob),
         RandomFlip(prob=args.trans_prob),
-        # RandomCenterRotate(degree=args.rg_rotate,
-        #                    prob=args.trans_prob),
+        RandomCenterRotate(degree=args.rg_rotate,
+                           prob=args.trans_prob),
         SyncToTensor()
     ])
 

### 2022-03-06 hrlcm/lr_scheduler.py

@@ -2,7 +2,7 @@ import torch
 import torch_optimizer as optim
 
 
-def get_compose_lr(model, epochs, min_lr=0.00001, max_lr=0.001, stage1=50, stage2=130, stage3=170):
+def get_compose_lr(model, epochs, min_lr=0.00001, max_lr=0.001, stage1=30, stage2=60, stage3=90):
     """Util function to customize a learning rate scheduler.
     Note: not a perfect function, user could customize this function based on needs.
         Args:
@@ -24,19 +24,19 @@ def get_compose_lr(model, epochs, min_lr=0.00001, max_lr=0.001, stage1=50, stage
         optimizer_lr.step()
         if i <= stage1:
             if i == stage1:
-                lr_scheduler_1 = torch.optim.lr_scheduler.CyclicLR(optimizer_lr, base_lr=max_lr - 0.0004,
-                                                                   max_lr=max_lr + 0.0004,
-                                                                   step_size_up=1, step_size_down=5,
-                                                                   gamma=0.97, cycle_momentum=False,
+                lr_scheduler_1 = torch.optim.lr_scheduler.CyclicLR(optimizer_lr, base_lr=0.0001,
+                                                                   max_lr=0.0005,
+                                                                   step_size_up=1, step_size_down=3,
+                                                                   gamma=0.9, cycle_momentum=False,
                                                                    mode='exp_range')
                 lr_scheduler_1.step()
         elif i <= stage2:
             lr_scheduler_1.step()
             if i == stage2:
-                lr_scheduler_2 = torch.optim.lr_scheduler.CyclicLR(optimizer_lr, base_lr=0.0001,
-                                                                   max_lr=0.0006,
-                                                                   step_size_up=1, step_size_down=5,
-                                                                   gamma=0.94, cycle_momentum=False,
+                lr_scheduler_2 = torch.optim.lr_scheduler.CyclicLR(optimizer_lr, base_lr=0.00001,
+                                                                   max_lr=0.0001,
+                                                                   step_size_up=1, step_size_down=3,
+                                                                   gamma=0.96, cycle_momentum=False,
                                                                    mode='exp_range')
                 lr_scheduler_2.step()
         elif stage2 < i <= stage3:

### 2022-03-06 tools/create_spot_instance.sh

@@ -112,7 +112,6 @@ if [ "$SPOTTYPE" = "persistent" ]; then
     --image-id $AMIID \
     --count 1 \
     --instance-type $ITYPE \
-    --subnet-id $SUBNETID \
     --iam-instance-profile 'Name="activemapper_planet_readwriteS3"' \
     --key-name $KEYNAME \
     --security-group-ids $SECGROUPID \
@@ -120,8 +119,7 @@ if [ "$SPOTTYPE" = "persistent" ]; then
     "[ { \"DeviceName\": \"/dev/sda1\", \"Ebs\": { \"VolumeSize\": $SDASIZE } } ]" \
     --tag-specifications 'ResourceType=instance,Tags=[{Key=Name,Value='$NEWINAME'}]' \
     --instance-market-options 'MarketType=spot,
-          SpotOptions={MaxPrice='$BID_PRICE',
-          SpotInstanceType='$SPOTTYPE',
+          SpotOptions={SpotInstanceType='$SPOTTYPE',
           ValidUntil='$VALIDUNTIL',
           InstanceInterruptionBehavior=stop}'
 else
@@ -136,8 +134,7 @@ else
     "[ { \"DeviceName\": \"/dev/sda1\", \"Ebs\": { \"VolumeSize\": $SDASIZE } } ]" \
     --tag-specifications 'ResourceType=instance,Tags=[{Key=Name,Value='$NEWINAME'}]' \
     --instance-market-options 'MarketType=spot,
-          SpotOptions={MaxPrice='$BID_PRICE',
-          SpotInstanceType='$SPOTTYPE',
+          SpotOptions={SpotInstanceType='$SPOTTYPE',
           InstanceInterruptionBehavior=terminate}'
 fi
 
@@ -148,5 +145,5 @@ NEWIID=$(aws ec2 describe-instances \
 
 echo $NEWIID
 
-# ./tools/create_spot_instance.sh ami-021ccd558170ad2bb g4dn.12xlarge \
-# sg-0a8bbc91697d6a76b tzlcm one-time 2021-05-15T23:00:00 lsong-keypair 200
+# ./tools/create_spot_instance.sh ami-0db6cdf40b45578e3 g5.12xlarge \
+# sg-0a8bbc91697d6a76b tzlcm persistent 2022-03-10T23:00:00 lsong-keypair 200

### 2022-03-09 docs/run_experiments.Rmd
Forgot to change the default final_lr back
Update some scripts

@@
 
-#### Hierachical training
+Experiments indicate using all of them can improve model performance.
 
-- Train a big model using the whole dataset over the whole area.
-- Fine tune (or transfer) the model into 5 sub zones.
+#### Loss functions
+
+No luck on using different loss function. The most effective loss function is still the balanced cross entropy loss function.
+
+According to the experiments, balanced cross entropy loss performs well.
+In summary (based on my knowledge), changing loss function is not an efficient and effective way to increase the model performance in this case.
+This might because the modeling task here does not have special characteristics that need special loss functions to deal with.
+For example, some loss functions were created to detect vessel-like objects.
+Instead, the problems here are mainly the noisy labels and not enough representative features (satellite image bands).
+
+#### Loss weights
+
+According to some experiments, the accuracy of cropland is relatively low.
+One reason is that the farming condition over Tanzania is complex and thus hard to model.
+Another reason is the validation of this class has relatively low quality as well.
+There are limited things we could do for these reasons.
+But we can let the model to consider more about cropland when training.
+The strategy can be increasing the loss weight of cropland class.
+However, the effect is not conclusive.
+
+#### Ensemble training
+
+When training a full model using the whole dataset, the main problem is cropland. One reason is that
+cropland highly relies on local climate and cultivating conditions and Tanzania is a large country.
+
+- Train multiple models with subset of labels.
+
+  - Zone 1, 2, 3, 4, 5 (composite learning rate)
+  - Zone 1, 2, 3, 4
+  - Zone 1, 2, 3, 5
+  - Zone 1, 2, 4, 5
+  - Zone 1, 3, 4, 5
+  - Zone 2, 3, 4, 5
+
+- Ensemble these models by voting, possibly at segment level.
 
@@
 
+Zone 1, 2, 3, 4, 5
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_all_norm_200 --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 201
+python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
+```
+Zone 1, 2, 3, 4
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
+```
+Zone 1, 2, 3, 5
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
+```
+Zone 1, 2, 4, 5
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
+```
+Zone 1, 3, 4, 5
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
+```
+Zone 2, 3, 4, 5
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
 ```
@@
 ```
-python hrlcm/predict.py --args_path 'results/dl/unet_all_norm_200/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_all_norm_200/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
+python hrlcm/predict.py --args_path 'results/dl/unet_zone1_12bs_4augs_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_zone1_12bs_4augs_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
 
-scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/dl
+scp -r ubuntu@ec2-54-163-146-125.compute-1.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/tanzania/prediction/unet_zone1_12bs_4augs_80epochs
 ```

### 2022-03-09 hrlcm/fit_compose_lr.py

@@ -272,7 +272,8 @@ def main():
         # Save checkpoint
         if epoch % args.save_freq == 0:
             trainer.export_model(model, optimizer=optimizer,
-                                 scheduler=None, name='interim')
+                                 scheduler=None, name='interim',
+                                 step=step)
 
         # Save learning rate to scalar
         writer.add_scalar("Train/lr",
@@ -282,7 +283,7 @@ def main():
         writer.flush()
 
     # Export final set of weights
-    trainer.export_model(model, optimizer, name="final")
+    trainer.export_model(model, optimizer, name="final", step=step)
 
 
 if __name__ == "__main__":

### 2022-03-09 hrlcm/fit_step_lr.py

@@ -270,7 +270,8 @@ def main():
         # Save checkpoint
         if epoch % args.save_freq == 0:
             trainer.export_model(model, optimizer=optimizer,
-                                 scheduler=lr_scheduler, name='interim')
+                                 scheduler=lr_scheduler, name='interim',
+                                 step=step)
 
         # Save learning rate to scalar
         writer.add_scalar("Train/lr",
@@ -280,7 +281,7 @@ def main():
         writer.flush()
 
     # Export final set of weights
-    trainer.export_model(model, optimizer, name="final")
+    trainer.export_model(model, optimizer, name="final", step=step)
 
 
 if __name__ == "__main__":

### 2022-03-09 hrlcm/predict.py

@@ -40,6 +40,7 @@ def main():
     parser.add_argument('--label_offset', type=int, default=1,
                         help='offset value to minus from label in order to start from 0 (default: 1)')
     parser.add_argument('--img_bands', type=str, choices=['all', 'nicfi'],
+                        default='all',
                         help='bands of satellite images to use. \
                         all means all bands, including RGB, NIR of NICFI tiles, intercept,  \
                         cos(2t) of VV and VH. (default: all)')

### 2022-03-18 docs/run_experiments.Rmd
Update and add utils

--- 2022-03-06 docs/run_experiments.Rmd
@@
   ```
-  replace the private IP with the public IP to open it in browser. If you can log in without issues, then it is ready to go.
+Replace the private IP with the public IP to open it in browser. If you can log in without issues, then it is ready to go.
 
@@
 ```
+
 Check arguments:
@@
 ```
-
+Or
 ```
@@
 
-#### Hierachical training
+Experiments indicate using all of them can improve model performance.
 
-- Train a big model using the whole dataset over the whole area.
-- Fine tune (or transfer) the model into 5 sub zones.
+#### Loss functions
 
-Records:
+No luck on using different loss function. The most effective loss function is still the balanced cross entropy loss function.
+
+According to the experiments, balanced cross entropy loss performs well.
+In summary (based on my knowledge), changing loss function is not an efficient and effective way to increase the model performance in this case.
+This might because the modeling task here does not have special characteristics that need special loss functions to deal with.
+For example, some loss functions were created to detect vessel-like objects.
+Instead, the problems here are mainly the noisy labels and not enough representative features (satellite image bands).
+
+#### Loss weights
+
+According to some previous experiments, the accuracy of cropland is relatively low.
+One reason is that the farming condition over Tanzania is complex and thus hard to model.
+Another reason is the validation of this class has relatively low quality as well.
+There are limited things we could do for these reasons.
+But we can let the model to consider more about cropland when training.
+The strategy can be increasing the loss weight of cropland class.
+However, the effect is not conclusive.
+
+Hum... Using a bigger weight for cropland in loss calculation increased the accuracy significantly.
+
+#### "Hierachical" training
+
+When training a full model using the whole dataset, the main problem is cropland. One reason is that
+cropland highly relies on local climate and cultivating conditions and Tanzania is a large country. To reduce this impact, we could shrink the study area gradually into each agro-ecological zone.
+
+- Modeling structure:
 
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_all_norm_200 --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 201
+1, 2, 4, 5 -> 1, 2, 5 -> 1, 2 -> 1
+                      -> 2, 5 -> 2
+                              -> 5
+2, 3, 4, 5 -> 2, 3, 4 -> 2, 3 -> 3
+                      -> 2, 4 -> 4
+```
+
+Within all groups, 1, 2, 4, 5/2, 3, 4, 5, and 1, 2, 5/2, 3, 4 update all weights. 1, 2/2, 5/2, 3/2, 4 update weights of last few layers.
+
+Update all weights:
+
+Zone 1, 2, 3, 4, 5
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 121
+```
+
+Then, comment out line 247 - 249 in `fit_compose_lr.py`, and modify `lr_scheduler.py` correspondingly. The learning rate scheduler is saved as a pickle as well.
+
+Zone 1, 2, 4, 5
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z1245_12bs_4augs_ft_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_full_12bs_4augs_120epochs/checkpoints/final.pth'
+```
+
+Zone 1, 2, 5
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z125_12bs_4augs_ft_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z1245_12bs_4augs_ft_80epochs/checkpoints/final.pth'
+```
+
+Zone 2, 3, 4, 5
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z2345_12bs_4augs_ft_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_full_12bs_4augs_120epochs/checkpoints/final.pth'
+```
+
+Zone 2, 3, 4
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z234_12bs_4augs_ft_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z2345_12bs_4augs_ft_80epochs/checkpoints/final.pth'
+```
+
+Freeze some layers, only update weights of last few layers:
+
+1 * 8 (initial) + 4 * 8 (down) + 4 * 8 (up) + 2 = 74 layers
+
+- 40: freeze all down layers
+- 56: freeze all down and the first two up blocks (works the best)
+- 64: freeze all down and the first three up blocks
+- 72: freeze all down and up blocks, just update the last two layers
+
+To ensure the class balance, we decided to use two zones together.
+
+Zone 1, 2 (For zone 1)
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z12_12bs_4augs_ft_fz56_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z125_12bs_4augs_ft_80epochs/checkpoints/final.pth'
+```
+
+Zone 2, 5 (For zone 2 & 5)
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z25_12bs_4augs_ft_fz56_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z125_12bs_4augs_ft_80epochs/checkpoints/final.pth'
+```
+
+Zone 2, 3 (For zone 3)
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z23_12bs_4augs_ft_fz56_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z234_12bs_4augs_ft_80epochs/checkpoints/final.pth'
+```
+
+Zone 2, 4 (For zone 4)
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z24_12bs_4augs_ft_fz56_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z234_12bs_4augs_ft_80epochs/checkpoints/final.pth'
 ```
@@
 ```
-python hrlcm/predict.py --args_path 'results/dl/unet_all_norm_200/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_all_norm_200/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/north' --out_dir 'results/prediction' --stats_dir 'results/north/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
+python hrlcm/predict.py --args_path 'results/dl/unet_z12_12bs_4augs_ft_fz56_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z12_12bs_4augs_ft_fz56_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction_z12' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
 
-scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/dl
+scp -r ubuntu@ec2-3-88-131-12.compute-1.amazonaws.com:~/hrlcm/results/prediction_z12 /Users/pinot/Dropbox/research/hrlcm/results/tanzania/prediction/z12
+```
+
+Records:
+
+```
+python hrlcm/predict.py --args_path 'results/dl/unet_z12_12bs_4augs_ft_fz56_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z12_12bs_4augs_ft_fz56_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 16 --batch_size 16 --gpu_devices '0'
+
+python hrlcm/predict.py --args_path 'results/dl/unet_z25_12bs_4augs_ft_fz56_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z25_12bs_4augs_ft_fz56_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 16 --batch_size 16 --gpu_devices '0'
+
+python hrlcm/predict.py --args_path 'results/dl/unet_z25_12bs_4augs_ft_fz56_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z25_12bs_4augs_ft_fz56_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone5.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 16 --batch_size 16 --gpu_devices '0'
+
+python hrlcm/predict.py --args_path 'results/dl/unet_z23_12bs_4augs_ft_fz56_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z23_12bs_4augs_ft_fz56_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone3.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 16 --batch_size 16 --gpu_devices '0'
+
+python hrlcm/predict.py --args_path 'results/dl/unet_z24_12bs_4augs_ft_fz56_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z24_12bs_4augs_ft_fz56_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone4.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 16 --batch_size 16 --gpu_devices '0'
+```
+
+```{r}
+# Get imgs in S3
+library(aws.s3)
+library(dplyr)
+library(parallel)
+items <- get_bucket(bucket = "activemapper", 
+                    prefix = "leisong/predict", 
+                    max = Inf)
+keys <- unlist(lapply(c(2: length(items)), function(i) {
+    gsub("leisong/", "", items[[i]]$Key)
+}))
+
+catalog_pred <- read.csv("results/tanzania/dl_catalog_predict.csv", 
+                         stringsAsFactors = FALSE)
+fns <- catalog_pred$img %>% unique()
+
+fns <- setdiff(fns, keys)
+pth_from <- '/Volumes/elephant'
+pth_to <- 's3://activemapper/leisong'
+mclapply(fns, function(tile_pth) {
+    print(tile_pth)
+    cmd <- sprintf('aws s3 cp %s/%s %s/%s',
+                   pth_from, tile_pth, pth_to, tile_pth)
+    system(cmd, intern = TRUE)
+}, mc.cores = 10)
 ```
@@
 ```
-python hrlcm/evaluate.py --args_path 'results/dl/unet_all_norm_200/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_all_norm_200/checkpoints/final.pth' --data_dir 'results/north' --out_dir 'results/evaluation' --stats_dir 'results/north/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
+python hrlcm/evaluate.py --args_path 'results/dl/unet_z12_12bs_4augs_ft_fz56_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z12_12bs_4augs_ft_fz56_80epochs/checkpoints/final.pth' --data_dir 'results/tanzania' --out_dir 'results/evaluation' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
 
@@
 ```
+
+#### Post-cleaning
+
+- Cropland/Water: Object fixing
+- Grassland/Shrubland/Forest/Build-up/Bareland: No fix
 
@@
 ```
+
+### Copy files from/in S3
+
+```
+while true; do aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1; sleep 50m; done
+```
+
+```
+aws s3 cp --recursive s3://activemapper/leisong/unet_z1245_12bs_4augs_ft_80epochs/ $HOME/hrlcm/results/dl/unet_z1245_12bs_4augs_ft_80epochs
+```

### 2022-03-18 hrlcm/evaluate.py

@@ -111,6 +111,11 @@ def main():
                         help='path of normalization params (default: ./norm_stats)')
     parser.add_argument('--label_offset', type=int, default=1,
                         help='offset value to minus from label in order to start from 0 (default: 1)')
+    parser.add_argument('--img_bands', type=str, choices=['all', 'nicfi'],
+                        default='all',
+                        help='bands of satellite images to use. \
+                        all means all bands, including RGB, NIR of NICFI tiles, intercept,  \
+                        cos(2t) of VV and VH. (default: all)')
     parser.add_argument('--num_workers', type=int, default=0,
                         help='number of worker(s) to load dataset (default: 0)')
 
@@ -146,18 +151,22 @@ def main():
     ])
 
     # Image transform
+    id_bands = list(range(1, 13)) if args.img_bands == "all" else list(range(1, 9))
     # Load mean and sd for normalization
     with open(os.path.join(args.stats_dir,
                            "means.pkl"), "rb") as input_file:
         mean = tuple(pkl.load(input_file))
+        mean = mean[0:len(id_bands)]
 
     with open(os.path.join(args.stats_dir,
                            "stds.pkl"), "rb") as input_file:
         std = tuple(pkl.load(input_file))
+        std = std[0:len(id_bands)]
     img_transform = ImgNorm(mean, std)
 
     # Get validate dataset
     validate_dataset = NFSEN1LC(data_dir=args.data_dir,
+                                bands=id_bands,
                                 usage='validate',
                                 label_offset=args.label_offset,
                                 sync_transform=val_transform,
@@ -215,6 +224,9 @@ def main():
     with torch.no_grad():
         for i, (image, labels) in enumerate(
                 tqdm(validate_loader, desc="Evaluate", dynamic_ncols=True)):
+            # Shrink labels
+            labels = labels[:, 4:-4, 4:-4]
+            
             # Move data to gpu if model is on gpu
             if args.use_gpu:
                 image = image.to(torch.device("cuda"))

### 2022-03-18 tools/parse_img_from_s3.R

@@ -1,0 +1,19 @@
+# Get imgs in S3
+library(aws.s3)
+library(dplyr)
+library(parallel)
+
+catalog_pred <- read.csv("results/tanzania/dl_catalog_predict_zone1_1.csv", 
+                         stringsAsFactors = FALSE)
+fns <- unlist(lapply(catalog_pred$tiles_relate, function(relates) {
+    strsplit(relates, ",")[[1]]})) %>% unique()
+fns <- fns[fns != "None"]
+
+pth_to <- 'ubuntu@:/home/ubuntu/hrlcm/results/tanzania'
+pth_from <- 's3://activemapper/leisong'
+mclapply(fns, function(tile_pth) {
+    print(tile_pth)
+    cmd <- sprintf('aws s3 cp %s/%s %s/%s',
+                   pth_from, tile_pth, pth_to, tile_pth)
+    system(cmd, intern = TRUE)
+}, mc.cores = 10)

### 2022-03-20 docs/run_experiments.Rmd
Add new loss and modify some details

@@
 
-Hum... Using a bigger weight for cropland in loss calculation increased the accuracy significantly.
+Hum... Using a bigger weight for cropland in loss calculation increased the overall accuracy a bit. However, the cost is the overestimation of cropland over sparse vegetation area.
 
@@
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 121
+python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_ew_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 121
 ```
@@
 python hrlcm/fit_compose_lr.py --exp_name unet_z24_12bs_4augs_ft_fz56_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z234_12bs_4augs_ft_80epochs/checkpoints/final.pth'
+```
+
+#### "Hierarchical" training with dynamic loss function
+
+First, train a general model with relatively large learning rate (0.001 - 0.0001), balanced cross entropy loss function, and full training dataset for 80 epochs:
+
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0001 --max_lr 0.001 --save_freq 20 --epochs 81
+```
+
+Then, transfer with updating weights of all layers. It uses relatively small learning rate (0.0001 - 0.000001) with a dynamic loss that is a weighted average of BCE and Lovász-Softmax.
+
+Take zone1 as an example:
+
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z1_12bs_4augs_ft_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.000001 --max_lr 0.0001 --save_freq 20 --epochs 121 --resume 'results/dl/unet_full_12bs_4augs_80epochs/checkpoints/final.pth'
 ```
@@
 ```
-while true; do aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1; sleep 50m; done
+while true; do aws s3 cp --recursive $HOME/hrlcm/results/prediction_zone1 s3://activemapper/leisong/prediction/zone1_only; sleep 50m; done
 ```
@@
 ```
-aws s3 cp --recursive s3://activemapper/leisong/unet_z1245_12bs_4augs_ft_80epochs/ $HOME/hrlcm/results/dl/unet_z1245_12bs_4augs_ft_80epochs
+aws s3 cp --recursive s3://activemapper/leisong/unet_full_12bs_4augs_120epochs/ $HOME/hrlcm/results/dl/unet_full_12bs_4augs_120epochs
 ```

### 2022-03-20 hrlcm/loss.py

@@ -1,9 +1,7 @@
 """
 This is a script of multiple losses.
 References:
-    https://github.com/bhanML/Co-teaching.git
-    https://github.com/xingruiyu/coteaching_plus.git
-    https://github.com/hongxin001/JoCoR.git
+    https://github.com/bermanmaxim/LovaszSoftmax
 Author: Lei Song, Boka Luo
 Maintainer: Lei Song (lsong@clarku.edu)
 """
@@ -11,6 +9,14 @@ Maintainer: Lei Song (lsong@clarku.edu)
 from __future__ import print_function
 import torch
 import torch.nn as nn
+from torch.autograd import Variable
+import torch.nn.functional as F
+import numpy as np
+
+try:
+    from itertools import ifilterfalse
+except ImportError:  # py3k
+    from itertools import filterfalse as ifilterfalse
 
 
 class BalancedCrossEntropyLoss(nn.Module):
@@ -77,9 +83,9 @@ def weighted_loss(predict, target, weights=None, ignore_index=-100):
         for i in range(len(unique)):
             lossWeight[unique[i]] = weight[i]
             counts[unique[i]] = unique_counts[i]
-            
+
         loss_fn = BalancedCrossEntropyLoss(ignore_index=ignore_index, reduction='none')
-        
+
         loss = loss_fn(predict, target)
         # Multiply image weights
         loss = torch.sum(loss, (1, 2)) * weights
@@ -87,3 +93,147 @@ def weighted_loss(predict, target, weights=None, ignore_index=-100):
         loss = loss.sum() / (lossWeight * counts).sum()
 
     return loss
+
+
+def lovasz_grad(gt_sorted):
+    """
+    Computes gradient of the Lovasz extension w.r.t sorted errors
+    See Alg. 1 in paper
+    """
+    p = len(gt_sorted)
+    gts = gt_sorted.sum()
+    intersection = gts - gt_sorted.float().cumsum(0)
+    union = gts + (1 - gt_sorted).float().cumsum(0)
+    jaccard = 1. - intersection / union
+    if p > 1:  # cover 1-pixel case
+        jaccard[1:p] = jaccard[1:p] - jaccard[0:-1]
+    return jaccard
+
+
+def iou(preds, labels, C, EMPTY=1., ignore=None, per_image=False):
+    """
+    Array of IoU for each (non ignored) class
+    """
+    if not per_image:
+        preds, labels = (preds,), (labels,)
+    ious = []
[…]

### 2022-03-20 tools/parse_img_from_s3.R

@@ -9,7 +9,7 @@ fns <- unlist(lapply(catalog_pred$tiles_relate, function(relates) {
     strsplit(relates, ",")[[1]]})) %>% unique()
 fns <- fns[fns != "None"]
 
-pth_to <- 'ubuntu@:/home/ubuntu/hrlcm/results/tanzania'
+pth_to <- '/home/ubuntu/hrlcm/results/tanzania'
 pth_from <- 's3://activemapper/leisong'
 mclapply(fns, function(tile_pth) {
     print(tile_pth)

### 2022-03-30 docs/run_experiments.Rmd
A few updates related to do prediction

--- 2022-03-09 docs/run_experiments.Rmd
@@
 
-According to some experiments, the accuracy of cropland is relatively low.
+According to some previous experiments, the accuracy of cropland is relatively low.
 One reason is that the farming condition over Tanzania is complex and thus hard to model.
@@
 
-#### Ensemble training
+Hum... Using a bigger weight for cropland in loss calculation increased the overall accuracy a bit. However, the cost is the overestimation of cropland over sparse vegetation area.
+
+#### Freeze layers
+
+Sometimes, people freeze some layers, only update weights of last few layers. The parameters for U-Net used in this project are:
+
+1 * 8 (initial) + 4 * 8 (down) + 4 * 8 (up) + 2 = 74 layers
+
+- 40: freeze all down layers
+- 56: freeze all down and the first two up blocks
+- 64: freeze all down and the first three up blocks
+- 72: freeze all down and up blocks, just update the last two layers
+
+#### U-Net structure
+
+Using `ConvTranspose2d` instead of `Upsample` could reduce the overestimation issue of built-up areas.
+Because upsampling just uses bilinear sampling method, which could smooth the whole image.
+However, built-up objects are usually tiny.
+Thus, they are affected by bilinear upsampling a lot.
+
+However, there are also cons of `ConvTranspose2d`.
+Using `ConvTranspose2d` loses the advantage of bilinear smoothing.
+Thus, at the boundary of an object, it might be some salt noises.
+If post-segmentation pruning is applied, this is not a big issue.
+
+Another issue is that because using `ConvTranspose2d` means add another learnable parameter layer, it slightly increases the need of computational resources. It really depends if this is an issue.
+
+Thus, whether using `ConvTranspose2d` or not depends what you want.
+
+#### "Hierachical" training
 
 When training a full model using the whole dataset, the main problem is cropland. One reason is that
-cropland highly relies on local climate and cultivating conditions and Tanzania is a large country.
+cropland highly relies on local climate and cultivating conditions and Tanzania is a large country. To reduce this impact, we could shrink the study area gradually into each agro-ecological zone.
 
-- Train multiple models with subset of labels.
+- Modeling structure:
 
-  - Zone 1, 2, 3, 4, 5 (composite learning rate)
-  - Zone 1, 2, 3, 4
-  - Zone 1, 2, 3, 5
-  - Zone 1, 2, 4, 5
-  - Zone 1, 3, 4, 5
-  - Zone 2, 3, 4, 5
-
-- Ensemble these models by voting, possibly at segment level.
-
-Records:
+```
+1, 2, 4, 5 -> 1, 2, 5 -> 1, 2 -> 1
+                      -> 2, 5 -> 2
+                              -> 5
+2, 3, 4, 5 -> 2, 3, 4 -> 2, 3 -> 3
+                      -> 2, 4 -> 4
+```
 
 Zone 1, 2, 3, 4, 5
+
+Comment out line 211 and add `learning_rates = [args.max_lr] * args.epochs` to use a fixed learning rate 0.001 to train.
+
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
+python hrlcm/fit_compose_lr.py --exp_name unet_full_startup_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --max_lr 0.001 --save_freq 20 --epochs 81
 ```
-Zone 1, 2, 3, 4
-```
-python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
-```
-Zone 1, 2, 3, 5
-```
-python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
-```
+
+Then, discard the changes above.
+
 Zone 1, 2, 4, 5
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
+python hrlcm/fit_compose_lr.py --exp_name unet_z1245_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 121 --resume 'results/dl/unet_full_startup_80epochs/checkpoints/final.pth'
 ```
-Zone 1, 3, 4, 5
+
+Comment out line 249 in `fit_compose_lr.py`, and modify `lr_scheduler.py` correspondingly. The learning rate scheduler is saved as a pickle as well.
+
+Zone 1, 2, 5
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
+python hrlcm/fit_compose_lr.py --exp_name unet_z125_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.0001 --save_freq 10 --epochs 81 --resume 'results/dl/unet_z1245_120epochs/checkpoints/final.pth'
+
+# Fine tune using a smaller learning rate
+python hrlcm/fit_compose_lr.py --exp_name unet_z125_ft_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.000001 --max_lr 0.00001 --save_freq 10 --epochs 81 --resume 'results/dl/unet_z125_80epochs/checkpoints/final.pth'
 ```
+
+Discard the changes above.
+
 Zone 2, 3, 4, 5
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_full_12bs_4augs_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 151
+python hrlcm/fit_compose_lr.py --exp_name unet_z2345_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 121 --resume 'results/dl/unet_full_startup_80epochs/checkpoints/final.pth'
+```
+
+Do the same as zone 1, 2, 5.
+
+Zone 2, 3, 4
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z234_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.0001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z2345_120epochs/checkpoints/final.pth'
+
+# Fine tune with a smaller learning rate
+python hrlcm/fit_compose_lr.py --exp_name unet_z234_ft_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.000001 --max_lr 0.00001 --save_freq 10 --epochs 81 --resume 'results/dl/unet_z234_80epochs/checkpoints/final.pth'
+```
+
+**[NOTE:]** _I tried multiple ways, which includes adding more training labels, using different types of loss functions (particularly ones to deal with class imbalance), and applying different model structure.
+No luck to get a reasonable balanced results if shrink the training area further into single zones.
+So I decided to stop here to use three zones as a group for the final result._
+
+_But if you like, or I get the right method to do further, go further to finish the following steps._
+
+_Zone 1_
+```
+# "Shrink" the model to zone1
+python hrlcm/fit_compose_lr.py --exp_name unet_z125_ew_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.0001 --save_freq 10 --epochs 81 --resume 'results/dl/unet_z125_80epochs/checkpoints/final.pth'
+
+# "Fine-tune" the zone1 model
+python hrlcm/fit_compose_lr.py --exp_name unet_z1_ft_72fz_cl_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --max_lr 0.00000001 --save_freq 10 --epochs 81 --resume 'results/dl/unet_z1_ew80epochs/checkpoints/final.pth'
+```
+
+_Zone 2, 5 (For zone 2 & 5)_
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z25_ew_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.0001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z125_80epochs/checkpoints/final.pth'
+```
+
+_Zone 2, 3 (For zone 3)_
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z23_12bs_4augs_ft_fz56_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z234_12bs_4augs_ft_80epochs/checkpoints/final.pth'
+```
+
+_Zone 2, 4 (For zone 4)_
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_z24_12bs_4augs_ft_fz56_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z234_12bs_4augs_ft_80epochs/checkpoints/final.pth'
 ```
@@
 ### Prediction
+
+Doing prediction is simple. Applying a model into its zones.
 
@@
 ```
-python hrlcm/predict.py --args_path 'results/dl/unet_zone1_12bs_4augs_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_zone1_12bs_4augs_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_test.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
+python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
 
-scp -r ubuntu@ec2-54-163-146-125.compute-1.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/tanzania/prediction/unet_zone1_12bs_4augs_80epochs
+aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction
+```
+
+Steps in production:
+
+```
+
+python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
+
+aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1
+
+rm -rf results/prediction
+```
+
+```{r}
+# Get imgs in S3
+library(aws.s3)
+library(dplyr)
+library(parallel)
+items <- get_bucket(bucket = "activemapper", 
+                    prefix = "leisong/predict", 
+                    max = Inf)
+keys <- unlist(lapply(c(2: length(items)), function(i) {
+    gsub("leisong/", "", items[[i]]$Key)
+}))
+
+catalog_pred <- read.csv("results/tanzania/dl_catalog_predict.csv", 
+                         stringsAsFactors = FALSE)
+fns <- catalog_pred$img %>% unique()
+
+fns <- setdiff(fns, keys)
+pth_from <- '/Volumes/elephant'
+pth_to <- 's3://activemapper/leisong'
+mclapply(fns, function(tile_pth) {
+    print(tile_pth)
+    cmd <- sprintf('aws s3 cp %s/%s %s/%s',
+                   pth_from, tile_pth, pth_to, tile_pth)
+    system(cmd, intern = TRUE)
+}, mc.cores = 10)
 ```
@@
 ```
+
+### Copy files from/to S3
+
+To:
+
+```
+aws s3 cp --recursive $HOME/hrlcm/results/dl s3://activemapper/leisong/model
+
+while true; do aws s3 cp --recursive $HOME/hrlcm/results/dl/unet_full_startup_80epochs s3://activemapper/leisong/model/unet_full_startup_80epochs; sleep 50m; done
+
+aws s3 cp --recursive $HOME/hrlcm/results/prediction_zone1_125 s3://activemapper/leisong/prediction/
+```
+
+From:
+
+```
+aws s3 cp --recursive s3://activemapper/leisong/unet_full_12bs_4augs_120epochs/ $HOME/hrlcm/results/dl/unet_full_12bs_4augs_120epochs
+```

### 2022-03-30 guess_model/10_split_catalog_into_zones.R

@@ -59,7 +59,7 @@ invisible(lapply(zone_groups, function(zone_ids) {
     if (zone_ids %in% c(1, 4)) {
         catalog_pred_zone1 <- catalog_pred_zone %>% 
             slice(1:(nrow(.) %/% 2))
-        catalog_pred_zone1 <- catalog_pred_zone %>% 
+        catalog_pred_zone2 <- catalog_pred_zone %>% 
             filter(!tile_id %in% catalog_pred_zone1$tile_id)
         write.csv(catalog_pred_zone1, 
                   sprintf('results/tanzania/dl_catalog_predict_zone%s_1.csv', 

### 2022-03-30 guess_model/7_2_predict_add_tiles.R

@@ -1,4 +1,4 @@
-# Title     : Script to make guess labels
+# Title     : Script to make guess labels for some special regions
 # Objective : To use random forest guesser
 #             to get new labels. At this stage,
 #             we used Google Open Buildings as built-up label
@@ -41,24 +41,27 @@ source('guess_model/functions.R')
 # Directories
 message("--Set directories")
 stack_dir <- '/Volumes/elephant/pred_stack'
-labels_dir <- here('results/tanzania/guess_labels')
+labels_dir <- here('results/tanzania/guess_labels_add')
 if (!dir.exists(labels_dir)) dir.create(labels_dir)
 
 # Read vectors
 message("--Read vectors")
 tiles <- read_sf('data/geoms/tiles_nicfi.geojson') %>% select(tile)
 # Subset tiles
-tiles_north <- read_sf('data/geoms/tiles_nicfi_north.geojson')
-tiles <- tiles %>% filter(!tile %in% tiles_north$tile)
+oversample_zones <- read_sf('data/geoms/oversample_zones.geojson')
+tiles <- tiles %>% slice(unique(unlist(st_intersects(oversample_zones, tiles))))
+# Remove existing ones
+catalog_exist <- read.csv("results/tanzania/dl_catalog_train.csv")
+tiles <- tiles %>% filter(!tile %in% unique(catalog_exist$tile))
+rm(catalog_exist)
+
 ## Remove the problematic tile
 tiles <- tiles %>% filter(tile != '1210-1018')
-set.seed(123)
-tiles <- tiles %>% sample_frac(0.5); rm(tiles_north)
 
-# Cut the tiles and make 4 samples
-# 3 for train, 1 for validate
+# Cut the tiles and make 3 samples
+# 3 just for train
 message('--Generate catalog')
-n_sample <- 4
+n_sample <- 1
 indices <- matrix(1:64, 8, 8)
 indices <- indices[, ncol(indices):1]
 sample_tiles <- do.call(rbind, lapply(1:nrow(tiles), function(n){
@@ -71,17 +74,8 @@ sample_tiles <- do.call(rbind, lapply(1:nrow(tiles), function(n){
         mutate(tile = tile$tile,
                index = as.vector(indices)) %>% 
         slice(sample(1:nrow(.), n_sample))
-}))
-# st_write(sample_tiles, here('results/tanzania/catalog_sample_tiles.geojson'))
-
-# Filter finished ones [IN CASE]
[…]

### 2022-03-30 hrlcm/loss.py

@@ -7,11 +7,12 @@ Maintainer: Lei Song (lsong@clarku.edu)
 """
 
 from __future__ import print_function
+
+import numpy as np
 import torch
 import torch.nn as nn
-from torch.autograd import Variable
 import torch.nn.functional as F
-import numpy as np
+from torch.autograd import Variable
 
 try:
     from itertools import ifilterfalse
@@ -47,8 +48,12 @@ class BalancedCrossEntropyLoss(nn.Module):
 
         lossWeight = torch.ones(predict.shape[1]).cuda() * 0.00001
         for i in range(len(unique)):
+            # Modify if you want to raise or reduce the weight of one class
             if unique[i] == 0:
                 lossWeight[unique[i]] = 2 * weight[i]
+            # # For 2-zone fine tune
+            # if unique[i] == 5:
+            #     lossWeight[unique[i]] = 0.5 * weight[i]
             else:
                 lossWeight[unique[i]] = weight[i]
         loss = nn.CrossEntropyLoss(weight=lossWeight, ignore_index=self.ignore_index, reduction=self.reduction)
@@ -182,6 +187,64 @@ def lovasz_softmax_flat(probas, labels, classes='present'):
     return mean(losses)
 
 
+def balanced_lovasz_softmax(predicts, labels, classes='present', per_image=False, ignore=None):
+    """
+    Multi-class Lovasz-Softmax loss
+      predicts: [B, C, H, W] Variable, class modeled result at each prediction.
+              Interpreted as binary (sigmoid) output with outputs of size [B, H, W].
+      labels: [B, H, W] Tensor, ground truth labels (between 0 and C - 1)
+      classes: 'all' for all, 'present' for classes present in labels, or a list of classes to average.
+      per_image: compute the loss per image instead of per batch
+      ignore: void class labels
+    """
+    probas = F.softmax(predicts, dim=1)
+    if per_image:
+        loss = mean(balanced_lovasz_softmax_flat(*flatten_probas(prob.unsqueeze(0), lab.unsqueeze(0), ignore))
+                    for prob, lab in zip(probas, labels))
+    else:
+        loss = balanced_lovasz_softmax_flat(*flatten_probas(probas, labels, ignore))
+    return loss
+
+
+def balanced_lovasz_softmax_flat(probas, labels):
+    """
+    Multi-class Lovasz-Softmax loss
+      probas: [P, C] Variable, class probabilities at each prediction (between 0 and 1)
[…]

### 2022-03-30 hrlcm/lr_scheduler.py

@@ -4,6 +4,7 @@ import torch_optimizer as optim
 
 def get_compose_lr(model, epochs, min_lr=0.00001, max_lr=0.001, stage1=30, stage2=60, stage3=90):
     """Util function to customize a learning rate scheduler.
+    For 0.001 - 0.00001
     Note: not a perfect function, user could customize this function based on needs.
         Args:
             model: the defined model
@@ -49,3 +50,54 @@ def get_compose_lr(model, epochs, min_lr=0.00001, max_lr=0.001, stage1=30, stage
         )
     del optimizer_lr
     return lrs
+
+
+# Small learning scheduler, like zone125 and zone234.
+# def get_compose_lr(model, epochs, min_lr=0.00001, max_lr=0.0001, stage1=10, stage2=40, stage3=70):
+#     """Util function to customize a learning rate scheduler.
+#     For 0.0001 - 0.00001
+#     Note: not a perfect function, user could customize this function based on needs.
+#         Args:
+#             model: the defined model
+#             epochs (int): the overall epochs
+#             min_lr (float): the last min learning rate
+#             max_lr (float): the initial max learning rate
+#             stage1 (int): epoch number 1 to change
+#             stage2 (int): epoch number 2 to change
+#             stage3 (int): epoch number 3 to change
+#         Returns:
+#             numpy.ndarray: the array of image values
+#         """
+# 
+#     # Use an arbitrary optimizer
+#     optimizer_lr = optim.AdaBound(model.parameters(), lr=max_lr, final_lr=0.01, amsbound=True)
+#     lrs = []
+#     for i in range(epochs):
+#         optimizer_lr.step()
+#         if i <= stage1:
+#             if i == stage1:
+#                 lr_scheduler_1 = torch.optim.lr_scheduler.CyclicLR(optimizer_lr, base_lr=0.00004,
+#                                                                    max_lr=0.00008,
+#                                                                    step_size_up=1, step_size_down=3,
+#                                                                    gamma=0.9, cycle_momentum=False,
+#                                                                    mode='exp_range')
+#                 lr_scheduler_1.step()
+#         elif i <= stage2:
+#             lr_scheduler_1.step()
+#             if i == stage2:
+#                 lr_scheduler_2 = torch.optim.lr_scheduler.CyclicLR(optimizer_lr, base_lr=0.00001,
+#                                                                    max_lr=0.00004,
+#                                                                    step_size_up=1, step_size_down=3,
[…]

### 2022-03-30 docs/run_experiments.Rmd
Modify options for sub regions

@@
 
+`tools/parse_img_from_s3.R` is a script to grab image stacks from S3 to local machine.
+
 Steps in production:
@@
 ```
+aws s3 cp --recursive s3://activemapper/leisong/model $HOME/hrlcm/results/dl
 
-python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
+cd ~/hrlcm
 
-aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1
-
-rm -rf results/prediction
-```
-
-```{r}
-# Get imgs in S3
-library(aws.s3)
-library(dplyr)
-library(parallel)
-items <- get_bucket(bucket = "activemapper", 
-                    prefix = "leisong/predict", 
-                    max = Inf)
-keys <- unlist(lapply(c(2: length(items)), function(i) {
-    gsub("leisong/", "", items[[i]]$Key)
-}))
-
-catalog_pred <- read.csv("results/tanzania/dl_catalog_predict.csv", 
-                         stringsAsFactors = FALSE)
-fns <- catalog_pred$img %>% unique()
-
-fns <- setdiff(fns, keys)
-pth_from <- '/Volumes/elephant'
-pth_to <- 's3://activemapper/leisong'
-mclapply(fns, function(tile_pth) {
-    print(tile_pth)
-    cmd <- sprintf('aws s3 cp %s/%s %s/%s',
-                   pth_from, tile_pth, pth_to, tile_pth)
-    system(cmd, intern = TRUE)
-}, mc.cores = 10)
+Rscript tools/parse_img_from_s3.R -z 1 -s 1;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1;rm -rf results/prediction;rm -rf results/predict;Rscript tools/parse_img_from_s3.R -z 1 -s 2;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1;rm -rf results/prediction;rm -rf results/predict;Rscript tools/parse_img_from_s3.R -z 2;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone2;rm -rf results/prediction;rm -rf results/predict;Rscript tools/parse_img_from_s3.R -z 5;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone5.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone5;rm -rf results/prediction;rm -rf results/predict;Rscript tools/parse_img_from_s3.R -z 3;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone3.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone3;rm -rf results/prediction;rm -rf results/predict;Rscript tools/parse_img_from_s3.R -z 4 -s 1;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone4_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone4;rm -rf results/prediction;rm -rf results/predict;Rscript tools/parse_img_from_s3.R -z 4 -s 2;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone4_2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone4;rm -rf results/prediction;rm -rf results/predict
 ```

### 2022-03-30 tools/parse_img_from_s3.R

@@ -3,7 +3,6 @@ library(aws.s3)
 library(dplyr)
 library(parallel)
 library(optparse)
-library(here)
 
 # Get command inputs
 option_list <- list(
@@ -16,9 +15,17 @@ option_list <- list(
 parms <- parse_args(OptionParser(option_list = option_list))
 
 # Do process
-pth <- file.path('/home/ubuntu/hrlcm/results/tanzania',
-                 sprintf('/dl_catalog_predict_zone%d_%d.csv',
-                         parms$zone, parms$sub_index))
+if (is.null(parms$sub_index)) {
+    pth <- file.path('/home/ubuntu/hrlcm/results/tanzania',
+                     sprintf('/dl_catalog_predict_zone%d.csv',
+                             parms$zone))
+} else {
+    pth <- file.path('/home/ubuntu/hrlcm/results/tanzania',
+                     sprintf('/dl_catalog_predict_zone%d_%d.csv',
+                             parms$zone, parms$sub_index))
+}
+
+message(pth)
 catalog_pred <- read.csv(pth, stringsAsFactors = FALSE)
 fns <- unlist(lapply(catalog_pred$tiles_relate, function(relates) {
     strsplit(relates, ",")[[1]]})) %>% unique()

### 2022-04-05 docs/run_experiments.Rmd
Update docs

--- 2022-03-30 docs/run_experiments.Rmd
@@
 ```
-1, 2, 4, 5 -> 1, 2, 5 -> 1, 2 -> 1
-                      -> 2, 5 -> 2
+1, 2, 4, 5 -> 1, 2, 5 -> 1
+                      -> 2
                       -> 5
-2, 3, 4, 5 -> 2, 3, 4 -> 2, 3 -> 3
-                      -> 2, 4 -> 4
+2, 3, 4, 5 -> 2, 3, 4 -> 3
+                      -> 4
 ```
@@
 
-Steps in production:
+`tools/parse_img_from_s3.R` is a script to grab image stacks from S3 to local machine.
+
+Steps in production (for records):
 
 ```
+# Grab models, it could be more specific because prediction just uses 2 final models
+aws s3 cp --recursive s3://activemapper/leisong/model $HOME/hrlcm/results/dl
 
-python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
+# Navigate to hrlcm
+cd ~/hrlcm
 
-aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1
-
-rm -rf results/prediction
-```
-
-```{r}
-# Get imgs in S3
-library(aws.s3)
-library(dplyr)
-library(parallel)
-items <- get_bucket(bucket = "activemapper", 
-                    prefix = "leisong/predict", 
-                    max = Inf)
-keys <- unlist(lapply(c(2: length(items)), function(i) {
-    gsub("leisong/", "", items[[i]]$Key)
-}))
-
-catalog_pred <- read.csv("results/tanzania/dl_catalog_predict.csv", 
-                         stringsAsFactors = FALSE)
-fns <- catalog_pred$img %>% unique()
-
-fns <- setdiff(fns, keys)
-pth_from <- '/Volumes/elephant'
-pth_to <- 's3://activemapper/leisong'
-mclapply(fns, function(tile_pth) {
-    print(tile_pth)
-    cmd <- sprintf('aws s3 cp %s/%s %s/%s',
-                   pth_from, tile_pth, pth_to, tile_pth)
-    system(cmd, intern = TRUE)
-}, mc.cores = 10)
+# Run all steps for different zones together 
+Rscript tools/parse_img_from_s3.R -z 1 -s 1;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 1 -s 2;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 2;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone2;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 5;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone5.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone5;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 3;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone3.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone3;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 4 -s 1;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone4_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone4;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 4 -s 2;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone4_2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone4;rm -rf results/prediction;rm -rf results/tanzania/predict
 ```
@@
 
-#### Post-cleaning
+#### Post-cleaning (TBD)
 

### 2022-04-25 docs/manuscript_figures.Rmd
Modifications for the paper

@@
 # Define example points
-pts_example <- read_sf(here('data/north/pts_example.shp')) %>% 
+pts_example <- read_sf(here('data/north/pts_example.geojson')) %>% 
     st_cast('POINT')
@@
                  values_to = "dB")
-rm(pts_vv_ts, pts_vh_ts)
+rm(pts_vv_fit, pts_vh_fit)
 
@@
               vjust = 3,
-              ncol = 2), 
+              nrow = 2), 
     ts_epl, ncol = 2)
@@
        width = 8, height = 2.7, dpi = 300)
+
+# Version 2
+ts_epl <- ggplot() + 
+    geom_point(data = pts_ts, 
+               aes(x = DOY, y = `dB`, 
+                   color = factor(ids)),
+               size = 0.6) +
+    geom_line(data = pts_fit,
+              aes(x = DOY, y = `dB`, 
+                  color = factor(ids))) +
+    facet_wrap(~polarization, 
+               scales = 'free_y', nrow = 2,
+               strip.position = "top") +
+    scale_color_manual("Land cover type",
+                       values = cols_lc$cols, 
+                       breaks = cols_lc$ids,
+                       labels = cols_lc$`Land cover type`) +
+    theme_bw() +
+    theme(text=element_text(size=8),
+          axis.text=element_text(size=8),
+          axis.title=element_text(size=8), 
+          plot.title=element_text(size=8), 
+          legend.text=element_text(size=8), 
+          legend.title=element_text(size=8))
+s1_fg <- ggarrange(
+    ggarrange(NA, vh_fg, NA, vv_fg, NA, nrow = 5,
+              heights = c(0.05, 1, 0.05, 1, 0.25),
+              labels = c(NA, 'VH', NA, 'VV', NA),
+              font.label = list(size = 8),
+              hjust = 0.05), 
+    ts_epl, ncol = 2, widths = c(1, 2.2))
+ggsave(here('docs/figures/s1_image_v2.png'),
+       s1_fg,
+       width = 6, height = 3.5, dpi = 300)
 ```
@@
 
-ggplot(tiles, aes(quality)) +
-  geom_bar(color = 'black',fill = 'cyan3') +
-  xlab('Quality (correctness, difficulty)') +
-  ylab('Count') +
-  theme_bw()
-
 quality_fig <- ggplot(
@@
   ylab('Count') +
-  theme_bw()
-
-ggplot(
-  tiles,
-  aes(fill = factor(hardiness), x = score)) + 
-  geom_bar(position = "stack") +
-  coord_polar("x") +
   theme_bw()
@@
 
-types <- c('Learning rate', 'Loss', 'AA', 'mIoU', 'Cropland', 'Forest', 
+types <- c('Learning rate', 'Loss', 'Average accuracy', 
+           'mIoU', 'Cropland', 'Forest/Dense tree', 
            'Grassland', 'Shrubland', 'Water', 
            'Built-up', 'Bareland')
-lc <- c('Cropland', 'Forest', 
+lc <- c('Cropland', 'Forest/Dense tree', 
         'Grassland', 'Shrubland', 'Water', 
-        'Built-up', 'Bareland', 'AA')
+        'Built-up', 'Bareland', 'Average accuracy')
+lb <- paste0(rep("(", 8), 1:8, rep(")", 8), rep(" ", 8), lc)
 content <- do.call(rbind, lapply(types, function(type){
@@
         item <- 'lr'
+    } else if (type == 'Average accuracy') {
+        item <- 'AA'
+    } else if (type == 'Forest/Dense tree') {
+        item <- 'Forest'
     } else {item <- type}
@@
     labs(y = expression(Learning ~ rate ~ (10^-3)), x = '') +
-    theme_bw()
+    ggtitle('A') +
+    theme_bw() +
+    theme(plot.title = element_text(hjust = 0.5))
 curve_loss <- content %>% 
@@
     labs(y = 'Loss', x = '') +
-    theme_bw()
+    ggtitle('B') +
+    theme_bw() +
+    theme(plot.title = element_text(hjust = 0.5))
 curve_iou <- content %>% 
@@
     labs(y = 'mIoU', x = '') +
-    theme_bw()
+    ggtitle('C') +
+    theme_bw() +
+    theme(plot.title = element_text(hjust = 0.5))
 curves_acc <- content %>% 
     filter(Item %in% lc) %>% 
-    mutate(Item = factor(Item, levels = lc)) %>% 
+    mutate(Item = factor(Item, levels = lc, labels = lb)) %>% 
     ggplot(aes(x = Epoch, y = Value)) +
@@
     labs(y = 'Accuracy') +
-    facet_wrap(~Item, scales = 'free_y', 
+    ggtitle('D') +
+    facet_wrap(~Item, 
+               # scales = 'free_y',
                nrow = 2, ncol = 4) +
-    theme_bw()
+    theme_bw() +
+    theme(plot.title = element_text(hjust = 0.5))
 curves <- ggarrange(
     ggarrange(curve_lr, curve_loss, curve_iou, ncol = 3),
-    curves_acc, nrow = 2, heights = c(1, 1.6))
-
-ggsave(here('docs/figures/curves_k15_only_final_mod.png'),
+    curves_acc, nrow = 2, heights = c(1, 1.7))
+
+ggsave(here('docs/figures/curves_k15_only_final_mod_v2.png'),
        curves,
-       width = 8, height = 5, dpi = 300)
+       width = 7, height = 5, dpi = 300)
 ```
@@
     id = 1:8,
-    type = c("Cropland", "Forest", 
+    type = c("Cropland", "Forest/Dense tree", 
              "Grassland", "Shrubland", 
@@
               '#fdbf6f', '#0ea591'))
-# pred <- read_stars(pred_path)
-pred <- rast(pred_path)
-setCats(pred, value = color_tb$type, index = color_tb$id)
-pred <- st_as_stars(pred)
+pred <- read_stars(pred_path)
+names(pred) <- 'landcover'
+# pred <- rast(pred_path)
+# set.cats(pred, value = color_tb$type, index = color_tb$id)
+# pred <- st_as_stars(pred)
 
@@
         tm_shape() + 
-        tm_raster("landcover_north", 
+        tm_raster("landcover", 
               n = 8, style = 'cat',
@@
 pred_final <- tm_shape(pred) +
-    tm_raster("landcover_north", 
+    tm_raster("landcover", 
               title = "Land cover types",
@@
           plot.margin = unit(rep(0, 4),"cm"))+
-    guides(fill = guide_legend(ncol = 2))
+    guides(fill = guide_legend(ncol = 8))
 legend_lc <- get_legend(legend_lc)
@@
        width = 7, height = 6, dpi = 300)
+```
+
+#### Class areas
+
+```{r}
+# Class proportion, class 1 - 7
+cls_prop <- cls_freq %>% 
+    slice(1:7) %>% 
+    mutate(proportion = ratio / sum(.$ratio)) %>% 
+    select(landcover, proportion)
+
+# Confusion matrix
+cf_orig <- data.frame(cf$table) %>% 
+    select(Prediction, Freq, Reference) %>% 
+    pivot_wider(names_from = Reference, 
+                values_from = Freq)
+cf_orig$num <- rowSums(cf_orig[, -1], na.rm = TRUE)
+cf_orig$proportion <- cls_prop$proportion
+cf_ratio <- do.call(rbind, lapply(1:nrow(cf_orig), function(n){
+    cf_orig[n, 2:8] / cf_orig[[n, 9]] * cf_orig[[n, 10]]
+}))
+
+## Get the adjusted proportion
+cf_ratio['Pj', ] <- colSums(cf_ratio)
+
+# Calculate the area of the whole image
+pred_area <- rast(pred_path)
+cell_num <- freq(pred_area)
+whole_area <- sum(cell_num[1:7, 3]) * 
+    (res(pred_area)[1] / 1000) * 
+    (res(pred_area)[2] / 1000)
+class_area <- cf_ratio["Pj", ] * whole_area
+class_area[, '8'] <- cell_num[[8, 3]] * 
+    (res(pred_area)[1] / 1000) * 
+    (res(pred_area)[2] / 1000)
+
+# Calculate the errors
+cf_ratio_error <- cf_ratio[1:7, ]
+cf_ratio_error$wi <- cf_orig$proportion
+cf_ratio_error$n <- cf_orig$num
+
+err_calc <- function(pi, wi, ni, whole_area) {
+    # 1.96 for 95% confidence
+    sqrt(sum((wi * pi - pi ^ 2) / (ni - 1))) * whole_area * 1.96
+}
+
+adjust_class_err <- unlist(lapply(1:7, function(n) {
+    err_calc(cf_ratio_error[, n], 
+             cf_ratio_error$wi, 
+             cf_ratio_error$n, whole_area)
+}))
+
+adjust_stats_area <- data.frame(
+    area = unlist(class_area),
+    confidence_interval = c(adjust_class_err, NA),
+    proportion = cls_freq[, 2])
+save(adjust_stats_area, file = 'docs/figures/adjust_stats_area.rda')
+
+# 3D pie
+cols <- color_tb$color
+lab <- paste(round(adjust_stats_area$area, 1), "km2")
+plotrix::pie3D(adjust_stats_area$proportion,
+      col = cols,
+      labels = lab,
+      explode = 0.15,
+      labelcex = 1,
+      radius = 1.1,
+      border = "white",
+      theta = 1.1)
+
+# Version 2 of final map
+tmap_mode("plot")
+pred_final <- tm_shape(pred) +
+    tm_raster("landcover_north_withwl.tif", 
+              #title = "Land cover types",
+              title = '',
+              n = 8, style = 'cat',
+              labels = color_tb$type,
+              palette = color_tb$color) +
+    tm_layout(frame = F,
+              legend.show = FALSE,
+              outer.margins = c(0.02, 0.01, 0, 0.01),
+              inner.margins = 0)
+pred_final <- tmap_grob(pred_final)
+
+r_df <- data.frame(x = 1:8, 
+                   y = 1:8,
+                   rst = as.factor(1:8))
+legend_lc <- ggplot() + 
+    geom_raster(
+        data = r_df, 
+        aes(x = x, y = y, 
+            fill = rst)) +
+    scale_fill_manual('',
+                      values = color_tb$color, 
+                      breaks = 1:8,
+                      labels = color_tb$type) +
+    theme_minimal() +
+    theme(legend.position = 'right',
+          axis.title.x = element_blank(),
+          axis.text.x = element_blank(),
+          axis.ticks.x = element_blank(),
+          axis.title.y = element_blank(),
+          axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(),
+          plot.margin = unit(rep(-1, 4),"cm"))+
+    guides(fill = guide_legend(ncol = 4))
+legend_lc <- get_legend(legend_lc)
+f1 <- ggarrange(pred_final, legend_lc, NA, 
+          nrow = 3, heights = c(5, 1, 0.5))
+
+# Get pie chart for class frequency
+cls_freq <- rast(pred_path)
+cls_freq <- freq(cls_freq) %>% 
+    data.frame() %>% 
+    mutate(landcover = value,
+           ratio = count / sum(.$count)) %>% 
+    select(landcover, ratio)
+save(cls_freq, file = 'docs/figures/cls_freq.rda')
+
+cls_freq <- cls_freq %>% arrange(landcover)
+cols <- color_tb$color
+lab <- paste0(round(cls_freq$ratio/sum(cls_freq$ratio) * 100, 1), "%")
+
+# Barplot
+cls_freq <- cls_freq %>% 
+    mutate(landcover = factor(landcover, 
+                              levels = cls_freq %>% 
+                               arrange(desc(ratio)) %>% 
+                               pull(landcover)),
+        label_ypos = 0.9 * ratio)
+barplot <- ggplot(data=cls_freq, aes(x=landcover, y=ratio)) +
+    geom_bar(stat="identity", aes(fill=as.factor(landcover))) +
+    geom_text(aes(y=label_ypos, label=lab), angle = 90,
+              color="black", size=3)+
+    scale_fill_manual(values = cols[as.integer(levels(cls_freq$landcover))]) +
+    theme_void() +
+    theme(legend.position = "none")
+
+# Table
+adjust_stats_area <- adjust_stats_area %>% 
+    mutate(Landcover = color_tb$type) %>% 
+    arrange(desc(area)) %>% 
+    mutate(`Error-adjusted area` = glue(
+        paste0('{format(round(area, digits = 1), nsmall = 1)}',
+               '\u00B1{format(round(confidence_interval, digits = 1), nsmall = 1)}',
+               ' km\u00B2'))) %>% 
+    select(Landcover, `Error-adjusted area`)
+adjust_stats_area[8, 2] <- '1435.7 km\u00B2*'
+
+tbl_theme <- gridExtra::ttheme_default(
+    core = list(fg_params=list(cex = 0.7, hjust = 0, x = 0.1,
+                               parse = TRUE),
+                bg_params = list(fill = 'gray95')),
+    colhead = list(fg_params=list(cex = 0.8)),
+    rowhead = list(fg_params=list(cex = 0.8)))
+tbl_conf <- tableGrob(adjust_stats_area, rows = NULL, theme = tbl_theme)
+
+pred_final_plt <- ggarrange(f1,
+                            ggarrange(NA, tbl_conf,
+                                      barplot, NA, 
+                                      nrow = 4,
+                                      labels = c(NA, 'B', 'C', NA),
+                                      hjust = c(2, 4, 2, 2),
+                                      heights = c(0.2, 1, 1, 0.3)), 
+                            NA,
+                            labels = c('A', NA, NA),
+                            vjust = 5, hjust = -1,
+                            ncol = 3, widths = c(6, 2, 0.5))
+ggsave(here('docs/figures/final_map.png'),
+       pred_final_plt,
+       width = 8, height = 5.5, dpi = 300)
+```
+
+```{r}
+library(terra)
+library(stars)
+library(tmap)
+library(ggpubr)
+library(gridExtra)
+
+pred_path <- here(file.path('results/dl/prediction',
+                            'unet_k15_only_clr_200epc',
+                            'landcover_north_withwl.tif'))
+color_tb <- data.frame(
+    id = 1:8,
+    type = c("Cropland", "Forest/Dense tree", 
+             "Grassland", "Shrubland", 
+             "Water", 'Built-up', "Bareland", 
+             'Wetland'),
+    color = c('#ff7f00', '#074702', '#b2df8a',
+              '#33a02c', '#3347f9', '#5a6057',
+              '#fdbf6f', '#0ea591'))
+pred <- read_stars(pred_path)
+names(pred) <- 'landcover'
+
+# Get examples
+id_selected <- c('1211-1008', '1209-997', '1221-1012', '1234-992')
+
+## Images
+library(ggpubr)
+library(RStoolbox)
+library(ggplot2)
+
+fnames_s1 <- file.path("data/plts_nicfi",
+                       sprintf('planet_medres_normalized_analytic_2017-12_2018-05_mosaic_%s.tif', 
+                               id_selected))
+fnames_s2 <- file.path("data/plts_nicfi",
+                       sprintf('planet_medres_normalized_analytic_2018-06_2018-11_mosaic_%s.tif', 
+                               id_selected))
+fg_s1 <- lapply(fnames_s1, function(fname) {
+    x <- stack(fname) %>% subset(1:3) %>% 
+        raster::stretch(minq = 0.02, maxq = 0.98)
+    tm <- tm_shape(x) +
+        tm_rgb(r = 1, g = 2, b = 3,
+               max.value = max(values(x)[, 1:3]))
+    tmap_grob(tm)
+    # stack(fname) %>% subset(1:4) %>% 
+    #     ggRGB(r = 1, g = 2, b = 3, 
+    #           scale = max(values(.)[, 1:3]), 
+    #           stretch = 'lin') +
+    #     theme_minimal() +
+    #     theme(axis.title.x = element_blank(),
+    #           axis.text.x = element_blank(),
+    #           axis.ticks.x = element_blank(),
+    #           axis.title.y = element_blank(),
+    #           axis.text.y = element_blank(),
+    #           axis.ticks.y = element_blank(),
+    #           plot.margin = unit(rep(0, 4),"cm"))
+})
+
+fg_s2 <- lapply(fnames_s2, function(fname) {
+    x <- stack(fname) %>% subset(1:3) %>% 
+        raster::stretch(minq = 0.02, maxq = 0.98)
+    tm <- tm_shape(x) +
+        tm_rgb(r = 1, g = 2, b = 3,
+               max.value = max(values(x)[, 1:3]))
+    tmap_grob(tm)
+    # stack(fname) %>% subset(1:4) %>% 
+    #     ggRGB(r = 1, g = 2, b = 3, 
+    #           scale = max(values(.)[, 1:3]), 
+    #           stretch = 'hist') +
+    #     theme_minimal() +
+    #     theme(axis.title.x = element_blank(),
+    #           axis.text.x = element_blank(),
+    #           axis.ticks.x = element_blank(),
+    #           axis.title.y = element_blank(),
+    #           axis.text.y = element_blank(),
+    #           axis.ticks.y = element_blank(),
+    #           plot.margin = unit(rep(0, 4),"cm"))
+})
+s1 <- ggarrange(fg_s1[[1]], fg_s1[[2]], 
+          fg_s1[[3]], fg_s1[[4]], 
+          nrow = 4, ncol = 1)
+s2 <- ggarrange(fg_s2[[1]], fg_s2[[2]], 
+          fg_s2[[3]], fg_s2[[4]], 
+          nrow = 4, ncol = 1)
+
+# Prediction
+tiles <- read_sf('data/geoms/tiles_nicfi_north.geojson')
+tiles <- tiles %>% filter(tile %in% id_selected) %>% 
+    st_transform(crs = crs(rast(pred_path))) %>% 
+    mutate(id = 1:nrow(.))
+rst_tiles <- lapply(1:nrow(tiles), function(n){
+    tm <- st_crop(pred, tiles %>% slice(n)) %>% 
+        tm_shape() + 
+        tm_raster("landcover", 
+                  n = 8, style = 'cat',
+                  labels = color_tb$type,
+                  palette = color_tb$color) +
+        tm_layout(frame = F,
+                  legend.show = F)
+    tmap_grob(tm)
+})
+pred_ours <- ggarrange(
+    rst_tiles[[2]], rst_tiles[[3]], rst_tiles[[1]], 
+    rst_tiles[[4]], nrow = 4, ncol = 1)
+
+ggarrange(s1, s2, pred_ours, ncol = 3)
+
+# ESA GLC
+colors <- c(color_tb$color[1:4], color_tb$color[8], 
+            color_tb$color[5], color_tb$color[6:7])
+labels <- c(color_tb$type[1:4], color_tb$type[8], 
+            color_tb$type[5], color_tb$type[6:7])
+tiles <- read_sf('data/geoms/tiles_nicfi_north.geojson')
+tiles <- tiles %>% filter(tile %in% id_selected)
+esa_glc <- read_stars('data/landcovers/esaglc_rcl.tif')
+fgs_esa <- lapply(1:nrow(tiles), function(n){
+    tm <- st_crop(esa_glc, tiles %>% slice(n)) %>% 
+        tm_shape() + 
+        tm_raster("esaglc_rcl.tif", 
+                  n = 8, style = 'cat',
+                  labels = labels,
+                  palette = colors) +
+        tm_layout(frame = F,
+                  legend.show = F)
+    tmap_grob(tm)
+})
+fgs_esa <- ggarrange(
+    fgs_esa[[2]], fgs_esa[[3]], fgs_esa[[1]], 
+    fgs_esa[[4]], nrow = 4, ncol = 1)
+
+ggarrange(s1, s2, pred_ours, fgs_esa, ncol = 4)
+
+# FROMGLC
+from_glc <- read_stars('data/landcovers/fromglc_rcl.tif')
+fgs_from <- lapply(1:nrow(tiles), function(n){
+    tm <- st_crop(from_glc, tiles %>% slice(n)) %>% 
+        tm_shape() + 
+        tm_raster("fromglc_rcl.tif", 
+                  n = 8, style = 'cat',
+                  labels = labels,
+                  palette = colors) +
+        tm_layout(frame = F,
+                  legend.show = F)
+    tmap_grob(tm)
+})
+fgs_from <- ggarrange(
+    fgs_from[[2]], fgs_from[[3]], fgs_from[[1]], 
+    fgs_from[[4]], nrow = 4, ncol = 1)
+
+# Get legend
+r_df <- data.frame(x = 1:8, 
+                   y = 1:8,
+                   rst = as.factor(1:8))
+legend_lc <- ggplot() + 
+    geom_raster(
+        data = r_df, 
+        aes(x = x, y = y, 
+            fill = rst)) +
+    scale_fill_manual('',
+                      values = color_tb$color, 
+                      breaks = 1:8,
+                      labels = color_tb$type) +
+    theme_minimal() +
+    theme(legend.position = 'right',
+          axis.title.x = element_blank(),
+          axis.text.x = element_blank(),
+          axis.ticks.x = element_blank(),
+          axis.title.y = element_blank(),
+          axis.text.y = element_blank(),
+          axis.ticks.y = element_blank(),
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(),
+          plot.margin = unit(rep(0, 4),"cm"))+
+    guides(fill = guide_legend(ncol = 8))
+legend_lc <- get_legend(legend_lc)
+
+ids <- ggplot() +  
+    annotate("text",
+             x = 0,
+             y = 1,
+             size = 5,
+             label = "(d)") + 
+    annotate("text",
+             x = 0,
+             y = 2,
+             size = 5,
+             label = "(c)") +
+    annotate("text",
+             x = 0,
+             y = 3,
+             size = 5,
+             label = "(b)") +
+    annotate("text",
+             x = 0,
+             y = 4,
+             size = 5,
+             label = "(a)") +
+    theme_void()
+
+examples <- ggarrange(ggarrange(ids, NA, nrow = 2, heights = c(1, 0.2)), 
+                      s1, s2, pred_ours, fgs_esa, fgs_from, 
+                      ncol = 6, widths = c(0.2, rep(1, 5)),
+          labels = c('', 'NICFI season 1', 'NICFI season 2', 
+                     'Prediction', 'CGLS_LC100m',
+                     'FROM-GLC 2017v1'),
+          hjust = -0.2, vjust = 63,
+          font.label = list(size = 10, color = "black"),
+          legend.grob = legend_lc,
+          legend = 'bottom')
+
+ggsave(here('docs/figures/compare_example.png'),
+       examples,
+       width = 8, height = 6.8, dpi = 300)
 ```

### 2022-05-07 docs/manuscript_figures.Rmd
Update appendix figures

@@
 lc_types <- data.frame(id = 1:7,
-                       type = c('cropland', 'forest', 'grassland',
+                       type = c('Cropland', 'Forest/dense tree', 'Grassland',
+                                'Shrubland', 'Water', 'Built-up',
+                                'Bareland'))
+lc_cvt <- data.frame(type_use = c('Cropland', 'Forest/dense tree', 'Grassland',
+                                'Shrubland', 'Water', 'Built-up',
+                                'Bareland'),
+                     type_record = c('cropland', 'forest', 'grassland',
                                 'shrubland', 'water', 'built-up',
                                 'bareland'))
+# pred_eval <- left_join(pred, lc_types, 
+#                        by = c('test' = 'type')) %>% 
+#     dplyr::select(-test) %>% 
+#     rename(test = id) %>% 
+#     mutate(predict = as.factor(predict),
+#            test = as.factor(test))
+
 pred_eval <- left_join(pred, lc_types, 
-                       by = c('test' = 'type')) %>% 
+                       by = c('predict' = 'id')) %>% 
+    dplyr::select(-predict) %>% 
+    rename(predict = type) %>% 
+    left_join(., lc_cvt, by = c('test' = 'type_record')) %>% 
     dplyr::select(-test) %>% 
-    rename(test = id) %>% 
-    mutate(predict = as.factor(predict),
-           test = as.factor(test))
+    rename(test = type_use) %>% 
+    mutate(predict = factor(predict, 
+                            levels = c('Cropland', 'Forest/dense tree', 
+                                       'Grassland', 'Shrubland', 'Water', 
+                                       'Built-up','Bareland')),
+           test = factor(test,
+                         levels = c('Cropland', 'Forest/dense tree', 
+                                    'Grassland', 'Shrubland', 'Water', 
+                                    'Built-up','Bareland')))
 
@@
                                 'bareland'))
-pred_eval <- left_join(pred_eval, lc_types, by = c('test' = 'type')) %>% 
+# pred_eval <- left_join(pred_eval, lc_types, by = c('test' = 'type')) %>% 
+#     dplyr::select(-test) %>% 
+#     rename(test = id) %>% 
+#     mutate(predict = as.factor(predict),
+#            test = as.factor(test))
+pred_eval <- left_join(pred_eval, lc_types, 
+                       by = c('predict' = 'id')) %>% 
+    dplyr::select(-predict) %>% 
+    rename(predict = type) %>% 
+    left_join(., lc_cvt, by = c('test' = 'type_record')) %>% 
     dplyr::select(-test) %>% 
-    rename(test = id) %>% 
-    mutate(predict = as.factor(predict),
-           test = as.factor(test))
+    rename(test = type_use) %>% 
+    mutate(predict = factor(predict, 
+                            levels = c('Cropland', 'Forest/dense tree', 
+                                       'Grassland', 'Shrubland', 'Water', 
+                                       'Built-up','Bareland')),
+           test = factor(test,
+                         levels = c('Cropland', 'Forest/dense tree', 
+                                    'Grassland', 'Shrubland', 'Water', 
+                                    'Built-up','Bareland')))
+
 cf <- confusionMatrix(data=pred_eval$predict, reference = pred_eval$test)
@@
 load("~/Dropbox/research/hrlcm/data/north/forest_vip.rda")
+# os 2017-12_2018-05, gs 2018-06_2018-11
+names(forest_vip$fit$variable.importance) <- 
+    c('B_S1', 'G_S1', 'R_S1', 'NIR_S1', 
+      'NDVI_S1', 'EVI_S1', 'SAVI_S1', 'ARVI_S1',
+      'B_S2', 'G_S2', 'R_S2', 'NIR_S2',
+      'NDVI_S1', 'EVI_S1', 'SAVI_S1', 'ARVI_S1',
+      'Intercept_VV', 'Slope_VV', 'Coef_sin(t)_VV',
+      'Coef_cos(t)_VV', 'Coef_sin(2t)_VV', 'Coef_cos(2t)_VV',
+      'Intercept_VH', 'Slope_VH', 'Coef_sin(t)_VH',
+      'Coef_cos(t)_VH', 'Coef_sin(2t)_VH', 'Coef_cos(2t)_VH')
 vip_figure <- vip(forest_vip, 
@@
        params_fig,
-       width = 8, height = 4, dpi = 300)
+       width = 6.5, height = 3.5, dpi = 300)
 ```
@@
              estimate = predict)
-cm_figure <- autoplot(cm, type = 'heatmap')
+cm_figure <- autoplot(cm, type = 'heatmap') +
+    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
 ggsave(here('docs/figures/rf_cm_heatmap.png'),
        cm_figure,
-       width = 4, height = 3, dpi = 300)
+       width = 5, height = 3.5, dpi = 300)
 ```
@@
              estimate = predict)
-cm_figure <- autoplot(cm, type = 'heatmap')
+cm_figure <- autoplot(cm, type = 'heatmap') +
+    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
 ggsave(here('docs/figures/unet_cm_heatmap.png'),
        cm_figure,
-       width = 4, height = 3, dpi = 300)
+       width = 5, height = 3.5, dpi = 300)
 ```
@@
 pred <- read_stars(pred_path)
+wetlands <- read_stars(file.path('results/dl/prediction',
+                                 'unet_k15_only_clr_200epc',
+                                 'wetland_add.tif'))
+pred[wetlands == 1] <- NA
 conf_fig <- tm_shape(pred) +

### 2022-07-15 docs/manuscript_figures.Rmd
Fix a bug in rf_tuning figure

@@
       'B_S2', 'G_S2', 'R_S2', 'NIR_S2',
-      'NDVI_S1', 'EVI_S1', 'SAVI_S1', 'ARVI_S1',
+      'NDVI_S2', 'EVI_S2', 'SAVI_S2', 'ARVI_S2',
       'Intercept_VV', 'Slope_VV', 'Coef_sin(t)_VV',
@@
       'Coef_cos(t)_VH', 'Coef_sin(2t)_VH', 'Coef_cos(2t)_VH')
-vip_figure <- vip(forest_vip, 
+vip_figure <- vip(vi(forest_vip), 
     num_features = forest_vip$fit$num.independent.variables,
@@
 params_fig <- ggarrange(vip_figure, tune_figure,
-                        ncol = 2, widths = c(1, 1.5))
+                        ncol = 2, widths = c(1, 1.2))
 ggsave(here('docs/figures/rf_tuning.png'),

### 2022-08-21 docs/manuscript_figures.Rmd
Modify a few figures

@@
                            '#fdbf6f'),
-                  `Land cover type` = c("Cropland", 'Forest', "Grassland", 
-                                        'Shrubland',  "Water", "Built-up",
-                                        'Bareland'),
+                  `Land cover type` = c("Cropland", 'Forest/dense tree', 
+                                        "Grassland", 'Shrubland',  "Water", 
+                                        "Built-up", 'Bareland'),
                   ids = as.factor(1:7))
@@
 
+# Replace Forest with Forest/dense tree
+pts_nicfi_all <- pts_nicfi_all %>% 
+    mutate(`Land cover type` = ifelse(
+        `Land cover type` == "Forest",
+        "Forest/dense tree", as.character(`Land cover type`)))
+
 # Figure
@@
 
+# Replace Forest with Forest/dense tree
+pts_ts <- pts_ts %>% 
+    mutate(`Land cover type` = ifelse(
+        `Land cover type` == "Forest",
+        "Forest/dense tree", `Land cover type`))
+pts_fit <- pts_fit %>% 
+    mutate(`Land cover type` = ifelse(
+        `Land cover type` == "Forest",
+        "Forest/dense tree", `Land cover type`))
+
 # Make figure
@@
 pts_fit <- merge(pts_fit, cols_lc[, 2:3])
+
 ts_epl <- ggplot() + 
@@
 
+```{r}
+library(tidyverse)
+library(gridExtra)
+
+# Define function
+get_curves <- function(experiment_name,
+                       step = 59,
+                       path = here('results/scalar/compare_score')){
+    # Get file names
+    fns <- list.files(path, 
+                      pattern = experiment_name,
+                      full.names = T)
+    fns <- fns[str_detect(fns, 'Validate')]
+
+    # Process each csv
+    scalars <- lapply(fns, function(fn){
+        scalar <- read.csv(fn, stringsAsFactors = F) %>% 
+            mutate(Step = Step / step) %>% # step of each epoch
+            dplyr::select(-Wall.time)
+    })
+    names(scalars) <- gsub(
+        '.csv', "", 
+        str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))
+
+    scalars
+}
+
+# Clean scalar csvs
+curves_no_weight <- get_curves(
+    'unet_no_weight',
+    path = here('results/scalar/compare_score'))
+curves_k05 <- get_curves(
+    'unet_k05_only',
+    path = here('results/scalar/compare_score'))
+curves_k15 <- get_curves(
+    'unet_k15_only',
+    path = here('results/scalar/compare_score'))
+curves_k30 <- get_curves(
+    'unet_k3_only',
+    path = here('results/scalar/compare_score'))
+
+types <- c('AA', 'mIoU', 'Cropland', 'Forest', 
+           'Grassland', 'Shrubland', 'Water', 
+           'Built-up', 'Bareland')
+content <- do.call(rbind, lapply(types, function(type){
+    if (type == 'Built-up') {
+        item <- 'Urban'
+    } else if (type == 'mIoU'){
+        item <- 'IoU'
+    } else {item <- type}
+    list(curves_no_weight[[item]],
+         curves_k05[[item]],
+         curves_k15[[item]],
+         curves_k30[[item]]) %>% 
+        reduce(left_join, by = "Step") %>% 
+        `colnames<-`(c("Epoch", '0', '0.5', '1.5', '3.0')) %>% 
+        mutate(Item = type) %>% 
+        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
+                     names_to = 'k of logistic function', 
+                     values_to = 'Value')
+})) %>% mutate(Item = factor(Item, levels = types),
+               `k of logistic function` = factor(
+                   `k of logistic function`, 
+                   levels = c('0', '0.5', '1.5', '3.0')))
+
+# Calculate mean and sd of last 10 epochs
+content_k <- content %>% 
+    filter(Epoch >= 26) %>% 
+    filter(Item == 'AA') %>% 
+    group_by(Item, `k of logistic function`) %>% 
+    summarise(Mean = mean(Value), 
+              sd = sd(Value))
+
+# Clean scalar csvs
+curves_k15_nohard <- get_curves(
+    'unet_k15_only',
+    path = here('results/scalar/compare_score'))
+curves_k15_h11 <- get_curves(
+    'unet_k15_hard11',
+    path = here('results/scalar/compare_score'))
+curves_k15_h12 <- get_curves(
+    'unet_k15_hard12',
+    path = here('results/scalar/compare_score'))
+curves_k15_h14 <- get_curves(
+    'unet_k15_hard14',
+    path = here('results/scalar/compare_score'))
+
+types <- c('AA', 'mIoU', 'Cropland', 'Forest', 
+           'Grassland', 'Shrubland', 'Water', 
+           'Built-up', 'Bareland')
+content <- do.call(rbind, lapply(types, function(type){
+    if (type == 'Built-up') {
+        item <- 'Urban'
+    } else if (type == 'mIoU'){
+        item <- 'IoU'
+    } else {item <- type}
+    list(curves_k15_nohard[[item]],
+         curves_k15_h11[[item]],
+         curves_k15_h12[[item]],
+         curves_k15_h14[[item]]) %>% 
+        reduce(left_join, by = "Step") %>% 
+        `colnames<-`(c("Epoch", '1', '1.1', '1.2', '1.4')) %>% 
+        mutate(Item = type) %>% 
+        pivot_longer(cols = setdiff(names(.), c("Epoch", 'Item')),
+                     names_to = 'Weight scale', 
+                     values_to = 'Value')
+})) %>% mutate(Item = factor(Item, levels = types),
+               `Weight scale` = factor(
+                   `Weight scale`, 
+                   levels = c('1', '1.1', '1.2', '1.4')))
+
+# Calculate mean and sd of last 10 epochs
+content_weight <- content %>% 
+    filter(Epoch >= 26) %>% 
+    filter(Item  == 'AA') %>% 
+    group_by(Item, `Weight scale`) %>% 
+    summarise(Mean = mean(Value), 
+              sd = sd(Value))
+
+# Get final plot
+curves_corr <- ggplot(
+    content_k, 
+    aes(x = `k of logistic function`, y = Mean)) + 
+    geom_point() +
+    geom_errorbar(aes(ymin = Mean - sd, ymax = Mean + sd), width=.2,
+                  position = position_dodge(0.05)) +
+    labs(y = 'Average accuracy (AA)', 
+         x = expression(paste(k, ' of logistic function'))) +
+    theme_bw()
+curves_diff <- ggplot(
+    content_weight, 
+    aes(x = `Weight scale`, y = Mean)) + 
+    geom_point() +
+    geom_errorbar(aes(ymin = Mean - sd, ymax = Mean + sd), width=.2,
+                  position = position_dodge(0.05)) +
+    labs(y = 'Average accuracy (AA)', x = expression(s[max])) +
+    theme_bw()
+
+params_cost <- ggarrange(curves_corr, curves_diff,
+                         ncol = 2)
+ggsave(here('docs/figures/sa_loss_params_v2.png'),
+       params_cost,
+       width = 6, height = 2, dpi = 300)
+
+```
+
 ### Sampling

### 2022-09-30 docs/manuscript_figures.Rmd
reviewer1_figure2

@@
 
-# Read example images
-# tile 1227-1002, 
-# this tile has a few different land cover types and obvious characteristics
+# Combine the Figure S2 and S3 into a single figure
+## The structure is the satellite images are on the top,
+## the signature curves are on the bottom.
+############### PREPROCESS THE DATASET ##################
+# Use tile 1227-1002, 
+# this tile has a few different land cover types 
+# and obvious characteristics
 # so it could be a good example tile.
+########################################################
 tile_id <- '1227-1002'
+######################## NICFI ########################
 fnames_nicfi <- list.files(here('data/plts_nicfi'),
@@
 
-# NICFI
 # Transform points
@@
 
-# Define colors
-cols_lc <- tibble(cols = c('#ff7f00', '#074702', '#b2df8a',
-                           '#33a02c', '#3347f9', '#5a6057',
-                           '#fdbf6f'),
-                  `Land cover type` = c("Cropland", 'Forest/dense tree', 
-                                        "Grassland", 'Shrubland',  "Water", 
-                                        "Built-up", 'Bareland'),
-                  ids = as.factor(1:7))
-
+# Spectral signature of examples
+# Extract values
+pts_nicfi_s1 <- raster::extract(nicfi_s1, pts_nicfi) %>% 
+    t() %>% data.frame() %>% 
+    `names<-`(pts_nicfi$type) %>% 
+    `rownames<-`(1:nrow(.)) %>% 
+    mutate(`Band name` = c('Blue', 'Green', 'Red', 'NIR'),
+           Band = 1:4) %>% 
+    pivot_longer(cols = names(.)[1:(ncol(.) - 2)], 
+                 names_to = 'Land cover type',
+                 values_to = 'Reflectance') %>% 
+    mutate(`Land cover type` = as.factor(`Land cover type`),
+           Season = 'NICFI (season 1)')
+pts_nicfi_s2 <- raster::extract(nicfi_s2, pts_nicfi) %>% 
+    t() %>% data.frame() %>% 
+    `names<-`(pts_nicfi$type) %>% 
+    `rownames<-`(1:nrow(.)) %>% 
+    mutate(`Band name` = c('Blue', 'Green', 'Red', 'NIR'),
+           Band = 1:4) %>% 
+    pivot_longer(cols = names(.)[1:(ncol(.) - 2)], 
+                 names_to = 'Land cover type',
+                 values_to = 'Reflectance') %>% 
+    mutate(`Land cover type` = as.factor(`Land cover type`),
+           Season = 'NICFI (season 2)')
+pts_nicfi_all <- rbind(pts_nicfi_s1, pts_nicfi_s2)
+rm(pts_nicfi_s1, pts_nicfi_s2)
+
+# Replace Forest with Forest/dense tree just for the label
+pts_nicfi_all <- pts_nicfi_all %>% 
+    mutate(`Land cover type` = ifelse(
+        `Land cover type` == "Forest",
+        "Forest/dense tree", as.character(`Land cover type`)))
+
+##### Sentinel-1 harmonic coefficient regression ######
+fnames_s1 <- list.files(here('data/s1_harmonic'),
+                        pattern = tile_id,
+                        full.names = T)
+vv_coefs <- stack(fnames_s1[str_detect(fnames_s1, 'VV')])
+vh_coefs <- stack(fnames_s1[str_detect(fnames_s1, 'VH')])
+
+# Time series and harmonic fitting of examples
+# out = cos((2 * pi * n0 * t) / freq - (n % 2) * pi / 2)
+# n_0 = {0,1,1,2,2}
+# n = {0,1,2,3,4}
+# freq = 365
+# Band1: intercept
+# Band2: slope
+# Band3: sin(x)
+# Band4: cos(x)
+# Band5: sin(2x)
+# Band6: cos(2x)
+
+# Real time series
+## Images
+vv_ts <- stack(
+    list.files(here('data/s1_timeseries_example/temp_ard_1227-1002'),
+               pattern = 'VV',
+               full.names = T)) 
+vh_ts <- stack(
+    list.files(here('data/s1_timeseries_example/temp_ard_1227-1002'),
+               pattern = 'VH',
+               full.names = T))
+
+# DOY
+doy <- c(0,   9,  12,  21,  33,  45,  48,  57,  69,  81,  93, 105, 117,
+         129, 141, 153, 165, 177, 189, 201, 213, 225, 237, 249, 261, 273,
+         285, 288, 293, 297, 300, 305, 309, 312, 317, 321, 324, 329, 333,
+         336, 345, 348, 357, 360)
+
+# Extract values
+pts_vv_ts <- raster::extract(vv_ts, pts_example) %>% 
+    t() %>% data.frame() %>% 
+    `names<-`(pts_example$type) %>% 
+    mutate(date = rownames(.)) %>% 
+    `rownames<-`(1:nrow(.)) %>% 
+    mutate(date = str_extract(date, '[0-9]{8}')) %>% 
+    arrange(date) %>% 
+    mutate(DOY = doy, polarization = 'Sentinel-1 (VV)',
+           type = 'Real value')
+
+pts_vh_ts <- raster::extract(vh_ts, pts_example) %>% 
+    t() %>% data.frame() %>% 
+    `names<-`(pts_example$type) %>% 
+    mutate(date = rownames(.)) %>% 
+    `rownames<-`(1:nrow(.)) %>% 
+    mutate(date = str_extract(date, '[0-9]{8}')) %>% 
+    arrange(date) %>% 
+    mutate(DOY = doy, polarization = 'Sentinel-1 (VH)',
+           type = 'Real value')
+
+pts_ts <- rbind(pts_vv_ts, pts_vh_ts) %>% 
+    dplyr::select(-date) %>% 
+    pivot_longer(names(.)[1:7], 
+                 names_to = "Land cover type", 
+                 values_to = "dB")
+rm(pts_vv_ts, pts_vh_ts)
+
+# Harmonic coefficients
+pts_vv <- raster::extract(vv_coefs, pts_example) %>% 
+    t() %>% data.frame() %>% 
+    `names<-`(pts_example$type) %>% 
+    `rownames<-`(1:nrow(.)) %>% 
+    mutate(`Band name` = c('Intersept', 'Slope', 
+                           'Sin(x)', 'Cos(x)', 
+                           'Sin(2x)', "Cos(2x)"), Band = 1:6)
+
+pts_vv_fit <- do.call(cbind, lapply(names(pts_vv)[1:7], function(typ){
+    coefs <- pts_vv %>% pull(typ)
+    data.frame(val = coefs[1] + coefs[2] * doy +
+                   coefs[3] * sin(2 * pi * doy /365) + 
+                   coefs[4] * cos(2 * pi * doy /365) + 
+                   coefs[5] * sin(4 * pi * doy /365) + 
+                   coefs[6] * cos(4 * pi * doy /365))
+})) %>% `names<-`(names(pts_vv)[1:7]) %>% 
+    mutate(DOY = doy) %>% 
+    mutate(polarization = 'Sentinel-1 (VV)',
+           type = 'Harmoic regression')
+
+pts_vh <- raster::extract(vh_coefs, pts_example) %>% 
+    t() %>% data.frame() %>% 
+    `names<-`(pts_example$type) %>% 
+    `rownames<-`(1:nrow(.)) %>% 
+    mutate(`Band name` = c('Intersept', 'Slope', 
+                           'Sin(x)', 'Cos(x)', 
+                           'Sin(2x)', "Cos(2x)"), Band = 1:6)
+
+pts_vh_fit <- do.call(cbind, lapply(names(pts_vh)[1:7], function(typ){
+    coefs <- pts_vh %>% pull(typ)
+    data.frame(val = coefs[1] + coefs[2] * doy +
+                   coefs[3] * sin(2 * pi * doy /365) + 
+                   coefs[4] * cos(2 * pi * doy /365) + 
+                   coefs[5] * sin(4 * pi * doy /365) + 
+                   coefs[6] * cos(4 * pi * doy /365))
+})) %>% `names<-`(names(pts_vh)[1:7]) %>% 
+    mutate(DOY = doy) %>% 
+    mutate(polarization = 'Sentinel-1 (VH)',
+           type = 'Harmoic regression')
+
+pts_fit <- rbind(pts_vv_fit, pts_vh_fit) %>% 
+    pivot_longer(names(.)[1:7], 
+                 names_to = "Land cover type", 
+                 values_to = "dB")
+rm(pts_vv_fit, pts_vh_fit)
+
+# Replace Forest with Forest/dense tree
+pts_ts <- pts_ts %>% 
+    mutate(`Land cover type` = ifelse(
+        `Land cover type` == "Forest",
+        "Forest/dense tree", `Land cover type`))
+pts_fit <- pts_fit %>% 
+    mutate(`Land cover type` = ifelse(
+        `Land cover type` == "Forest",
+        "Forest/dense tree", `Land cover type`))
+
+#################### Make the figure ##################
+# Satellite images
 # Image of season 1
@@
                        labels = cols_lc$`Land cover type`) +
-    theme_minimal() +
+    ggtitle("NICFI (season 1)") +
+    theme_void() +
     theme(axis.title.x = element_blank(),
@@
           axis.ticks.y = element_blank(),
-          plot.margin = unit(rep(0, 4),"cm"))
+          plot.title = element_text(size = 10, hjust = 0.5),
+          plot.margin = unit(rep(-0.1, 4),"cm"))
 
@@
                        labels = cols_lc$`Land cover type`) +
-    theme_minimal() +
+    ggtitle("NICFI (season 2)") +
+    theme_void() +
     theme(axis.title.x = element_blank(),
@@
           axis.ticks.y = element_blank(),
-          plot.margin = unit(rep(0, 4),"cm"))
-
-# Spectral signature of examples
-# Extract values
-pts_nicfi_s1 <- raster::extract(nicfi_s1, pts_nicfi) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_nicfi$type) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(`Band name` = c('Blue', 'Green', 'Red', 'NIR'),
-           Band = 1:4) %>% 
-    pivot_longer(cols = names(.)[1:(ncol(.) - 2)], 
-                 names_to = 'Land cover type',
-                 values_to = 'Reflectance') %>% 
-    mutate(`Land cover type` = as.factor(`Land cover type`),
-           Season = 'Season 1')
-pts_nicfi_s2 <- raster::extract(nicfi_s2, pts_nicfi) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_nicfi$type) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(`Band name` = c('Blue', 'Green', 'Red', 'NIR'),
-           Band = 1:4) %>% 
-    pivot_longer(cols = names(.)[1:(ncol(.) - 2)], 
-                 names_to = 'Land cover type',
-                 values_to = 'Reflectance') %>% 
-    mutate(`Land cover type` = as.factor(`Land cover type`),
-           Season = 'Season 2')
-pts_nicfi_all <- rbind(pts_nicfi_s1, pts_nicfi_s2)
-rm(pts_nicfi_s1, pts_nicfi_s2)
-
-# Replace Forest with Forest/dense tree
-pts_nicfi_all <- pts_nicfi_all %>% 
-    mutate(`Land cover type` = ifelse(
-        `Land cover type` == "Forest",
-        "Forest/dense tree", as.character(`Land cover type`)))
-
-# Figure
-pts_nicfi_all <- merge(pts_nicfi_all, cols_lc[, 2:3])
-ref_epl <- ggplot(pts_nicfi_all,
-                  aes(x = Band, y = Reflectance / 1000,
-                      color = ids)) +
-    geom_point() + geom_line(show.legend = 'line') +
-    ylab(bquote('Reflectance'~(10^3))) + 
-    scale_color_manual("Land cover type",
-                       values = cols_lc$cols, 
-                       breaks = cols_lc$ids,
-                       labels = cols_lc$`Land cover type`) +
-    scale_x_discrete(limit = factor(1:4),
-                     labels = unique(pts_nicfi_all$`Band name`)) +
-    theme_bw() +
-    theme(axis.title.x = element_blank()) +
-    facet_wrap(~ Season, nrow = 2, 
-               scales = "free_y",
-               strip.position = "top")
-
-nicfi_fg <- ggarrange(
-    ggarrange(s1_fg, s2_fg,
-              labels = c('Season 1', 'Season 2'),
-              font.label = list(size = 12),
-              vjust = 3,
-              ncol = 2), 
-    ref_epl, ncol = 2)
-ggsave(here('docs/figures/nicfi_image.png'),
-       nicfi_fg,
-       width = 8, height = 2.7, dpi = 300)
-
-# Sentinel-1 harmonic coefficient regression
-fnames_s1 <- list.files(here('data/s1_harmonic'),
-                        pattern = tile_id,
-                        full.names = T)
-vv_coefs <- stack(fnames_s1[str_detect(fnames_s1, 'VV')])
-vh_coefs <- stack(fnames_s1[str_detect(fnames_s1, 'VH')])
+          plot.title = element_text(size = 10, hjust = 0.5),
+          plot.margin = unit(rep(-0.1, 4),"cm"))
 
@@
                        labels = cols_lc$`Land cover type`) +
-    theme_minimal() +
+    ggtitle("Sentinel-1 (VV)") +
+    theme_void() +
     theme(axis.title.x = element_blank(),
@@
                        labels = cols_lc$`Land cover type`) +
-    theme_minimal() +
+    ggtitle("Sentinel-1 (VH)") +
+    theme_void() +
     theme(axis.title.x = element_blank(),
@@
           axis.ticks.y = element_blank(),
-          plot.margin = unit(rep(0, 4),"cm"))
-
-# Time series and harmonic fitting of examples
-# out = cos((2 * pi * n0 * t) / freq - (n % 2) * pi / 2)
-# n_0 = {0,1,1,2,2}
-# n = {0,1,2,3,4}
-# freq = 365
-# Band1: intercept
-# Band2: slope
-# Band3: sin(x)
-# Band4: cos(x)
-# Band5: sin(2x)
-# Band6: cos(2x)
-
-# Real time series
-## Images
-vv_ts <- stack(
-    list.files(here('data/s1_timeseries_example/temp_ard_1227-1002'),
-               pattern = 'VV',
-               full.names = T)) 
-vh_ts <- stack(
-    list.files(here('data/s1_timeseries_example/temp_ard_1227-1002'),
-               pattern = 'VH',
-               full.names = T))
-
-# DOY
-doy <- c(0,   9,  12,  21,  33,  45,  48,  57,  69,  81,  93, 105, 117,
-       129, 141, 153, 165, 177, 189, 201, 213, 225, 237, 249, 261, 273,
-       285, 288, 293, 297, 300, 305, 309, 312, 317, 321, 324, 329, 333,
-       336, 345, 348, 357, 360)
-
-# Extract values
-pts_vv_ts <- raster::extract(vv_ts, pts_example) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_example$type) %>% 
-    mutate(date = rownames(.)) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(date = str_extract(date, '[0-9]{8}')) %>% 
-    arrange(date) %>% 
-    mutate(DOY = doy, polarization = 'VV',
-           type = 'Real value')
-
-pts_vh_ts <- raster::extract(vh_ts, pts_example) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_example$type) %>% 
-    mutate(date = rownames(.)) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(date = str_extract(date, '[0-9]{8}')) %>% 
-    arrange(date) %>% 
-    mutate(DOY = doy, polarization = 'VH',
-           type = 'Real value')
-
-pts_ts <- rbind(pts_vv_ts, pts_vh_ts) %>% 
-    dplyr::select(-date) %>% 
-    pivot_longer(names(.)[1:7], 
-                 names_to = "Land cover type", 
-                 values_to = "dB")
-rm(pts_vv_ts, pts_vh_ts)
-
-# Harmonic coefficients
-pts_vv <- raster::extract(vv_coefs, pts_example) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_example$type) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(`Band name` = c('Intersept', 'Slope', 
-                           'Sin(x)', 'Cos(x)', 
-                           'Sin(2x)', "Cos(2x)"), Band = 1:6)
-
-pts_vv_fit <- do.call(cbind, lapply(names(pts_vv)[1:7], function(typ){
-    coefs <- pts_vv %>% pull(typ)
-    data.frame(val = coefs[1] + coefs[2] * doy +
-    coefs[3] * sin(2 * pi * doy /365) + 
-    coefs[4] * cos(2 * pi * doy /365) + 
-    coefs[5] * sin(4 * pi * doy /365) + 
-    coefs[6] * cos(4 * pi * doy /365))
-})) %>% `names<-`(names(pts_vv)[1:7]) %>% 
-    mutate(DOY = doy) %>% 
-    mutate(polarization = 'VV',
-           type = 'Harmoic regression')
-
-pts_vh <- raster::extract(vh_coefs, pts_example) %>% 
-    t() %>% data.frame() %>% 
-    `names<-`(pts_example$type) %>% 
-    `rownames<-`(1:nrow(.)) %>% 
-    mutate(`Band name` = c('Intersept', 'Slope', 
-                           'Sin(x)', 'Cos(x)', 
-                           'Sin(2x)', "Cos(2x)"), Band = 1:6)
-
-pts_vh_fit <- do.call(cbind, lapply(names(pts_vh)[1:7], function(typ){
-    coefs <- pts_vh %>% pull(typ)
-    data.frame(val = coefs[1] + coefs[2] * doy +
-    coefs[3] * sin(2 * pi * doy /365) + 
-    coefs[4] * cos(2 * pi * doy /365) + 
-    coefs[5] * sin(4 * pi * doy /365) + 
-    coefs[6] * cos(4 * pi * doy /365))
-})) %>% `names<-`(names(pts_vh)[1:7]) %>% 
-    mutate(DOY = doy) %>% 
-    mutate(polarization = 'VH',
-           type = 'Harmoic regression')
-
-pts_fit <- rbind(pts_vv_fit, pts_vh_fit) %>% 
-    pivot_longer(names(.)[1:7], 
-                 names_to = "Land cover type", 
-                 values_to = "dB")
-rm(pts_vv_fit, pts_vh_fit)
-
-# Replace Forest with Forest/dense tree
-pts_ts <- pts_ts %>% 
-    mutate(`Land cover type` = ifelse(
-        `Land cover type` == "Forest",
-        "Forest/dense tree", `Land cover type`))
-pts_fit <- pts_fit %>% 
-    mutate(`Land cover type` = ifelse(
-        `Land cover type` == "Forest",
-        "Forest/dense tree", `Land cover type`))
-
-# Make figure
+          plot.title = element_text(size = 10, hjust = 0.5),
+          plot.margin = unit(rep(-0.1, 4),"cm"))
+
+images <- ggarrange(
+    s1_fg, s2_fg, vh_fg, vv_fg,
+    ncol = 4)
+
+## Signatures
+# Define colors
+cols_lc <- tibble(
+    cols = c('#ff7f00', '#074702', '#b2df8a',
+             '#33a02c', '#3347f9', '#5a6057',
+             '#fdbf6f'),
+    `Land cover type` = c("Cropland", 'Forest/dense tree', 
+                          "Grassland", 'Shrubland',  "Water", 
+                          "Built-up", 'Bareland'),
+    ids = as.factor(1:7))
+
+# Burn the color table in
+pts_nicfi_all <- merge(pts_nicfi_all, cols_lc[, 2:3])
 pts_ts <- merge(pts_ts, cols_lc[, 2:3])
 pts_fit <- merge(pts_fit, cols_lc[, 2:3])
+
+ref_epl <- ggplot(pts_nicfi_all,
+                  aes(x = Band, y = Reflectance / 1000,
+                      color = ids)) +
+    geom_point() + geom_line(show.legend = 'line') +
+    ylab(bquote('Reflectance'~(10^3))) + 
+    xlab("Band") +
+    scale_color_manual("Land cover type",
+                       values = cols_lc$cols, 
+                       breaks = cols_lc$ids,
+                       labels = cols_lc$`Land cover type`) +
+    scale_x_discrete(limit = factor(1:4),
+                     labels = unique(pts_nicfi_all$`Band name`)) +
+    theme_bw() +
+    facet_wrap(~ Season, nrow = 2, 
+               scales = "free_y",
+               strip.position = "top") +
+    theme(text = element_text(size = 11))
 
@@
                        labels = cols_lc$`Land cover type`) +
-    theme_bw()
-
-s1_fg <- ggarrange(
-    ggarrange(vv_fg, vh_fg,
-              labels = c('VV', 'VH'),
-              font.label = list(size = 12),
-              vjust = 3,
-              nrow = 2), 
-    ts_epl, ncol = 2)
-
-ggsave(here('docs/figures/s1_image.png'),
-       s1_fg,
-       width = 8, height = 2.7, dpi = 300)
-
-# Version 2
-ts_epl <- ggplot() + 
-    geom_point(data = pts_ts, 
-               aes(x = DOY, y = `dB`, 
-                   color = factor(ids)),
-               size = 0.6) +
-    geom_line(data = pts_fit,
-              aes(x = DOY, y = `dB`, 
-                  color = factor(ids))) +
-    facet_wrap(~polarization, 
-               scales = 'free_y', nrow = 2,
-               strip.position = "top") +
-    scale_color_manual("Land cover type",
-                       values = cols_lc$cols, 
-                       breaks = cols_lc$ids,
-                       labels = cols_lc$`Land cover type`) +
-    theme_bw() +
-    theme(text=element_text(size=8),
-          axis.text=element_text(size=8),
-          axis.title=element_text(size=8), 
-          plot.title=element_text(size=8), 
-          legend.text=element_text(size=8), 
-          legend.title=element_text(size=8))
-s1_fg <- ggarrange(
-    ggarrange(NA, vh_fg, NA, vv_fg, NA, nrow = 5,
-              heights = c(0.05, 1, 0.05, 1, 0.25),
-              labels = c(NA, 'VH', NA, 'VV', NA),
-              font.label = list(size = 8),
-              hjust = 0.05), 
-    ts_epl, ncol = 2, widths = c(1, 2.2))
-ggsave(here('docs/figures/s1_image_v2.png'),
-       s1_fg,
-       width = 6, height = 3.5, dpi = 300)
+    theme_bw() + theme(text = element_text(size = 11))
+
+epl <- ggarrange(
+    ref_epl, ts_epl,
+    common.legend = TRUE, 
+    legend = "bottom",
+    ncol = 2)
+
+fg <- ggarrange(images, epl, nrow = 2, heights = c(1, 2.5))
+ggsave(here('docs/figures/satellite_images.tiff'),
+       fg, bg = "white",
+       width = 6, height = 6, dpi = 600)
 ```

### 2022-09-30 docs/manuscript_figures.Rmd
Figure 1 for revision

@@
 # Get the surrounding countries
-countries <- ne_countries(type = 'countries', scale = 'large',
+sf_use_s2(FALSE)
+countries <- ne_countries(
+    type = 'countries', scale = 'large',
     returnclass = 'sf') %>% 
-    st_intersection(., st_bbox(tz_bry) %>% 
+    st_intersection(
+        ., st_bbox(tz_bry) %>% 
             st_as_sfc() %>% 
@@
                       ymin = -2.3, ymax = -0.5) +
-    annotation_scale(location = 'br', text_cex = 1) +
-    annotation_north_arrow(which_north = "true", location = 'tl') +
-    theme_minimal() + 
-    theme(axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          legend.text = element_text(size = 12),
-          plot.margin = unit(rep(0, 4),"cm"))
-
-ggsave(here('docs/figures/study_area.png'),
-       main_fg,
-       width = 10, height = 5.7, dpi = 600)
-main_fg
+    annotation_scale(location = 'br', text_cex = 0.8) +
+    annotation_north_arrow(which_north = "true", location = 'tl',
+                           height = unit(1.0, "cm"), width = unit(1.0, "cm")) +
+    theme_void() + 
+    theme(legend.position = "bottom",
+          text = element_text(size = 13),
+          plot.margin = unit(c(0.3, rep(0, 3)),"cm")) +
+    guides(fill = guide_legend(nrow = 4, title.position = "top"),
+           color = guide_legend(nrow = 2))
+
+ggsave(here('docs/figures/figure1_study_area.tiff'),
+       main_fg, bg = "white", units = "px", 
+       width = 1772, height = 1772)
 ```
@@
     theme_void() +
-    theme(axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          plot.title = element_text(size = 10, hjust = 0.5),
+    theme(plot.title = element_text(size = 10, hjust = 0.5),
           plot.margin = unit(rep(-0.1, 4),"cm"))
@@
     geom_sf(color = 'blue', fill = NA, lwd = 0.3) + 
-    geom_sf_text(aes(label = index), size = 2.5) +
-    theme_minimal() +
+    geom_sf_text(aes(label = index), size = 3) +
+    theme_void() +
     theme(legend.position = 'bottom',
-          axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(),
           plot.title = element_text(hjust = -0.15, vjust = -6),
@@
     id = 1:7,
-    type = c("Cropland", "Forest", 
+    type = c("Cropland", "Forest/Dense tree", 
              "Grassland", "Shrubland", 
@@
                 color = 'blue', fill = NA,
-                lty = 'dotted', lwd = 0.4) +
-        theme_minimal() +
+                lwd = 0.4) +
+        theme_void() +
         theme(legend.position = 'none',
-              axis.title.x = element_blank(),
-              axis.text.x = element_blank(),
-              axis.ticks.x = element_blank(),
-              axis.title.y = element_blank(),
-              axis.text.y = element_blank(),
-              axis.ticks.y = element_blank(),
-              panel.grid.major = element_blank(), 
-              panel.grid.minor = element_blank(),
-              plot.margin = unit(rep(0, 4),"cm"))
+              plot.margin = unit(rep(-0.1, 4),"cm"))
 }
@@
                       breaks = 1:7,
-                      labels = c("Cropland", 'Forest', "Grassland", 
+                      labels = c("Cropland", 'Forest/Dense tree', "Grassland", 
                                  'Shrubland',  "Water", "Built-up",
@@
     theme(legend.position = 'right',
-          axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(),
           plot.margin = unit(rep(0, 4),"cm"))+
@@
 legend_lc <- get_legend(legend_lc)
-sub_tiling_fg <- ggarrange(NULL, sub_tiling_fg, legend_lc, NULL,
-                           nrow = 4, heights = c(0.3, 2, 1, 0.3))
+sub_tiling_fg <- ggarrange(NULL, legend_lc, NULL, sub_tiling_fg, NULL,
+                           nrow = 5, heights = c(0.2, 1, 0.2, 2, 0.1))
 
@@
                     labels = sub_tiles$index,
-                    hjust = -2.5)
+                    font.label = list(size = 12, color = "black", 
+                                   face = "plain"),
+                    hjust = -3, vjust = 0.1)
 guess_fg <- ggarrange(plotlist = plots_guess, ncol = 4)
 refine_fg <- ggarrange(plotlist = plots_refine, ncol = 4)
-fgs <- ggarrange(esb_fg, guess_fg, refine_fg, nrow = 3,
-                 labels = c('A', 'B', 'C'),
-                 hjust = 0.4, vjust = 6,
-                 font.label = list(face = "plain"))
+
+id_selected <- '1240-995'
+# Read tiles
+nicfi_tiles <- read_sf(
+    here('data/geoms/tiles_nicfi_north.geojson'))
+
+# Sub-tiling
+indices <- matrix(1:64, 8, 8)
+indices <- indices[, ncol(indices):1]
+sub_tiling <- nicfi_tiles %>% 
+    filter(tile == id_selected) %>% 
+    st_make_grid(n = c(8, 8)) %>% 
+    st_sf() %>% 
+    mutate(index = as.vector(indices))
+trains_inside <- sub_tiling %>% 
+    filter(index %in% (read.csv(
+        here('results/north/dl_catalog_train.csv'),
+        stringsAsFactors = F) %>% 
+            filter(tile == id_selected) %>% 
+            pull(index))) %>% 
+    mutate(Usage = 'Train')
+valids_inside <- sub_tiling %>% 
+    filter(index %in% (read.csv(
+        here('results/north/dl_catalog_valid.csv'),
+        stringsAsFactors = F) %>% 
+            filter(tile == id_selected) %>% 
+            pull(index))) %>% 
+    mutate(Usage = 'Validate')
+# Labels of each sub-tile
+sub_tiles <- rbind(trains_inside, valids_inside) %>% 
+    arrange(index); rm(trains_inside, valids_inside)
+
+# Add satellite images for reference
+# Satellite images
+images <- lapply(sub_tiles$index, function(id){
+    prefix <- glue('/Volumes/elephant/pred_stack/{id_selected}')
+    rst <- stack(here(glue('{prefix}.tif')))
+    bry <- sub_tiles %>% filter(index == id) %>% 
+        st_transform(crs = crs(rst))
+    crop(rst, bry)
+}); names(images) <- sub_tiles$index
+
+# Plot
+plot_img <- function(rst, bry){
+    # plot
+    ggRGB(rst, r = 1, g = 2, b = 3, 
+          scale = max(values(rst)),
+          stretch = 'hist') +
+        geom_sf(data = bry, 
+                color = 'blue', fill = NA,
+                lwd = 0.4) +
+        theme_void() +
+        theme(plot.title = element_text(size = 10, hjust = 0.5),
+              plot.margin = unit(rep(-0.1, 4),"cm"))
+}
+s1_plots <- lapply(1:length(images), function(n) {
+    nm <- names(images)[n]
+    bry <- sub_tiles %>% filter(index == nm) %>% 
+        st_transform(crs = crs(images[[n]]))
+    rst <- subset(images[[n]], c(4, 3, 2)) # 1, 2, 3
+    plot_img(rst, bry)
+})
+s1_fg <- ggarrange(plotlist = s1_plots, ncol = 4)
+
+s2_plots <- lapply(1:length(images), function(n) {
+    nm <- names(images)[n]
+    bry <- sub_tiles %>% filter(index == nm) %>% 
+        st_transform(crs = crs(images[[n]]))
+    rst <- subset(images[[n]], c(12, 11, 10)) # 9, 10, 11
+    plot_img(rst, bry)
+})
+s2_fg <- ggarrange(plotlist = s2_plots, ncol = 4)
+
+fgs <- ggarrange(esb_fg, guess_fg, refine_fg, s1_fg, s2_fg, nrow = 5,
+                 labels = c('A', 'B', 'C', "S1", "S2"),
+                 font.label = list(size = 12, color = "black", 
+                                   face = "plain"),
+                 hjust = 0.9, vjust = 6)
 labels_fg <- ggarrange(NULL, fgs, sub_tiling_fg, 
-                       ncol = 3, widths = c(0.1, 2, 1))
-
-ggsave(here('docs/figures/labels.png'),
-       labels_fg,
-       width = 8, height = 4, dpi = 300)
+                       ncol = 3, widths = c(0.1, 2, 1)) +
+    theme(plot.margin = margin(0.3, 0 ,0, 0, "cm"))
+
+ggsave(here('docs/figures/labels.tiff'),
+       labels_fg, bg = "white",
+       width = 8, height = 6.5, dpi = 600)
 ```

### 2022-09-30 docs/manuscript_figures.Rmd
Figure 2 for revision"

@@
 
+# Figure 1, combination art
+# Single column figure, 1772 * 1772 at 500 dpi
 ggsave(here('docs/figures/figure1_study_area.tiff'),
@@
 #################### Make the figure ##################
+# Define colors
+cols_lc <- tibble(
+    cols = c('#ff7f00', '#074702', '#b2df8a',
+             '#33a02c', '#3347f9', '#5a6057',
+             '#fdbf6f'),
+    `Land cover type` = c("Cropland", 'Forest/dense tree', 
+                          "Grassland", 'Shrubland',  "Water", 
+                          "Built-up", 'Bareland'),
+    ids = as.factor(1:7))
 # Satellite images
@@
 ## Signatures
-# Define colors
-cols_lc <- tibble(
-    cols = c('#ff7f00', '#074702', '#b2df8a',
-             '#33a02c', '#3347f9', '#5a6057',
-             '#fdbf6f'),
-    `Land cover type` = c("Cropland", 'Forest/dense tree', 
-                          "Grassland", 'Shrubland',  "Water", 
-                          "Built-up", 'Bareland'),
-    ids = as.factor(1:7))
-
 # Burn the color table in
@@
 fg <- ggarrange(images, epl, nrow = 2, heights = c(1, 2.5))
+
 ggsave(here('docs/figures/satellite_images.tiff'),
@@
        width = 6, height = 6, dpi = 600)
+
+# Figure 2, combination art
+# Double column figure, 3740 * 3740 at 500 dpi
+ggsave(here('docs/figures/figure2_satellite_images.tiff'),
+       main_fg, bg = "white", units = "px", 
+       width = 3740, height = 3740)
 ```

### 2022-09-30 docs/manuscript_figures.Rmd
Figure 4 for revision

@@
     theme_void() +
-    theme(plot.title = element_text(size = 10, hjust = 0.5),
-          plot.margin = unit(rep(-0.1, 4),"cm"))
+    theme(plot.title = element_text(size = 12, hjust = 0.5),
+          plot.margin = unit(c(-0.1, rep(-0.5, 3)),"cm"))
 
@@
     theme_void() +
-    theme(axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          plot.title = element_text(size = 10, hjust = 0.5),
-          plot.margin = unit(rep(-0.1, 4),"cm"))
+    theme(plot.title = element_text(size = 12, hjust = 0.5),
+          plot.margin = unit(c(-0.1, rep(-0.5, 3)),"cm"))
 
@@
                       color = ids)) +
-    geom_point() + geom_line(show.legend = 'line') +
+    geom_point(size = 1.6) + geom_line(show.legend = 'line', size = 0.8) +
     ylab(bquote('Reflectance'~(10^3))) + 
@@
                strip.position = "top") +
-    theme(text = element_text(size = 11))
+    theme(text = element_text(size = 14),
+          legend.text = element_text(size = 13))
 
@@
                    color = factor(ids)),
-               size = 0.6) +
+               size = 1.6) +
     geom_line(data = pts_fit,
               aes(x = DOY, y = `dB`, 
-                  color = factor(ids))) +
+                  color = factor(ids)),
+              size = 0.8) +
     facet_wrap(~polarization, 
@@
                        labels = cols_lc$`Land cover type`) +
-    theme_bw() + theme(text = element_text(size = 11))
+    theme_bw() + theme(text = element_text(size = 14),
+          legend.text = element_text(size = 13))
 
@@
 
-ggsave(here('docs/figures/satellite_images.tiff'),
-       fg, bg = "white", 
-       width = 6, height = 6, dpi = 600)
-
 # Figure 2, combination art
-# Double column figure, 3740 * 3740 at 500 dpi
+# 1.5 column figure, 2756 * 2500 at 500 dpi
 ggsave(here('docs/figures/figure2_satellite_images.tiff'),
-       main_fg, bg = "white", units = "px", 
-       width = 3740, height = 3740)
+       fg, bg = "white", units = "px", 
+       width = 2756, height = 2500)
 ```
@@
     geom_sf(color = 'blue', fill = NA, lwd = 0.3) + 
-    geom_sf_text(aes(label = index), size = 3) +
+    geom_sf_text(aes(label = index), size = 5) +
     theme_void() +
     theme(legend.position = 'bottom',
+          text = element_text(size = 17),
           plot.title = element_text(hjust = -0.15, vjust = -6),
@@
     theme(legend.position = 'right',
+          text = element_text(size = 17),
           plot.margin = unit(rep(0, 4),"cm"))+
@@
                     labels = sub_tiles$index,
-                    font.label = list(size = 12, color = "black", 
+                    font.label = list(size = 16, color = "black", 
                                    face = "plain"),
-                    hjust = -3, vjust = 0.1)
+                    hjust = -3, vjust = 0.25)
 guess_fg <- ggarrange(plotlist = plots_guess, ncol = 4)
 refine_fg <- ggarrange(plotlist = plots_refine, ncol = 4)
-
-id_selected <- '1240-995'
-# Read tiles
-nicfi_tiles <- read_sf(
-    here('data/geoms/tiles_nicfi_north.geojson'))
-
-# Sub-tiling
-indices <- matrix(1:64, 8, 8)
-indices <- indices[, ncol(indices):1]
-sub_tiling <- nicfi_tiles %>% 
-    filter(tile == id_selected) %>% 
-    st_make_grid(n = c(8, 8)) %>% 
-    st_sf() %>% 
-    mutate(index = as.vector(indices))
-trains_inside <- sub_tiling %>% 
-    filter(index %in% (read.csv(
-        here('results/north/dl_catalog_train.csv'),
-        stringsAsFactors = F) %>% 
-            filter(tile == id_selected) %>% 
-            pull(index))) %>% 
-    mutate(Usage = 'Train')
-valids_inside <- sub_tiling %>% 
-    filter(index %in% (read.csv(
-        here('results/north/dl_catalog_valid.csv'),
-        stringsAsFactors = F) %>% 
-            filter(tile == id_selected) %>% 
-            pull(index))) %>% 
-    mutate(Usage = 'Validate')
-# Labels of each sub-tile
-sub_tiles <- rbind(trains_inside, valids_inside) %>% 
-    arrange(index); rm(trains_inside, valids_inside)
 
@@
         theme_void() +
-        theme(plot.title = element_text(size = 10, hjust = 0.5),
-              plot.margin = unit(rep(-0.1, 4),"cm"))
+        theme(plot.margin = unit(rep(-0.1, 4),"cm"))
 }
@@
                  labels = c('A', 'B', 'C', "S1", "S2"),
-                 font.label = list(size = 12, color = "black", 
+                 font.label = list(size = 16, color = "black", 
                                    face = "plain"),
@@
 
-ggsave(here('docs/figures/labels.tiff'),
-       labels_fg, bg = "white",
-       width = 8, height = 6.5, dpi = 600)
+# Figure 4, combination art
+# 2 column figure, 3150 * 2560 at 500 dpi
+ggsave(here('docs/figures/figure4_labels_example.tiff'),
+       labels_fg, bg = "white", units = "px", 
+       width = 3150, height = 2560)
 ```

### 2022-09-30 docs/manuscript_figures.Rmd
Figure5 for revision

@@
   ylab('Count') +
-  theme_bw()
-
-ggsave(here('docs/figures/humancheck_quality.png'),
-       quality_fig,
-       width = 4, height = 4, dpi = 300)
+  theme_bw() +
+    theme(text = element_text(size = 16))
+
+# Figure 5, combination art
+# Single figure (3.2 in in width), 1600 * 1600 at 500 dpi
+ggsave(here('docs/figures/figure5_humancheck_quality.tiff'),
+       quality_fig, bg = "white", units = "px", 
+       width = 1600, height = 1600)
 ```

### 2022-09-30 docs/manuscript_figures.Rmd
Figure 6 for revision

@@
 
-ggsave(here('docs/figures/curves_k15_only_final_mod_v2.png'),
-       curves,
-       width = 7, height = 5, dpi = 300)
+# Figure 6, line art
+# Double figure (7 in in width), 7000 * 5000 at 1000 dpi
+ggsave(here('docs/figures/figure6_training_curves.tiff'),
+       curves, bg = "white", width = 7, height = 5, dpi = 1000)
 ```

### 2022-09-30 docs/manuscript_figures.Rmd
Figure 7 for revision

@@
 names(pred) <- 'landcover'
-# pred <- rast(pred_path)
-# set.cats(pred, value = color_tb$type, index = color_tb$id)
-# pred <- st_as_stars(pred)
 
@@
 tiles <- read_sf('data/geoms/tiles_nicfi_north.geojson')
-id_selected <- c('1226-1012', '1227-1005', '1209-997', '1219-1017',
-                 '1234-992', '1211-1008', '1236-1007','1220-995')
+id_selected <- c('1211-1008', '1209-997', '1221-1012', '1234-992')
 tiles <- tiles %>% filter(tile %in% id_selected) %>% 
     st_transform(crs = crs(rast(pred_path))) %>% 
-    mutate(id = 1:nrow(.))
-rst_tiles <- lapply(1:nrow(tiles), function(n){
-    tm <- st_crop(pred, tiles %>% slice(n)) %>% 
-        tm_shape() + 
-        tm_raster("landcover", 
-              n = 8, style = 'cat',
-              labels = color_tb$type,
-              palette = color_tb$color) +
-        tm_layout(frame = F,
-                  legend.show = F,
-                  title.position = c(0, 0.9),
-                  title = tiles %>% slice(n) %>% pull(id))
-     tmap_grob(tm)
-})
-plot_left <- ggarrange(
-    rst_tiles[[1]], rst_tiles[[2]], rst_tiles[[3]], 
-    rst_tiles[[4]], ncol = 1, nrow = 4)
-plot_right <- ggarrange(
-    rst_tiles[[5]], rst_tiles[[6]], rst_tiles[[7]],
-    rst_tiles[[8]], ncol = 1, nrow = 4)
-
-tmap_mode("plot")
-pred_final <- tm_shape(pred) +
-    tm_raster("landcover", 
-              title = "Land cover types",
-              n = 8, style = 'cat',
-              labels = color_tb$type,
-              palette = color_tb$color) +
-    tm_shape(tiles) +
-    tm_borders("black", lwd = 1.2) +
-    tm_text("id", col = 'black', fontface = "bold", size = 0.8) +
-    tm_layout(frame = F,
-              legend.show = F,
-              outer.margins = c(0.02, 0.01, 0, 0.01),
-              inner.margins = 0)
-pred_final <- tmap_grob(pred_final)
-
-# Get legend
-r_df <- data.frame(x = 1:8, 
-                   y = 1:8,
-                   rst = as.factor(1:8))
-legend_lc <- ggplot() + 
-    geom_raster(
-        data = r_df, 
-        aes(x = x, y = y, 
-            fill = rst)) +
-    scale_fill_manual('Land cover',
-                      values = color_tb$color, 
-                      breaks = 1:8,
-                      labels = color_tb$type) +
-    theme_minimal() +
-    theme(legend.position = 'right',
-          axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(),
-          plot.margin = unit(rep(0, 4),"cm"))+
-    guides(fill = guide_legend(ncol = 8))
-legend_lc <- get_legend(legend_lc)
-
-tbl_theme <- gridExtra::ttheme_default(
-    core = list(fg_params=list(cex = 0.6),
-                bg_params = list(fill = 'gray95')),
-    colhead = list(fg_params=list(cex = 0.7)),
-    rowhead = list(fg_params=list(cex = 0.7)))
-tbl_conf <- tableGrob(mean_std, rows = NULL, theme = tbl_theme)
-legend_lc <- ggarrange(NA, tbl_conf, NA, legend_lc, NA,
-                       ncol = 5, widths = c(1, 2, 1, 2, 1))
-
-pred_final_plt <- ggarrange(pred_final, legend_lc, NA,
-                        nrow = 3, heights = c(5, 1, 0.6))
-pred_example <- ggarrange(plot_left, pred_final_plt, plot_right,
-          ncol = 3, widths = c(1, 3, 1))
-ggsave(here('docs/figures/pred_example.png'),
-       pred_example,
-       width = 7, height = 6, dpi = 300)
+    mutate(id = letters[1:4])
 ```
@@
 # Confusion matrix
+load("docs/figures/test_conf.rda")
 cf_orig <- data.frame(cf$table) %>% 
@@
 
-# 3D pie
-cols <- color_tb$color
-lab <- paste(round(adjust_stats_area$area, 1), "km2")
-plotrix::pie3D(adjust_stats_area$proportion,
-      col = cols,
-      labels = lab,
-      explode = 0.15,
-      labelcex = 1,
-      radius = 1.1,
-      border = "white",
-      theta = 1.1)
-
 # Version 2 of final map
@@
 pred_final <- tm_shape(pred) +
-    tm_raster("landcover_north_withwl.tif", 
+    tm_raster("landcover", 
               #title = "Land cover types",
@@
               palette = color_tb$color) +
+    tm_shape(tiles) +
+    tm_borders("black", lwd = 1.2) +
+    tm_text("id", col = 'black', fontface = "bold", 
+            size = 1.3, xmod = 1.1,ymod = 0.1) +
     tm_layout(frame = F,
               legend.show = FALSE,
-              outer.margins = c(0.02, 0.01, 0, 0.01),
+              outer.margins = rep(0, 4),
               inner.margins = 0)
@@
             fill = rst)) +
+    geom_polygon(data = r_df, fill = NA, color = "black", size = 1,
+            aes(x = x, y = y, lty = 'solid')) +
     scale_fill_manual('',
@@
                       labels = color_tb$type) +
-    theme_minimal() +
+    scale_linetype_identity(name = '',
+                            breaks = c('solid'),
+                            labels = c('Examples in Figure 7'),
+                            guide = 'legend') +
+    theme_void() +
     theme(legend.position = 'right',
-          axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(),
+          text = element_text(size = 14),
+          legend.text = element_text(size = 14),
           plot.margin = unit(rep(-1, 4),"cm"))+
@@
 
-# Get pie chart for class frequency
-cls_freq <- rast(pred_path)
-cls_freq <- freq(cls_freq) %>% 
-    data.frame() %>% 
-    mutate(landcover = value,
-           ratio = count / sum(.$count)) %>% 
-    select(landcover, ratio)
-save(cls_freq, file = 'docs/figures/cls_freq.rda')
-
-cls_freq <- cls_freq %>% arrange(landcover)
-cols <- color_tb$color
-lab <- paste0(round(cls_freq$ratio/sum(cls_freq$ratio) * 100, 1), "%")
+# # Get pie chart for class frequency
+# cls_freq <- rast(pred_path)
+# cls_freq <- freq(cls_freq) %>% 
+#     data.frame() %>% 
+#     mutate(landcover = value,
+#            ratio = count / sum(.$count)) %>% 
+#     select(landcover, ratio)
+# save(cls_freq, file = 'docs/figures/cls_freq.rda')
+# 
+# 
+# cls_freq <- cls_freq %>% arrange(landcover)
+# cols <- color_tb$color
+# lab <- paste0(round(cls_freq$ratio/sum(cls_freq$ratio) * 100, 1), "%")
+# 
+# # Barplot
+# cls_freq <- cls_freq %>% 
+#     mutate(landcover = factor(landcover, 
+#                               levels = cls_freq %>% 
+#                                arrange(desc(ratio)) %>% 
+#                                pull(landcover)),
+#         label_ypos = 0.9 * ratio)
+# barplot <- ggplot(data=cls_freq, aes(x=landcover, y=ratio)) +
+#     geom_bar(stat="identity", aes(fill=as.factor(landcover))) +
+#     geom_text(aes(y=label_ypos, label=lab), angle = 90,
+#               color="black", size = 4)+
+#     scale_fill_manual(values = cols[as.integer(levels(cls_freq$landcover))]) +
+#     theme_void() +
+#     theme(legend.position = "none",
+#           plot.margin = unit(c(-0.1, -0.1, 0.1, -0.1),"cm"))
 
 # Barplot
+cls_freq <- data.frame(area = unlist(class_area) / whole_area * 100,
+                       err = c(adjust_class_err / whole_area * 100, 0),
+                       landcover = color_tb$id) %>% 
+    mutate(err_adjust_prop = glue(
+        paste0('{format(round(area, digits = 1), nsmall = 1)}',
+               '\u00B1{format(round(err, digits = 1), nsmall = 1)}',
+               '%'))) %>% 
+    arrange(-area) %>% 
+    mutate(label_ypos = c(0.75, 0.75, 0.52, 2.9, 3, 3.8, 5.2, 12)* area)
 cls_freq <- cls_freq %>% 
@@
                               levels = cls_freq %>% 
-                               arrange(desc(ratio)) %>% 
-                               pull(landcover)),
-        label_ypos = 0.9 * ratio)
-barplot <- ggplot(data=cls_freq, aes(x=landcover, y=ratio)) +
+                                  arrange(desc(area)) %>% 
+                                  pull(landcover)))
+barplot <- ggplot(data=cls_freq, aes(x=landcover, y = area)) +
     geom_bar(stat="identity", aes(fill=as.factor(landcover))) +
-    geom_text(aes(y=label_ypos, label=lab), angle = 90,
-              color="black", size=3)+
+    geom_errorbar(aes(ymin = area - err, ymax = area + err), 
+                  width = .4, color = "black", size = 0.6,
+                  position = position_dodge(.9)) +
+    geom_text(aes(y=label_ypos, label=err_adjust_prop), angle = 90,
+              color="black", size = 4)+
     scale_fill_manual(values = cols[as.integer(levels(cls_freq$landcover))]) +
     theme_void() +
-    theme(legend.position = "none")
+    theme(legend.position = "none",
+          plot.margin = unit(c(-0.1, -0.1, 0.1, -0.1),"cm"))
 
@@
 tbl_theme <- gridExtra::ttheme_default(
-    core = list(fg_params=list(cex = 0.7, hjust = 0, x = 0.1,
+    core = list(fg_params=list(cex = 1, hjust = 0, x = 0.1,
                                parse = TRUE),
                 bg_params = list(fill = 'gray95')),
-    colhead = list(fg_params=list(cex = 0.8)),
-    rowhead = list(fg_params=list(cex = 0.8)))
+    colhead = list(fg_params=list(cex = 1)),
+    rowhead = list(fg_params=list(cex = 1)))
 tbl_conf <- tableGrob(adjust_stats_area, rows = NULL, theme = tbl_theme)
 
-pred_final_plt <- ggarrange(f1,
+pred_final_plt <- ggarrange(
+    f1,
     ggarrange(NA, tbl_conf,
@@
               labels = c(NA, 'B', 'C', NA),
-                                      hjust = c(2, 4, 2, 2),
-                                      heights = c(0.2, 1, 1, 0.3)), 
+              font.label = list(face = "plain", size = 16),
+              hjust = c(2, 6, 2, 2),
+              heights = c(0.1, 1, 1, 0.1)), 
     NA,
     labels = c('A', NA, NA),
+    font.label = list(face = "plain", size = 16),
     vjust = 5, hjust = -1,
     ncol = 3, widths = c(6, 2, 0.5))
-ggsave(here('docs/figures/final_map.png'),
-       pred_final_plt,
-       width = 8, height = 5.5, dpi = 300)
+
+# Figure 7, combination art
+# 1.5 column figure , 2756 * 1700 at 500 dpi
+ggsave(here('docs/figures/figure7_final_map.tiff'),
+       pred_final_plt, bg = "white", 
+       width = 2756, height = 1700, 
+       units = "px")
 ```
@@
 
-fnames_s1 <- file.path("data/plts_nicfi",
+fnames_s1 <- file.path(
+    "data/plts_nicfi",
     sprintf('planet_medres_normalized_analytic_2017-12_2018-05_mosaic_%s.tif', 
                                id_selected))
-fnames_s2 <- file.path("data/plts_nicfi",
+fnames_s2 <- file.path(
+    "data/plts_nicfi",
     sprintf('planet_medres_normalized_analytic_2018-06_2018-11_mosaic_%s.tif', 
@@
     tmap_grob(tm)
-    # stack(fname) %>% subset(1:4) %>% 
-    #     ggRGB(r = 1, g = 2, b = 3, 
-    #           scale = max(values(.)[, 1:3]), 
-    #           stretch = 'lin') +
-    #     theme_minimal() +
-    #     theme(axis.title.x = element_blank(),
-    #           axis.text.x = element_blank(),
-    #           axis.ticks.x = element_blank(),
-    #           axis.title.y = element_blank(),
-    #           axis.text.y = element_blank(),
-    #           axis.ticks.y = element_blank(),
-    #           plot.margin = unit(rep(0, 4),"cm"))
 })
@@
     tmap_grob(tm)
-    # stack(fname) %>% subset(1:4) %>% 
-    #     ggRGB(r = 1, g = 2, b = 3, 
-    #           scale = max(values(.)[, 1:3]), 
-    #           stretch = 'hist') +
-    #     theme_minimal() +
-    #     theme(axis.title.x = element_blank(),
-    #           axis.text.x = element_blank(),
-    #           axis.ticks.x = element_blank(),
-    #           axis.title.y = element_blank(),
-    #           axis.text.y = element_blank(),
-    #           axis.ticks.y = element_blank(),
-    #           plot.margin = unit(rep(0, 4),"cm"))
 })

### 2022-10-01 docs/manuscript_figures.Rmd
Figure 8 for revision

@@
 
-ggarrange(s1, s2, pred_ours, ncol = 3)
-
 # ESA GLC
@@
 
-ggarrange(s1, s2, pred_ours, fgs_esa, ncol = 4)
-
 # FROMGLC
@@
                       labels = color_tb$type) +
-    theme_minimal() +
+    theme_void() +
     theme(legend.position = 'right',
-          axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(),
-          plot.margin = unit(rep(0, 4),"cm"))+
+          plot.margin = unit(rep(0, 4),"cm"),
+          text = element_text(size = 14),
+          legend.text = element_text(size = 14))+
     guides(fill = guide_legend(ncol = 8))
@@
              label = "(a)") +
-    theme_void()
+    theme_void() +
+    theme(text = element_text(size = 14))
 
@@
                      'FROM-GLC 2017v1'),
-          hjust = -0.2, vjust = 63,
-          font.label = list(size = 10, color = "black"),
+          hjust = -0.1, vjust = 59,
+          font.label = list(size = 14, color = "black", face = "plain"),
           legend.grob = legend_lc,
@@
 
-ggsave(here('docs/figures/compare_example.png'),
-       examples,
-       width = 8, height = 6.8, dpi = 300)
+# Figure 8, combination art
+# 2 column figure (6.2 in) , 3150 * 2600 at 500 dpi
+ggsave(here('docs/figures/figure8_compare_examples.tiff'),
+       examples, bg = "white", 
+       width = 3150, height = 2600, 
+       units = "px")
 ```

### 2022-10-10 docs/manuscript_figures.Rmd
Update figures in manuscript for revision

@@
     geom_sf(fill = 'lightblue', color = 'grey') +
-    geom_sf_text(aes(label = geounit), size = 4) +
+    geom_sf_text(aes(label = geounit), size = 5) +
     geom_sf(data = countries, fill = NA, color = 'grey') +
@@
     theme_bw() +
-    theme(axis.title.x = element_blank(),
-          axis.text.x = element_blank(),
-          axis.ticks.x = element_blank(),
-          axis.title.y = element_blank(),
-          axis.text.y = element_blank(),
-          axis.ticks.y = element_blank(),
-          plot.margin = unit(rep(0, 4), "cm")))
+    theme(axis.title = element_blank(),
+          axis.text = element_blank(),
+          axis.ticks = element_blank(),
+          panel.grid.major = element_blank(),
+          panel.background = element_rect(fill = "gray100",
+                                          color = "black"),
+          plot.margin = unit(rep(0, 4), "cm"),
+          plot.background = element_rect(fill = "white")))
 
@@
     annotation_custom(grob = overview, 
-                      xmin = 36.5, xmax = 38.5,
-                      ymin = -2.3, ymax = -0.5) +
+                      xmin = 36.64, xmax = 38.54,
+                      ymin = -2.3, ymax = -0.62) +
     annotation_scale(location = 'br', text_cex = 0.8) +
@@
                            height = unit(1.0, "cm"), width = unit(1.0, "cm")) +
-    theme_void() + 
+    theme_linedraw() + 
     theme(legend.position = "bottom",
-          text = element_text(size = 13),
+          text = element_text(size = 18),
+          legend.spacing = unit(-1, "cm"),
           plot.margin = unit(c(0.3, rep(0, 3)),"cm")) +
-    guides(fill = guide_legend(nrow = 4, title.position = "top"),
-           color = guide_legend(nrow = 2))
+    guides(fill = guide_legend(ncol = 1, title.position = "top", order = 1),
+           color = guide_legend(nrow = 2, order = 2),
+           linetype = guide_legend(nrow = 2, order = 2))
 
@@
        main_fg, bg = "white", units = "px", 
-       width = 1772, height = 1772)
+       width = 1772, height = 2200)
 ```
@@
 
-pred_eval <- left_join(pred, lc_types, 
+pred_eval_rf <- left_join(pred, lc_types, 
                        by = c('predict' = 'id')) %>% 
@@
 
-cf <- confusionMatrix(data = pred_eval$predict, 
-                      reference = pred_eval$test)
-save(cf, file = here('docs/figures/rf_test_conf.rda'))
-
-acc_test <- cf$byClass
-write.csv(acc_test, here('docs/figures/rf_test_acc.csv'),
+cf_rf <- confusionMatrix(data = pred_eval_rf$predict, 
+                      reference = pred_eval_rf$test)
+
+save(pred_eval_rf, file = here('docs/figures/rf_test_eval.rda'))
+save(cf_rf, file = here('docs/figures/rf_test_conf.rda'))
+
+acc_test_rf <- cf_rf$byClass
+write.csv(acc_test_rf, here('docs/figures/rf_test_acc.csv'),
           row.names = F)
@@
 sample_test <- vect(sample_test %>% st_transform(crs = crs(pred)))
-pred_eval <- terra::extract(pred, sample_test, list = T)
-pred_eval <- do.call(rbind, lapply(1:length(pred_eval), function(n){
-    rst_vals <- pred_eval[[n]][[1]]
-    data.frame(predict = rst_vals,
-               test = sample_test[n, ]$landcover)
+pred_eval <- terra::extract(pred, sample_test)
+
+sample_test <- read_sf(here('data/north/plys_holdout_check.geojson')) %>% 
+    st_drop_geometry() %>% pull(landcover)
+pred_eval <- do.call(rbind, lapply(1:nrow(pred_eval), function(n){
+    rst_vals <- pred_eval[n, ]
+    data.frame(predict = rst_vals$landcover_north,
+               test = sample_test[rst_vals$ID])
 }))
 
-lc_types <- data.frame(id = 1:7,
-                       type = c('cropland', 'forest', 'grassland',
-                                'shrubland', 'water', 'built-up',
-                                'bareland'))
-# pred_eval <- left_join(pred_eval, lc_types, by = c('test' = 'type')) %>% 
-#     dplyr::select(-test) %>% 
-#     rename(test = id) %>% 
-#     mutate(predict = as.factor(predict),
-#            test = as.factor(test))
 pred_eval <- left_join(pred_eval, lc_types, 
@@
 
-cf <- confusionMatrix(data=pred_eval$predict, reference = pred_eval$test)
+cf <- confusionMatrix(data = pred_eval$predict, reference = pred_eval$test)
+
+save(pred_eval, file = here('docs/figures/test_eval.rda'))
 save(cf, file = here('docs/figures/test_conf.rda'))
@@
 ```{r}
+# Area adjust and projection adjust area
+cls_area <- terra::zonal(cell_area, pred_area, fun = "sum", na.rm = TRUE)
+cls_ratio <- cls_area %>% 
+    mutate(ratio = area / sum(area))
+
 # Class proportion, class 1 - 7
-cls_prop <- cls_freq %>% 
+cls_prop <-  data.frame(cls_area) %>% 
+    rename(landcover = landcover_north, area_orig = area) %>% 
     slice(1:7) %>% 
-    mutate(proportion = ratio / sum(.$ratio)) %>% 
+    mutate(proportion = area_orig / sum(.$area_orig)) %>% 
     select(landcover, proportion)
@@
 # Calculate the area of the whole image
-pred_area <- rast(pred_path)
-cell_num <- freq(pred_area)
-whole_area <- sum(cell_num[1:7, 3]) * 
-    (res(pred_area)[1] / 1000) * 
-    (res(pred_area)[2] / 1000)
+whole_area <- sum(cls_area$area[1:7]) / 1000^2
 class_area <- cf_ratio["Pj", ] * whole_area
-class_area[, '8'] <- cell_num[[8, 3]] * 
-    (res(pred_area)[1] / 1000) * 
-    (res(pred_area)[2] / 1000)
+class_area[, '8'] <- cls_area$area[8] / 1000^2
 
@@
 
+whole_area_add_wtl <- sum(cls_area$area) / 1000^2
 adjust_stats_area <- data.frame(
@@
     confidence_interval = c(adjust_class_err, NA),
-    proportion = cls_freq[, 2])
-save(adjust_stats_area, file = 'docs/figures/adjust_stats_area.rda')
+    proportion = unlist(class_area) / whole_area_add_wtl,
+    prop_interval = c(adjust_class_err / whole_area_add_wtl, NA))
+
+save(adjust_stats_area, file = 'docs/figures/adjust_modified_stats_area.rda')
 
@@
                             breaks = c('solid'),
-                            labels = c('Examples in Figure 7'),
+                            labels = c('Examples in Figure 10'),
                             guide = 'legend') +
@@
 
-# # Get pie chart for class frequency
-# cls_freq <- rast(pred_path)
-# cls_freq <- freq(cls_freq) %>% 
-#     data.frame() %>% 
-#     mutate(landcover = value,
-#            ratio = count / sum(.$count)) %>% 
-#     select(landcover, ratio)
-# save(cls_freq, file = 'docs/figures/cls_freq.rda')
-# 
-# 
-# cls_freq <- cls_freq %>% arrange(landcover)
-# cols <- color_tb$color
-# lab <- paste0(round(cls_freq$ratio/sum(cls_freq$ratio) * 100, 1), "%")
-# 
-# # Barplot
-# cls_freq <- cls_freq %>% 
-#     mutate(landcover = factor(landcover, 
-#                               levels = cls_freq %>% 
-#                                arrange(desc(ratio)) %>% 
-#                                pull(landcover)),
-#         label_ypos = 0.9 * ratio)
-# barplot <- ggplot(data=cls_freq, aes(x=landcover, y=ratio)) +
-#     geom_bar(stat="identity", aes(fill=as.factor(landcover))) +
-#     geom_text(aes(y=label_ypos, label=lab), angle = 90,
-#               color="black", size = 4)+
-#     scale_fill_manual(values = cols[as.integer(levels(cls_freq$landcover))]) +
-#     theme_void() +
-#     theme(legend.position = "none",
-#           plot.margin = unit(c(-0.1, -0.1, 0.1, -0.1),"cm"))
-
 # Barplot
-cls_freq <- data.frame(area = unlist(class_area) / whole_area * 100,
-                       err = c(adjust_class_err / whole_area * 100, 0),
+cls_freq <- data.frame(area = adjust_stats_area$proportion * 100,
+                       err = c(adjust_stats_area$prop_interval[1:7] * 100, 0),
                        landcover = color_tb$id) %>% 
@@
     arrange(-area) %>% 
-    mutate(label_ypos = c(0.75, 0.75, 0.52, 2.9, 3, 3.8, 5.2, 12)* area)
+    mutate(label_ypos = c(0.75, 0.75, 0.52, 2.9, 3, 3.8, 5.2, 9)* area)
+cls_freq[8, 4] <- '0.6%'
+cls_freq <- cls_freq %>% arrange(landcover)
+cols <- color_tb$color
+
 cls_freq <- cls_freq %>% 
@@
     geom_text(aes(y=label_ypos, label=err_adjust_prop), angle = 90,
-              color="black", size = 4)+
+              color="black", size = 4) +
     scale_fill_manual(values = cols[as.integer(levels(cls_freq$landcover))]) +
@@
     select(Landcover, `Error-adjusted area`)
-adjust_stats_area[8, 2] <- '1435.7 km\u00B2*'
+adjust_stats_area[8, 2] <- '1420 km\u00B2*'
 
@@
 
-# Figure 7, combination art
+# Figure 9, combination art
 # 1.5 column figure , 2756 * 1700 at 500 dpi
-ggsave(here('docs/figures/figure7_final_map.tiff'),
+ggsave(here('docs/figures/figure9_final_map.tiff'),
        pred_final_plt, bg = "white", 
@@
 
-# Figure 8, combination art
+# Figure 10, combination art
 # 2 column figure (6.2 in) , 3150 * 2600 at 500 dpi
-ggsave(here('docs/figures/figure8_compare_examples.tiff'),
+ggsave(here('docs/figures/figure10_compare_examples.tiff'),
        examples, bg = "white", 
@@
 ```{r}
-cm <- pred_eval %>% 
+cm_rf <- pred_eval_rf %>% 
     conf_mat(truth = test, 
              estimate = predict)
-cm_figure <- autoplot(cm, type = 'heatmap') +
-    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
-ggsave(here('docs/figures/rf_cm_heatmap.png'),
-       cm_figure,
-       width = 5, height = 3.5, dpi = 300)
+cm_rf_fg <- autoplot(cm_rf, type = 'heatmap', label_size = 5) +
+    theme(axis.text.x = element_text(
+        angle = 90, vjust = 0.5, hjust = 1,
+        color = "black"),
+        axis.text = element_text(color = "black"),
+        text = element_text(size = 20))
+
+# Figure 7, combination art
+# Single column figure, 1772 * 1772 at 500 dpi
+ggsave(here('docs/figures/sup_rf_cm_heatmap.tiff'),
+       cm_rf_fg, bg = "white", units = "px", 
+       width = 1772, height = 1772)
 ```
@@
              estimate = predict)
-cm_figure <- autoplot(cm, type = 'heatmap') +
-    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
-ggsave(here('docs/figures/unet_cm_heatmap.png'),
-       cm_figure,
-       width = 5, height = 3.5, dpi = 300)
+cm_figure <- autoplot(cm, type = 'heatmap', label_size = 5) +
+    theme(axis.text.x = element_text(
+        angle = 90, vjust = 0.5, hjust = 1,
+        color = "black"),
+        axis.text = element_text(color = "black"),
+        text = element_text(size = 20))
+
+# Figure 7, combination art
+# Single column figure, 1772 * 1772 at 500 dpi
+ggsave(here('docs/figures/figure7_net_cm_heatmap.tiff'),
+       cm_figure, bg = "white", units = "px", 
+       width = 1772, height = 1772)
 ```
@@
 pred[wetlands == 1] <- NA
+
 conf_fig <- tm_shape(pred) +
     tm_raster("landcover_confidence_north_withwl.tif", 
-              title = "Confidence",
+              title = "Confidence\n(18 - 99)",
               style = 'cont',
@@
                                  contrast=c(.25, 1)))) +
-    tm_layout(frame = F,
-              legend.position = c(0.8, 0.7))
-tmap_save(conf_fig, 
-          here('docs/figures/conf_figure.png'), 
-          width = 4, height = 4, units = 'in',
-          dpi = 300)
+    tm_layout(frame = FALSE,
+              legend.text.size = 1.1,
+              legend.title.size = 1.3,
+              legend.title.fontface = "bold",
+              legend.height = 1,
+              legend.position = c("right", "top"),
+              outer.margins = c(0, 0, 0, 0.01),
+              inner.margins = rep(0, 4))
+conf_fig <- tmap_grob(conf_fig)
+conf_fig <- ggarrange(conf_fig)
+
+# Figure 6, confidence map
+# single column figure , 2756 * 1700 at 500 dpi
+ggsave(here('docs/figures/figure8_conf_map.tiff'),
+       conf_fig, bg = "white", 
+       width = 1772, height = 1772,
+       units = "px")
 ```
+
+### Figures added for manuscript revision
+
+```{r}
+# Figures for reviewer1
+## Harmonic fitting
+t <- seq(0, 365, 1)
+y <- sin(2 * pi * t / 365)
+z <- cos(2 * pi * t / 365)
+one_cycle <- data.frame(t = t, sin = y, cos = z)
+
+y <- sin(4 * pi * t / 365)
+z <- cos(4 * pi * t / 365)
+two_cycle <- data.frame(t = t, sin = y, cos = z)
+
+plot(t, z, type = "l", xlab = "time")
+
+g1 <- ggplot(one_cycle) +
+    geom_line(aes(x = t, y = sin), color = "black") +
+    geom_line(aes(x = t, y = cos), color = "blue") +
+    theme_bw() + xlab("Time") + ylab("Value") + ggtitle("One cycle (k = 1)")
+
+g2 <- ggplot(two_cycle) +
+    geom_line(aes(x = t, y = sin), color = "black") +
+    geom_line(aes(x = t, y = cos), color = "blue") +
+    theme_bw() + xlab("Time") + ylab("Value") + ggtitle("Two cycles (k = 2)")
+g <- ggarrange(g1, g2, ncol = 2)
+
+ggsave("/Users/pinot/downloads/harmonics.png", g,
+       width = 8, height = 3)
+
+## LC products dis-selected after pre-assessment
+# Read the boundary
+tiles <- vect(here('data/geoms/tiles_nicfi_north.geojson'))
+
+# ESRI 10m land use/land cover
+fnames <- list.files("/Volumes/elephant/landcovers/ESRI_LC_2018",
+                     full.names = TRUE)
+fnames <- fnames[grep("37M|36M", fnames)]
+esri_lc <- do.call(merge, lapply(fnames, function(fname) {
+    rast(fname) %>% project("epsg:4326")
+})) %>% crop(tiles) %>% mask(tiles)
+
+writeRaster(esri_lc, "/Volumes/elephant/landcovers/esri_lc_2018.tif",
+            datatype = "INT1U")
+
+# ESACCI
+esacci <- rast(file.path("/Volumes/elephant/landcovers",
+                         "ESACCI-LC-L4-LC10-Map-20m-P1Y-2016-v1",
+                         "ESACCI-LC-L4-LC10-Map-20m-P1Y-2016-v1.0.tif")) %>% 
+    crop(tiles) %>% mask(tiles)
+
+writeRaster(esacci, "/Volumes/elephant/landcovers/esacci_2016.tif",
+            datatype = "INT1U")
+
+# Globland30
+globeland <- rast(file.path("/Volumes/elephant/landcovers",
+                         "globeland30",
+                         "tanzania_2020LC030.tif")) %>% 
+    crop(tiles) %>% mask(tiles)
+writeRaster(globeland, "/Volumes/elephant/landcovers/globeland30.tif",
+            datatype = "INT1U")
+
+# Color table
+color_tb <- data.frame(
+    id_us = 1:8,
+    id_orig = c(1, 2, 3, 4, 6, 7, 8, 5),
+    id_esri_lc = c(5, 2, 11, 11, 1, 7, 8, 4),
+    id_esacci = c(4, 1, 3, 2, 10, 8, 7, 5),
+    id_globeland = c(10, 20, 30, 40, 60, 80, 90, 50),
+    type = c("Cropland", "Forest/Dense tree", 
+             "Grassland", "Shrubland", 
+             "Water", 'Built-up', "Bareland", 
+             'Wetland'),
+    color = c('#ff7f00', '#074702', '#b2df8a',
+              '#33a02c', '#3347f9', '#5a6057',
+              '#fdbf6f', '#0ea591'))
+
+library(tidyterra)
+library(ggpubr)
+
+esri_lc <- rast("/Volumes/elephant/landcovers/esri_lc_2018.tif")
+esri_lc <- as.factor(esri_lc)
+levels(esri_lc) <- data.frame(value = color_tb$id_esri_lc, 
+                              Landcover = color_tb$type) %>% slice(-3) %>% 
+    mutate(Landcover = ifelse(Landcover == 'Shrubland', 
+                              "Rangeland", Landcover))
+coltab(esri_lc) <- data.frame(values = color_tb$id_esri_lc[-3], 
+                              cols = color_tb$color[-3])
+esri_fg <- ggplot() +
+    geom_spatraster(data = esri_lc, aes(fill = Landcover), na.rm = TRUE) +
+    scale_fill_manual('',
+                      values = color_tb$color[-3], 
+                      na.value = "transparent",
+                      na.translate = FALSE,
+                      drop = TRUE) +
+    theme_void()
+
+esacci <- rast("/Volumes/elephant/landcovers/esacci_2016.tif")
+esacci <- as.factor(esacci)
+levels(esacci) <- data.frame(value = color_tb$id_esacci, 
+                             Landcover = color_tb$type)
+coltab(esacci) <- data.frame(values = color_tb$id_esacci, cols = color_tb$color)
+esacci_fg <- ggplot() +
+    geom_spatraster(data = esacci, aes(fill = Landcover)) +
+    scale_fill_manual('',
+                      values = color_tb$color, 
+                      na.translate = F, drop = TRUE,
+                      na.value = "transparent") +
+    theme_void()
+
+globeland <- rast("/Volumes/elephant/landcovers/globeland30.tif")
+globeland <- as.factor(globeland)
+levels(globeland) <- data.frame(value = color_tb$id_globeland, 
+                             Landcover = color_tb$type)
+coltab(globeland) <- data.frame(values = color_tb$id_globeland,
+                             cols = color_tb$color)
+globeland_fg <- ggplot() +
+    geom_spatraster(data = globeland, aes(fill = Landcover)) +
+    scale_fill_manual("",
+                      values = color_tb$color, 
+                      na.translate = F, drop = TRUE,
+                      na.value = "transparent") +
+    theme_void()
+
+esaglc <- rast("data/landcovers/esaglc_rcl.tif") %>% 
+    crop(tiles) %>% mask(tiles)
+esaglc <- as.factor(esaglc)
+levels(esaglc) <- data.frame(value = color_tb$id_orig, 
+                                Landcover = color_tb$type)
+coltab(esaglc) <- data.frame(values = color_tb$id_orig,
+                                cols = color_tb$color)
+esaglc_fg <- ggplot() +
+    geom_spatraster(data = esaglc, aes(fill = Landcover)) +
+    scale_fill_manual("",
+                      values = color_tb$color, 
+                      na.translate = F, drop = TRUE,
+                      na.value = "transparent") +
+    theme_void()
+
+fromglc <- rast("data/landcovers/fromglc_rcl.tif") %>% 
+    crop(tiles) %>% mask(tiles)
+fromglc <- as.factor(fromglc)
+levels(fromglc) <- data.frame(value = color_tb$id_orig, 
+                              Landcover = color_tb$type)
+coltab(fromglc) <- data.frame(values = color_tb$id_orig,
+                              cols = color_tb$color)
+fromglc_fg <- ggplot() +
+    geom_spatraster(data = fromglc, aes(fill = Landcover)) +
+    scale_fill_manual("",
+                      values = color_tb$color, 
+                      na.translate = F, drop = TRUE,
+                      na.value = "transparent") +
+    theme_void()
+
+gfsad <- rast("data/landcovers/gfsad_rcl.tif") %>% 
+    crop(tiles) %>% mask(tiles)
+gfsad[gfsad == 6] <- NA
+tansis <- rast("data/tansis/TZ_CP_preds_2018.tif") %>% 
+    subset(7) %>% project("epsg:4326") %>% 
+    crop(tiles) %>% mask(tiles) %>% 
+    project(gfsad, method = "near")
+gfsad[is.na(gfsad)] <- 0
+tansis[is.na(tansis)] <- 0
+tansis[tansis == 1] <- 3
+crop_mask <- gfsad + tansis
+crop_mask[crop_mask == 0] <- NA
+
+crop_mask <- as.factor(crop_mask)
+levels(crop_mask) <- data.frame(value = c(1, 3, 4), 
+                             Landcover = c("Only GFSAD30", "Only TanSIS", "Overlap"))
+coltab(crop_mask) <- data.frame(values = c(1, 3, 4),
+                             cols = c("#c6e92b", "red", "#ff7f00"))
+
+crop_fg <- ggplot() +
+    geom_spatraster(data = crop_mask, na.rm = TRUE) +
+    scale_fill_manual("",
+                      values = c("#c6e92b", "red", "#ff7f00"), 
+                      na.translate = F, drop = TRUE,
+                      na.value = "transparent") +
+    theme_void()
+
+fg_prds <- ggarrange(esacci_fg, globeland_fg, esri_fg, 
+                     esaglc_fg, fromglc_fg, crop_fg, 
+                     labels = c("ESACCI S2 prototype LC (2016)",
+                                "GLOBELAND30 (2010)",
+                                "Esri Land Cover (2018)",
+                                "CGLS_LC (2018)", "FROM-GLC (2017)",
+                                "GFSAD30 + TanSIS"),
+                     font.label = list(face = "plain", size = 12),
+                     hjust = c(-0.1, -0.2, -0.2, -0.2, -0.2, -0.2),
+                     ncol = 3, nrow = 2, common.legend = TRUE,
+                     legend = "bottom")
+
+ggsave(here('docs/figures/sup_figure_products.tiff'),
+       fg_prds, bg = "white", 
+       width = 8, height = 5.5, dpi = 300)
+
+# Label editing
+## Type 0: No need to do any edits (This does not mean the label is perfect).
+## Type 1: Include classes that do not exit, e.g. no cropland in one tile.
+### Human-part editing: Interpret the error, 
+#### if the misclassfied class is clearly another class, 
+#### then run the script tp directly change the class index.
+#### if not, set 0 as the probability weight and run the script to 
+#### recalculate the classes. Then double check the result.
+## Type 2: The ratio of classes are improper.
+## This case can be fixed by signing a smaller/higher weight to the probability
+## and recalculate the land cover classes.
+## For example, cropland is overestimated and shrubland is underestimated.
+## Type 3: Some objects are missed/misclassfied in the tile. 
+## This case cannot be fixed by the method proposed in type 2. 
+## For example, some small pieces of farms are missed.
+## Some road features are missed.
+## Type 4: Too complex to fix by simple method. Tried the methods in type 1-3,
+## leave it as it is, and give it a lower score.
+
+# Examples
+examples <- data.frame(id = c("1219-994_53", "1223-1014_10",
+                              "1216-1016_54", "1228-997_40",
+                              "1233-993_64"),
+                       type = c("Type 0", "Type 2", "Type 1", 
+                                "Type 3", "Type 4"))
+guess_path <- "results/north/guess_labels"
+refine_path <- "results/north/refine_labels"
+
+fgs <- lapply(examples$type, function(tp){
+    id <- examples %>% filter(type == tp) %>% pull(id)
+    guess_lb <- rast(file.path(guess_path, 
+                               sprintf("guess_%s.tif", id))) %>% 
+        as.factor()
+    levels(guess_lb) <- data.frame(value = color_tb$id_us, 
+                              Landcover = color_tb$type)
+    coltab(guess_lb) <- data.frame(values = color_tb$id_us, 
+                                   cols = color_tb$color)
+
+    refine_lb <- rast(file.path(refine_path, 
+                                sprintf("%s_label.tif", id))) %>% 
+        as.factor()
+    levels(refine_lb) <- data.frame(value = color_tb$id_us, 
+                              Landcover = color_tb$type)
+    coltab(refine_lb) <- data.frame(values = color_tb$id_us, 
+                                    cols = color_tb$color)
+
+    lbs <- c(guess_lb, refine_lb)
+    names(lbs) <- c("Gap-filled label", "Human refined label")
+
+    if (tp == "Type 3") {
+        draws <- read_sf("results/north/mask_vct.geojson") %>% 
+            st_crop(read_sf("results/north/catalog_sample_tiles.geojson") %>% 
+                        mutate(index = paste(tile, index, sep = "_")) %>% 
+                        filter(index == id))
+
+        ggplot() +
+            geom_spatraster(data = lbs) +
+            geom_sf(data = draws, fill = "transparent", color = 'black') +
+            facet_wrap(~lyr, ncol = 2) +
+            scale_fill_manual("",
+                              values = color_tb %>% 
+                                  filter(
+                                      id_us %in% unique(as.vector(unique(values(lbs))))) %>% 
+                                  pull(color),
+                              na.translate = F, drop = TRUE,
+                              na.value = "transparent") +
+            theme_void() +
+            theme(text = element_text(size = 14),
+                  panel.spacing = unit(0, "lines"))
+
+    } else {
+        ggplot() +
+            geom_spatraster(data = lbs) +
+            facet_wrap(~lyr, ncol = 2) +
+            scale_fill_manual("",
+                              values = color_tb %>% 
+                                  filter(
+                                      id_us %in% unique(as.vector(unique(values(lbs))))) %>% 
+                                  pull(color),
+                              na.translate = F, drop = TRUE,
+                              na.value = "transparent") +
+            theme_void() +
+            theme(text = element_text(size = 14),
+                  panel.spacing = unit(0, "lines"))
+    }
+})
+
+exp_fgs <- ggarrange(fgs[[1]], fgs[[3]], fgs[[2]], fgs[[4]],
+                     labels = c("Type 0/4", "Type 1", "Type 2", "Type 3"),
+                     font.label = list(size = 14, face = "plain"),
+                     hjust = c(-2.1, rep(-3, 3)),
+                     nrow = 2, ncol = 2,
+                     common.legend = TRUE,
+                     legend = "bottom")
+
+ggsave(here('docs/figures/sup_figure_label_types.tiff'),
+       exp_fgs, bg = "white", 
+       width = 8, height = 5.5, dpi = 300)
+```

### 2023-10-03 docs/run_experiments.Rmd
Update code for the multi-year workflow

@@
 
-## Set up GPU environment
-### AWS based method
-#### Launch AWS instance
-If you decide to use AWS instance, here are some basic steps.
-The information of instance that we used:
+## GPU Resources
 
-- AMI ID: `ami-0643df3b347740189`, which is our customized deep learning AWS instance. Or this one `ami-005050e76c11b3b16`, which includes datasets already.
-- Instance type: a few instance could use based on different needs.
+It is very straightforward to use ASU Sol cluster to run the experiments.
+I every time start a GPU RStudio Server to run the scripts.
+It is convenient to check something interactively and quickly.
+More importantly, I have no idea why the conda environment cannot work in other nodes.
+At least, I am happy with this way for now.
+The setting of RStudio Server is:
 
-  - `g3.8xlarge`, 2 GPU, 16G GPU memory, 32 CPUs, 244 GB CPU memory, $0.684/hr for SPOT instance.
-  - `g3.16xlarge`, 4 GPU, 32G GPU memory, 64 CPUs, 488 GB CPU memory, $1.368/hr for SPOT instance.
-  - `g4dn.8xlarge`, 1 GPU, 16G GPU memory, 32 CPUs, 128 GB CPU memory, $0.6528/hr for SPOT instance.
-  - `g4dn.12xlarge`, 4 GPUs, 64G GPU memory, 48 CPUs, 192 GB CPU memory, $1.1819/hr for SPOT instance.
-  - `g5.xlarge`, 1 GPU, 24 GPU memory, 4 CPUs, 16 GB CPU memory (on-demand $1.212/hr, spot 0.3018/hr).
-  - `g5.2xlarge`, 1 GPU, 24 GPU memory, 8 CPUs, 32 GB CPU memory (on-demand $1.624/hr, spot 0.3636/hr).
-  - `g5.4xlarge`, 1 GPU, 24 GPU memory, 16 CPUs, 64 GB CPU memory (on-demand $2.448/hr, spot 0.4872/hr).
-  - `g5.8xlarge`, 1 GPU, 24 GPU memory, 32 CPUs, 128 GB CPU memory (on-demand $4.096/hr, spot 0.967/hr).
-  - `g5.12xlarge`, 4 GPUs, 96 GPU memory, 48 CPUs, 192 GB CPU memory (on-demand $5.672/hr, 1.7016/hr).
+- CPU cores: 35
+- Rstudio Wall Time: 2 days is way more than enough.
+- R version: 4.2.1
+- GPU resources: gpu:a100:4
+- CPU RAM: --mem=400G
 
-- Security group: `labeller-security`.
+## Conda environment
 
-Before run this script, do the following steps. Just need step one for Linux machine. Didn't test Windows machine.
+`pytorch_spatial` is the conda environment to run all scripts. The users can get into the environment by:
 
-1. `brew install awscli`, then `aws configure` to configure AWS credential.
-2. `brew install jq`
-3. `brew install coreutils`. to use gdata on macOS.
-
-Then:
 ```
-cd tools
-chmod 777 create_spot_instance.sh
-create_spot_instance.sh <ami_id> <instance_type> <security_group_id> <new_instance_name> <spot_type> <valid_until> <key_name> <volume_size>
-```
-For example:
-```
-cd tools
-chmod 777 create_spot_instance.sh
-create_spot_instance.sh ami-0643df3b347740189 g3.16xlarge sg-0a8bbc91697d6a76b lc_dl_tz persistent 2021-01-22T23:00:00 lsong-keypair 200
+module load mamba/latest
+source activate pytorch_spatial
 ```
 
-#### Instance setting
-After successfully launched the instance, then it is ready to get into the instance to work.
-
-The most essential work are arguably to clone project and set jupyter notebook:
-
-- STEP 1: Set up GitHub token (because the repo is private).
-More details could be found in this [tutorial](https://docs.github.com/en/free-pro-team@latest/github/authenticating-to-github/generating-a-new-ssh-key-and-adding-it-to-the-ssh-agent).
-
-  ```
-  ssh-keygen -t ed25519 -C "your_email@example.com"
-  eval "$(ssh-agent -s)"
-  ssh-add ~/.ssh/id_ed25519
-  vim ~/.ssh/id_ed25519.pub
-  ```
-  Copy out the ssh key, and type `:q` to exit, and then go to GitHub page to add into the records.
-
-- STEP 2: Clone the repo into instance:
+If this is the first time ever for this work, clone the repo into instance:
 
@@
 
-- STEP 3: Set up jupyter notebook
+## Run experiments
+
+### Fit models
 
 ```
-  jupyter notebook password
-  ```
-  to set a log in password for jupyter notebook, then
-  ```
-  jupyter notebook
-  ```
-Replace the private IP with the public IP to open it in browser. If you can log in without issues, then it is ready to go.
-
-### Other cloud computing platform
-
-The users could set up the deep learning environment with similar steps used on AWS. For example, Colab can be used as long as the GPU power is enough for your computation.
-
-## Run experiments
-
-### Parse dataset
-
-```
-cd path/of/hrlcm
-./hrlcm/utils/parse_dataset.sh path/to/save
-```
-
-### Run models
-
-```
-cd path/of/hrlcm
-python hrlcm/fit_step_lr.py --arg arg_value
-```
-
-Check arguments:
-```
-python hrlcm/fit_step_lr.py --help
-```
-
-For example:
-```
-python hrlcm/fit_step_lr.py --exp_name unet_one_tile --num_workers 32 --gpu_devices '0,1,2,3'
-```
-Or
-```
-python hrlcm/fit_compose_lr.py --exp_name unet_all_norm_200 --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 201
+python hrlcm/fit_compose_lr.py --exp_name unet_20bs_sbaug_startup --num_workers 30 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --epochs 201
 ```

### 2023-10-03 hrlcm/dataset.py

@@ -170,7 +170,8 @@ class NFSEN1LC(Dataset):
     Which is short for NICFI + SENTINEL-1 land cover classification
     """
 
-    def __init__(self, data_dir,
+    def __init__(self, 
+                 data_dir,
                  bands,
                  usage='train',
                  label_offset=1,
@@ -178,6 +179,7 @@ class NFSEN1LC(Dataset):
                  sync_transform=None,
                  img_transform=None,
                  label_transform=None,
+                 predict_catalog=None,
                  tile_id='1207-996'):
         """Initialize the dataset
         Args:
@@ -215,7 +217,7 @@ class NFSEN1LC(Dataset):
         self.n_channels = len(self.bands)
 
         # Check inputs
-        assert usage in ['train', 'validate', 'predict']
+        assert usage in ['train', 'validate', 'predict', "ipredict"]
         assert os.path.exists(data_dir)
 
         # Read catalog
@@ -224,33 +226,28 @@ class NFSEN1LC(Dataset):
         elif self.usage == 'validate':
             catalog_nm = 'dl_catalog_valid.csv'
         elif self.usage == 'predict':
-            catalog_nm = 'dl_catalog_predict.csv'
+            catalog_nm = predict_catalog
+        elif self.usage == "ipredict":
+            catalog_nm = predict_catalog
         else:
             sys.exit('Not valid usage setting.')
         catalog_full = pd.read_csv(os.path.join(self.data_dir, catalog_nm))
 
         # Read chips for train and validate
-        if self.usage in ['train', 'validate']:
+        if self.usage in ['train', 'validate', 'ipredict']:
             self.catalog = catalog_full
             # Load all images here before the training to save time
-            # img_ls = []
-            # label_ls = []
-            # for index in range(len(self.catalog)):
-            #     tile_info = self.catalog.iloc[index]
-            #     tile_info = tile_info.replace(tile_info['img'], os.path.join(self.data_dir, tile_info["img"]))
-            #     tile_info = tile_info.replace(tile_info['label'], os.path.join(self.data_dir, tile_info["label"]))
-            #     img, label = load_tile(tile_info, bands=self.bands, offset=self.label_offset)
-            #     img_ls.append(img)
-            #     label_ls.append(label)
-            # self.img_ls = img_ls
-            # self.label_ls = label_ls
             args = [(index, catalog_full, bands, label_offset, data_dir) for index in range(len(catalog_full))]
-            with mp.Pool(processes=30) as pool:
[…]

### 2023-10-03 hrlcm/fit_compose_lr.py

@@ -228,8 +228,9 @@ def main():
     # learning_rates = get_compose_lr(model, args.epochs, args.min_lr, args.max_lr)
     
     # # Modify stages
-    # learning_rates = get_compose_lr(model, args.epochs, args.min_lr, args.max_lr,
-    #                                 stage1=50, stage2=100, stage3=150)
+    learning_rates = get_compose_lr(model, args.epochs, args.min_lr, args.max_lr,
+                                    stage1=110, stage2=145, stage3=180)
+    learning_rates[191:201] = [0.00001] * 10
     
     # # Modify stages and change some values
     # learning_rates = get_compose_lr(model, args.epochs, args.min_lr, args.max_lr, 
@@ -238,7 +239,7 @@ def main():
     # learning_rates[72:81] = [0.000001] * 10
     
     # # Use fixed values
-    learning_rates = [args.max_lr] * args.epochs
+    # learning_rates = [args.max_lr] * args.epochs
     # learning_rates = [args.max_lr] * 11 + [args.min_lr] * 10
     
     # # Fine tune scheduler
@@ -275,6 +276,8 @@ def main():
     # Start train
     step = 0
     epoch = 0
+    best_aa = 0.85
+    best_miou = 0.55
     # Resume model based on settings
     if args.resume:
         if os.path.isfile(args.resume):
@@ -319,9 +322,21 @@ def main():
         model, step = trainer.train(model, train_loader, loss_fn,
                                     optimizer, writer, step=step)
         # Run validation
-        trainer.validate(model, validate_loader, step, loss_fn_valid, writer)
+        aa, miou = trainer.validate(model, validate_loader, step, loss_fn_valid, writer)
 
-        # Save checkpoint
+        # Save checkpoint when get a better model based on AA or mIOU
+        if aa > best_aa:
+            trainer.export_model(model, optimizer=optimizer,
+                                 scheduler=None, name='best_aa',
+                                 step=step)
+            best_aa = aa
+        if miou > best_miou:
+            trainer.export_model(model, optimizer=optimizer,
+                                 scheduler=None, name='best_miou',
+                                 step=step)
+            best_miou = miou
+        
+        # Save checkpoint regularly
         if epoch % args.save_freq == 0:
             trainer.export_model(model, optimizer=optimizer,
                                  scheduler=None, name='interim',

### 2023-10-03 hrlcm/predict.py

@@ -26,6 +26,8 @@ def main():
                         help='path to checkpoint file (default: ./checkpoint.pth)')
 
     # Dataset
+    parser.add_argument('--year', type=str,
+                        default='2018', help='The year for the prediction.')
     parser.add_argument('--fname_predict', type=str,
                         default='dl_catalog_predict.csv',
                         help='the csv file name to do prediction.')
@@ -52,8 +54,8 @@ def main():
                              'none: no score map. (default: overall)')
 
     # Hyper-parameters of GPU
-    parser.add_argument('--batch_size', type=int, default=16,
-                        help='mini-batch size (default: 16)')
+    parser.add_argument('--batch_size', type=int, default=64,
+                        help='mini-batch size (default: 64)')
     parser.add_argument('--gpu_devices', type=str, default=None,
                         help='the gpu devices to use (default: None) (format: 1, 2)')
 
@@ -74,6 +76,7 @@ def main():
     print()
 
     # Create output dir
+    args.out_dir = os.path.join(args.out_dir, args.year)
     os.makedirs(args.out_dir, exist_ok=True)
     # Set and create paths
     score_path = os.path.join(args.out_dir, 'score')
@@ -115,22 +118,26 @@ def main():
 
     # Predict
     # Image transform
-    id_bands = list(range(1, 13)) if args.img_bands == "all" else list(range(1, 9))
+    bands_all = [1,2,3,4,5,7,9,10,11,12,13,15,17,18,19,20] + list(range(23,27))
+    bands_opt = [1,2,3,4,9,10,11,12]
+    id_bands = bands_all if args.img_bands == "all" else bands_opt
+    
     # Load mean and sd for normalization
     with open(os.path.join(args.stats_dir,
-                           "means.pkl"), "rb") as input_file:
+                           "means_2018.pkl"), "rb") as input_file:
         mean = tuple(pkl.load(input_file))
-        mean = mean[0:len(id_bands)]
+        mean = tuple([mean[i-1] for i in id_bands])
 
     with open(os.path.join(args.stats_dir,
-                           "stds.pkl"), "rb") as input_file:
+                           "stds_2018.pkl"), "rb") as input_file:
         std = tuple(pkl.load(input_file))
-        std = std[0:len(id_bands)]
+        std = tuple([std[i-1] for i in id_bands])
     pred_transform = ComposeImg([
         ImgToTensor(),
         ImgNorm(mean, std)
     ])
-
+    
+    # Read catalog with full path
[…]

### 2023-10-03 hrlcm/predict_interm_label.py

@@ -1,0 +1,167 @@
+"""
+This is a script to do prediction using final model.
+Author: Lei Song
+Maintainer: Lei Song (lsong@clarku.edu)
+"""
+
+import argparse
+from augmentation import *
+from dataset import *
+from torch.utils.data import DataLoader
+import torch.nn.functional as F
+import pickle as pkl
+from models.unet import UNet
+
+
+def main():
+    # Get in-line arguments
+    # define and parse arguments
+    parser = argparse.ArgumentParser()
+
+    # config
+    parser.add_argument('--args_path', type=str, default="args.pkl",
+                        help='path to config file (default: ./args.pkl)')
+    parser.add_argument('--checkpoint_file', type=str, default="checkpoint.pth",
+                        help='path to checkpoint file (default: ./checkpoint.pth)')
+
+    # Dataset
+    parser.add_argument('--year', type=str,
+                        default='2018', help='The year for the prediction.')
+    parser.add_argument('--fname_predict', type=str,
+                        default='dl_catalog_predict.csv',
+                        help='the csv file name to do prediction.')
+    parser.add_argument('--data_dir', type=str, default=None,
+                        help='path to dataset')
+    parser.add_argument('--out_dir', type=str, default="prediction",
+                        help='path to output dir (default: ./prediction)')
+    parser.add_argument('--stats_dir', type=str, default="norm_stats",
+                        help='path of normalization params (default: ./norm_stats)')
+    parser.add_argument('--num_workers', type=int, default=0,
+                        help='number of worker(s) to load dataset (default: 0)')
+    parser.add_argument('--label_offset', type=int, default=1,
+                        help='offset value to minus from label in order to start from 0 (default: 1)')
+    parser.add_argument('--img_bands', type=str, choices=['all', 'nicfi'],
+                        default='all',
+                        help='bands of satellite images to use. \
+                        all means all bands, including RGB, NIR of NICFI tiles, intercept,  \
+                        cos(2t) of VV and VH. (default: all)')
+
+    # Hyper-parameters of GPU
+    parser.add_argument('--batch_size', type=int, default=64,
+                        help='mini-batch size (default: 64)')
+    parser.add_argument('--gpu_devices', type=str, default=None,
[…]

### 2023-10-03 hrlcm/train.py

@@ -138,6 +138,9 @@ class Trainer:
 
         # Flush to disk
         writer.flush()
+        
+        # Return the average accuracy
+        return conf_mat.get_aa(), conf_mat.get_mIoU()
 
     def export_model(self, model, optimizer=None, scheduler=None, name=None, step=None):
         # Set output filename

### 2023-10-05 docs/run_experiments.Rmd
Add function to make interm labels and update document

@@
 ## Run experiments
-
-### Fit models
-
-```
-python hrlcm/fit_compose_lr.py --exp_name unet_20bs_sbaug_startup --num_workers 30 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --epochs 201
-```
-
 ### Tensorboard
@@
 
-### Hyperparameter tunning
-#### Network parameter
+### Fit the model
 
-Before official running, test a bit about the largest values of `num_worker`, `train_batch_size`, `val_batch_size` that could be used. For `g5.12xlarge`, these values can be:
-
-- `num_worker`:48 (CPU cores)
-- `train_batch_size`: 32 (could be a bit bigger, but it is recommended to use $2^n$)
-- `val_batch_size`: 32
-
-#### Learning rate
-Also, test the optimal learning rate and scheduler to use:
-
-- 0.001 is a good start point.
-- 0.00001 is a good end point with middle value of 0.0001.
-
-`final_lr` for `optim.AdaBound`:
-
-- 0.01 still works fine. The default value is robust for many cases.
-
-#### Augmentation
-
-- Random flip (always use)
-- Random scale
-- Random center rotate
-- Normalization: Dataset based standardization.
-*Among dataset-based standardization, image-based standardization, image-based normalization, and no such transformation, dataset-based standardization works the best because the U-Net learned much faster.*
-
-Experiments indicate using all of them can improve model performance.
-
-#### Loss functions
-
-No luck on using different loss function. The most effective loss function is still the balanced cross entropy loss function.
-
-According to the experiments, balanced cross entropy loss performs well.
-In summary (based on my knowledge), changing loss function is not an efficient and effective way to increase the model performance in this case.
-This might because the modeling task here does not have special characteristics that need special loss functions to deal with.
-For example, some loss functions were created to detect vessel-like objects.
-Instead, the problems here are mainly the noisy labels and not enough representative features (satellite image bands).
-
-#### Loss weights
-
-According to some previous experiments, the accuracy of cropland is relatively low.
-One reason is that the farming condition over Tanzania is complex and thus hard to model.
-Another reason is the validation of this class has relatively low quality as well.
-There are limited things we could do for these reasons.
-But we can let the model to consider more about cropland when training.
-The strategy can be increasing the loss weight of cropland class.
-However, the effect is not conclusive.
-
-Hum... Using a bigger weight for cropland in loss calculation increased the overall accuracy a bit. However, the cost is the overestimation of cropland over sparse vegetation area.
-
-#### Freeze layers
-
-Sometimes, people freeze some layers, only update weights of last few layers. The parameters for U-Net used in this project are:
-
-1 * 8 (initial) + 4 * 8 (down) + 4 * 8 (up) + 2 = 74 layers
-
-- 40: freeze all down layers
-- 56: freeze all down and the first two up blocks
-- 64: freeze all down and the first three up blocks
-- 72: freeze all down and up blocks, just update the last two layers
-
-#### U-Net structure
-
-Using `ConvTranspose2d` instead of `Upsample` could reduce the overestimation issue of built-up areas.
-Because upsampling just uses bilinear sampling method, which could smooth the whole image.
-However, built-up objects are usually tiny.
-Thus, they are affected by bilinear upsampling a lot.
-
-However, there are also cons of `ConvTranspose2d`.
-Using `ConvTranspose2d` loses the advantage of bilinear smoothing.
-Thus, at the boundary of an object, it might be some salt noises.
-If post-segmentation pruning is applied, this is not a big issue.
-
-Another issue is that because using `ConvTranspose2d` means add another learnable parameter layer, it slightly increases the need of computational resources. It really depends if this is an issue.
-
-Thus, whether using `ConvTranspose2d` or not depends what you want.
-
-#### "Hierachical" training
-
-When training a full model using the whole dataset, the main problem is cropland. One reason is that
-cropland highly relies on local climate and cultivating conditions and Tanzania is a large country. To reduce this impact, we could shrink the study area gradually into each agro-ecological zone.
-
-- Modeling structure:
+Load conda environment:
 
 ```
-1, 2, 4, 5 -> 1, 2, 5 -> 1
-                      -> 2
-                      -> 5
-2, 3, 4, 5 -> 2, 3, 4 -> 3
-                      -> 4
+module load mamba/latest
+source activate pytorch_spatial
+```
+Run script to fit the model:
+
+```
+python hrlcm/fit_compose_lr.py --exp_name unet_128_20bs_sbaug_startup --num_workers 30 --gpu_devices '0,1,2,3'
+python hrlcm/fit_compose_lr.py --exp_name unet_128_20bs_sbaug_tune --num_workers 30 --gpu_devices '0,1,2,3' --resume '/scratch/lsong36/tanzania/results/unet_128_20bs_sbaug_startup/checkpoints/final.pth'
 ```
 
-Zone 1, 2, 3, 4, 5
+### Predict of labels of years
 
-Comment out line 211 and add `learning_rates = [args.max_lr] * args.epochs` to use a fixed learning rate 0.001 to train.
+One GPU and use batch size 32 is enough. This step would be very fast as long as CPU RAM can load the dataset.
+
+2018:
 
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_full_startup_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --max_lr 0.001 --save_freq 20 --epochs 81
+python hrlcm/predict_interm_label.py --args_path '/scratch/lsong36/tanzania/results/unet_128_20bs_sbaug_tune/checkpoints/args.pkl' --checkpoint_file '/scratch/lsong36/tanzania/results/unet_128_20bs_sbaug_tune/checkpoints/final.pth' --year '2018' --fname_predict 'training/dl_catalog_ipredict_2018.csv' --data_dir '/scratch/lsong36/tanzania' --out_dir '/scratch/lsong36/tanzania/training/label' --stats_dir '/scratch/lsong36/tanzania/training/norm_stats' --num_workers 24 --batch_size 64 --gpu_devices '0,1' --label_format 'full'
 ```
 
-Then, discard the changes above.
+2019:
 
-Zone 1, 2, 4, 5
 ```
-python hrlcm/fit_compose_lr.py --exp_name unet_z1245_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 121 --resume 'results/dl/unet_full_startup_80epochs/checkpoints/final.pth'
+python hrlcm/predict_interm_label.py --args_path '/scratch/lsong36/tanzania/results/unet_128_20bs_sbaug_tune/checkpoints/args.pkl' --checkpoint_file '/scratch/lsong36/tanzania/results/unet_128_20bs_sbaug_tune/checkpoints/final.pth' --year '2019' --fname_predict 'training/dl_catalog_ipredict_2019.csv' --data_dir '/scratch/lsong36/tanzania' --out_dir '/scratch/lsong36/tanzania/training_2019/label' --stats_dir '/scratch/lsong36/tanzania/training/norm_stats' --num_workers 24 --batch_size 64 --gpu_devices '0,1' --label_format 'intersect'
 ```
 
-Comment out line 249 in `fit_compose_lr.py`, and modify `lr_scheduler.py` correspondingly. The learning rate scheduler is saved as a pickle as well.
+### Predict
 
-Zone 1, 2, 5
-```
-python hrlcm/fit_compose_lr.py --exp_name unet_z125_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.0001 --save_freq 10 --epochs 81 --resume 'results/dl/unet_z1245_120epochs/checkpoints/final.pth'
-
-# Fine tune using a smaller learning rate
-python hrlcm/fit_compose_lr.py --exp_name unet_z125_ft_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.000001 --max_lr 0.00001 --save_freq 10 --epochs 81 --resume 'results/dl/unet_z125_80epochs/checkpoints/final.pth'
-```
-
-Discard the changes above.
-
-Zone 2, 3, 4, 5
-```
-python hrlcm/fit_compose_lr.py --exp_name unet_z2345_120epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.001 --save_freq 20 --epochs 121 --resume 'results/dl/unet_full_startup_80epochs/checkpoints/final.pth'
-```
-
-Do the same as zone 1, 2, 5.
-
-Zone 2, 3, 4
-```
-python hrlcm/fit_compose_lr.py --exp_name unet_z234_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.0001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z2345_120epochs/checkpoints/final.pth'
-
-# Fine tune with a smaller learning rate
-python hrlcm/fit_compose_lr.py --exp_name unet_z234_ft_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.000001 --max_lr 0.00001 --save_freq 10 --epochs 81 --resume 'results/dl/unet_z234_80epochs/checkpoints/final.pth'
-```
-
-**[NOTE:]** _I tried multiple ways, which includes adding more training labels, using different types of loss functions (particularly ones to deal with class imbalance), and applying different model structure.
-No luck to get a reasonable balanced results if shrink the training area further into single zones.
-So I decided to stop here to use three zones as a group for the final result._
-
-_But if you like, or I get the right method to do further, go further to finish the following steps._
-
-_Zone 1_
-```
-# "Shrink" the model to zone1
-python hrlcm/fit_compose_lr.py --exp_name unet_z125_ew_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.0001 --save_freq 10 --epochs 81 --resume 'results/dl/unet_z125_80epochs/checkpoints/final.pth'
-
-# "Fine-tune" the zone1 model
-python hrlcm/fit_compose_lr.py --exp_name unet_z1_ft_72fz_cl_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --max_lr 0.00000001 --save_freq 10 --epochs 81 --resume 'results/dl/unet_z1_ew80epochs/checkpoints/final.pth'
-```
-
-_Zone 2, 5 (For zone 2 & 5)_
-```
-python hrlcm/fit_compose_lr.py --exp_name unet_z25_ew_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.00001 --max_lr 0.0001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z125_80epochs/checkpoints/final.pth'
-```
-
-_Zone 2, 3 (For zone 3)_
-```
-python hrlcm/fit_compose_lr.py --exp_name unet_z23_12bs_4augs_ft_fz56_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z234_12bs_4augs_ft_80epochs/checkpoints/final.pth'
-```
-
-_Zone 2, 4 (For zone 4)_
-```
-python hrlcm/fit_compose_lr.py --exp_name unet_z24_12bs_4augs_ft_fz56_80epochs --num_workers 48 --gpu_devices '0,1,2,3' --min_lr 0.0000001 --max_lr 0.00001 --save_freq 20 --epochs 81 --resume 'results/dl/unet_z234_12bs_4augs_ft_80epochs/checkpoints/final.pth'
-```
-
-### Prediction
-
-Doing prediction is simple. Applying a model into its zones.
+No need to use intensive GPU resource because the prediction is made tile by tile. Use one A100 GPU with batch size 64, 35 cores, CPU RAM 100G:
 
 ```
-cd path/of/hrlcm
-python hrlcm/predict.py --arg arg_value
+python hrlcm/predict.py --args_path '/scratch/lsong36/tanzania/results/unet_128_20bs_sbaug_tune/checkpoints/args.pkl' --checkpoint_file '/scratch/lsong36/tanzania/results/unet_128_20bs_sbaug_tune/checkpoints/final.pth' --year '2019' --fname_predict 'training/dl_catalog_predict_2019.csv' --data_dir '/scratch/lsong36/tanzania' --out_dir '/scratch/lsong36/tanzania/prediction' --stats_dir '/scratch/lsong36/tanzania/training/norm_stats' --num_workers 35 --batch_size 64 --gpu_devices '0'
 ```
-Check arguments:
-```
-python hrlcm/predict.py --help
-```
-
-For example:
-```
-python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
-
-aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction
-```
-
-`tools/parse_img_from_s3.R` is a script to grab image stacks from S3 to local machine.
-
-Steps in production (for records):
-
-```
-# Grab models, it could be more specific because prediction just uses 2 final models
-aws s3 cp --recursive s3://activemapper/leisong/model $HOME/hrlcm/results/dl
-
-# Navigate to hrlcm
-cd ~/hrlcm
-
-# Run all steps for different zones together 
-Rscript tools/parse_img_from_s3.R -z 1 -s 1;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 1 -s 2;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 2;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone2;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 5;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone5.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone5;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 3;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone3.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone3;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 4 -s 1;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone4_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone4;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 4 -s 2;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone4_2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone4;rm -rf results/prediction;rm -rf results/tanzania/predict
-```
-
-### Evaluation
-
-```
-cd path/of/hrlcm
-python hrlcm/evaluate.py --arg arg_value
-```
-Check arguments:
-```
-python hrlcm/evaluate.py --help
-```
-
-For example:
-```
-python hrlcm/evaluate.py --args_path 'results/dl/unet_z12_12bs_4augs_ft_fz56_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z12_12bs_4augs_ft_fz56_80epochs/checkpoints/final.pth' --data_dir 'results/tanzania' --out_dir 'results/evaluation' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'
-
-scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/evaluation /Users/pinot/Dropbox/research/hrlcm/results/dl/unet_score08_hardiness2_epoch200
-```
-
-#### Post-cleaning (TBD)
-
-- Cropland/Water: Object fixing
-- Grassland/Shrubland/Forest/Build-up/Bareland: No fix
 

### 2023-10-05 hrlcm/predict_interm_label.py

@@ -51,6 +51,11 @@ def main():
                         help='mini-batch size (default: 64)')
     parser.add_argument('--gpu_devices', type=str, default=None,
                         help='the gpu devices to use (default: None) (format: 1, 2)')
+    
+    # Output format
+    parser.add_argument('--label_format', type=str, choices=['full', 'intersect'],
+                        default='intersect',
+                        help='the format of the output labels. (default: intersect)')
 
     args = parser.parse_args()
     assert args.img_bands in ['all', 'nicfi']
@@ -148,8 +153,10 @@ def main():
             output = prediction[n, :, :]
             output = output.astype(np.uint8)
             output = np.pad(output, 4, 'constant', constant_values = 255)
-            label_to_compare = orig_label[n, :, :]
-            output[output != label_to_compare] = 255
+            
+            if args.label_format == "intersect":
+                label_to_compare = orig_label[n, :, :]
+                output[output != label_to_compare] = 255
             
             # Read meta
             tile_index = tile_ids[n]
